---
title: "Figure4"
output: html_document
---

# Import library & Setup environment
```{r, Import libraries}
library(dplyr)
library(stringr)
library(tidyr)
library(ggpubr)
library(doParallel)
library(foreach)
library(xgboost)
library(SHAPforxgboost)
library(randomForest)
library(fastshap)
library(shapviz)
library(lightgbm)
library(pROC)
library(purrr)
library(ggplot2)
library(tidymodels)
```

```{r, Load data into environment}
load(paste0(getwd(), "/Data_preparation.RData"))
load(paste0(getwd(), '/XGBoost.RData'))
```

# Retrieve XGBoost performance with VL at symptom onset & VL at diagnosis
```{r, Compile models performance}
xgb_acc_vlsymp <- xgb_vlsymp_metrics_summary$accuracy_test_mean
xgb_acc_low_vlsymp <- xgb_vlsymp_metrics_summary$low_acc_test
xgb_acc_upp_vlsymp <- xgb_vlsymp_metrics_summary$upp_acc_test
xgb_sens_vlsymp <- xgb_vlsymp_metrics_summary$sensitivity_mean
xgb_sens_low_vlsymp <- xgb_vlsymp_metrics_summary$low_sens
xgb_sens_upp_vlsymp <- xgb_vlsymp_metrics_summary$upp_sens
xgb_spec_vlsymp <- xgb_vlsymp_metrics_summary$specificity_mean
xgb_spec_low_vlsymp <- xgb_vlsymp_metrics_summary$low_spec
xgb_spec_upp_vlsymp <- xgb_vlsymp_metrics_summary$upp_spec
xgb_prec_vlsymp <- xgb_vlsymp_metrics_summary$precision_mean
xgb_prec_low_vlsymp <- xgb_vlsymp_metrics_summary$low_prec
xgb_prec_upp_vlsymp <- xgb_vlsymp_metrics_summary$upp_prec
xgb_f1_vlsymp <- xgb_vlsymp_metrics_summary$F1_score_mean
xgb_f1_low_vlsymp <- xgb_vlsymp_metrics_summary$low_f1_sc
xgb_f1_upp_vlsymp <- xgb_vlsymp_metrics_summary$upp_f1_sc
xgb_auc_vlsymp <- xgb_vlsymp_metrics_summary$AUC_mean
xgb_auc_low_vlsymp <- xgb_vlsymp_metrics_summary$low_auc
xgb_auc_upp_vlsymp <- xgb_vlsymp_metrics_summary$upp_auc

xgb_acc_vldiag <- xgb_vldiag_metrics_summary$accuracy_test_mean
xgb_acc_low_vldiag <- xgb_vldiag_metrics_summary$low_acc_test
xgb_acc_upp_vldiag <- xgb_vldiag_metrics_summary$upp_acc_test
xgb_sens_vldiag <- xgb_vldiag_metrics_summary$sensitivity_mean
xgb_sens_low_vldiag <- xgb_vldiag_metrics_summary$low_sens
xgb_sens_upp_vldiag <- xgb_vldiag_metrics_summary$upp_sens
xgb_spec_vldiag <- xgb_vldiag_metrics_summary$specificity_mean
xgb_spec_low_vldiag <- xgb_vldiag_metrics_summary$low_spec
xgb_spec_upp_vldiag <- xgb_vldiag_metrics_summary$upp_spec
xgb_prec_vldiag <- xgb_vldiag_metrics_summary$precision_mean
xgb_prec_low_vldiag <- xgb_vldiag_metrics_summary$low_prec
xgb_prec_upp_vldiag <- xgb_vldiag_metrics_summary$upp_prec
xgb_f1_vldiag <- xgb_vldiag_metrics_summary$F1_score_mean
xgb_f1_low_vldiag <- xgb_vldiag_metrics_summary$low_f1_sc
xgb_f1_upp_vldiag <- xgb_vldiag_metrics_summary$upp_f1_sc
xgb_auc_vldiag <- xgb_vldiag_metrics_summary$AUC_mean
xgb_auc_low_vldiag <- xgb_vldiag_metrics_summary$low_auc
xgb_auc_upp_vldiag <- xgb_vldiag_metrics_summary$upp_auc

df_perf_summary <- data.frame(
    models = c("XGBoost (Viral load at symptom onset)", "XGBoost (Viral load at diagnosis)"),
    Accuracy = c(xgb_acc_vlsymp, xgb_acc_vldiag),
    acc_low = c(xgb_acc_low_vlsymp, xgb_acc_low_vldiag),
    acc_upp = c(xgb_acc_upp_vlsymp, xgb_acc_upp_vldiag),
    Sensitivity = c(xgb_sens_vlsymp, xgb_sens_vldiag),
    sens_low = c(xgb_sens_low_vlsymp, xgb_sens_low_vldiag),
    sens_upp = c(xgb_sens_upp_vlsymp, xgb_sens_upp_vldiag),
    Specificity = c(xgb_spec_vlsymp, xgb_spec_vldiag),
    spec_low = c(xgb_spec_low_vlsymp, xgb_spec_low_vldiag),
    spec_upp = c(xgb_spec_upp_vlsymp, xgb_spec_upp_vldiag),
    Precision = c(xgb_prec_vlsymp, xgb_prec_vldiag),
    prec_low = c(xgb_prec_low_vlsymp, xgb_prec_low_vldiag),
    prec_upp = c(xgb_prec_upp_vlsymp, xgb_prec_upp_vldiag),
    `F1-Score` = c(xgb_f1_vlsymp, xgb_f1_vldiag),
    f1_low = c(xgb_f1_low_vlsymp, xgb_f1_low_vldiag),
    f1_upp = c(xgb_f1_upp_vlsymp, xgb_f1_upp_vldiag),
    AUROC = c(xgb_auc_vlsymp, xgb_auc_vldiag),
    auc_low = c(xgb_auc_low_vlsymp, xgb_auc_low_vldiag),
    auc_upp = c(xgb_auc_upp_vlsymp, xgb_auc_upp_vldiag)
)
df_perf_summary
```

# XGBoost with sequential VL after diagnosis
```{r, Setup CPU clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r}
xgb_seq_diag_list <- foreach(i = 1:100, .packages = c("dplyr", "xgboost", "pROC", "SHAPforxgboost")) %dopar% {
  split <- split_list_p[[i]]
  
  lapply(1:10, function(j) {
    col_nm <- paste0("vl_dp", j)
    
    train_df <- split$train %>% select(age, gender, vaccination, comorbidity, col_nm, outcome)
    test_df <- split$test %>% select(age, gender, vaccination, comorbidity, col_nm, outcome)
    
    train_x <- model.matrix(outcome ~ ., data = train_df)[, -1]
    test_x <- model.matrix(outcome ~ ., data = test_df)[, -1]
    
    dtrain <- xgb.DMatrix(data = train_x, label = as.numeric(as.factor(train_df$outcome)) - 1)
    dtest <- xgb.DMatrix(data = test_x, label = as.numeric(as.factor(test_df$outcome)) - 1)
    
    xgb_model <- xgboost(data = dtrain, nrounds = 1000, verbose = 0, objective = "binary:logistic")
    
    xgb_pred <- predict(xgb_model, dtest)
    xgb_pred_label <- ifelse(xgb_pred < 0.5, 0, 1)
    xgb_pred_res <- ifelse(xgb_pred_label == 0, "Non severe", "Severe")
    
    cfm_xgb <- table(Predicted = xgb_pred_res, Actual = test_df$outcome)
    accuracy_xgb <- sum(cfm_xgb["Non severe", "Non severe"], cfm_xgb["Severe", "Severe"]) / sum(cfm_xgb)
    
    xgb_pred_train <- predict(xgb_model, dtrain)
    xgb_pred_train_label <- ifelse(xgb_pred_train < 0.5, 0, 1)
    xgb_pred_train_res <- ifelse(xgb_pred_train_label == 0, "Non severe", "Severe")
    
    cfm_xgb_train <- table(Predicted = xgb_pred_train_res, Actual = train_df$outcome)
    accuracy_xgb_train <- sum(cfm_xgb_train["Non severe", "Non severe"], cfm_xgb_train["Severe", "Severe"]) / sum(cfm_xgb_train)

    TP <- cfm_xgb["Severe", "Severe"]
    FP <- cfm_xgb["Severe", "Non severe"]
    TN <- cfm_xgb["Non severe", "Non severe"]
    FN <- cfm_xgb["Non severe", "Severe"]
    
    sensitivity_xgb <- TP / (TP + FN)
    specificity_xgb <- TN / (TN + FP)
    prec_xgb <- TP / (TP + FP)
    f1_sc_xgb <- 2 * ((prec_xgb * sensitivity_xgb) / (prec_xgb + sensitivity_xgb))
    
    roc_xgb <- roc(test_df$outcome, xgb_pred)
    auc_val_xgb <- auc(roc_xgb)
    
    shap_contrib <- predict(xgb_model, dtrain, predcontrib = TRUE)
    shap_long <- shap.prep(xgb_model, X_train = train_x)
    
    list(
      #model = xgb_model,
      confusion_matrix = cfm_xgb,
      accuracy_training = accuracy_xgb_train,
      accuracy_testing = accuracy_xgb,
      sensitivity = sensitivity_xgb,
      specificity = specificity_xgb,
      precision = prec_xgb,
      F1_score = f1_sc_xgb,
      AUC_value = auc_val_xgb,
      SHAP_values = shap_long,
      prediction = xgb_pred_res
    )
  })
}
```

```{r, Stop CPU clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
xgb_seq_diag_metrics_df <- map2_dfr(
  .x = xgb_seq_diag_list,
  .y = seq_along(xgb_seq_diag_list),
  .f = function(model_list, run_index) {
    map2_dfr(model_list, 1:10, function(model_result, var_index) {
      tibble(
        run = run_index,
        variable = var_index,
        accuracy_train = round(model_result$accuracy_training * 100, 4),
        accuracy_test = round(model_result$accuracy_testing * 100, 4),
        sensitivity = round(model_result$sensitivity * 100, 4),
        specificity = round(model_result$specificity * 100, 4),
        precision = round(model_result$precision * 100, 4),
        F1_score = round(model_result$F1_score, 4),
        AUC_value = round(model_result$AUC_value * 100, 4)
      )
    })
  }
)

xgb_seq_diag_metrics_df

xgb_seq_diag_metrics_summary <- xgb_seq_diag_metrics_df %>%
  group_by(variable) %>%
  summarise(
    across(
      .cols = c(accuracy_train, accuracy_test, sensitivity, specificity, precision, F1_score, AUC_value),
      .fns = list(mean = mean, sd = sd, low = ~ quantile(.x, 0.025), upp = ~ quantile(.x, 0.975)),
      .names = "{.col}_{.fn}"
    )
  ) %>%
  ungroup()

xgb_seq_diag_metrics_summary
```

```{r, Model performance visualization}
xgb_perf_viz_diag_df <- xgb_seq_diag_metrics_summary %>%
  select(-c("accuracy_train_mean", "accuracy_train_sd", "accuracy_train_upp", "accuracy_train_low")) %>%
  pivot_longer(
    cols = -variable,
    names_to = "metrics",
    values_to = "perf"
  ) %>%
  mutate(
    Metrics = case_when(
      str_starts(metrics, "accuracy_") ~ "Accuracy",
      str_starts(metrics, "sensitivity") ~ "Sensitivity",
      str_starts(metrics, "specificity") ~ "Specificity",
      str_starts(metrics, "precision") ~ "Precision",
      str_starts(metrics, "F1_score") ~ "F1_score",
      str_starts(metrics, "AUC_value") ~ "AUROC_value"
    ),
    bound = case_when(
      str_ends(metrics, "_low") ~ "lower",
      str_ends(metrics, "_upp") ~ "upper",
      str_ends(metrics, "_sd") ~ "sd",
      TRUE ~ "estimate"
    )
  ) %>%
  select(c("variable", "Metrics", "bound", "perf")) %>%
  pivot_wider(names_from = bound, values_from = perf) %>%
  select(-sd)

xgb_perf_viz_df3 <- df_perf_summary %>%
  filter(models == "XGBoost (Viral load at diagnosis)") %>%
  pivot_longer(
    cols = -models,
    names_to = "metrics",
    values_to = "Perf"
    ) %>%
  mutate(Metrics = case_when(
    str_starts(metrics, 'acc_') ~ "Accuracy",
    str_starts(metrics, "sens_") ~ "Sensitivity",
    str_starts(metrics, "spec_") ~ "Specificity",
    str_starts(metrics, "prec_") ~ "Precision",
    str_starts(metrics, "f1_") ~ "F1_score",
    str_starts(metrics, "auc_") ~ "AUROC_value",
    metrics == "Accuracy" ~ "Accuracy",
    metrics == "Sensitivity" ~ "Sensitivity",
    metrics == "Specificity" ~ "Specificity",
    metrics == "Precision" ~ "Precision",
    metrics == "F1.Score" ~ "F1_score",
    metrics == "AUROC" ~ "AUROC_value"
    ),
    bound = case_when(
      str_ends(metrics, "_low") ~ "lower",
      str_ends(metrics, "_upp") ~ "upper",
      TRUE ~ "estimate"
      )) %>%
  select(c("models", "Metrics", "bound", "Perf")) %>%
  rename("variable" = "models") %>%
  pivot_wider(names_from = bound, values_from = Perf) %>%
  mutate(variable = 0)

xgb_perf_viz_df_all2 <- dplyr::bind_rows(xgb_perf_viz_diag_df, xgb_perf_viz_df3) %>%
  dplyr::arrange(Metrics, variable)
```

## Figure 4A
```{r, Fig4A}
fig4a <- ggplot(data = xgb_perf_viz_df_all2 %>% filter(Metrics %in% c("Accuracy", "AUROC_value", "Sensitivity")), aes(x = variable, y = estimate, color = Metrics)) +
  geom_col(data = xgb_perf_viz_df_all2 %>% filter(Metrics %in% c("Sensitivity")), aes(x = variable, y = estimate, fill = Metrics), alpha = 0.8) +
  geom_errorbar(data = xgb_perf_viz_df_all2 %>% filter(Metrics %in% c("Sensitivity")), aes(ymin = lower, ymax = upper), linewidth = 1.2, width = 0.3, 
                color = "black") +
  geom_line(data = xgb_perf_viz_df_all2 %>% filter(Metrics %in% c("AUROC_value")), aes(x = variable, y = estimate, color = Metrics), linewidth = rel(2), linetype = "solid") +
  geom_point(data = xgb_perf_viz_df_all2 %>% filter(Metrics %in% c("AUROC_value")), aes(x = variable, y = estimate, color = Metrics), size = rel(4)) +
  geom_line(data = xgb_perf_viz_df_all2 %>% filter(Metrics %in% c("Accuracy")), aes(x = variable, y = estimate, color = Metrics), linewidth = rel(2), linetype = "dashed") +
  geom_point(data = xgb_perf_viz_df_all2 %>% filter(Metrics %in% c("Accuracy")), aes(x = variable, y = estimate, color = Metrics), size = rel(4)) +
  xlab("Day since diagnosis (days)") +
  ylab("Metrics (%)") +
  scale_fill_manual(name = "", values = c(Sensitivity = "#0072B2")) +
  scale_color_manual(name = "", values = c(AUROC_value = "#FFC001", Accuracy = "#FA766E")) +
  guides(
    fill  = guide_legend(order = 1, override.aes = list(alpha = 0.6)),
    color = guide_legend(order = 2, override.aes = list(linetype = 1, shape = 16))
  ) +
  scale_x_continuous(limits = c(-0.5, 10.5), breaks = seq(0, 10, 1)) +
  coord_cartesian(ylim = c(88, 98)) +
  theme_classic(base_family = "Helvetica")+
  theme(axis.text = element_text(color = "black"),
        axis.text.x = element_text(vjust = 0.5, hjust = 0.5, face = "bold", size = rel(4)),
        axis.text.y = element_text(face = "bold", size = rel(4)),
        axis.line = element_line(color = "black"),
        strip.text.x = element_text(vjust = 0.5, face = "bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        legend.position = "none",
        legend.box = "horizontal",
        legend.text = element_text(size = rel(2)),
        axis.title.x = element_text(size = rel(4)),
        axis.title.y = element_text(size = rel(4))
        )
fig4a
#ggsave("Figure4A.png", fig4a, width = 16, height = 12)
```

# Comparison between model with viral load point at different time point
```{r, McNemar Test}
mc_xgb_seqcomp_diag_list <- list()
for(i in 1:100) {
  # Normalize all factors
  actual_xgb_vldiag <- factor(split_list_vldiag[[i]]$test$outcome)
  actual_xgb <- factor(split_list[[i]]$test$outcome)

  pred_xgb_vldiag <- factor(xgb_vldiag_list[[i]]$prediction, levels = levels(actual_xgb_vldiag))
  pred_xgb_day1 <- factor(xgb_seq_diag_list[[i]][[1]]$prediction, levels = levels(actual_xgb))
  pred_xgb_day2 <- factor(xgb_seq_diag_list[[i]][[2]]$prediction, levels = levels(actual_xgb))
  pred_xgb_day5 <- factor(xgb_seq_diag_list[[i]][[5]]$prediction, levels = levels(actual_xgb))

  pos_case <- "Severe"

  idx_pos_vldiag <- actual_xgb_vldiag == pos_case
  idx_pos_xgb <- actual_xgb == pos_case

  xgb_correct_vldiag <- pred_xgb_vldiag[idx_pos_vldiag] == actual_xgb_vldiag[idx_pos_vldiag]
  xgb_correct_day1 <- pred_xgb_day1[idx_pos_xgb] == actual_xgb[idx_pos_xgb]
  xgb_correct_day2 <- pred_xgb_day2[idx_pos_xgb] == actual_xgb[idx_pos_xgb]
  xgb_correct_day5 <- pred_xgb_day5[idx_pos_xgb] == actual_xgb[idx_pos_xgb]

  # Forming the table for McNemar test
  mc_tab_xgb_diagvday1 <- mc_tab(xgb_correct_vldiag, xgb_correct_day1)
  mc_tab_xgb_diagvday2 <- mc_tab(xgb_correct_vldiag, xgb_correct_day2)
  mc_tab_xgb_diagvday5 <- mc_tab(xgb_correct_vldiag, xgb_correct_day5)
  
  mc_tab_xgb_day1vday2 <- mc_tab(xgb_correct_day1, xgb_correct_day2)
  mc_tab_xgb_day1vday5 <- mc_tab(xgb_correct_day1, xgb_correct_day5)
  
  mc_tab_xgb_day2vday5 <- mc_tab(xgb_correct_day2, xgb_correct_day5)

  # Perform McNemar test
  mc_xgb_diagvday1 <- mcnemar.test(mc_tab_xgb_diagvday1, correct = FALSE)
  mc_xgb_diagvday2 <- mcnemar.test(mc_tab_xgb_diagvday2, correct = FALSE)
  mc_xgb_diagvday5 <- mcnemar.test(mc_tab_xgb_diagvday5, correct = FALSE)
  
  mc_xgb_day1vday2 <- mcnemar.test(mc_tab_xgb_day1vday2, correct = FALSE)
  mc_xgb_day1vday5 <- mcnemar.test(mc_tab_xgb_day1vday5, correct = FALSE)
  
  mc_xgb_day2vday5 <- mcnemar.test(mc_tab_xgb_day2vday5, correct = FALSE)
  
  # Getting the p-value of McNemar test
  mc_xgb_diagvday1_p <- tidy(mc_xgb_diagvday1)$p.value
  mc_xgb_diagvday2_p <- tidy(mc_xgb_diagvday2)$p.value
  mc_xgb_diagvday5_p <- tidy(mc_xgb_diagvday5)$p.value
  
  mc_xgb_day1vday2_p <- tidy(mc_xgb_day1vday2)$p.value
  mc_xgb_day1vday5_p <- tidy(mc_xgb_day1vday5)$p.value
  
  mc_xgb_day2vday5_p <- tidy(mc_xgb_day2vday5)$p.value

  mc_xgb_summary <- tibble(
      group1 = c("XGBoost (Day 0)", "XGBoost (Day 0)", "XGBoost (Day 0)", "XGBoost (Day 1)", "XGBoost (Day 1)", "XGBoost (Day 2)",
                 "XGBoost (Day 1)", "XGBoost (Day 2)", "XGBoost (Day 5)", "XGBoost (Day 2)", "XGBoost (Day 5)", "XGBoost (Day 5)",
                 "XGBoost (Day 0)", "XGBoost (Day 1)", "XGBoost (Day 2)", "XGBoost (Day 5)"),

      group2 = c("XGBoost (Day 1)", "XGBoost (Day 2)", "XGBoost (Day 5)", "XGBoost (Day 2)", "XGBoost (Day 5)", "XGBoost (Day 5)",
                 "XGBoost (Day 0)", "XGBoost (Day 0)", "XGBoost (Day 0)", "XGBoost (Day 1)", "XGBoost (Day 1)", "XGBoost (Day 2)",
                 "XGBoost (Day 0)", "XGBoost (Day 1)", "XGBoost (Day 2)", "XGBoost (Day 5)"),

      p.value = c(mc_xgb_diagvday1_p, mc_xgb_diagvday2_p, mc_xgb_diagvday5_p, mc_xgb_day1vday2_p, mc_xgb_day1vday5_p, mc_xgb_day2vday5_p,
                  mc_xgb_diagvday1_p, mc_xgb_diagvday2_p, mc_xgb_diagvday5_p, mc_xgb_day1vday2_p, mc_xgb_day1vday5_p, mc_xgb_day2vday5_p,
                  2, 2, 2, 2)
  ) %>%
  mutate(label = case_when(
      is.na(p.value) ~ "NS",
      p.value < 0.001 ~ "***",
      p.value < 0.01 ~ "**",
      p.value < 0.05 ~ "*",
      p.value == 2 ~ "NA",
      TRUE ~ "NS"
  ))

  mc_xgb_heatmap <- mc_xgb_summary %>%
                      select(group1, group2, label) %>%
                      pivot_wider(names_from = group1, values_from = label) %>%
                      column_to_rownames("group2")


  mcnemar_xgb_long <- as.data.frame(as.table(as.matrix(mc_xgb_heatmap)))
  colnames(mcnemar_xgb_long) <- c("Model1", "Model2", "Significance")

  mc_xgb_seqcomp_diag_list[[i]] <- mcnemar_xgb_long %>%
                        mutate(
                          Model1 = case_when(
                          Model1 == "XGBoost (Day 0)" ~ "0",
                          Model1 == "XGBoost (Day 1)" ~ "1",
                          Model1 == "XGBoost (Day 2)" ~ "2",
                          Model1 == "XGBoost (Day 5)" ~ "5"
                          ),
                          Model2 = case_when(
                          Model2 == "XGBoost (Day 0)" ~ "0",
                          Model2 == "XGBoost (Day 1)" ~ "1",
                          Model2 == "XGBoost (Day 2)" ~ "2",
                          Model2 == "XGBoost (Day 5)" ~ "5"
                          ),
                          Model1 = factor(Model1, levels = c("5", "2", "1", "0")),
                          Model2 = factor(Model2, levels = c("0", "1", "2", "5"))
                        )
}

# Summarise the percentage of significance in each scenario cases
mc_xgb_seqcomp_diag_percent_sum <- dplyr::bind_rows(
  lapply(seq_along(mc_xgb_seqcomp_diag_list), function(i) {
    mc_xgb_seqcomp_diag_list[[i]] %>% mutate(run = i)
    })
  )

# Define labels of statistically significant
sig_labels <- c("*", "**", "***")

# Summarize the percentage significant for each scenario
sig_xgb_seqcomp_diag_sum <- mc_xgb_seqcomp_diag_percent_sum %>%
                mutate(is_significant = Significance %in% sig_labels) %>%
                group_by(Model1, Model2) %>%
                summarize(
                  n_sig = sum(is_significant),
                  n_total = n(),
                  percent_sig = 100 * n_sig / n_total,
                  .groups = "drop"
                ) %>%
                mutate(percent_sig = ifelse(Model1 == Model2, NA, percent_sig)) %>%
                mutate(
                  fill = case_when(
                      is.na(percent_sig) ~ "black",
                      percent_sig < 40 ~ "white",
                      percent_sig >= 40 & percent_sig < 60 ~ "grey90",
                      percent_sig >=60 & percent_sig <80 ~ "gold",
                      percent_sig >= 80 ~ "orange"
                    ),
                  percent_label = ifelse(is.na(percent_sig), "", sprintf("%.1f%%", percent_sig))
                )
sig_xgb_seqcomp_diag_sum
```

```{r, Heatmap}
# Plot heatmap
mc_plot_xgbseq_diag <- ggplot(sig_xgb_seqcomp_diag_sum, aes(x = Model2, y = Model1, fill = fill)) +
                  geom_tile(color = "black") +
                  geom_text(aes(label = percent_label), color = "black", size = rel(5), fontface = "bold") +
                  scale_fill_manual(values = c("black"= "black", "white" = "white", "grey90" = "grey90", "orange" = "orange", "gold" = "gold"), guide = "none") +
                  theme_classic() +
                  theme(axis.text.x = element_text(hjust = 0.5, face = "bold", size = rel(2)),
                        axis.text.y = element_text(face = "bold", size = rel(2)),
                        axis.title.x = element_blank(),
                        axis.title.y = element_blank(),
                        legend.position = "none")
mc_plot_xgbseq_diag
```

## Figure 4B
```{r, Fig4B_diag}
xgb_sens_comp_diag <- xgb_perf_viz_df_all2 %>%
                filter(Metrics == "Sensitivity" & variable %in% c("0", "1", "2", "5"))

# Function to convert the percentage of significant to annotation
pct_to_stars <- function(p) dplyr::case_when(
  is.na(p) ~ "NA",
  p >= 80 ~ "****",
  p >= 60 ~ "***",
  p >= 40 ~ "**",
  p >= 20 ~ "*",
  TRUE ~ ""
)

# Function to extract the percentage of significant
get_pair_percents <- function(sig_df) {
  sig_df %>%
    filter(!is.na(percent_sig)) %>%
    mutate(
      a = pmin(as.character(Model1), as.character(Model2)),
      b = pmax(as.character(Model1), as.character(Model2)),
      pair = paste0(a, "-", b)
    ) %>%
    distinct(pair, percent_sig) %>%
    select(pair, percent_sig) %>%
    tibble::deframe()
}

# Function to build bracket information for one row facet for each model family
row_signif_2 <- function(sig_df, perf_all) {
  fam_sens <- perf_all
  if (nrow(fam_sens) == 0) {
    return(NULL)
  }
  
  pairs <- list(c("0", "1"), c("0", "2"), c("0", "5"))
  
  pp <- get_pair_percents(sig_df)
  pct_vec <- c(pp[["0-1"]], pp[["0-2"]], pp[["0-5"]])
  ann <- pct_to_stars(pct_vec)
  
  y_top <- max(fam_sens$upper, fam_sens$estimate, na.rm = TRUE)
  gap <- 0.01 * (y_top %||% 1)
  y_pos <- y_top + gap * (1:6)
  
  # Return the list compiled
  list(family = family, pairs = pairs, annotations = ann, y = y_pos)
}

# Compile the results of comparisons
xgb_row_diag <- row_signif_2(sig_xgb_seqcomp_diag_sum, xgb_sens_comp_diag)

# Function to add the row of results of comparisons into plot
add_row_signif_diag <- function(p, row_spec) {
  if (is.null(row_spec)) {
    return(p)
  }
  p + geom_signif(
    data = xgb_sens_comp_diag,
    inherit.aes = FALSE,
    aes(x = as.factor(variable), y = estimate),
    comparisons = row_spec$pairs,
    annotations = row_spec$annotations,
    y_position = row_spec$y,
    textsize = 4,
    size = 0.8,
    vjust = -0.1
  )
}

fig_4b_diag <- ggplot(data = xgb_sens_comp_diag, aes(x = as.factor(variable), y = estimate)) +
                geom_col(data = xgb_sens_comp_diag, aes(x = as.factor(variable), y = estimate, fill = Metrics), alpha = 0.8) +
                geom_errorbar(aes(ymin = lower, ymax = upper, color = Metrics), width = 0.1, linewidth = 1.2) +
                scale_x_discrete(limits = c("0", "1", "2", "5")) +
                xlab("Time since diagnosis (days)") +
                ylab("Sensitivity (%)") +
                scale_fill_manual(name = "", values = c(Sensitivity = "#0072B2")) +
                scale_color_manual(name = "", values = c(Sensitivity = "black")) +
                coord_cartesian(ylim = c(88, 100)) +
                theme_classic(base_family = "Helvetica") +
                theme(axis.text = element_text(color = "black"),
                      axis.text.x = element_text(vjust = 0.5, hjust = 0.5, face = "bold", size = rel(4)),
                      axis.text.y.left = element_text(face = "bold", size = rel(4)),
                      axis.line = element_line(color = "black"),
                      strip.text.x = element_text(angle = 360, vjust = 0.5, face = "bold", size = rel(2)),
                      strip.text.y = element_text(face = "bold", size = rel(2)),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.background = element_blank(),
                      legend.position = "none",
                      axis.title.y = element_text(size = rel(4)),
                      axis.title.x = element_text(size = rel(4))
                      )
fig4b_diag <- fig_4b_diag %>%
        add_row_signif_diag(xgb_row_diag)
fig4b_diag
#ggsave("Figure4B.png", fig4b_diag, width = 16, height = 12)
```

# Adding one additional viral load to the model (Diagnosis)
## Day 2
### Setup CPU clusters
```{r, Setup CPU clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

### Fitting data into XGBoost
```{r, Inclusion of additional time point into model}
xgb_add2_list <- foreach(i = 1:100, .packages = c("dplyr", "xgboost", "pROC", "shapviz")) %dopar% {
  split <- split_list[[i]]
  
  train_df <- split$train %>% select(age, gender, vaccination, comorbidity, vl_sim, vl_sim2, outcome) %>% rename("diagnosis" = "vl_sim", "day2" = "vl_sim2")
  test_df <- split$test %>% select(age, gender, vaccination, comorbidity, vl_sim, vl_sim2, outcome) %>% rename("diagnosis" = "vl_sim", "day2" = "vl_sim2")
  
  train_x <- model.matrix(outcome ~ ., data = train_df)[, -1]
  test_x <- model.matrix(outcome ~ ., data = test_df)[, -1]
  
  dtrain <- xgb.DMatrix(data = train_x, label = as.numeric(as.factor(train_df$outcome)) - 1)
  dtest <- xgb.DMatrix(data = test_x, label = as.numeric(as.factor(test_df$outcome)) - 1)
  
  xgb_model <- xgboost(data = dtrain, nrounds = 1000, verbose = 0, objective = "binary:logistic")
  
  xgb_pred <- predict(xgb_model, dtest)
  xgb_pred_label <- ifelse(xgb_pred < 0.5, 0, 1)
  xgb_pred_res <- ifelse(xgb_pred_label == 1, "Severe", "Non severe")
  
  cfm_xgb <- table(Predicted = xgb_pred_res, Actual = test_df$outcome)
  accuracy_xgb <- sum(cfm_xgb["Severe", "Severe"], cfm_xgb["Non severe", "Non severe"]) / sum(cfm_xgb)
  
  xgb_pred_train <- predict(xgb_model, dtrain)
  xgb_pred_train_label <- ifelse(xgb_pred_train < 0.5, 0, 1)
  xgb_pred_train_res <- ifelse(xgb_pred_train_label == 1, "Severe", "Non severe")
  
  cfm_xgb_train <- table(Predicted = xgb_pred_train_res, Actual = train_df$outcome)
  accuracy_xgb_train <- sum(cfm_xgb_train["Severe", "Severe"], cfm_xgb_train["Non severe", "Non severe"]) / sum(cfm_xgb_train)
  
  TP <- cfm_xgb["Severe", "Severe"]
  FP <- cfm_xgb["Severe", "Non severe"]
  TN <- cfm_xgb["Non severe", "Non severe"]
  FN <- cfm_xgb["Non severe", "Severe"]
    
  sensitivity_xgb <- TP / (TP + FN)
  specificity_xgb <- TN / (TN + FP)
  prec_xgb <- TP / (TP + FP)
  f1_sc_xgb <- 2 * ((prec_xgb * sensitivity_xgb) / (prec_xgb + sensitivity_xgb))
    
  roc_xgb <- roc(test_df$outcome, xgb_pred)
  auc_val_xgb <- auc(roc_xgb)
    
  shap_long <- shapviz(xgb_model, X_pred = train_x, X = as.data.frame(train_x))
    
  list(model = xgb_model, confusion_matrix = cfm_xgb, accuracy_training = accuracy_xgb_train, accuracy_testing = accuracy_xgb, sensitivity = sensitivity_xgb,
       specificity = specificity_xgb, precision = prec_xgb, F1_score = f1_sc_xgb, AUC_value = auc_val_xgb, SHAP_values = shap_long, prediction = xgb_pred_res, roc = roc_xgb)
}
```

### Stop CPU clusters
```{r, Stop CPU clusters}
stopCluster(cl)
```

### Compile model performance metrics 
```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
xgb_add2_metrics_df <- map_dfr(seq_along(xgb_add2_list), function(i) {
  result <- xgb_add2_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
xgb_add2_metrics_df <- as.data.frame(xgb_add2_metrics_df)

xgb_add2_metrics_summary <- xgb_add2_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(xgb_add2_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(xgb_add2_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(xgb_add2_metrics_df$sensitivity, 0.025)
low_spec <- quantile(xgb_add2_metrics_df$specificity, 0.025)
low_prec <- quantile(xgb_add2_metrics_df$precision, 0.025)
low_f1_sc <- quantile(xgb_add2_metrics_df$F1_score, 0.025)
low_auc <- quantile(xgb_add2_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(xgb_add2_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(xgb_add2_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(xgb_add2_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(xgb_add2_metrics_df$specificity, 0.975)
upp_prec <- quantile(xgb_add2_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(xgb_add2_metrics_df$F1_score, 0.975)
upp_auc <- quantile(xgb_add2_metrics_df$AUC_value, 0.975)

xgb_add2_metrics_summary['low_acc_train'] <- low_acc_train
xgb_add2_metrics_summary['low_acc_test'] <- low_acc_test
xgb_add2_metrics_summary['low_sens'] <- low_sens
xgb_add2_metrics_summary['low_spec'] <- low_spec
xgb_add2_metrics_summary['low_prec'] <- low_prec
xgb_add2_metrics_summary['low_f1_sc'] <- low_f1_sc
xgb_add2_metrics_summary['low_auc'] <- low_auc

xgb_add2_metrics_summary['upp_acc_train'] <- upp_acc_train
xgb_add2_metrics_summary['upp_acc_test'] <- upp_acc_test
xgb_add2_metrics_summary['upp_sens'] <- upp_sens
xgb_add2_metrics_summary['upp_spec'] <- upp_spec
xgb_add2_metrics_summary['upp_prec'] <- upp_prec
xgb_add2_metrics_summary['upp_f1_sc'] <- upp_f1_sc
xgb_add2_metrics_summary['upp_auc'] <- upp_auc

xgb_add2_metrics_summary
```

## Day 1
### Setup CPU clusters
```{r, Setup CPU clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

### Fitting data into XGBoost
```{r, Inclusion of additional time point into model}
xgb_add3_list <- foreach(i = 1:100, .packages = c("dplyr", "xgboost", "pROC", "shapviz")) %dopar% {
  split <- split_list_p[[i]]
  
  train_df <- split$train %>% select(age, gender, vaccination, comorbidity, vl_sim, vl_dp1, outcome) %>% rename("diagnosis" = "vl_sim", "day1" = "vl_dp1")
  test_df <- split$test %>% select(age, gender, vaccination, comorbidity, vl_sim, vl_dp1, outcome) %>% rename("diagnosis" = "vl_sim", "day1" = "vl_dp1")
  
  train_x <- model.matrix(outcome ~ ., data = train_df)[, -1]
  test_x <- model.matrix(outcome ~ ., data = test_df)[, -1]
  
  dtrain <- xgb.DMatrix(data = train_x, label = as.numeric(as.factor(train_df$outcome)) - 1)
  dtest <- xgb.DMatrix(data = test_x, label = as.numeric(as.factor(test_df$outcome)) - 1)
  
  xgb_model <- xgboost(data = dtrain, nrounds = 1000, verbose = 0, objective = "binary:logistic")
  
  xgb_pred <- predict(xgb_model, dtest)
  xgb_pred_label <- ifelse(xgb_pred < 0.5, 0, 1)
  xgb_pred_res <- ifelse(xgb_pred_label == 1, "Severe", "Non severe")
  
  cfm_xgb <- table(Predicted = xgb_pred_res, Actual = test_df$outcome)
  accuracy_xgb <- sum(cfm_xgb["Severe", "Severe"], cfm_xgb["Non severe", "Non severe"]) / sum(cfm_xgb)
  
  xgb_pred_train <- predict(xgb_model, dtrain)
  xgb_pred_train_label <- ifelse(xgb_pred_train < 0.5, 0, 1)
  xgb_pred_train_res <- ifelse(xgb_pred_train_label == 1, "Severe", "Non severe")
  
  cfm_xgb_train <- table(Predicted = xgb_pred_train_res, Actual = train_df$outcome)
  accuracy_xgb_train <- sum(cfm_xgb_train["Severe", "Severe"], cfm_xgb_train["Non severe", "Non severe"]) / sum(cfm_xgb_train)
  
  TP <- cfm_xgb["Severe", "Severe"]
  FP <- cfm_xgb["Severe", "Non severe"]
  TN <- cfm_xgb["Non severe", "Non severe"]
  FN <- cfm_xgb["Non severe", "Severe"]
    
  sensitivity_xgb <- TP / (TP + FN)
  specificity_xgb <- TN / (TN + FP)
  prec_xgb <- TP / (TP + FP)
  f1_sc_xgb <- 2 * ((prec_xgb * sensitivity_xgb) / (prec_xgb + sensitivity_xgb))
    
  roc_xgb <- roc(test_df$outcome, xgb_pred)
  auc_val_xgb <- auc(roc_xgb)
    
  shap_long <- shapviz(xgb_model, X_pred = train_x, X = as.data.frame(train_x))
    
  list(model = xgb_model, confusion_matrix = cfm_xgb, accuracy_training = accuracy_xgb_train, accuracy_testing = accuracy_xgb, sensitivity = sensitivity_xgb,
       specificity = specificity_xgb, precision = prec_xgb, F1_score = f1_sc_xgb, AUC_value = auc_val_xgb, SHAP_values = shap_long, prediction = xgb_pred_res, roc = roc_xgb)
}
```

### Stop CPU clusters
```{r, Stop CPU clusters}
stopCluster(cl)
```

### Compile model performance metrics 
```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
xgb_add3_metrics_df <- map_dfr(seq_along(xgb_add3_list), function(i) {
  result <- xgb_add3_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
xgb_add3_metrics_df <- as.data.frame(xgb_add3_metrics_df)

xgb_add3_metrics_summary <- xgb_add3_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(xgb_add3_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(xgb_add3_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(xgb_add3_metrics_df$sensitivity, 0.025)
low_spec <- quantile(xgb_add3_metrics_df$specificity, 0.025)
low_prec <- quantile(xgb_add3_metrics_df$precision, 0.025)
low_f1_sc <- quantile(xgb_add3_metrics_df$F1_score, 0.025)
low_auc <- quantile(xgb_add3_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(xgb_add3_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(xgb_add3_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(xgb_add3_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(xgb_add3_metrics_df$specificity, 0.975)
upp_prec <- quantile(xgb_add3_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(xgb_add3_metrics_df$F1_score, 0.975)
upp_auc <- quantile(xgb_add3_metrics_df$AUC_value, 0.975)

xgb_add3_metrics_summary['low_acc_train'] <- low_acc_train
xgb_add3_metrics_summary['low_acc_test'] <- low_acc_test
xgb_add3_metrics_summary['low_sens'] <- low_sens
xgb_add3_metrics_summary['low_spec'] <- low_spec
xgb_add3_metrics_summary['low_prec'] <- low_prec
xgb_add3_metrics_summary['low_f1_sc'] <- low_f1_sc
xgb_add3_metrics_summary['low_auc'] <- low_auc

xgb_add3_metrics_summary['upp_acc_train'] <- upp_acc_train
xgb_add3_metrics_summary['upp_acc_test'] <- upp_acc_test
xgb_add3_metrics_summary['upp_sens'] <- upp_sens
xgb_add3_metrics_summary['upp_spec'] <- upp_spec
xgb_add3_metrics_summary['upp_prec'] <- upp_prec
xgb_add3_metrics_summary['upp_f1_sc'] <- upp_f1_sc
xgb_add3_metrics_summary['upp_auc'] <- upp_auc

xgb_add3_metrics_summary
```

#### Compile all the performance metrics
```{r, Compile performance metrics for Figure 4C}
xgb_acc_add2 <- xgb_add2_metrics_summary$accuracy_test_mean
xgb_acc_low_add2 <- xgb_add2_metrics_summary$low_acc_test
xgb_acc_upp_add2 <- xgb_add2_metrics_summary$upp_acc_test
xgb_sens_add2 <- xgb_add2_metrics_summary$sensitivity_mean
xgb_sens_low_add2 <- xgb_add2_metrics_summary$low_sens
xgb_sens_upp_add2 <- xgb_add2_metrics_summary$upp_sens
xgb_spec_add2 <- xgb_add2_metrics_summary$specificity_mean
xgb_spec_low_add2 <- xgb_add2_metrics_summary$low_spec
xgb_spec_upp_add2 <- xgb_add2_metrics_summary$upp_spec
xgb_prec_add2 <- xgb_add2_metrics_summary$precision_mean
xgb_prec_low_add2 <- xgb_add2_metrics_summary$low_prec
xgb_prec_upp_add2 <- xgb_add2_metrics_summary$upp_prec
xgb_f1_add2 <- xgb_add2_metrics_summary$F1_score_mean
xgb_f1_low_add2 <- xgb_add2_metrics_summary$low_f1_sc
xgb_f1_upp_add2 <- xgb_add2_metrics_summary$upp_f1_sc
xgb_auc_add2 <- xgb_add2_metrics_summary$AUC_mean
xgb_auc_low_add2 <- xgb_add2_metrics_summary$low_auc
xgb_auc_upp_add2 <- xgb_add2_metrics_summary$upp_auc

xgb_acc_add3 <- xgb_add3_metrics_summary$accuracy_test_mean
xgb_acc_low_add3 <- xgb_add3_metrics_summary$low_acc_test
xgb_acc_upp_add3 <- xgb_add3_metrics_summary$upp_acc_test
xgb_sens_add3 <- xgb_add3_metrics_summary$sensitivity_mean
xgb_sens_low_add3 <- xgb_add3_metrics_summary$low_sens
xgb_sens_upp_add3 <- xgb_add3_metrics_summary$upp_sens
xgb_spec_add3 <- xgb_add3_metrics_summary$specificity_mean
xgb_spec_low_add3 <- xgb_add3_metrics_summary$low_spec
xgb_spec_upp_add3 <- xgb_add3_metrics_summary$upp_spec
xgb_prec_add3 <- xgb_add3_metrics_summary$precision_mean
xgb_prec_low_add3 <- xgb_add3_metrics_summary$low_prec
xgb_prec_upp_add3 <- xgb_add3_metrics_summary$upp_prec
xgb_f1_add3 <- xgb_add3_metrics_summary$F1_score_mean
xgb_f1_low_add3 <- xgb_add3_metrics_summary$low_f1_sc
xgb_f1_upp_add3 <- xgb_add3_metrics_summary$upp_f1_sc
xgb_auc_add3 <- xgb_add3_metrics_summary$AUC_mean
xgb_auc_low_add3 <- xgb_add3_metrics_summary$low_auc
xgb_auc_upp_add3 <- xgb_add3_metrics_summary$upp_auc

perf_metrics_diag <- data.frame(
  models = c("Diagnosis + Day 2 post diagnosis", "Diagnosis + Day 1 post diagnosis"),
  Accuracy = c(xgb_acc_add2, xgb_acc_add3),
  acc_low = c(xgb_acc_low_add2, xgb_acc_low_add3),
  acc_upp = c(xgb_acc_upp_add2, xgb_acc_upp_add3),
  Sensitivity = c(xgb_sens_add2, xgb_sens_add3),
  sens_low = c(xgb_sens_low_add2, xgb_sens_low_add3),
  sens_upp = c(xgb_sens_upp_add2, xgb_sens_upp_add3),
  Specificity = c(xgb_spec_add2, xgb_spec_add3),
  spec_low = c(xgb_spec_low_add2, xgb_spec_low_add3),
  spec_upp = c(xgb_spec_upp_add2, xgb_spec_upp_add3),
  Precision = c(xgb_prec_add2, xgb_prec_add3),
  prec_low = c(xgb_prec_low_add2, xgb_prec_low_add3),
  prec_upp = c(xgb_prec_upp_add2, xgb_prec_upp_add3),
  `F1-Score` = c(xgb_f1_add2, xgb_f1_add3),
  f1_low = c(xgb_f1_low_add2, xgb_f1_low_add3),
  f1_upp = c(xgb_f1_upp_add2, xgb_f1_upp_add3),
  AUROC = c(xgb_auc_add2, xgb_auc_add3),
  auc_low = c(xgb_auc_low_add2, xgb_auc_low_add3),
  auc_upp = c(xgb_auc_upp_add2, xgb_auc_upp_add3)
)
df_perf_metrics3 <- dplyr::bind_rows(df_perf_summary, perf_metrics_diag) %>%
  filter(models %in% c("XGBoost (Viral load at symptom onset)", "XGBoost (Viral load at diagnosis)", "Diagnosis + Day 2 post diagnosis", "Diagnosis + Day 1 post diagnosis")) %>%
  mutate(models = case_when(
    models == "XGBoost (Viral load at symptom onset)" ~ "Onset only",
    models == "XGBoost (Viral load at diagnosis)" ~ "Diagnosis only",
    TRUE ~ models))
df_perf_metrics3
```

##### Perform McNemar Test
```{r, McNemar test for XGBoost in three scenarios}
mc_xgb_compare_list2 <- list()
for(i in 1:100) {
  # Normalize all factors
  actual_xgb_vlsymp <- factor(split_list_vlsim_symp[[i]]$test$outcome)
  actual_xgb_vldiag <- factor(split_list_vldiag[[i]]$test$outcome)
  actual_xgb <- factor(split_list[[i]]$test$outcome)

  pred_xgb_vlsymp <- factor(xgb_vlsymp_list[[i]]$prediction, levels = levels(actual_xgb_vlsymp))
  pred_xgb_vldiag <- factor(xgb_vldiag_list[[i]]$prediction, levels = levels(actual_xgb_vldiag))
  pred_xgb_add3 <- factor(xgb_add3_list[[i]]$prediction, levels = levels(actual_xgb))
  pred_xgb_add2 <- factor(xgb_add2_list[[i]]$prediction, levels = levels(actual_xgb))

  pos_case <- "Severe"

  idx_pos_vlsymp <- actual_xgb_vlsymp == pos_case
  idx_pos_vldiag <- actual_xgb_vldiag == pos_case
  idx_pos_xgb <- actual_xgb == pos_case

  xgb_correct_vlsymp <- pred_xgb_vlsymp[idx_pos_vlsymp] == actual_xgb_vlsymp[idx_pos_vlsymp]
  xgb_correct_vldiag <- pred_xgb_vldiag[idx_pos_vldiag] == actual_xgb_vldiag[idx_pos_vldiag]
  xgb_correct_add3 <- pred_xgb_add3[idx_pos_xgb] == actual_xgb[idx_pos_xgb]
  xgb_correct_add2 <- pred_xgb_add2[idx_pos_xgb] == actual_xgb[idx_pos_xgb]

  # Forming the table for McNemar test
  mc_tab_xgb_sympvdiag <- mc_tab(xgb_correct_vlsymp, xgb_correct_vldiag)
  mc_tab_xgb_sympvadd3 <- mc_tab(xgb_correct_vlsymp, xgb_correct_add3)
  mc_tab_xgb_sympvadd2 <- mc_tab(xgb_correct_vlsymp, xgb_correct_add2)
  
  mc_tab_xgb_diagvadd3 <- mc_tab(xgb_correct_vldiag, xgb_correct_add3)
  mc_tab_xgb_diagvadd2 <- mc_tab(xgb_correct_vldiag, xgb_correct_add2)
  
  mc_tab_xgb_add3vadd2 <- mc_tab(xgb_correct_add3, xgb_correct_add2)
  
  # Perform McNemar test
  mc_xgb_sympvdiag <- mcnemar.test(mc_tab_xgb_sympvdiag, correct = FALSE)
  mc_xgb_sympvadd3 <- mcnemar.test(mc_tab_xgb_sympvadd3, correct = FALSE)
  mc_xgb_sympvadd2 <- mcnemar.test(mc_tab_xgb_sympvadd2, correct = FALSE)
  
  mc_xgb_diagvadd3 <- mcnemar.test(mc_tab_xgb_diagvadd3, correct = FALSE)
  mc_xgb_diagvadd2 <- mcnemar.test(mc_tab_xgb_diagvadd2, correct = FALSE)
  
  mc_xgb_add3vadd2 <- mcnemar.test(mc_tab_xgb_add3vadd2, correct = FALSE)
  
  # Getting the p-value of McNemar test
  mc_xgb_sympvdiag_p <- tidy(mc_xgb_sympvdiag)$p.value
  mc_xgb_sympvadd3_p <- tidy(mc_xgb_sympvadd3)$p.value
  mc_xgb_sympvadd2_p <- tidy(mc_xgb_sympvadd2)$p.value
  
  mc_xgb_diagvadd3_p <- tidy(mc_xgb_diagvadd3)$p.value
  mc_xgb_diagvadd2_p <- tidy(mc_xgb_diagvadd2)$p.value
  
  mc_xgb_add3vadd2_p <- tidy(mc_xgb_add3vadd2)$p.value
  
  mc_xgb_compare_summary <- tibble(
      group1 = c("Onset only", "Onset only", "Onset only",
                 "Diagnosis only", "Diagnosis only",
                 "Diagnosis + Day 1 post diagnosis", 
                 
                 "Diagnosis only", "Diagnosis + Day 1 post diagnosis", "Diagnosis + Day 2 post diagnosis",
                 "Diagnosis + Day 1 post diagnosis", "Diagnosis + Day 2 post diagnosis",
                 "Diagnosis + Day 2 post diagnosis",
                 
                 "Onset only", "Diagnosis only", "Diagnosis + Day 1 post diagnosis", "Diagnosis + Day 2 post diagnosis"),

      group2 = c("Diagnosis only", "Diagnosis + Day 1 post diagnosis", "Diagnosis + Day 2 post diagnosis",
                 "Diagnosis + Day 1 post diagnosis", "Diagnosis + Day 2 post diagnosis",
                 "Diagnosis + Day 2 post diagnosis",
                 
                 "Onset only", "Onset only", "Onset only",
                 "Diagnosis only", "Diagnosis only",
                 "Diagnosis + Day 1 post diagnosis",
                
                 "Onset only", "Diagnosis only", "Diagnosis + Day 1 post diagnosis", "Diagnosis + Day 2 post diagnosis"),

      p.value = c(mc_xgb_sympvdiag_p, mc_xgb_sympvadd3_p,mc_xgb_sympvadd2_p,
                  mc_xgb_diagvadd3_p, mc_xgb_diagvadd2_p,
                  mc_xgb_add3vadd2_p,
                  mc_xgb_sympvdiag_p, mc_xgb_sympvadd3_p,mc_xgb_sympvadd2_p,
                  mc_xgb_diagvadd3_p, mc_xgb_diagvadd2_p,
                  mc_xgb_add3vadd2_p,
                  #mc_xgb_sympvdiag_p, mc_xgb_sympvadd_p, mc_xgb_sympvadd2_p, mc_xgb_diagvadd_p, mc_xgb_diagvadd2_p, mc_xgb_addvadd2_p,
                  2, 2, 2, 2)
  ) %>%
  mutate(label = case_when(
      is.na(p.value) ~ "NS",
      p.value < 0.001 ~ "***",
      p.value < 0.01 ~ "**",
      p.value < 0.05 ~ "*",
      p.value == 2 ~ "NA",
      TRUE ~ "NS"
  ))

  mc_xgb_compare_heatmap <- mc_xgb_compare_summary %>%
                      select(group1, group2, label) %>%
                      pivot_wider(names_from = group1, values_from = label) %>%
                      column_to_rownames("group2")


  mcnemar_xgb_compare_long <- as.data.frame(as.table(as.matrix(mc_xgb_compare_heatmap)))
  colnames(mcnemar_xgb_compare_long) <- c("Model1", "Model2", "Significance")

  mc_xgb_compare_list2[[i]] <- mcnemar_xgb_compare_long %>%
                        mutate(
                          Model1 = factor(Model1, levels = c("Diagnosis + Day 2 post diagnosis", "Diagnosis + Day 1 post diagnosis", "Diagnosis only", "Onset only")),
                          Model2 = factor(Model2, levels = c("Onset only", "Diagnosis only", "Diagnosis + Day 1 post diagnosis", "Diagnosis + Day 2 post diagnosis"))
                        )
}

# Summarise the percentage of significance in each scenario cases
mc_xgb_compare_percent_sum2 <- dplyr::bind_rows(
  lapply(seq_along(mc_xgb_compare_list2), function(i) {
    mc_xgb_compare_list2[[i]] %>% mutate(run = i)
    })
  )

# Define labels of statistically significant
sig_labels <- c("*", "**", "***")

# Summarize the percentage significant for each scenario
sig_xgb_compare_sum2 <- mc_xgb_compare_percent_sum2 %>%
                mutate(is_significant = Significance %in% sig_labels) %>%
                group_by(Model1, Model2) %>%
                summarize(
                  n_sig = sum(is_significant),
                  n_total = n(),
                  percent_sig = 100 * n_sig / n_total,
                  .groups = "drop"
                ) %>%
                mutate(percent_sig = ifelse(Model1 == Model2, NA, percent_sig)) %>%
                mutate(
                  fill = case_when(
                      is.na(percent_sig) ~ "black",
                      percent_sig < 40 ~ "white",
                      percent_sig >= 40 & percent_sig < 60 ~ "grey90",
                      percent_sig >=60 & percent_sig <80 ~ "gold",
                      percent_sig >= 80 ~ "orange"
                    ),
                  percent_label = ifelse(is.na(percent_sig), "", sprintf("%.1f%%", percent_sig))
                )
sig_xgb_compare_sum2
```

```{r, Heatmap}
# Plot heatmap
mc_plot_xgbcomp2 <- ggplot(sig_xgb_compare_sum2, aes(x = Model2, y = Model1, fill = fill)) +
                  geom_tile(color = "black") +
                  geom_text(aes(label = percent_label), color = "black", size = rel(5), fontface = "bold") +
                  scale_fill_manual(values = c("black"= "black", "white" = "white", "grey90" = "grey90", "orange" = "orange", "gold" = "gold"), guide = "none") +
                  theme_classic() +
                  theme(axis.text.x = element_text(hjust = 0.5, face = "bold", size = rel(1)),
                        axis.text.y = element_text(face = "bold", size = rel(1)),
                        axis.title.x = element_blank(),
                        axis.title.y = element_blank(),
                        legend.position = "none")
mc_plot_xgbcomp2
```

## Figure 4C
```{r, Fig4C_diag}
model_perf_comp2 <- df_perf_metrics3 %>%
                pivot_longer(
                    cols = -models,
                    names_to = "metrics",
                    values_to = "Perf"
                ) %>%
                mutate(Metrics = case_when(
                    str_starts(metrics, 'acc_') ~ "Accuracy",
                    str_starts(metrics, "sens_") ~ "Sensitivity",
                    str_starts(metrics, "spec_") ~ "Specificity",
                    str_starts(metrics, "prec_") ~ "Precision",
                    str_starts(metrics, "f1_") ~ "F1-Score",
                    str_starts(metrics, "auc_") ~ "AUROC",
                    metrics == "Accuracy" ~ "Accuracy",
                    metrics == "Sensitivity" ~ "Sensitivity",
                    metrics == "Specificity" ~ "Specificity",
                    metrics == "Precision" ~ "Precision",
                    metrics == "F1.Score" ~ "F1-Score",
                    metrics == "AUROC" ~ "AUROC"
                ),
                bound = case_when(
                    str_ends(metrics, "_low") ~ "lower",
                    str_ends(metrics, "_upp") ~ "upper",
                    TRUE ~ "estimate"
                )) %>%
                select(c("models", "Metrics", "bound", "Perf")) %>%
                pivot_wider(names_from = bound, values_from = Perf) %>%
                mutate(models = factor(models, levels = c("Onset only", "Diagnosis only", "Diagnosis + Day 1 post diagnosis", "Diagnosis + Day 2 post diagnosis")))

# AUROC text positioned just above the Sensitivity upper CI for each model
ann_auroc2 <- model_perf_comp2 %>%
  filter(Metrics %in% c("Sensitivity", "AUROC")) %>%
  select(models, Metrics, estimate, upper) %>%
  pivot_wider(names_from = Metrics, values_from = c(estimate, upper)) %>%
  transmute(
    models,
    Metrics = "AUROC",
    # place text a bit above the Sensitivity bar/errorbar
    y = pmax(upper_Sensitivity, estimate_Sensitivity, na.rm = TRUE) + 1,
    label = sprintf("%.1f", estimate_AUROC)
  )

# Accuracy text positioned just above the Sensitivity upper CI for each model
ann_acc2 <- model_perf_comp2 %>%
  filter(Metrics %in% c("Sensitivity", "Accuracy")) %>%
  select(models, Metrics, estimate, upper) %>%
  pivot_wider(names_from = Metrics, values_from = c(estimate, upper)) %>%
  transmute(
    models,
    Metrics = "Accuracy",
    # place text a bit above the Sensitivity bar/errorbar
    y = pmax(upper_Sensitivity, estimate_Sensitivity, na.rm = TRUE) + 0.4,
    label = sprintf("%.1f", estimate_Accuracy)
  )

# Function to build bracket information for one row facet for each model family
row_signif_comp_diag <- function(sig_df, perf_all, offsets = c(1, 2, 3.2, 4.6, 6.4, 8.5)) {
  fam_sens <- perf_all
  if (nrow(fam_sens) == 0) {
    return(NULL)
  }
  
  pairs <- list(c("Onset only", "Diagnosis only"), c("Diagnosis only", "Diagnosis + Day 1 post diagnosis"), c("Diagnosis + Day 1 post diagnosis", "Diagnosis + Day 2 post diagnosis"),
                c("Diagnosis only", "Diagnosis + Day 2 post diagnosis"), c("Onset only", "Diagnosis + Day 1 post diagnosis"), c("Onset only", "Diagnosis + Day 2 post diagnosis"))
  
  pp <- get_pair_percents(sig_df)
  pct_vec <- c(pp[["Diagnosis only-Onset only"]], pp[["Diagnosis + Day 1 post diagnosis-Diagnosis only"]], pp[["Diagnosis + Day 1 post diagnosis-Diagnosis + Day 2 post diagnosis"]],
               pp[["Diagnosis + Day 2 post diagnosis-Diagnosis only"]], pp[["Diagnosis + Day 1 post diagnosis-Onset only"]], pp[["Diagnosis + Day 2 post diagnosis-Onset only"]])
  ann <- pct_to_stars(pct_vec)
  
  y_top <- max(fam_sens$estimate, na.rm = TRUE)
  
  # Return the list compiled
  list(pairs = pairs, annotations = ann, y = y_top - 3 + offsets)
}

xgb_row_compare_diag <- row_signif_comp_diag(sig_xgb_compare_sum2, model_perf_comp2)
#xgb_row_compare['pairs'] <- factor(xgb_row_compare['pairs'], levels = c())

# Function to add the row of results of comparisons into plot
add_row_signif_compare2 <- function(p, row_spec) {
  if (is.null(row_spec)) {
    return(p)
  }
  p + geom_signif(
    data = model_perf_comp2,
    inherit.aes = FALSE,
    aes(x = as.factor(models), y = estimate),
    comparisons = row_spec$pairs,
    annotations = row_spec$annotations,
    y_position = row_spec$y,
    textsize = 8,
    size = 0.8,
    tip_length = 0.008,
    vjust = 0.1
  )
}

fig4c_temp2 <- ggplot(data = model_perf_comp2 %>% filter(Metrics %in% c("AUROC", "Sensitivity")), aes(x = models, y = estimate, color = Metrics)) +
  geom_col(data = model_perf_comp2 %>% filter(Metrics %in% c("Sensitivity")), aes(x = models, y = estimate, fill = models), alpha = 0.8) +
  geom_errorbar(data = model_perf_comp2 %>% filter(Metrics %in% c("Sensitivity")), aes(ymin = lower, ymax = upper), linewidth = 1.2, width = 0.3, 
                color = "black") +
  geom_text(data = ann_auroc2 %>% filter(Metrics %in% c("AUROC")), aes(x = models, y = y, label = paste0("AUROC = ", label, "%"), color = Metrics), inherit.aes = FALSE, size = rel(6),
            vjust = 0) +
  geom_text(data = ann_acc2 %>% filter(Metrics %in% c("Accuracy")), aes(x = models, y = y, label = paste0("Accuracy = ", label, "%"), color = Metrics), inherit.aes = FALSE, size = rel(6),
            vjust = 0) +
  ylab("Sensitivity (%)") +
  scale_fill_manual(name = "", values = c("#0072B2", "#BDBDBD", "#5F9AFB", "#CC79A7")) +
  scale_color_manual(name = "", values = c(AUROC = "#FFC001", Accuracy = "#FA766E")) +
  guides(
    fill  = guide_legend(order = 1, override.aes = list(alpha = 0.6)),
    color = guide_legend(order = 2, override.aes = list(linetype = 1, shape = 16))
  ) +
  scale_x_discrete(labels=c("Onset only", "Diagnosis only", "Diagnosis + Day 1", "Diagnosis + Day 2")) +
  scale_y_continuous(breaks = seq(85, 100, 2.5)) +
  coord_cartesian(ylim = c(85, 110)) +
  theme_classic(base_family = "Helvetica") +
  theme(axis.text = element_text(color = "black"),
        axis.text.x = element_text(vjust = 0.5, hjust = 0.5, face = "bold", size = rel(3)),
        axis.text.y = element_text(face = "bold", size = rel(3)),
        axis.line = element_line(color = "black"),
        strip.text.x = element_text(vjust = 0.5, face = "bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        legend.position = "none",
        legend.box = "horizontal",
        legend.text = element_text(size = rel(4)),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = rel(4))
        )
fig4c2 <- fig4c_temp2 %>%
  add_row_signif_compare2(xgb_row_compare_diag)
fig4c2
#ggsave("Figure4C.png", fig4c_2, width = 16, height = 12)
```

# Comparison of sensitivity with features aggregated
## Preparation for Figure 4D
```{r, Compiling the dataframe of testing set, prediction from model with symptom onset, diagnosis & onset + day 2, diagnosis + day 2, diagnosis + day 1}
testing_df <- map2_dfr(
  .x = split_list,
  .y = seq_along(split_list),
  ~ .x$test %>%
    mutate(simulation = .y) %>%
    select(simulation, age, gender, vaccination, comorbidity, outcome)
)

pred_onset_df <- imap_dfr(
  xgb_vlsymp_list,
  ~ tibble(
    simulation = .y,
    pred_onset = .x$prediction
  )
)

pred_diag_df <- imap_dfr(
  xgb_vldiag_list,
  ~ tibble(
    simulation = .y,
    pred_diag = .x$prediction
  )
)

pred_add2_df <- imap_dfr(
  xgb_add2_list,
  ~ tibble(
    simulation = .y,
    pred_add2 = .x$prediction
  )
)

pred_add3_df <- imap_dfr(
  xgb_add3_list,
  ~ tibble(
    simulation = .y,
    pred_add3 = .x$prediction
  )
)

testing_df['pred_onset'] <- pred_onset_df$pred_onset
testing_df['pred_diag'] <- pred_diag_df$pred_diag
testing_df['pred_add2'] <- pred_add2_df$pred_add2
testing_df['pred_add3'] <- pred_add3_df$pred_add3
```

```{r, Define functions for compute aggregated performance metrics}
# Define function to compute performance metrics
metrics_comp <- function(df_comp, cols) {
  cols <- as.character(cols)
  actual_chr <- trimws(as.character(df_comp$outcome))
  pred_chr   <- trimws(as.character(df_comp[[cols]]))
  keep <- !is.na(actual_chr) & !is.na(pred_chr)
  
  actual <- factor(actual_chr[keep], levels = c("Non severe", "Severe"))
  pred   <- factor(pred_chr[keep],   levels = c("Non severe", "Severe"))
  
  pred_num <- ifelse(pred == "Severe", 1, 0)
  
  cfm <- table(pred, actual, dnn = c("pred", "actual"))
  
  TP <- cfm["Severe", "Severe"]
  FP <- cfm["Severe", "Non severe"]
  TN <- cfm["Non severe", "Non severe"]
  FN <- cfm["Non severe", "Severe"]
  
  acc <- sum(TP, TN) / sum(cfm)
  sens <- TP / (TP + FN)
  spec <- TN / (TN + FP)
  prec <- TP / (TP + FP)
  f1_sc <- 2 * ((prec * sens) / (prec + sens))
    
  roc <- roc(actual, pred_num)
  auc_val <- auc(roc)
  
  list(confusion_matrix = cfm, accuracy = acc, sensitivity = sens, specificity = spec, precision = prec, f1_score = f1_sc, roc_val = roc, AUC = auc_val)
}

# Define function for parallel compute the aggregated performance metrics over 100 simulations
func_agg_met <- function(df_for_comp, criteria, criteria_fil, cols_comp) {
  num_cores <- parallel::detectCores() - 1
  cl <- makeCluster(num_cores)
  registerDoParallel(cl)
  on.exit(parallel::stopCluster(cl), add = TRUE)
  
  res <- foreach(i = 1:100, .packages = c("dplyr", "pROC", "tibble"), .export = c("metrics_comp")) %dopar% {
    df_temp <- df_for_comp[[i]]
    df_temp2 <- dplyr::filter(df_temp, .data[[criteria]] == criteria_fil)
    
    met_list <- metrics_comp(df_temp2, cols = cols_comp)
    
    list(confusion_matrix = met_list$confusion_matrix, accuracy = met_list$accuracy, sensitivity = met_list$sensitivity, specificity = met_list$specificity,
         precision = met_list$specificity, f1_score = met_list$f1_score, roc_val = met_list$roc_val, AUC = met_list$AUC)
  }
  res
}

# Define function to aggregate the computed performance metrics into a dataframe
met_sum_func <- function(perf_list) {
  temp_df <- map_dfr(seq_along(perf_list), function(i) {
    result <- perf_list[[i]]
    
    tibble(
    run = i,
    accuracy = round(result$accuracy * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$f1_score, 4),
    AUC_value = round(result$AUC * 100, 4))
  })
  
  temp_df2 <- as.data.frame(temp_df)
  return(temp_df2)
}

# Define function to compile & compute the confidence interval
met_cic_func <- function(perf_df, mod_name) {
  summary_df <- perf_df %>%
    summarise(
      across(
        .cols = c(accuracy, sensitivity, specificity, precision, F1_score, AUC_value),
        .fns = list(mean = mean, low = ~ quantile(.x, 0.025), upp = ~ quantile(.x, 0.975)),
        .names = "{.col}_{.fn}"
      )
    ) %>%
    ungroup() %>%
    mutate(models = as.character(mod_name)) %>%
    pivot_longer(
      cols = -models,
      names_to = "metrics",
      values_to = "perf"
      ) %>%
    mutate(
      Metrics = case_when(
        str_starts(metrics, "accuracy_") ~ "Accuracy",
        str_starts(metrics, "sensitivity") ~ "Sensitivity",
        str_starts(metrics, "specificity") ~ "Specificity",
        str_starts(metrics, "precision") ~ "Precision",
        str_starts(metrics, "F1_score") ~ "F1_score",
        str_starts(metrics, "AUC_value") ~ "AUROC_value"
        ),
      bound = case_when(
        str_ends(metrics, "_low") ~ "lower",
        str_ends(metrics, "_upp") ~ "upper",
        TRUE ~ "estimate"
        )
      ) %>%
    select(c("models", "Metrics", "bound", "perf")) %>%
    pivot_wider(names_from = bound, values_from = perf)
  return(summary_df)
}
```

```{r, Compute sensitivity according the specific features filtering}
# Splitting the dataframe into list
testing_df_list <- list()
for(i in 1:100) {
  testing_df_list[[i]] <- testing_df %>% filter(simulation == i)
}

# Compute the performance metrics of model with viral load since symptom onset which aggregate with different scenario
perf_com3_onset <- func_agg_met(testing_df_list, criteria = "comorbidity", criteria_fil = ">=3", cols_comp = "pred_onset")
perf_com12_onset <- func_agg_met(testing_df_list, criteria = "comorbidity", criteria_fil = "1-2", cols_comp = "pred_onset")
perf_age60_onset <- func_agg_met(testing_df_list, criteria = "age", criteria_fil = "60-79", cols_comp = "pred_onset")
perf_age80_onset <- func_agg_met(testing_df_list, criteria = "age", criteria_fil = ">=80", cols_comp = "pred_onset")
perf_vacfull_onset <- func_agg_met(testing_df_list, criteria = "vaccination", criteria_fil = "Full", cols_comp = "pred_onset")
perf_vacboost_onset <- func_agg_met(testing_df_list, criteria = "vaccination", criteria_fil = "Booster", cols_comp = "pred_onset")

# Compute the performance metrics of model with viral load at diagnosis which aggregate with different scenario
perf_com3_diag <- func_agg_met(testing_df_list, criteria = "comorbidity", criteria_fil = ">=3", cols_comp = "pred_diag")
perf_com12_diag <- func_agg_met(testing_df_list, criteria = "comorbidity", criteria_fil = "1-2", cols_comp = "pred_diag")
perf_age60_diag <- func_agg_met(testing_df_list, criteria = "age", criteria_fil = "60-79", cols_comp = "pred_diag")
perf_age80_diag <- func_agg_met(testing_df_list, criteria = "age", criteria_fil = ">=80", cols_comp = "pred_diag")
perf_vacfull_diag <- func_agg_met(testing_df_list, criteria = "vaccination", criteria_fil = "Full", cols_comp = "pred_diag")
perf_vacboost_diag <- func_agg_met(testing_df_list, criteria = "vaccination", criteria_fil = "Booster", cols_comp = "pred_diag")

# Compute the performance metrics of model with viral load at diagnosis and viral load at day 2 after diagnosis which aggregate with different scenario
perf_com3_add2 <- func_agg_met(testing_df_list, criteria = "comorbidity", criteria_fil = ">=3", cols_comp = "pred_add2")
perf_com12_add2 <- func_agg_met(testing_df_list, criteria = "comorbidity", criteria_fil = "1-2", cols_comp = "pred_add2")
perf_age60_add2 <- func_agg_met(testing_df_list, criteria = "age", criteria_fil = "60-79", cols_comp = "pred_add2")
perf_age80_add2 <- func_agg_met(testing_df_list, criteria = "age", criteria_fil = ">=80", cols_comp = "pred_add2")
perf_vacfull_add2 <- func_agg_met(testing_df_list, criteria = "vaccination", criteria_fil = "Full", cols_comp = "pred_add2")
perf_vacboost_add2 <- func_agg_met(testing_df_list, criteria = "vaccination", criteria_fil = "Booster", cols_comp = "pred_add2")

# Compute the performance metrics of model with viral load at diagnosis and viral load at day 1 after diagnosis which aggregate with different scenario
perf_com3_add3 <- func_agg_met(testing_df_list, criteria = "comorbidity", criteria_fil = ">=3", cols_comp = "pred_add3")
perf_com12_add3 <- func_agg_met(testing_df_list, criteria = "comorbidity", criteria_fil = "1-2", cols_comp = "pred_add3")
perf_age60_add3 <- func_agg_met(testing_df_list, criteria = "age", criteria_fil = "60-79", cols_comp = "pred_add3")
perf_age80_add3 <- func_agg_met(testing_df_list, criteria = "age", criteria_fil = ">=80", cols_comp = "pred_add3")
perf_vacfull_add3 <- func_agg_met(testing_df_list, criteria = "vaccination", criteria_fil = "Full", cols_comp = "pred_add3")
perf_vacboost_add3 <- func_agg_met(testing_df_list, criteria = "vaccination", criteria_fil = "Booster", cols_comp = "pred_add3")

com3_onset_df <- met_sum_func(perf_com3_onset)
com3_onset_sum <- met_cic_func(com3_onset_df, mod_name = "onset_com3")

com12_onset_df <- met_sum_func(perf_com12_onset)
com12_onset_sum <- met_cic_func(com12_onset_df, mod_name = "onset_com12")

age80_onset_df <- met_sum_func(perf_age80_onset)
age80_onset_sum <- met_cic_func(age80_onset_df, mod_name = "onset_age80")

age60_onset_df <- met_sum_func(perf_age60_onset)
age60_onset_sum <- met_cic_func(age60_onset_df, mod_name = "onset_age60")

vacfull_onset_df <- met_sum_func(perf_vacfull_onset)
vacfull_onset_sum <- met_cic_func(vacfull_onset_df, mod_name = "onset_vacfull")

vacboost_onset_df <- met_sum_func(perf_vacboost_onset)
vacboost_onset_sum <- met_cic_func(vacboost_onset_df, mod_name = "onset_vacboost")

com3_diag_df <- met_sum_func(perf_com3_diag)
com3_diag_sum <- met_cic_func(com3_diag_df, mod_name = "diag_com3")

com12_diag_df <- met_sum_func(perf_com12_diag)
com12_diag_sum <- met_cic_func(com12_diag_df, mod_name = "diag_com12")

age80_diag_df <- met_sum_func(perf_age80_diag)
age80_diag_sum <- met_cic_func(age80_diag_df, mod_name = "diag_age80")

age60_diag_df <- met_sum_func(perf_age60_diag)
age60_diag_sum <- met_cic_func(age60_diag_df, mod_name = "diag_age60")

vacfull_diag_df <- met_sum_func(perf_vacfull_diag)
vacfull_diag_sum <- met_cic_func(vacfull_diag_df, mod_name = "diag_vacfull")

vacboost_diag_df <- met_sum_func(perf_vacboost_diag)
vacboost_diag_sum <- met_cic_func(vacboost_diag_df, mod_name = "diag_vacboost")

com3_add2_df <- met_sum_func(perf_com3_add2)
com3_add2_sum <- met_cic_func(com3_add2_df, mod_name = "add2_com3")

com12_add2_df <- met_sum_func(perf_com12_add2)
com12_add2_sum <- met_cic_func(com12_add2_df, mod_name = "add2_com12")

age80_add2_df <- met_sum_func(perf_age80_add2)
age80_add2_sum <- met_cic_func(age80_add2_df, mod_name = "add2_age80")

age60_add2_df <- met_sum_func(perf_age60_add2)
age60_add2_sum <- met_cic_func(age60_add2_df, mod_name = "add2_age60")

vacfull_add2_df <- met_sum_func(perf_vacfull_add2)
vacfull_add2_sum <- met_cic_func(vacfull_add2_df, mod_name = "add2_vacfull")

vacboost_add2_df <- met_sum_func(perf_vacboost_add2)
vacboost_add2_sum <- met_cic_func(vacboost_add2_df, mod_name = "add2_vacboost")

com3_add3_df <- met_sum_func(perf_com3_add3)
com3_add3_sum <- met_cic_func(com3_add3_df, mod_name = "add3_com3")

com12_add3_df <- met_sum_func(perf_com12_add3)
com12_add3_sum <- met_cic_func(com12_add3_df, mod_name = "add3_com12")

age80_add3_df <- met_sum_func(perf_age80_add3)
age80_add3_sum <- met_cic_func(age80_add3_df, mod_name = "add3_age80")

age60_add3_df <- met_sum_func(perf_age60_add3)
age60_add3_sum <- met_cic_func(age60_add3_df, mod_name = "add3_age60")

vacfull_add3_df <- met_sum_func(perf_vacfull_add3)
vacfull_add3_sum <- met_cic_func(vacfull_add3_df, mod_name = "add3_vacfull")

vacboost_add3_df <- met_sum_func(perf_vacboost_add3)
vacboost_add3_sum <- met_cic_func(vacboost_add3_df, mod_name = "add3_vacboost")

com3_df <- dplyr::bind_rows(com3_onset_sum, com3_diag_sum, com3_add2_sum, com3_add3_sum)
com12_df <- dplyr::bind_rows(com12_onset_sum, com12_diag_sum, com12_add2_sum, com12_add3_sum)
age80_df <- dplyr::bind_rows(age80_onset_sum, age80_diag_sum, age80_add2_sum, age80_add3_sum)
age60_df <- dplyr::bind_rows(age60_onset_sum, age60_diag_sum, age60_add2_sum, age60_add3_sum)
vacfull_df <- dplyr::bind_rows(vacfull_onset_sum, vacfull_diag_sum, vacfull_add2_sum, vacfull_add3_sum)
vacboost_df <- dplyr::bind_rows(vacboost_onset_sum, vacboost_diag_sum, vacboost_add2_sum, vacboost_add3_sum)

agg_df <- dplyr::bind_rows(com3_df, com12_df, age80_df, age60_df, vacfull_df, vacboost_df) %>%
  mutate(scenario = case_when(
    str_ends(models, "_com3") ~ "Comorbidity >= 3",
    str_ends(models, "_com12") ~ "Comorbidity 1-2",
    str_ends(models, "_age80") ~ "Age >= 80",
    str_ends(models, "_age60") ~ "Age 60-79",
    str_ends(models, "_vacfull") ~ "Vaccination 2 dose",
    str_ends(models, "_vacboost") ~ "Vaccination 3 dose"
  ),
  scenario = factor(scenario, levels = c("Comorbidity 1-2", "Comorbidity >= 3", "Age 60-79", "Age >= 80", "Vaccination 2 dose", "Vaccination 3 dose")),
  model_sce = case_when(
    str_starts(models, "onset_") ~ "Onset",
    str_starts(models, "diag_") ~ "Diagnosis",
    str_starts(models, "add2_") ~ "Diagnosis + day 2 post diagnosis",
    str_starts(models, "add3_") ~ "Diagnosis + day 1 post diagnosis"
  ),
  model_sce = factor(model_sce, levels = c("Onset", "Diagnosis", "Diagnosis + day 1 post diagnosis", "Diagnosis + day 2 post diagnosis")))
```

```{r}
sens_onset <- as.numeric(model_perf_comp %>% filter(models == "Onset only" & Metrics == "Sensitivity") %>% select(estimate))
sens_diag <- as.numeric(model_perf_comp %>% filter(models == "Diagnosis only" & Metrics == "Sensitivity") %>% select(estimate))
sens_add2 <- as.numeric(model_perf_comp %>% filter(models == "Diagnosis + Day 2 post diagnosis" & Metrics == "Sensitivity") %>% select(estimate))
sens_add3 <- as.numeric(model_perf_comp2 %>% filter(models == "Diagnosis + Day 1 post diagnosis" & Metrics == "Sensitivity") %>% select(estimate))

agg_df2 <- agg_df %>%
  mutate(sens_diff = case_when(
    model_sce == "Onset" & Metrics == "Sensitivity" ~ round((estimate - sens_onset), 4),
    model_sce == "Diagnosis" & Metrics == "Sensitivity" ~ round((estimate - sens_diag), 4),
    model_sce == "Diagnosis + day 1 post diagnosis" & Metrics == "Sensitivity" ~ round((estimate - sens_add3), 4),
    model_sce == "Diagnosis + day 2 post diagnosis" & Metrics == "Sensitivity" ~ round((estimate - sens_add2), 4)
  ))
```

## Figure 4D
```{r, Figure 4D}
fig4d_diag <- ggplot(data = agg_df2 %>% filter(Metrics == "Sensitivity") %>%
                    mutate(model_sce = case_when(model_sce == "Diagnosis + day 2 post diagnosis" ~ "Diagnosis + day 2",
                                                 model_sce == "Diagnosis + day 1 post diagnosis" ~ "Diagnosis + day 1",
                                                 TRUE ~ model_sce),
                           model_sce = factor(model_sce, levels = c("Onset", "Diagnosis", "Diagnosis + day 1", "Diagnosis + day 2"))),
                  aes(x = factor(scenario), y = estimate, fill = model_sce)) +
  geom_bar(position = position_dodge(0.8), stat = "identity", width = 0.8) +
  geom_errorbar(aes(ymin = lower, ymax = upper), linewidth = 1.2, width = 0.3, color = "black", position = position_dodge(0.8)) +
  #geom_text(aes(x = scenario, y = upper + 0.5, label = paste0("Diff \n", round(sens_diff, 2), "%"), color = model_sce), size = rel(4), vjust = 0, position = position_dodge(width = 0.8)) +
  scale_y_continuous(breaks = seq(65, 100, 5)) +
  scale_x_discrete(labels = function(x) {
    x <- gsub(">=", "≥", x)                    
    x <- sub("\\s+(?=(?:≥|\\d))", "\n", x, perl = TRUE)
    x
  }) +
  coord_cartesian(ylim = c(65, 102)) +
  scale_fill_manual(name = "", values = c("Onset" = "#0072B2", "Diagnosis" = "#BDBDBD", "Diagnosis + day 1" = "#5F9AFB", "Diagnosis + day 2" = "#CC79A7")) +
  scale_color_manual(name = "", values = c("Onset" = "#0072B2", "Diagnosis" = "#BDBDBD", "Diagnosis + day 1" = "#5F9AFB", "Diagnosis + day 2" = "#CC79A7")) +
  ylab("Sensitivity (%)") +
  labs(fill = "Scenario") +
  theme_classic(base_family = "Helvetica") +
  theme(axis.text = element_text(color = "black"),
        axis.text.x = element_text(vjust = 0.5, hjust = 0.5, face = "bold", size = rel(3)),
        axis.text.y = element_text(face = "bold", size = rel(3)),
        axis.line = element_line(color = "black"),
        strip.text.x = element_text(vjust = 0.5, face = "bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        legend.position = "top",
        legend.box = "horizontal",
        legend.text = element_text(size = rel(4)),
        #legend.title = element_text(size = rel(2)),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = rel(4))
        )
fig4d_diag
```

```{r, Saving all Figures}
figure4 <- ggarrange(fig4a, fig4b_diag, fig4c, fig4d_diag, nrow = 2, ncol = 2, widths = c(1, 1), height = c(1, 1))
figure4
```

# Saving all data in this session
```{r, Saving RData file}
save.image(file = paste0(getwd(), '/seq_model.RData'))
```

# Session Info
```{r, Session Information}
sessionInfo()
```