---
title: "Figure2_and_data_preparation"
output: html_document
---

# Import libraries & environment setup
```{r, Import libraries}
library(foreach)
library(doParallel)
library(ggplot2)
library(dplyr)
library(stringr)
library(tidyr)
library(smotefamily)
library(deSolve)
library(purrr)
library(dgof)
library(ggpubr)
library(gtsummary)
library(webshot2)
library(broom)
library(ggsignif)
library(ggcorrplot)
library(caret)
```

```{r, Import dataset}
df <- read.csv("~/cluster_uniqID_symptom.csv")
df2 <- read.csv("~/cluster_longVL_symptom.csv")
head(df)
```

```{r, Check the structure of the data}
dim(df)
```

```{r, Check the type of each columns}
sapply(df, typeof)
```

```{r, Check the columns available in dataframe}
names(df)
```

# Exploratory Data Analysis
## Visualise observed viral load trajectories
```{r, Figure 2a1}
f2a1 <- ggplot() +
        ggtitle("Severe") +
        geom_point(data = df2 %>% filter(VL <= log10(10^1.31) & outcome == "Severe"), aes(x = Day_since_symptom, y = VL), color = "grey", alpha = 2, size = 4) +
        geom_point(data = df2 %>% filter(VL > log10(10^1.31) & outcome == "Severe"), aes(x = Day_since_symptom, y = VL), color = "#E97132", alpha = 2, size = 4) +
        xlab("Time since symptom onset (days)") +
        ylab("Viral RNA load (log10 copies/mL)") +
        scale_y_continuous(breaks = seq(0, 10, by = 2), limits = c(0, 10)) +
        scale_x_continuous(breaks = seq(-20, 40, by = 10), limits = c(-20, 40)) +
        theme(plot.title = element_text(colour = "#E97132", size = rel(5)),
                axis.text = element_text(color = "black"),
                axis.ticks = element_line(color = "black"),
                axis.line = element_line(color = "black"),
                panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(),
                panel.background = element_blank(),
                legend.position = "none",
                axis.text.x = element_text(size = rel(5)),
                axis.text.y = element_text(size = rel(5)),
                axis.title.x = element_text(size = rel(4)),
                axis.title.y = element_text(size = rel(4)))
f2a1
```

```{r, Figure 2a2}
f2a2 <- ggplot() +
        ggtitle("Non-severe") +
        geom_point(data = df2 %>% filter(VL <= log10(10^1.31) & outcome == "Non severe"), aes(x = Day_since_symptom, y = VL), color = "grey", alpha = 2, size = 4) +
        geom_point(data = df2 %>% filter(VL > log10(10^1.31) & outcome == "Non severe"), aes(x = Day_since_symptom, y = VL), color = "#196B24", alpha = 2, size = 4) +
        xlab("Time since symptom onset (days)") +
        ylab("Viral RNA load (log10 copies/mL)") +
        scale_y_continuous(breaks = seq(0, 10, by = 2), limits = c(0, 10)) +
        scale_x_continuous(breaks = seq(-20, 40, by = 10), limits = c(-20, 40)) +
        theme(plot.title = element_text(colour = "#196B24", size = rel(5)),
                axis.text = element_text(color = "black"),
                axis.ticks = element_line(color = "black"),
                axis.line = element_line(color = "black"),
                panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(),
                panel.background = element_blank(),
                legend.position = "none",
                axis.text.x = element_text(family="Helvetica", size = rel(5)),
                axis.text.y = element_text(family="Helvetica", size = rel(5)),
                axis.title.x = element_text(family="Helvetica", size = rel(4)),
                axis.title.y = element_text(family="Helvetica", size = rel(4)))
f2a2
```

```{r, Figure 2a; Save Image}
f2a <- ggarrange(f2a1, f2a2, nrow = 1, ncol = 2, align = "hv", widths = c(1, 1))
f2a
#ggsave("Figure2A.png", f2a, width = 16*2, height = 12)
```

## Summarised the dataset in table
```{r, Select variables from raw data}
df_tab <- df %>%
  select(c("age_cat", "sex", "vaccination", "comorbidity", "log10beta_mode", "log10pi_mode", "log10rho_mode", "log10phi_mode", "delta_mode", "tau_mode", "outcome")) %>%
  rename("age" = "age_cat", "gender" = "sex")
head(df_tab)
```

```{r}
cols <- c("age", "gender", "vaccination", "comorbidity", "outcome")
# Transform the categorical variables into factor
for (i in cols){
  df_tab[[i]] <- as.factor(df_tab[[i]])}
sapply(df_tab, typeof)
```

```{r}
summary(df_tab)
```

```{r, Setting the referene level for the categorical variables}
df_tab$age <- relevel(df_tab$age, ref = "18-59")
df_tab$gender <- relevel(df_tab$gender, ref = "Male")
df_tab$vaccination <- relevel(df_tab$vaccination, ref = "Notfull")
df_tab$comorbidity <- relevel(df_tab$comorbidity, ref = "0")
df_tab$outcome <- relevel(df_tab$outcome, ref = "Non severe")
```

```{r, Tabulate data summary}
table0 <- tbl_summary(df_tab, include = c(age, gender, vaccination, comorbidity, log10beta_mode, log10pi_mode, log10rho_mode, log10phi_mode, delta_mode, tau_mode),
                        by = outcome, label = list(
                            age = "Age",
                            gender = "Gender",
                            vaccination = "Vaccination",
                            comorbidity = "Number of Comorbidity",
                            log10beta_mode = "Beta",
                            log10pi_mode = "Pi",
                            log10rho_mode = "Rho",
                            log10phi_mode = "Phi",
                            delta_mode = "Delta",
                            tau_mode = "Tau"
                        ),
                        missing = "no") %>%
                        modify_header(label = "**Variable**") %>%
                        bold_labels()
tbl <- as_gt(table0)
#Sys.setenv(CHROMOTE_CHROME = "C:/Program Files (x86)/Microsoft/Edge/Application/msedge.exe")
#gtsave(tbl, filename = "Summary_before_smote.pdf")
```

## SMOTE (For handling imbalance data)
```{r, Prepare dataframe for SMOTE}
df_for_smote5 <- df_tab %>% 
mutate(
    age = case_when(
        age == "18-59" ~ 1,
        age == "60-79" ~ 2,
        age == ">=80" ~ 3),
    gender = case_when(
        gender == "Male" ~ 1,
        gender == "Female"~ 0),
    vaccination = case_when(
        vaccination == "Notfull" ~ 1,
        vaccination == "Full" ~ 2,
        vaccination == "Booster" ~ 3),
    comorbidity = case_when(
        comorbidity == "0" ~ 1,
        comorbidity == "1-2" ~ 2,
        comorbidity == ">=3" ~ 3),
    outcome = case_when(
        outcome == "Non severe" ~ 0,
        outcome == "Severe" ~ 1)
    )
set.seed(123)
smote_res2 <- SMOTE(X = df_for_smote5[, -11], target = df_for_smote5$outcome, K = 2, dup_size = 33)
```

```{r, Perform SMOTE on dataset}
df_smote5 <- data.frame(smote_res2$data)
df_smote5 <- df_smote5 %>% 
mutate(
    age = case_when(
        age <= 1 ~ "18-59",
        age > 1 & age <= 2 ~ "60-79",
        age > 2 ~ ">=80"),
    gender = case_when(
        gender >= 0.5 ~ "Male",
        gender < 0.5 ~ "Female"),
    vaccination = case_when(
        vaccination <= 1 ~ "Notfull",
        vaccination > 1 & vaccination <= 2 ~ "Full",
        vaccination > 2 ~ "Booster"),
    comorbidity = case_when(
        comorbidity <= 1 ~ "0",
        comorbidity > 1 & comorbidity <= 2 ~ "1-2",
        comorbidity > 2 ~ ">=3"),
    class = case_when(
        class == 1 ~ "Severe",
        class == 0 ~ "Non severe")
    ) %>%
    rename("outcome" = "class")
col_cat <- c("age", "gender", "vaccination", "comorbidity", "outcome")
for (i in col_cat){
  df_smote5[[i]] <- as.factor(df_smote5[[i]])}
summary(df_smote5)
```

```{r, Setting the reference level for the categorical variables}
df_smote5$age <- relevel(df_smote5$age, ref = "18-59")
df_smote5$gender <- relevel(df_smote5$gender, ref = "Male")
df_smote5$vaccination <- relevel(df_smote5$vaccination, ref = "Notfull")
df_smote5$comorbidity <- relevel(df_smote5$comorbidity, ref = "0")
df_smote5$outcome <- relevel(df_smote5$outcome, ref = "Non severe")
```

```{r, Tabulate the summary of balanced data}
table1 <- tbl_summary(df_smote5, include = c(age, gender, vaccination, comorbidity, log10beta_mode, log10pi_mode, log10rho_mode, log10phi_mode, delta_mode, tau_mode),
                        by = outcome, label = list(
                            age = "Age",
                            gender = "Gender",
                            vaccination = "Vaccination",
                            comorbidity = "Number of Comorbidity",
                            log10beta_mode = "Beta",
                            log10pi_mode = "Pi",
                            log10rho_mode = "Rho",
                            log10phi_mode = "Phi",
                            delta_mode = "Delta",
                            tau_mode = "Tau"
                        ),
                        missing = "no") %>%
                        modify_header(label = "**Variable**") %>%
                        bold_labels()
tbl1 <- as_gt(table1)
#Sys.setenv(CHROMOTE_CHROME = "C:/Program Files (x86)/Microsoft/Edge/Application/msedge.exe")
#gtsave(tbl1, filename = "Summary_after_smote.pdf")
```

## Simulate the viral load trajectories based on the Ordinary Differential Equation from the individual parameters
```{r, TREIV model}
ode_TREIV <- function(pars){
  
  beta <- as.numeric(pars[1])
  pi <- as.numeric(pars[2])
  rho <- as.numeric(pars[3])
  phi <- as.numeric(pars[4])
  delta <- as.numeric(pars[5])
  tau <- as.numeric(pars[6])
  
  derivs <- function(time, y, pars){
    with(as.list(c(pars, y)), {
      
      dT <- -beta * T * V - phi * I * T + rho * R
      dR <- phi * I * T - rho * R
      dE <- beta * T * V - 4 * E
      dI <- 4 * E - delta * I
      dV <- pi * I - 15 * V
        
      return(list(c(dT, dR, dE, dI, dV)))
    })
  }
  y <- c(T = 10^7, R = 0, E = 1, I = 0, V = 1)
  
  times <- round(seq(-tau, -tau + Time, step_size), -log10(step_size))
  out <- lsoda(y = y, parms = pars, times = times, func = derivs, rtol = tol, atol = tol)
  out2 <- cbind(Day_since_symp = out[, 1], VL_sim = log10(pmax(out[, 6], tol)))
  as.data.frame(out2)
}

#individual fit for TREIV model
ind_fit_plt <- function(Est){
  
  Fit <- list()
  for(i in 1:nrow(Est)){
    pars <- c(beta = 10 ^ (Est$log10beta_mode[i]),
              pi = 10 ^ (Est$log10pi_mode[i]),
              rho = 10 ^ (Est$log10rho_mode[i]),
              phi = 10 ^ (Est$log10phi_mode[i]),
              delta = Est$delta_mode[i],
              tau = Est$tau_mode[i])
    fitted <- ode_TREIV(pars)

    hosp_id <- Est$hosp_id[i]
    Fit[[i]] <- data.frame(hosp_id, fitted)
  }
  
  ind_fit <- map_df(Fit, ~ as.data.frame(.x))
  
  return(ind_fit)
}
```

```{r, Setup CPU clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Simulate the individual viral load trajectory}
#setting
Time <- 60
step_size <- 0.1
tol <- 10^-10

#setting the dummy id for each individual
hosp_id_dum <- seq_len(nrow(df_smote5))
df_sim <- df_smote5
df_sim['hosp_id'] <- hosp_id_dum

est_VL_list <- foreach(i = 1:nrow(df_sim), .packages = c("purrr", "deSolve", "ggpubr", "dplyr")) %dopar% {
    pars <- c(beta = 10 ^ (df_sim$log10beta_mode[i]),
              pi = 10 ^ (df_sim$log10pi_mode[i]),
              rho = 10 ^ (df_sim$log10rho_mode[i]),
              phi = 10 ^ (df_sim$log10phi_mode[i]),
              delta = df_sim$delta_mode[i],
              tau = df_sim$tau_mode[i])
    fitted <- ode_TREIV(pars)
    hospid <- i

    list(hosp_id = hospid, Day_since_symp = fitted$Day_since_symp, VL_sim = fitted$VL_sim)
}

est_VL_df <- map_dfr(seq_along(est_VL_list), function(i) {
    est <- est_VL_list[[i]]

    tibble(
        hosp_id = est$hosp_id,
        Day_since_symp = est$Day_since_symp,
        VL_sim = est$VL_sim
    )
})

est_VL_full <- as.data.frame(est_VL_df)
est_VL_full_pivot <- est_VL_full %>%
                        filter(Day_since_symp >= 0 & Day_since_symp <= 20) %>%
                        pivot_wider(id_cols = hosp_id, names_from = Day_since_symp, values_from = VL_sim)
day_list <- as.character(seq(0.1, 20, by = 0.1))

df_adj <- df_sim %>%
  left_join(est_VL_full_pivot, by = "hosp_id") %>%
  select(-c(log10beta_mode, log10pi_mode, log10rho_mode, log10phi_mode, delta_mode, tau_mode))

head(df_adj)
```

```{r, Stop clusters}
stopCluster(cl)
```

## Rerun the EDA
```{r, Figure 2b}
mean_vl_severe <- c()
mean_vl_nonsevere <- c()
minvl_severe <- c()
maxvl_severe <- c()
minvl_nonsevere <- c()
maxvl_nonsevere <- c()
for (i in 1:length(day_list)) {
    x <- day_list[i]
    mean_vl_severe[i] <- mean(df_adj %>%
                                filter(outcome == "Severe") %>%
                                pull(!!sym(x)))
    
    mean_vl_nonsevere[i] <- mean(df_adj %>%
                                filter(outcome == "Non severe") %>%
                                pull(!!sym(x)))
    
    minvl_severe[i] <- apply(df_adj %>% filter(outcome == "Severe") %>% select(x), 2, function(x){quantile(x, 0.025)})
    minvl_nonsevere[i] <- apply(df_adj %>% filter(outcome == "Non severe") %>% select(x), 2, function(x){quantile(x, 0.025)})
    maxvl_severe[i] <- apply(df_adj %>% filter(outcome == "Severe") %>% select(x), 2, function(x){quantile(x, 0.975)})
    maxvl_nonsevere[i] <- apply(df_adj %>% filter(outcome == "Non severe") %>% select(x), 2, function(x){quantile(x, 0.975)})
}

df_vl_viz <- data.frame(
    "Day_since_symptom" = seq(0.1, 20, by = 0.1),
    "vl_severe" = mean_vl_severe,
    "vl_nonsevere" = mean_vl_nonsevere,
    "minvl_severe" = minvl_severe,
    "minvl_nonsevere" = minvl_nonsevere,
    "maxvl_severe" = maxvl_severe,
    "maxvl_nonsevere" = maxvl_nonsevere
)

df_vl_viz2 <- df_vl_viz %>%
                mutate(
                    minvl_severe = if_else(minvl_severe < 0, 0, minvl_severe),
                    maxvl_severe = if_else(maxvl_severe < 0, 0, maxvl_severe),
                    minvl_nonsevere = if_else(minvl_nonsevere < 0, 0, minvl_nonsevere),
                    maxvl_nonsevere = if_else(maxvl_nonsevere < 0, 0, maxvl_nonsevere)
                )

fig2b <- ggplot(data = df_vl_viz, aes(x = Day_since_symptom)) +
    geom_ribbon(data = df_vl_viz2, aes(ymin = minvl_severe, ymax = maxvl_severe, fill = factor("Severe")), alpha = 0.2) +
    geom_ribbon(data = df_vl_viz2, aes(ymin = minvl_nonsevere, ymax = maxvl_nonsevere, fill = ("Non severe")), alpha = 0.2) +
    geom_line(aes(y = vl_severe, color = factor("Severe")), linewidth = 3) +
    geom_line(aes(y = vl_nonsevere, color = factor("Non severe")), linewidth = 3) +
    geom_hline(aes(yintercept = log10(10^1.31)), color = "dark grey", linewidth = 3) +
    xlab("Time since symptom onset (days)") +
    ylab("Viral RNA load (log10 copies/mL)") +
    scale_colour_manual(name = "Outcome", values = c("Severe" = "#E97132", "Non severe" = "#196B24")) +
    scale_fill_manual(name = "Outcome", values = c("Severe" = "#E97132", "Non severe" = "#196B24")) +
    scale_x_continuous(breaks = seq(0, 20, by = 5),limits = c(0, 20)) +
    scale_y_continuous(breaks = seq(0, 10, by = 2), limits = c(0, 10)) +
    theme(axis.text = element_text(color = "black"),
            axis.ticks = element_line(color = "black"),
            axis.line = element_line(color = "black"),
            legend.position = "none",
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(),
            axis.text.x = element_text(family = "Helvetica", size = rel(5)),
            axis.text.y = element_text(family = "Helvetica", size = rel(5)),
            axis.title.x = element_text(family = "Helvetica", size = rel(4)),
            axis.title.y = element_text(family = "Helvetica", size = rel(4)))
fig2b
#ggsave("Figure2B.png", plot = fig2b, width = 16, height = 12)
```

```{r, Aggregate data}
df_vl_viz_longi <- df_adj %>%
                pivot_longer(
                    cols = c(day_list),
                    names_to = "Day_since_symp",
                    values_to = "VL_sim"
                ) %>%
                select(c(hosp_id, Day_since_symp, VL_sim, outcome))

df_vl_max <- df_vl_viz_longi %>%
                        group_by(hosp_id) %>%
                        summarise(max_VL_sim = max(VL_sim, na.rm = TRUE)) %>%
                        ungroup()

df_VL_max <- df_vl_viz_longi %>%
                left_join(df_vl_max, by = "hosp_id") %>%
                select(hosp_id, max_VL_sim, outcome) %>%
                group_by(hosp_id) %>%
                slice_head(n = 1) %>%
                ungroup() %>%
                mutate(
                  outcome = factor(outcome, levels = c("Severe", "Non severe"))
                  )

df_vl_detlim <- df_vl_viz_longi %>%
                    group_by(hosp_id) %>%
                    filter(VL_sim <= log10(10^1.31)) %>%
                    slice_head(n = 1) %>%
                    ungroup() %>%
                    mutate(
                      outcome = factor(outcome, levels = c("Severe", "Non severe"))
                    )
```

### Normality test
```{r, Normality test with Komolgorov-Smirnov}
ks_summary <- list()

# Peak viral load
ks_peak <- tidy(ks.test(df_VL_max$max_VL_sim, y = "pnorm"))
ks_summary[['Peak viral load (log10 copies/mL)']] <- ks_peak %>% mutate(variable = 'Peak viral load (log10 copies/mL)')
ks_sum_df <- bind_rows(ks_summary)

df_vl_detlim$Day_since_symp <- as.numeric(df_vl_detlim$Day_since_symp)
ks_det <- tidy(ks.test(df_vl_detlim$Day_since_symp, y = "pnorm"))
ks_summary[['Detection duration (days)']] <- ks_det %>% mutate(variable = 'Detection duration (days)')
ks_sum_df <- bind_rows(ks_summary)

ks_sum_df
```

```{r, Normality test with Shapiro Wilk}
sw_summary <- list()

# Peak viral load
sw_peak <- tidy(shapiro.test(df_VL_max$max_VL_sim))
sw_summary[['Peak viral load (log10 copies/mL)']] <- sw_peak %>% mutate(variable = 'Peak viral load (log10 copies/mL)')
sw_sum_df <- bind_rows(sw_summary)

df_vl_detlim$Day_since_symp <- as.numeric(df_vl_detlim$Day_since_symp)
sw_det <- tidy(shapiro.test(df_vl_detlim$Day_since_symp))
sw_summary[['Detection duration (days)']] <- sw_det %>% mutate(variable = 'Detection duration (days)')
sw_sum_df <- bind_rows(sw_summary)

sw_sum_df
```

```{r, QQ plot}
print(ggqqplot(df_VL_max$max_VL_sim, color = "steel blue") + labs(title = paste0("QQ plot for Peak viral load (log10 copies/mL)")))
print(ggqqplot(df_vl_detlim$Day_since_symp, color = "steel blue") + labs(title = paste0("QQ plot for Detection duration (days)")))
```

```{r, Wilcoxon test}
fig2c1 <- ggplot(df_VL_max, aes(y = max_VL_sim, x = outcome, fill = outcome)) +
            geom_boxplot(size = 1.5, outlier.size = 4, outlier.colour = "black") +
            stat_summary(fun = mean, colour = "black", geom = "point", shape = 4, size = 8, stroke = 2, show.legend = FALSE) +
            labs(y = "Peak viral load (log10 copies/mL)") +
            scale_y_continuous(breaks = seq(-3, 12, 3), limits = c(-3, 12)) +
            scale_x_discrete(labels = c("Severe", "Non-severe")) +
            geom_signif(comparisons = list(c("Severe", "Non severe")),
                        map_signif_level = TRUE,
                        size = 1.5,
                        textsize = 20,
                        test = "wilcox.test") +
            scale_fill_manual(name = "Outcome", values = c("Severe" = "#E97132", "Non severe" = "#196B24")) +
            theme(legend.position = 'None',
            axis.text = element_text(colour = "black"),
            axis.line = element_line(colour = "black"),
            axis.text.y = element_text(family = "Helvetica", size = rel(5)),
            axis.text.x = element_text(family = "Helvetica", size = rel(5)),
            axis.title.y = element_text(family = "Helvetica", size = rel(4)),
            axis.title.x = element_blank(),
            panel.grid = element_blank(),
            panel.background = element_blank())
#fig2c1

fig2c2_2 <- ggplot(df_vl_detlim, aes(y = as.numeric(Day_since_symp), x = outcome, fill = outcome)) +
            geom_boxplot(size = 1.5, outlier.size = 4, outlier.colour = "black") +
            stat_summary(fun = mean, colour = "black", geom = "point", shape = 4, size = 8, stroke = 2, show.legend = FALSE) +
            scale_y_continuous(breaks = seq(0, 25, 5), limits = c(0, 25)) +
            scale_x_discrete(labels = c("Severe", "Non-severe")) +
            ylab("Duration of virus shedding (days)") +
            geom_signif(comparisons = list(c("Severe", "Non severe")),
                        map_signif_level = TRUE,
                        size = 1.5,
                        textsize = 20,
                        test = "wilcox.test") +
            scale_fill_manual(name = "Outcome", values = c("Severe" = "#E97132", "Non severe" = "#196B24")) +
            theme(legend.position = 'None',
            axis.text = element_text(colour = "black"),
            axis.line = element_line(colour = "black"),
            axis.text.y = element_text(family = "Helvetica", size = rel(5)),
            axis.text.x = element_text(family = "Helvetica", size = rel(5)),
            axis.title.y = element_text(family = "Helvetica", size = rel(4)),
            axis.title.x = element_blank(),
            panel.grid = element_blank(),
            panel.background = element_blank())
#fig2c2

fig2c_2 <- ggarrange(fig2c1, fig2c2_2, nrow = 1, ncol = 2, align = "hv", widths = c(1, 1))
fig2c_2
#ggsave("Figure2C.png", plot = fig2c, width = 16*2, height = 12)
```

```{r}
mean_severe_pvl <- df_VL_max %>%
  filter(outcome == "Severe") %>%
  summarise(mean_severe_pvl = mean(as.numeric(max_VL_sim), na.rm = TRUE)) %>%
  pull(mean_severe_pvl)

mean_nonsevere_pvl <- df_VL_max %>%
  filter(outcome == "Non severe") %>%
  summarise(mean_nonsevere_pvl = mean(as.numeric(max_VL_sim), na.rm = TRUE)) %>%
  pull(mean_nonsevere_pvl)

print(paste0("Mean of peak viral load for severe case: ", round(mean_severe_pvl, 2)))
print(paste0("Mean of peak viral load for non-severe case: ", round(mean_nonsevere_pvl, 2)))

w_pvl <- tidy(wilcox.test(max_VL_sim ~ outcome, data = df_VL_max, exact = FALSE, conf.int = TRUE))
w_pvl

mean_severe_dtdur <- df_vl_detlim %>%
  filter(outcome == "Severe") %>%
  summarise(mean_severe_dtdur = mean(as.numeric(Day_since_symp), na.rm = TRUE)) %>%
  pull(mean_severe_dtdur)

mean_nonsevere_dtdur <- df_vl_detlim %>%
  filter(outcome == "Non severe") %>%
  summarise(mean_nonsevere_dtdur = mean(as.numeric(Day_since_symp), na.rm = TRUE)) %>%
  pull(mean_nonsevere_dtdur)

print(paste0("Mean of duration of virus shedding for severe case: ", round(mean_severe_dtdur, 2)))
print(paste0("Mean of duration of virus shedding for non-severe case: ", round(mean_nonsevere_dtdur, 2)))

w_dtdur <- tidy(wilcox.test(as.numeric(Day_since_symp) ~ outcome, data = df_vl_detlim, exact = FALSE, conf.int = TRUE))
w_dtdur
```

```{r, Spearman Correlation Analysis 2}
df_corr3 <- df_adj %>%
                select(c(hosp_id, age, gender, vaccination, comorbidity, outcome))
df_corr3 <- df_corr3 %>%
                left_join(df_VL_max, by = "hosp_id") %>%
                left_join(df_vl_detlim, by = "hosp_id") %>%
                select(age, gender, vaccination, comorbidity, Day_since_symp, max_VL_sim, outcome) %>%
                rename("peak viral load" = max_VL_sim,
                        "duration of virus shedding" = Day_since_symp)

df_corr3 <- df_corr3 %>% 
                mutate(
                    age = case_when(
                        age == "18-59" ~ 1,
                        age == "60-79" ~ 2,
                        age == ">=80" ~ 3),
                    gender = case_when(
                        gender == "Male" ~ 1,
                        gender == "Female"~ 0),
                    vaccination = case_when(
                        vaccination == "Notfull" ~ 1,
                        vaccination == "Full" ~ 2,
                        vaccination == "Booster" ~ 3),
                    comorbidity = case_when(
                        comorbidity == "0" ~ 1,
                        comorbidity == "1-2" ~ 2,
                        comorbidity == ">=3" ~ 3),
                    outcome = case_when(
                        outcome == "Non severe" ~ 0,
                        outcome == "Severe" ~ 1)
                )

df_corr3['duration of virus shedding'] <- as.numeric(df_corr3$`duration of virus shedding`)

corr_res2 <- cor(df_corr3, method = "spearman", use = "pairwise.complete.obs")
fig2d <- ggcorrplot(corr_res2,
                        type = "lower",
                        legend.title = "Spearman \n Coef",
                        ggtheme = theme_classic(base_family = "Helvetica"),
                            outline = "black",
                            lab = TRUE,
                            lab_size = rel(10)) +
                            theme(panel.background = element_blank(),
                                    panel.grid = element_blank(),
                                    axis.text.x = element_text(color = "black", size = rel(4)),
                                    axis.text.y = element_text(color = "black", size = rel(4)),
                                    axis.title.x = element_blank(),
                                    axis.title.y = element_blank(),
                                    legend.text = element_text(size = 20),
                                    legend.title = element_text(size = 30),
                                    legend.key.size = unit(2.5, "cm"))
fig2d
#ggsave("Figure2D.png", fig2d, width = 16, height = 12)
```

```{r, Saving all Figures}
sfn <- "Figure2.pdf"
pdf(sfn, width = 16*3, height = 12*2)
figure2 <- ggarrange(f2a1, f2a2, fig2b, fig2c1, fig2c2, fig2d, nrow = 2, ncol = 3, widths = c(1, 1, 1), height = c(1, 1))
figure2
dev.off()
```

# Fitting dataframe into machine learning models
## Splitting the data into training and testing set
```{r, Split data}
set.seed(123)

# Initialize list to hold the day of diagnosis assigned
diag_day_list <- list()

# Initialize list to hold train/test splits
split_list <- list()

# Perform 100 random splits
for(i in 1:100) {
  # Generate random numbers from lognormal
  random_lognorm <- rlnorm(n = 100000, meanlog = 3.12, sdlog = sqrt(10.36))

  # Setting the upper limit to 6
  random_lognorm <- random_lognorm[random_lognorm >= 0.5 & random_lognorm <= 6]

  # Round value to nearest 0.5
  random_lognorm_rounded <- as.data.frame(round(random_lognorm * 2) / 2)
  random_lognorm_rounded <- random_lognorm_rounded[1:nrow(df_adj), ]

  df_copy <- df_adj

  temp_df_lognorm <- df_copy %>%
                      select("hosp_id") %>%
                      mutate(day_det = random_lognorm_rounded,
                             day_det2 = random_lognorm_rounded + 2)

  est_VL_full3 <- df_copy %>%
                    pivot_longer(
                        cols = c(all_of(day_list)),
                        names_to = "day_symp",
                        values_to = "vl_sim"
                    ) %>%
                    left_join(temp_df_lognorm, by = "hosp_id")

  fil_est2 <- est_VL_full3 %>%
                group_by("hosp_id") %>%
                filter(day_symp == day_det) %>%
                ungroup() %>%
                select(c("hosp_id", "vl_sim", "day_det"))
  
  fil_est3 <- est_VL_full3 %>%
                group_by("hosp_id") %>%
                filter(day_symp == day_det2) %>%
                ungroup() %>%
                select(c("hosp_id", "vl_sim")) %>%
                rename("vl_sim2" = "vl_sim")

  df_adj2 <- df_copy %>%
              left_join(fil_est2, by = "hosp_id") %>%
              left_join(fil_est3, by = "hosp_id")

  index <- createDataPartition(df_adj2$outcome, p = 0.7, list = FALSE)
  
  train_df <- df_adj2[index, ]
  test_df  <- df_adj2[-index, ]
  
  split_list[[i]] <- list(train = train_df, test = test_df)
  diag_day_list[[i]] <- list(hosp_id = temp_df_lognorm$hosp_id, diag_day = temp_df_lognorm$day_det, diag_day_p2 = temp_df_lognorm$day_det2)
}
```

## Fitting data without any VL information
```{r, Create training & testing set without any VL information}
fea_without_vl <- c("age", "gender", "vaccination", "comorbidity", "outcome")

split_list_fil <- list()
for (i in 1:100) {
    train_df <- split_list[[i]]$train %>% select(all_of(fea_without_vl))
    test_df <- split_list[[i]]$test %>% select(all_of(fea_without_vl))

    split_list_fil[[i]] <- list(train = train_df, test = test_df)
}
```

## Fitting data with VL since symptom onset
```{r, Create training & testing set with VL since symptom onset}
fea_vlsim_symp <- c("age", "gender", "vaccination", "comorbidity", "0", "outcome")

split_list_vlsim_symp <- list()
for (i in 1:100) {
    train_df <- split_list[[i]]$train %>% select(all_of(fea_vlsim_symp)) %>% rename("vl_sim_symp" = "0")
    test_df <- split_list[[i]]$test %>% select(all_of(fea_vlsim_symp)) %>% rename("vl_sim_symp" = "0")

    split_list_vlsim_symp[[i]] <- list(train = train_df, test = test_df)
}
```

## Fitting data with VL at diagnosis
```{r, Create training & testing set with VL at diagnosis}
fea_vldiag <- c("age", "gender", "vaccination", "comorbidity", "vl_sim", "outcome")

split_list_vldiag <- list()
for (i in 1:100) {
    train_df <- split_list[[i]]$train %>% select(all_of(fea_vldiag))
    test_df <- split_list[[i]]$test %>% select(all_of(fea_vldiag))

    split_list_vldiag[[i]] <- list(train = train_df, test = test_df)
}
```

## Getting the sequential VL after diagnosis
```{r, Setup CPU clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Creating training & testing set with sequential VL after diagnosis}
split_list_p <- foreach (i = 1:100, .packages = c("dplyr", "tidyr")) %dopar% {
  split <- split_list[[i]]
  diag_day_lis <- data.frame(diag_day_list[[i]])
  
  train_id_list <- unique(split$train$hosp_id)
  test_id_list <- unique(split$test$hosp_id)
  
  diag_day_lis <- diag_day_lis %>%
    mutate(diag_p1 = diag_day + 1,
           diag_p2 = diag_day_p2,
           diag_p3 = diag_day + 3,
           diag_p4 = diag_day + 4,
           diag_p5 = diag_day + 5,
           diag_p6 = diag_day + 6,
           diag_p7 = diag_day + 7,
           diag_p8 = diag_day + 8,
           diag_p9 = diag_day + 9,
           diag_p10 = diag_day + 10) %>%
    select(c(hosp_id, starts_with("diag_p")))
  
  pivot_long_train <- split$train %>%
    pivot_longer(
      cols = c(all_of(day_list)),
      names_to = "day_symp",
      values_to = "simulated_vl"
    )
  
  pivot_long_test <- split$test %>%
    pivot_longer(
      cols = c(all_of(day_list)),
      names_to = "day_symp",
      values_to = "simulated_vl"
    )
  
  train_dp1 <- diag_day_lis %>%
    filter(hosp_id %in% train_id_list) %>%
    left_join(pivot_long_train, by = "hosp_id") %>%
    group_by(hosp_id) %>%
    filter(day_symp == diag_p1) %>%
    ungroup() %>%
    select(c(hosp_id, simulated_vl)) %>%
    rename("vl_dp1" = "simulated_vl")
  
  train_dp2 <- diag_day_lis %>%
    filter(hosp_id %in% train_id_list) %>%
    left_join(pivot_long_train, by = "hosp_id") %>%
    group_by(hosp_id) %>%
    filter(day_symp == diag_p2) %>%
    ungroup() %>%
    select(c(hosp_id, simulated_vl)) %>%
    rename("vl_dp2" = "simulated_vl")
  
  train_dp3 <- diag_day_lis %>%
    filter(hosp_id %in% train_id_list) %>%
    left_join(pivot_long_train, by = "hosp_id") %>%
    group_by(hosp_id) %>%
    filter(day_symp == diag_p3) %>%
    ungroup() %>%
    select(c(hosp_id, simulated_vl)) %>%
    rename("vl_dp3" = "simulated_vl")
  
  train_dp4 <- diag_day_lis %>%
    filter(hosp_id %in% train_id_list) %>%
    left_join(pivot_long_train, by = "hosp_id") %>%
    group_by(hosp_id) %>%
    filter(day_symp == diag_p4) %>%
    ungroup() %>%
    select(c(hosp_id, simulated_vl)) %>%
    rename("vl_dp4" = "simulated_vl")
  
  train_dp5 <- diag_day_lis %>%
    filter(hosp_id %in% train_id_list) %>%
    left_join(pivot_long_train, by = "hosp_id") %>%
    group_by(hosp_id) %>%
    filter(day_symp == diag_p5) %>%
    ungroup() %>%
    select(c(hosp_id, simulated_vl)) %>%
    rename("vl_dp5" = "simulated_vl")
  
  train_dp6 <- diag_day_lis %>%
    filter(hosp_id %in% train_id_list) %>%
    left_join(pivot_long_train, by = "hosp_id") %>%
    group_by(hosp_id) %>%
    filter(day_symp == diag_p6) %>%
    ungroup() %>%
    select(c(hosp_id, simulated_vl)) %>%
    rename("vl_dp6" = "simulated_vl")
  
  train_dp7 <- diag_day_lis %>%
    filter(hosp_id %in% train_id_list) %>%
    left_join(pivot_long_train, by = "hosp_id") %>%
    group_by(hosp_id) %>%
    filter(day_symp == diag_p7) %>%
    ungroup() %>%
    select(c(hosp_id, simulated_vl)) %>%
    rename("vl_dp7" = "simulated_vl")
  
  train_dp8 <- diag_day_lis %>%
    filter(hosp_id %in% train_id_list) %>%
    left_join(pivot_long_train, by = "hosp_id") %>%
    group_by(hosp_id) %>%
    filter(day_symp == diag_p8) %>%
    ungroup() %>%
    select(c(hosp_id, simulated_vl)) %>%
    rename("vl_dp8" = "simulated_vl")
  
  train_dp9 <- diag_day_lis %>%
    filter(hosp_id %in% train_id_list) %>%
    left_join(pivot_long_train, by = "hosp_id") %>%
    group_by(hosp_id) %>%
    filter(day_symp == diag_p9) %>%
    ungroup() %>%
    select(c(hosp_id, simulated_vl)) %>%
    rename("vl_dp9" = "simulated_vl")
  
  train_dp10 <- diag_day_lis %>%
    filter(hosp_id %in% train_id_list) %>%
    left_join(pivot_long_train, by = "hosp_id") %>%
    group_by(hosp_id) %>%
    filter(day_symp == diag_p10) %>%
    ungroup() %>%
    select(c(hosp_id, simulated_vl)) %>%
    rename("vl_dp10" = "simulated_vl")
  
  test_dp1 <- diag_day_lis %>%
    filter(hosp_id %in% test_id_list) %>%
    left_join(pivot_long_test, by = "hosp_id") %>%
    group_by(hosp_id) %>%
    filter(day_symp == diag_p1) %>%
    ungroup() %>%
    select(c(hosp_id, simulated_vl)) %>%
    rename("vl_dp1" = "simulated_vl")
  
  test_dp2 <- diag_day_lis %>%
    filter(hosp_id %in% test_id_list) %>%
    left_join(pivot_long_test, by = "hosp_id") %>%
    group_by(hosp_id) %>%
    filter(day_symp == diag_p2) %>%
    ungroup() %>%
    select(c(hosp_id, simulated_vl)) %>%
    rename("vl_dp2" = "simulated_vl")
  
  test_dp3 <- diag_day_lis %>%
    filter(hosp_id %in% test_id_list) %>%
    left_join(pivot_long_test, by = "hosp_id") %>%
    group_by(hosp_id) %>%
    filter(day_symp == diag_p3) %>%
    ungroup() %>%
    select(c(hosp_id, simulated_vl)) %>%
    rename("vl_dp3" = "simulated_vl")
  
  test_dp4 <- diag_day_lis %>%
    filter(hosp_id %in% test_id_list) %>%
    left_join(pivot_long_test, by = "hosp_id") %>%
    group_by(hosp_id) %>%
    filter(day_symp == diag_p4) %>%
    ungroup() %>%
    select(c(hosp_id, simulated_vl)) %>%
    rename("vl_dp4" = "simulated_vl")
  
  test_dp5 <- diag_day_lis %>%
    filter(hosp_id %in% test_id_list) %>%
    left_join(pivot_long_test, by = "hosp_id") %>%
    group_by(hosp_id) %>%
    filter(day_symp == diag_p5) %>%
    ungroup() %>%
    select(c(hosp_id, simulated_vl)) %>%
    rename("vl_dp5" = "simulated_vl")
  
  test_dp6 <- diag_day_lis %>%
    filter(hosp_id %in% test_id_list) %>%
    left_join(pivot_long_test, by = "hosp_id") %>%
    group_by(hosp_id) %>%
    filter(day_symp == diag_p6) %>%
    ungroup() %>%
    select(c(hosp_id, simulated_vl)) %>%
    rename("vl_dp6" = "simulated_vl")
  
  test_dp7 <- diag_day_lis %>%
    filter(hosp_id %in% test_id_list) %>%
    left_join(pivot_long_test, by = "hosp_id") %>%
    group_by(hosp_id) %>%
    filter(day_symp == diag_p7) %>%
    ungroup() %>%
    select(c(hosp_id, simulated_vl)) %>%
    rename("vl_dp7" = "simulated_vl")
  
  test_dp8 <- diag_day_lis %>%
    filter(hosp_id %in% test_id_list) %>%
    left_join(pivot_long_test, by = "hosp_id") %>%
    group_by(hosp_id) %>%
    filter(day_symp == diag_p8) %>%
    ungroup() %>%
    select(c(hosp_id, simulated_vl)) %>%
    rename("vl_dp8" = "simulated_vl")
  
  test_dp9 <- diag_day_lis %>%
    filter(hosp_id %in% test_id_list) %>%
    left_join(pivot_long_test, by = "hosp_id") %>%
    group_by(hosp_id) %>%
    filter(day_symp == diag_p9) %>%
    ungroup() %>%
    select(c(hosp_id, simulated_vl)) %>%
    rename("vl_dp9" = "simulated_vl")
  
  test_dp10 <- diag_day_lis %>%
    filter(hosp_id %in% test_id_list) %>%
    left_join(pivot_long_test, by = "hosp_id") %>%
    group_by(hosp_id) %>%
    filter(day_symp == diag_p10) %>%
    ungroup() %>%
    select(c(hosp_id, simulated_vl)) %>%
    rename("vl_dp10" = "simulated_vl")
  
  df_train <- split$train %>%
    select(c(hosp_id, age, gender, vaccination, comorbidity, vl_sim, outcome)) %>%
    left_join(train_dp1, by = "hosp_id") %>%
    left_join(train_dp2, by = "hosp_id") %>%
    left_join(train_dp3, by = "hosp_id") %>%
    left_join(train_dp4, by = "hosp_id") %>%
    left_join(train_dp5, by = "hosp_id") %>%
    left_join(train_dp6, by = "hosp_id") %>%
    left_join(train_dp7, by = "hosp_id") %>%
    left_join(train_dp8, by = "hosp_id") %>%
    left_join(train_dp9, by = "hosp_id") %>%
    left_join(train_dp10, by = "hosp_id") %>%
    select(c(age, gender, vaccination, comorbidity, vl_sim, starts_with("vl_dp"), outcome))
  
  df_test <- split$test %>%
    select(c(hosp_id, age, gender, vaccination, comorbidity, vl_sim, outcome)) %>%
    left_join(test_dp1, by = "hosp_id") %>%
    left_join(test_dp2, by = "hosp_id") %>%
    left_join(test_dp3, by = "hosp_id") %>%
    left_join(test_dp4, by = "hosp_id") %>%
    left_join(test_dp5, by = "hosp_id") %>%
    left_join(test_dp6, by = "hosp_id") %>%
    left_join(test_dp7, by = "hosp_id") %>%
    left_join(test_dp8, by = "hosp_id") %>%
    left_join(test_dp9, by = "hosp_id") %>%
    left_join(test_dp10, by = "hosp_id") %>%
    select(c(age, gender, vaccination, comorbidity, vl_sim, starts_with("vl_dp"), outcome))
  
  list(train = df_train, test = df_test)
}
```

```{r, Stop CPU clusters}
stopCluster(cl)
```

# Fitting data excluding Comorbidity
## Without any VL information
```{r, Creating dataframe without VL information & comorbidity}
fea_without_vlncom <- c("age", "gender", "vaccination", "outcome")

split_list_wvlncom <- list()
for (i in 1:100) {
    train_df <- split_list[[i]]$train %>% select(all_of(fea_without_vlncom))
    test_df <- split_list[[i]]$test %>% select(all_of(fea_without_vlncom))

    split_list_wvlncom[[i]] <- list(train = train_df, test = test_df)
}
```

## With VL since symptom onset
```{r, Creating dataframe without comorbidity & with VL since symptom onset}
fea_vlsim_symp_wcom <- c("age", "gender", "vaccination", "0", "outcome")

split_list_vlsim_symp_wcom <- list()
for (i in 1:100) {
    train_df <- split_list[[i]]$train %>% select(all_of(fea_vlsim_symp_wcom)) %>% rename("vl_sim_symp" = "0")
    test_df <- split_list[[i]]$test %>% select(all_of(fea_vlsim_symp_wcom)) %>% rename("vl_sim_symp" = "0")

    split_list_vlsim_symp_wcom[[i]] <- list(train = train_df, test = test_df)
}
```

## With VL at diagnosis
```{r, Creating dataframe without comorbidity & with VL at diagnosis}
fea_vldiag_wcom <- c("age", "gender", "vaccination", "vl_sim", "outcome")

split_list_vldiag_wcom <- list()
for (i in 1:100) {
    train_df <- split_list[[i]]$train %>% select(all_of(fea_vldiag_wcom))
    test_df <- split_list[[i]]$test %>% select(all_of(fea_vldiag_wcom))

    split_list_vldiag_wcom[[i]] <- list(train = train_df, test = test_df)
}
```

# Fitting data excluding Age
## Without any VL information
```{r, Creating dataframe without VL information & age}
fea_without_vlnage <- c("gender", "vaccination", "comorbidity", "outcome")

split_list_wvlnage <- list()
for (i in 1:100) {
    train_df <- split_list[[i]]$train %>% select(all_of(fea_without_vlnage))
    test_df <- split_list[[i]]$test %>% select(all_of(fea_without_vlnage))

    split_list_wvlnage[[i]] <- list(train = train_df, test = test_df)
}
```

## With VL since symptom onset
```{r, Creating dataframe without age & with VL since symptom onset}
fea_vlsim_symp_wage <- c("gender", "vaccination", "comorbidity", "0", "outcome")

split_list_vlsim_symp_wage <- list()
for (i in 1:100) {
    train_df <- split_list[[i]]$train %>% select(all_of(fea_vlsim_symp_wage)) %>% rename("vl_sim_symp" = "0")
    test_df <- split_list[[i]]$test %>% select(all_of(fea_vlsim_symp_wage)) %>% rename("vl_sim_symp" = "0")

    split_list_vlsim_symp_wage[[i]] <- list(train = train_df, test = test_df)
}
```

## With VL at diagnosis
```{r, Creating dataframe without age & with VL at diagnosis}
fea_vldiag_wage <- c("gender", "vaccination", "comorbidity", "vl_sim", "outcome")

split_list_vldiag_wage <- list()
for (i in 1:100) {
    train_df <- split_list[[i]]$train %>% select(all_of(fea_vldiag_wage))
    test_df <- split_list[[i]]$test %>% select(all_of(fea_vldiag_wage))

    split_list_vldiag_wage[[i]] <- list(train = train_df, test = test_df)
}
```

# Fitting data excluding Comorbidity & Age
## Without any VL information
```{r, Creating dataframe without VL information, age & comorbidity}
fea_without_vlnagecom <- c("gender", "vaccination", "outcome")

split_list_wvlnagecom <- list()
for (i in 1:100) {
    train_df <- split_list[[i]]$train %>% select(all_of(fea_without_vlnagecom))
    test_df <- split_list[[i]]$test %>% select(all_of(fea_without_vlnagecom))

    split_list_wvlnagecom[[i]] <- list(train = train_df, test = test_df)
}
```

## With VL since symptom onset
```{r, Creating dataframe without comorbidity and age & with VL since symptom onset}
fea_vlsim_symp_wagecom <- c("gender", "vaccination", "0", "outcome")

split_list_vlsim_symp_wagecom <- list()
for (i in 1:100) {
    train_df <- split_list[[i]]$train %>% select(all_of(fea_vlsim_symp_wagecom)) %>% rename("vl_sim_symp" = "0")
    test_df <- split_list[[i]]$test %>% select(all_of(fea_vlsim_symp_wagecom)) %>% rename("vl_sim_symp" = "0")

    split_list_vlsim_symp_wagecom[[i]] <- list(train = train_df, test = test_df)
}
```

## With VL at diagnosis
```{r, Creating dataframe without comorbidity and age & with VL at diagnosis}
fea_vldiag_wagecom <- c("gender", "vaccination", "vl_sim", "outcome")

split_list_vldiag_wagecom <- list()
for (i in 1:100) {
    train_df <- split_list[[i]]$train %>% select(all_of(fea_vldiag_wagecom))
    test_df <- split_list[[i]]$test %>% select(all_of(fea_vldiag_wagecom))

    split_list_vldiag_wagecom[[i]] <- list(train = train_df, test = test_df)
}
```

# Saving all data in this session
```{r, Save data}
save.image(file = paste0(getwd(), "/Data_preparation.RData")) # This file will be used for the following analysis
```

# Show the session info
```{r, Session Info}
sessionInfo()
```
