---
title: "LightGBM"
output: html_document
---

# Setup environment, clusters & load data
```{r, Import libraries}
library(foreach)
library(doParallel)
library(dplyr)
library(purrr)
library(pROC)
library(lightgbm)
library(shapviz)
library(ggplot2)
```

```{r, Load data into environment}
load(paste0(getwd(), "/Data_preparation.RData"))
```

# Fitting data with full dataframe
## Fitting data without any VL information
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Full dataframe without VL information}
lightgbm_fil_list <- foreach(i = 1: 100, .packages = c("lightgbm", "pROC", "shapviz")) %dopar% {
    split <- split_list_fil[[i]]
    train_df <- split$train
    test_df <- split$test

    # Convert categorical variables to numeric format using one-hot encoding
    train_x_fil <- model.matrix(outcome ~ ., data = train_df) [, -1]
    test_x_fil <- model.matrix(outcome ~ ., data = test_df) [, -1]

    # Convert data to XGBoost matrix format
    dtrain_fil <- lgb.Dataset(data = train_x_fil, label = as.numeric(as.factor(train_df$outcome)) - 1)
    dtest_fil <- lgb.Dataset(data = test_x_fil, label = as.numeric(as.factor(test_df$outcome)) - 1)

    lgb_model_fil <- lgb.train(data = dtrain_fil,
                      nrounds = 1000,
                      verbose = 0,
                      params = list(
                        objective = "binary")
                      )

    # Make prediction on the testing set
    lgb_pred_fil <- predict(lgb_model_fil, newdata = test_x_fil, type = "response")
    lgb_pred_fil <- ifelse(lgb_pred_fil >= 0.5, 1, 0)
    lgb_pred_fil_res <- ifelse(lgb_pred_fil == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_fil <- table(lgb_pred_fil_res, test_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_fil <- sum(cfm_lgb_fil["Severe", "Severe"], cfm_lgb_fil["Non severe", "Non severe"])/sum(cfm_lgb_fil)
    
    # Make prediction on the training set
    lgb_pred_fil_train <- predict(lgb_model_fil, newdata = train_x_fil, type = "response")
    lgb_pred_fil_train <- ifelse(lgb_pred_fil_train >= 0.5, 1, 0)
    lgb_pred_fil_train_res <- ifelse(lgb_pred_fil_train == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_fil_train <- table(lgb_pred_fil_train_res, train_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_fil_train <- sum(cfm_lgb_fil_train["Severe", "Severe"], cfm_lgb_fil_train["Non severe", "Non severe"])/sum(cfm_lgb_fil_train)

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_lgb_fil["Severe", "Severe"]
    FP <- cfm_lgb_fil["Severe", "Non severe"]
    TN <- cfm_lgb_fil["Non severe", "Non severe"]
    FN <- cfm_lgb_fil["Non severe", "Severe"]

    sensitivity_lgb_fil <- TP / (TP + FN)
    specificity_lgb_fil <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_lgb_fil <- TP / (TP + FP)
    f1_sc_lgb_fil <- 2 * ((prec_lgb_fil * sensitivity_lgb_fil) / (prec_lgb_fil + sensitivity_lgb_fil))

    # Compute AUROC
    roc_lgb_fil <- roc(test_df$outcome, lgb_pred_fil)
    auc_val_lgb_fil <- auc(roc_lgb_fil)

    ## SHAP Summary
    shp_lgb_fil <- shapviz(lgb_model_fil, X_pred = train_x_fil, X = as.data.frame(train_x_fil))
    
    list(model = lgb_model_fil, confusion_matrix = cfm_lgb_fil, accuracy_training = accuracy_lgb_fil_train, accuracy_testing = accuracy_lgb_fil,
          sensitivity = sensitivity_lgb_fil, specificity = specificity_lgb_fil, precision = prec_lgb_fil,
          F1_score = f1_sc_lgb_fil, AUC_value = auc_val_lgb_fil, SHAP_values = shp_lgb_fil, prediction = lgb_pred_fil_res)
}
```

```{r, Stop CPU clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
lgb_fil_metrics_df <- map_dfr(seq_along(lightgbm_fil_list), function(i) {
  result <- lightgbm_fil_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
lgb_fil_metrics_df <- as.data.frame(lgb_fil_metrics_df)

lgb_fil_metrics_summary <- lgb_fil_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(lgb_fil_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(lgb_fil_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(lgb_fil_metrics_df$sensitivity, 0.025)
low_spec <- quantile(lgb_fil_metrics_df$specificity, 0.025)
low_prec <- quantile(lgb_fil_metrics_df$precision, 0.025)
low_f1_sc <- quantile(lgb_fil_metrics_df$F1_score, 0.025)
low_auc <- quantile(lgb_fil_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(lgb_fil_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(lgb_fil_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(lgb_fil_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(lgb_fil_metrics_df$specificity, 0.975)
upp_prec <- quantile(lgb_fil_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(lgb_fil_metrics_df$F1_score, 0.975)
upp_auc <- quantile(lgb_fil_metrics_df$AUC_value, 0.975)

lgb_fil_metrics_summary['low_acc_train'] <- low_acc_train
lgb_fil_metrics_summary['low_acc_test'] <- low_acc_test
lgb_fil_metrics_summary['low_sens'] <- low_sens
lgb_fil_metrics_summary['low_spec'] <- low_spec
lgb_fil_metrics_summary['low_prec'] <- low_prec
lgb_fil_metrics_summary['low_f1_sc'] <- low_f1_sc
lgb_fil_metrics_summary['low_auc'] <- low_auc

lgb_fil_metrics_summary['upp_acc_train'] <- upp_acc_train
lgb_fil_metrics_summary['upp_acc_test'] <- upp_acc_test
lgb_fil_metrics_summary['upp_sens'] <- upp_sens
lgb_fil_metrics_summary['upp_spec'] <- upp_spec
lgb_fil_metrics_summary['upp_prec'] <- upp_prec
lgb_fil_metrics_summary['upp_f1_sc'] <- upp_f1_sc
lgb_fil_metrics_summary['upp_auc'] <- upp_auc

lgb_fil_metrics_summary
```

## Fitting data with VL since symptom onset
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Full dataframe with VL since symptom onset}
lightgbm_vlsymp_list <- foreach(i = 1: 100, .packages = c("lightgbm", "pROC", "shapviz")) %dopar% {
    split <- split_list_vlsim_symp[[i]]
    train_df <- split$train
    test_df <- split$test

    # Convert categorical variables to numeric format using one-hot encoding
    train_x_vlsymp <- model.matrix(outcome ~ ., data = train_df) [, -1]
    test_x_vlsymp <- model.matrix(outcome ~ ., data = test_df) [, -1]

    # Convert data to XGBoost matrix format
    dtrain_vlsymp <- lgb.Dataset(data = train_x_vlsymp, label = as.numeric(as.factor(train_df$outcome)) - 1)
    dtest_vlsymp <- lgb.Dataset(data = test_x_vlsymp, label = as.numeric(as.factor(test_df$outcome)) - 1)

    lgb_model_vlsymp <- lgb.train(data = dtrain_vlsymp,
                      nrounds = 1000,
                      verbose = 0,
                      params = list(
                        objective = "binary")
                      )

    # Make prediction on the testing set
    lgb_pred_vlsymp <- predict(lgb_model_vlsymp, newdata = test_x_vlsymp, type = "response")
    lgb_pred_vlsymp <- ifelse(lgb_pred_vlsymp >= 0.5, 1, 0)
    lgb_pred_vlsymp_res <- ifelse(lgb_pred_vlsymp == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_vlsymp <- table(lgb_pred_vlsymp_res, test_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_vlsymp <- sum(cfm_lgb_vlsymp["Severe", "Severe"], cfm_lgb_vlsymp["Non severe", "Non severe"])/sum(cfm_lgb_vlsymp)
    
    # Make prediction on the training set
    lgb_pred_vlsymp_train <- predict(lgb_model_vlsymp, newdata = train_x_vlsymp, type = "response")
    lgb_pred_vlsymp_train <- ifelse(lgb_pred_vlsymp_train >= 0.5, 1, 0)
    lgb_pred_vlsymp_train_res <- ifelse(lgb_pred_vlsymp_train == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_vlsymp_train <- table(lgb_pred_vlsymp_train_res, train_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_vlsymp_train <- sum(cfm_lgb_vlsymp_train["Severe", "Severe"], cfm_lgb_vlsymp_train["Non severe", "Non severe"])/sum(cfm_lgb_vlsymp_train)

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_lgb_vlsymp["Severe", "Severe"]
    FP <- cfm_lgb_vlsymp["Severe", "Non severe"]
    TN <- cfm_lgb_vlsymp["Non severe", "Non severe"]
    FN <- cfm_lgb_vlsymp["Non severe", "Severe"]

    sensitivity_lgb_vlsymp <- TP / (TP + FN)
    specificity_lgb_vlsymp <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_lgb_vlsymp <- TP / (TP + FP)
    f1_sc_lgb_vlsymp <- 2 * ((prec_lgb_vlsymp * sensitivity_lgb_vlsymp) / (prec_lgb_vlsymp + sensitivity_lgb_vlsymp))

    # Compute AUROC
    roc_lgb_vlsymp <- roc(test_df$outcome, lgb_pred_vlsymp)
    auc_val_lgb_vlsymp <- auc(roc_lgb_vlsymp)
    
    ## SHAP Summary
    shp_lgb_vlsymp <- shapviz(lgb_model_vlsymp, X_pred = train_x_vlsymp, X = as.data.frame(train_x_vlsymp))
    
    list(model = lgb_model_vlsymp, confusion_matrix = cfm_lgb_vlsymp, accuracy_training = accuracy_lgb_vlsymp_train, accuracy_testing = accuracy_lgb_vlsymp,
          sensitivity = sensitivity_lgb_vlsymp, specificity = specificity_lgb_vlsymp, precision = prec_lgb_vlsymp,
          F1_score = f1_sc_lgb_vlsymp, AUC_value = auc_val_lgb_vlsymp, SHAP_values = shp_lgb_vlsymp, prediction = lgb_pred_vlsymp_res)
}
```

```{r, Stop CPU clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
lgb_vlsymp_metrics_df <- map_dfr(seq_along(lightgbm_vlsymp_list), function(i) {
  result <- lightgbm_vlsymp_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
lgb_vlsymp_metrics_df <- as.data.frame(lgb_vlsymp_metrics_df)

lgb_vlsymp_metrics_summary <- lgb_vlsymp_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(lgb_vlsymp_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(lgb_vlsymp_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(lgb_vlsymp_metrics_df$sensitivity, 0.025)
low_spec <- quantile(lgb_vlsymp_metrics_df$specificity, 0.025)
low_prec <- quantile(lgb_vlsymp_metrics_df$precision, 0.025)
low_f1_sc <- quantile(lgb_vlsymp_metrics_df$F1_score, 0.025)
low_auc <- quantile(lgb_vlsymp_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(lgb_vlsymp_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(lgb_vlsymp_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(lgb_vlsymp_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(lgb_vlsymp_metrics_df$specificity, 0.975)
upp_prec <- quantile(lgb_vlsymp_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(lgb_vlsymp_metrics_df$F1_score, 0.975)
upp_auc <- quantile(lgb_vlsymp_metrics_df$AUC_value, 0.975)

lgb_vlsymp_metrics_summary['low_acc_train'] <- low_acc_train
lgb_vlsymp_metrics_summary['low_acc_test'] <- low_acc_test
lgb_vlsymp_metrics_summary['low_sens'] <- low_sens
lgb_vlsymp_metrics_summary['low_spec'] <- low_spec
lgb_vlsymp_metrics_summary['low_prec'] <- low_prec
lgb_vlsymp_metrics_summary['low_f1_sc'] <- low_f1_sc
lgb_vlsymp_metrics_summary['low_auc'] <- low_auc

lgb_vlsymp_metrics_summary['upp_acc_train'] <- upp_acc_train
lgb_vlsymp_metrics_summary['upp_acc_test'] <- upp_acc_test
lgb_vlsymp_metrics_summary['upp_sens'] <- upp_sens
lgb_vlsymp_metrics_summary['upp_spec'] <- upp_spec
lgb_vlsymp_metrics_summary['upp_prec'] <- upp_prec
lgb_vlsymp_metrics_summary['upp_f1_sc'] <- upp_f1_sc
lgb_vlsymp_metrics_summary['upp_auc'] <- upp_auc

lgb_vlsymp_metrics_summary
```

## Fitting data with VL at diagnosis
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Full dataframe with VL at diagnosis}
lightgbm_vldiag_list <- foreach(i = 1: 100, .packages = c("lightgbm", "pROC", "shapviz")) %dopar% {
    split <- split_list_vldiag[[i]]
    train_df <- split$train
    test_df <- split$test

    # Convert categorical variables to numeric format using one-hot encoding
    train_x_vldiag <- model.matrix(outcome ~ ., data = train_df) [, -1]
    test_x_vldiag <- model.matrix(outcome ~ ., data = test_df) [, -1]

    # Convert data to XGBoost matrix format
    dtrain_vldiag <- lgb.Dataset(data = train_x_vldiag, label = as.numeric(as.factor(train_df$outcome)) - 1)
    dtest_vldiag <- lgb.Dataset(data = test_x_vldiag, label = as.numeric(as.factor(test_df$outcome)) - 1)

    lgb_model_vldiag <- lgb.train(data = dtrain_vldiag,
                      nrounds = 1000,
                      verbose = 0,
                      params = list(
                        objective = "binary")
                      )

    # Make prediction on the testing set
    lgb_pred_vldiag <- predict(lgb_model_vldiag, newdata = test_x_vldiag, type = "response")
    lgb_pred_vldiag <- ifelse(lgb_pred_vldiag >= 0.5, 1, 0)
    lgb_pred_vldiag_res <- ifelse(lgb_pred_vldiag == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_vldiag <- table(lgb_pred_vldiag_res, test_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_vldiag <- sum(cfm_lgb_vldiag["Severe", "Severe"], cfm_lgb_vldiag["Non severe", "Non severe"])/sum(cfm_lgb_vldiag)
    
    # Make prediction on the training set
    lgb_pred_vldiag_train <- predict(lgb_model_vldiag, newdata = train_x_vldiag, type = "response")
    lgb_pred_vldiag_train <- ifelse(lgb_pred_vldiag_train >= 0.5, 1, 0)
    lgb_pred_vldiag_train_res <- ifelse(lgb_pred_vldiag_train == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_vldiag_train <- table(lgb_pred_vldiag_train_res, train_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_vldiag_train <- sum(cfm_lgb_vldiag_train["Severe", "Severe"], cfm_lgb_vldiag_train["Non severe", "Non severe"])/sum(cfm_lgb_vldiag_train)

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_lgb_vldiag["Severe", "Severe"]
    FP <- cfm_lgb_vldiag["Severe", "Non severe"]
    TN <- cfm_lgb_vldiag["Non severe", "Non severe"]
    FN <- cfm_lgb_vldiag["Non severe", "Severe"]

    sensitivity_lgb_vldiag <- TP / (TP + FN)
    specificity_lgb_vldiag <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_lgb_vldiag <- TP / (TP + FP)
    f1_sc_lgb_vldiag <- 2 * ((prec_lgb_vldiag * sensitivity_lgb_vldiag) / (prec_lgb_vldiag + sensitivity_lgb_vldiag))

    # Compute AUROC
    roc_lgb_vldiag <- roc(test_df$outcome, lgb_pred_vldiag)
    auc_val_lgb_vldiag <- auc(roc_lgb_vldiag)
    
    ## SHAP Summary
    shp_lgb_vldiag <- shapviz(lgb_model_vldiag, X_pred = train_x_vldiag, X = as.data.frame(train_x_vldiag))
    
    list(model = lgb_model_vldiag, confusion_matrix = cfm_lgb_vldiag, accuracy_training = accuracy_lgb_vldiag_train, accuracy_testing = accuracy_lgb_vldiag,
          sensitivity = sensitivity_lgb_vldiag, specificity = specificity_lgb_vldiag, precision = prec_lgb_vldiag,
          F1_score = f1_sc_lgb_vldiag, AUC_value = auc_val_lgb_vldiag, SHAP_values = shp_lgb_vldiag, prediction = lgb_pred_vldiag_res)
}
```

```{r, Stop CPU clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
lgb_vldiag_metrics_df <- map_dfr(seq_along(lightgbm_vldiag_list), function(i) {
  result <- lightgbm_vldiag_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
lgb_vldiag_metrics_df <- as.data.frame(lgb_vldiag_metrics_df)

lgb_vldiag_metrics_summary <- lgb_vldiag_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(lgb_vldiag_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(lgb_vldiag_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(lgb_vldiag_metrics_df$sensitivity, 0.025)
low_spec <- quantile(lgb_vldiag_metrics_df$specificity, 0.025)
low_prec <- quantile(lgb_vldiag_metrics_df$precision, 0.025)
low_f1_sc <- quantile(lgb_vldiag_metrics_df$F1_score, 0.025)
low_auc <- quantile(lgb_vldiag_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(lgb_vldiag_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(lgb_vldiag_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(lgb_vldiag_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(lgb_vldiag_metrics_df$specificity, 0.975)
upp_prec <- quantile(lgb_vldiag_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(lgb_vldiag_metrics_df$F1_score, 0.975)
upp_auc <- quantile(lgb_vldiag_metrics_df$AUC_value, 0.975)

lgb_vldiag_metrics_summary['low_acc_train'] <- low_acc_train
lgb_vldiag_metrics_summary['low_acc_test'] <- low_acc_test
lgb_vldiag_metrics_summary['low_sens'] <- low_sens
lgb_vldiag_metrics_summary['low_spec'] <- low_spec
lgb_vldiag_metrics_summary['low_prec'] <- low_prec
lgb_vldiag_metrics_summary['low_f1_sc'] <- low_f1_sc
lgb_vldiag_metrics_summary['low_auc'] <- low_auc

lgb_vldiag_metrics_summary['upp_acc_train'] <- upp_acc_train
lgb_vldiag_metrics_summary['upp_acc_test'] <- upp_acc_test
lgb_vldiag_metrics_summary['upp_sens'] <- upp_sens
lgb_vldiag_metrics_summary['upp_spec'] <- upp_spec
lgb_vldiag_metrics_summary['upp_prec'] <- upp_prec
lgb_vldiag_metrics_summary['upp_f1_sc'] <- upp_f1_sc
lgb_vldiag_metrics_summary['upp_auc'] <- upp_auc

lgb_vldiag_metrics_summary
```

# Fitting data excluding Comorbidity
## Fitting data without any VL information
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Dataframe excluding Comorbidity & VL information}
lightgbm_wvlncom_list <- foreach(i = 1: 100, .packages = c("lightgbm", "pROC", "shapviz")) %dopar% {
    split <- split_list_wvlncom[[i]]
    train_df <- split$train
    test_df <- split$test

    # Convert categorical variables to numeric format using one-hot encoding
    train_x_wvlncom <- model.matrix(outcome ~ ., data = train_df) [, -1]
    test_x_wvlncom <- model.matrix(outcome ~ ., data = test_df) [, -1]

    # Convert data to XGBoost matrix format
    dtrain_wvlncom <- lgb.Dataset(data = train_x_wvlncom, label = as.numeric(as.factor(train_df$outcome)) - 1)
    dtest_wvlncom <- lgb.Dataset(data = test_x_wvlncom, label = as.numeric(as.factor(test_df$outcome)) - 1)

    lgb_model_wvlncom <- lgb.train(data = dtrain_wvlncom,
                      nrounds = 1000,
                      verbose = 0,
                      params = list(
                        objective = "binary")
                      )

    # Make prediction on the testing set
    lgb_pred_wvlncom <- predict(lgb_model_wvlncom, newdata = test_x_wvlncom, type = "response")
    lgb_pred_wvlncom <- ifelse(lgb_pred_wvlncom >= 0.5, 1, 0)
    lgb_pred_wvlncom_res <- ifelse(lgb_pred_wvlncom == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_wvlncom <- table(lgb_pred_wvlncom_res, test_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_wvlncom <- sum(cfm_lgb_wvlncom["Severe", "Severe"], cfm_lgb_wvlncom["Non severe", "Non severe"])/sum(cfm_lgb_wvlncom)
    
    # Make prediction on the training set
    lgb_pred_wvlncom_train <- predict(lgb_model_wvlncom, newdata = train_x_wvlncom, type = "response")
    lgb_pred_wvlncom_train <- ifelse(lgb_pred_wvlncom_train >= 0.5, 1, 0)
    lgb_pred_wvlncom_train_res <- ifelse(lgb_pred_wvlncom_train == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_wvlncom_train <- table(lgb_pred_wvlncom_train_res, train_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_wvlncom_train <- sum(cfm_lgb_wvlncom_train["Severe", "Severe"], cfm_lgb_wvlncom_train["Non severe", "Non severe"])/sum(cfm_lgb_wvlncom_train)

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_lgb_wvlncom["Severe", "Severe"]
    FP <- cfm_lgb_wvlncom["Severe", "Non severe"]
    TN <- cfm_lgb_wvlncom["Non severe", "Non severe"]
    FN <- cfm_lgb_wvlncom["Non severe", "Severe"]

    sensitivity_lgb_wvlncom <- TP / (TP + FN)
    specificity_lgb_wvlncom <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_lgb_wvlncom <- TP / (TP + FP)
    f1_sc_lgb_wvlncom <- 2 * ((prec_lgb_wvlncom * sensitivity_lgb_wvlncom) / (prec_lgb_wvlncom + sensitivity_lgb_wvlncom))

    # Compute AUROC
    roc_lgb_wvlncom <- roc(test_df$outcome, lgb_pred_wvlncom)
    auc_val_lgb_wvlncom <- auc(roc_lgb_wvlncom)
    
    ## SHAP Summary Plot
    shp_lgb_wvlncom <- shapviz(lgb_model_wvlncom, X_pred = train_x_wvlncom, X = as.data.frame(train_x_wvlncom))
    
    list(model = lgb_model_wvlncom, confusion_matrix = cfm_lgb_wvlncom, accuracy_training = accuracy_lgb_wvlncom_train, accuracy_testing = accuracy_lgb_wvlncom,
         sensitivity = sensitivity_lgb_wvlncom, specificity = specificity_lgb_wvlncom, precision = prec_lgb_wvlncom, F1_score = f1_sc_lgb_wvlncom,
         AUC_value = auc_val_lgb_wvlncom, SHAP_values = shp_lgb_wvlncom, prediction = lgb_pred_wvlncom_res)
}
```

```{r, Stop CPU clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
lgb_wvlncom_metrics_df <- map_dfr(seq_along(lightgbm_wvlncom_list), function(i) {
  result <- lightgbm_wvlncom_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
lgb_wvlncom_metrics_df <- as.data.frame(lgb_wvlncom_metrics_df)

lgb_wvlncom_metrics_summary <- lgb_wvlncom_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(lgb_wvlncom_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(lgb_wvlncom_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(lgb_wvlncom_metrics_df$sensitivity, 0.025)
low_spec <- quantile(lgb_wvlncom_metrics_df$specificity, 0.025)
low_prec <- quantile(lgb_wvlncom_metrics_df$precision, 0.025)
low_f1_sc <- quantile(lgb_wvlncom_metrics_df$F1_score, 0.025)
low_auc <- quantile(lgb_wvlncom_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(lgb_wvlncom_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(lgb_wvlncom_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(lgb_wvlncom_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(lgb_wvlncom_metrics_df$specificity, 0.975)
upp_prec <- quantile(lgb_wvlncom_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(lgb_wvlncom_metrics_df$F1_score, 0.975)
upp_auc <- quantile(lgb_wvlncom_metrics_df$AUC_value, 0.975)

lgb_wvlncom_metrics_summary['low_acc_train'] <- low_acc_train
lgb_wvlncom_metrics_summary['low_acc_test'] <- low_acc_test
lgb_wvlncom_metrics_summary['low_sens'] <- low_sens
lgb_wvlncom_metrics_summary['low_spec'] <- low_spec
lgb_wvlncom_metrics_summary['low_prec'] <- low_prec
lgb_wvlncom_metrics_summary['low_f1_sc'] <- low_f1_sc
lgb_wvlncom_metrics_summary['low_auc'] <- low_auc

lgb_wvlncom_metrics_summary['upp_acc_train'] <- upp_acc_train
lgb_wvlncom_metrics_summary['upp_acc_test'] <- upp_acc_test
lgb_wvlncom_metrics_summary['upp_sens'] <- upp_sens
lgb_wvlncom_metrics_summary['upp_spec'] <- upp_spec
lgb_wvlncom_metrics_summary['upp_prec'] <- upp_prec
lgb_wvlncom_metrics_summary['upp_f1_sc'] <- upp_f1_sc
lgb_wvlncom_metrics_summary['upp_auc'] <- upp_auc

lgb_wvlncom_metrics_summary
```

## Fitting data with VL since symptom onset
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Dataframe excluding Comorbidity & with VL since symptom onset}
lightgbm_vlsymp_wcom_list <- foreach(i = 1: 100, .packages = c("lightgbm", "pROC", "shapviz")) %dopar% {
    split <- split_list_vlsim_symp_wcom[[i]]
    train_df <- split$train
    test_df <- split$test

    # Convert categorical variables to numeric format using one-hot encoding
    train_x_vlsymp_wcom <- model.matrix(outcome ~ ., data = train_df) [, -1]
    test_x_vlsymp_wcom <- model.matrix(outcome ~ ., data = test_df) [, -1]

    # Convert data to XGBoost matrix format
    dtrain_vlsymp_wcom <- lgb.Dataset(data = train_x_vlsymp_wcom, label = as.numeric(as.factor(train_df$outcome)) - 1)
    dtest_vlsymp_wcom <- lgb.Dataset(data = test_x_vlsymp_wcom, label = as.numeric(as.factor(test_df$outcome)) - 1)

    lgb_model_vlsymp_wcom <- lgb.train(data = dtrain_vlsymp_wcom,
                      nrounds = 1000,
                      verbose = 0,
                      params = list(
                        objective = "binary")
                      )

    # Make prediction on the testing set
    lgb_pred_vlsymp_wcom <- predict(lgb_model_vlsymp_wcom, newdata = test_x_vlsymp_wcom, type = "response")
    lgb_pred_vlsymp_wcom <- ifelse(lgb_pred_vlsymp_wcom >= 0.5, 1, 0)
    lgb_pred_vlsymp_wcom_res <- ifelse(lgb_pred_vlsymp_wcom == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_vlsymp_wcom <- table(lgb_pred_vlsymp_wcom_res, test_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_vlsymp_wcom <- sum(cfm_lgb_vlsymp_wcom["Severe", "Severe"], cfm_lgb_vlsymp_wcom["Non severe", "Non severe"])/sum(cfm_lgb_vlsymp_wcom)
    
    # Make prediction on the training set
    lgb_pred_vlsymp_wcom_train <- predict(lgb_model_vlsymp_wcom, newdata = train_x_vlsymp_wcom, type = "response")
    lgb_pred_vlsymp_wcom_train <- ifelse(lgb_pred_vlsymp_wcom_train >= 0.5, 1, 0)
    lgb_pred_vlsymp_wcom_train_res <- ifelse(lgb_pred_vlsymp_wcom_train == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_vlsymp_wcom_train <- table(lgb_pred_vlsymp_wcom_train_res, train_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_vlsymp_wcom_train <- sum(cfm_lgb_vlsymp_wcom_train["Severe", "Severe"], cfm_lgb_vlsymp_wcom_train["Non severe", "Non severe"])/sum(cfm_lgb_vlsymp_wcom_train)

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_lgb_vlsymp_wcom["Severe", "Severe"]
    FP <- cfm_lgb_vlsymp_wcom["Severe", "Non severe"]
    TN <- cfm_lgb_vlsymp_wcom["Non severe", "Non severe"]
    FN <- cfm_lgb_vlsymp_wcom["Non severe", "Severe"]

    sensitivity_lgb_vlsymp_wcom <- TP / (TP + FN)
    specificity_lgb_vlsymp_wcom <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_lgb_vlsymp_wcom <- TP / (TP + FP)
    f1_sc_lgb_vlsymp_wcom <- 2 * ((prec_lgb_vlsymp_wcom * sensitivity_lgb_vlsymp_wcom) / (prec_lgb_vlsymp_wcom + sensitivity_lgb_vlsymp_wcom))

    # Compute AUROC
    roc_lgb_vlsymp_wcom <- roc(test_df$outcome, lgb_pred_vlsymp_wcom)
    auc_val_lgb_vlsymp_wcom <- auc(roc_lgb_vlsymp_wcom)
    
    ## SHAP Summary
    shp_lgb_vlsymp_wcom <- shapviz(lgb_model_vlsymp_wcom, X_pred = train_x_vlsymp_wcom, X = as.data.frame(train_x_vlsymp_wcom))
    
    list(model = lgb_model_vlsymp_wcom, confusion_matrix = cfm_lgb_vlsymp_wcom, accuracy_training = accuracy_lgb_vlsymp_wcom_train,
         accuracy_testing = accuracy_lgb_vlsymp_wcom, sensitivity = sensitivity_lgb_vlsymp_wcom, specificity = specificity_lgb_vlsymp_wcom,
         precision = prec_lgb_vlsymp_wcom, F1_score = f1_sc_lgb_vlsymp_wcom, AUC_value = auc_val_lgb_vlsymp_wcom, SHAP_values = shp_lgb_vlsymp_wcom,
         prediction = lgb_pred_vlsymp_wcom_res)
}
```

```{r, Stop CPU clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
lgb_vlsymp_wcom_metrics_df <- map_dfr(seq_along(lightgbm_vlsymp_wcom_list), function(i) {
  result <- lightgbm_vlsymp_wcom_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
lgb_vlsymp_wcom_metrics_df <- as.data.frame(lgb_vlsymp_wcom_metrics_df)

lgb_vlsymp_wcom_metrics_summary <- lgb_vlsymp_wcom_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(lgb_vlsymp_wcom_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(lgb_vlsymp_wcom_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(lgb_vlsymp_wcom_metrics_df$sensitivity, 0.025)
low_spec <- quantile(lgb_vlsymp_wcom_metrics_df$specificity, 0.025)
low_prec <- quantile(lgb_vlsymp_wcom_metrics_df$precision, 0.025)
low_f1_sc <- quantile(lgb_vlsymp_wcom_metrics_df$F1_score, 0.025)
low_auc <- quantile(lgb_vlsymp_wcom_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(lgb_vlsymp_wcom_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(lgb_vlsymp_wcom_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(lgb_vlsymp_wcom_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(lgb_vlsymp_wcom_metrics_df$specificity, 0.975)
upp_prec <- quantile(lgb_vlsymp_wcom_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(lgb_vlsymp_wcom_metrics_df$F1_score, 0.975)
upp_auc <- quantile(lgb_vlsymp_wcom_metrics_df$AUC_value, 0.975)

lgb_vlsymp_wcom_metrics_summary['low_acc_train'] <- low_acc_train
lgb_vlsymp_wcom_metrics_summary['low_acc_test'] <- low_acc_test
lgb_vlsymp_wcom_metrics_summary['low_sens'] <- low_sens
lgb_vlsymp_wcom_metrics_summary['low_spec'] <- low_spec
lgb_vlsymp_wcom_metrics_summary['low_prec'] <- low_prec
lgb_vlsymp_wcom_metrics_summary['low_f1_sc'] <- low_f1_sc
lgb_vlsymp_wcom_metrics_summary['low_auc'] <- low_auc

lgb_vlsymp_wcom_metrics_summary['upp_acc_train'] <- upp_acc_train
lgb_vlsymp_wcom_metrics_summary['upp_acc_test'] <- upp_acc_test
lgb_vlsymp_wcom_metrics_summary['upp_sens'] <- upp_sens
lgb_vlsymp_wcom_metrics_summary['upp_spec'] <- upp_spec
lgb_vlsymp_wcom_metrics_summary['upp_prec'] <- upp_prec
lgb_vlsymp_wcom_metrics_summary['upp_f1_sc'] <- upp_f1_sc
lgb_vlsymp_wcom_metrics_summary['upp_auc'] <- upp_auc

lgb_vlsymp_wcom_metrics_summary
```

## Fitting data with VL at diagnosis
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Dataframe excluding Comorbidity & with VL at diagnosis}
lightgbm_vldiag_wcom_list <- foreach(i = 1: 100, .packages = c("lightgbm", "pROC", "shapviz")) %dopar% {
    split <- split_list_vldiag_wcom[[i]]
    train_df <- split$train
    test_df <- split$test

    # Convert categorical variables to numeric format using one-hot encoding
    train_x_vldiag_wcom <- model.matrix(outcome ~ ., data = train_df) [, -1]
    test_x_vldiag_wcom <- model.matrix(outcome ~ ., data = test_df) [, -1]

    # Convert data to XGBoost matrix format
    dtrain_vldiag_wcom <- lgb.Dataset(data = train_x_vldiag_wcom, label = as.numeric(as.factor(train_df$outcome)) - 1)
    dtest_vldiag_wcom <- lgb.Dataset(data = test_x_vldiag_wcom, label = as.numeric(as.factor(test_df$outcome)) - 1)

    lgb_model_vldiag_wcom <- lgb.train(data = dtrain_vldiag_wcom,
                      nrounds = 1000,
                      verbose = 0,
                      params = list(
                        objective = "binary")
                      )

    # Make prediction on the testing set
    lgb_pred_vldiag_wcom <- predict(lgb_model_vldiag_wcom, newdata = test_x_vldiag_wcom, type = "response")
    lgb_pred_vldiag_wcom <- ifelse(lgb_pred_vldiag_wcom >= 0.5, 1, 0)
    lgb_pred_vldiag_wcom_res <- ifelse(lgb_pred_vldiag_wcom == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_vldiag_wcom <- table(lgb_pred_vldiag_wcom_res, test_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_vldiag_wcom <- sum(cfm_lgb_vldiag_wcom["Severe", "Severe"], cfm_lgb_vldiag_wcom["Non severe", "Non severe"])/sum(cfm_lgb_vldiag_wcom)
    
    # Make prediction on the training set
    lgb_pred_vldiag_wcom_train <- predict(lgb_model_vldiag_wcom, newdata = train_x_vldiag_wcom, type = "response")
    lgb_pred_vldiag_wcom_train <- ifelse(lgb_pred_vldiag_wcom_train >= 0.5, 1, 0)
    lgb_pred_vldiag_wcom_train_res <- ifelse(lgb_pred_vldiag_wcom_train == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_vldiag_wcom_train <- table(lgb_pred_vldiag_wcom_train_res, train_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_vldiag_wcom_train <- sum(cfm_lgb_vldiag_wcom_train["Severe", "Severe"], cfm_lgb_vldiag_wcom_train["Non severe", "Non severe"])/sum(cfm_lgb_vldiag_wcom_train)

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_lgb_vldiag_wcom["Severe", "Severe"]
    FP <- cfm_lgb_vldiag_wcom["Severe", "Non severe"]
    TN <- cfm_lgb_vldiag_wcom["Non severe", "Non severe"]
    FN <- cfm_lgb_vldiag_wcom["Non severe", "Severe"]

    sensitivity_lgb_vldiag_wcom <- TP / (TP + FN)
    specificity_lgb_vldiag_wcom <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_lgb_vldiag_wcom <- TP / (TP + FP)
    f1_sc_lgb_vldiag_wcom <- 2 * ((prec_lgb_vldiag_wcom * sensitivity_lgb_vldiag_wcom) / (prec_lgb_vldiag_wcom + sensitivity_lgb_vldiag_wcom))

    # Compute AUROC
    roc_lgb_vldiag_wcom <- roc(test_df$outcome, lgb_pred_vldiag_wcom)
    auc_val_lgb_vldiag_wcom <- auc(roc_lgb_vldiag_wcom)
    
    ## SHAP Summary Plot
    shp_lgb_vldiag_wcom <- shapviz(lgb_model_vldiag_wcom, X_pred = train_x_vldiag_wcom, X = as.data.frame(train_x_vldiag_wcom))
     
    list(model = lgb_model_vldiag_wcom, confusion_matrix = cfm_lgb_vldiag_wcom, accuracy_training = accuracy_lgb_vldiag_wcom_train,
         accuracy_testing = accuracy_lgb_vldiag_wcom, sensitivity = sensitivity_lgb_vldiag_wcom, specificity = specificity_lgb_vldiag_wcom,
         precision = prec_lgb_vldiag_wcom, F1_score = f1_sc_lgb_vldiag_wcom, AUC_value = auc_val_lgb_vldiag_wcom,
         SHAP_values = shp_lgb_vldiag_wcom, prediction = lgb_pred_vldiag_wcom_res)
}
```

```{r, Stop CPU clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
lgb_vldiag_wcom_metrics_df <- map_dfr(seq_along(lightgbm_vldiag_wcom_list), function(i) {
  result <- lightgbm_vldiag_wcom_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
lgb_vldiag_wcom_metrics_df <- as.data.frame(lgb_vldiag_wcom_metrics_df)

lgb_vldiag_wcom_metrics_summary <- lgb_vldiag_wcom_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(lgb_vldiag_wcom_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(lgb_vldiag_wcom_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(lgb_vldiag_wcom_metrics_df$sensitivity, 0.025)
low_spec <- quantile(lgb_vldiag_wcom_metrics_df$specificity, 0.025)
low_prec <- quantile(lgb_vldiag_wcom_metrics_df$precision, 0.025)
low_f1_sc <- quantile(lgb_vldiag_wcom_metrics_df$F1_score, 0.025)
low_auc <- quantile(lgb_vldiag_wcom_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(lgb_vldiag_wcom_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(lgb_vldiag_wcom_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(lgb_vldiag_wcom_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(lgb_vldiag_wcom_metrics_df$specificity, 0.975)
upp_prec <- quantile(lgb_vldiag_wcom_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(lgb_vldiag_wcom_metrics_df$F1_score, 0.975)
upp_auc <- quantile(lgb_vldiag_wcom_metrics_df$AUC_value, 0.975)

lgb_vldiag_wcom_metrics_summary['low_acc_train'] <- low_acc_train
lgb_vldiag_wcom_metrics_summary['low_acc_test'] <- low_acc_test
lgb_vldiag_wcom_metrics_summary['low_sens'] <- low_sens
lgb_vldiag_wcom_metrics_summary['low_spec'] <- low_spec
lgb_vldiag_wcom_metrics_summary['low_prec'] <- low_prec
lgb_vldiag_wcom_metrics_summary['low_f1_sc'] <- low_f1_sc
lgb_vldiag_wcom_metrics_summary['low_auc'] <- low_auc

lgb_vldiag_wcom_metrics_summary['upp_acc_train'] <- upp_acc_train
lgb_vldiag_wcom_metrics_summary['upp_acc_test'] <- upp_acc_test
lgb_vldiag_wcom_metrics_summary['upp_sens'] <- upp_sens
lgb_vldiag_wcom_metrics_summary['upp_spec'] <- upp_spec
lgb_vldiag_wcom_metrics_summary['upp_prec'] <- upp_prec
lgb_vldiag_wcom_metrics_summary['upp_f1_sc'] <- upp_f1_sc
lgb_vldiag_wcom_metrics_summary['upp_auc'] <- upp_auc

lgb_vldiag_wcom_metrics_summary
```

# Fitting data excluding Age
## Fitting data without any VL information
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Dataframe excluding Age & VL information}
lightgbm_wvlnage_list <- foreach(i = 1: 100, .packages = c("lightgbm", "pROC", "shapviz")) %dopar% {
    split <- split_list_wvlnage[[i]]
    train_df <- split$train
    test_df <- split$test

    # Convert categorical variables to numeric format using one-hot encoding
    train_x_wvlnage <- model.matrix(outcome ~ ., data = train_df) [, -1]
    test_x_wvlnage <- model.matrix(outcome ~ ., data = test_df) [, -1]

    # Convert data to XGBoost matrix format
    dtrain_wvlnage <- lgb.Dataset(data = train_x_wvlnage, label = as.numeric(as.factor(train_df$outcome)) - 1)
    dtest_wvlnage <- lgb.Dataset(data = test_x_wvlnage, label = as.numeric(as.factor(test_df$outcome)) - 1)

    lgb_model_wvlnage <- lgb.train(data = dtrain_wvlnage,
                      nrounds = 1000,
                      verbose = 0,
                      params = list(
                        objective = "binary")
                      )

    # Make prediction on the testing set
    lgb_pred_wvlnage <- predict(lgb_model_wvlnage, newdata = test_x_wvlnage, type = "response")
    lgb_pred_wvlnage <- ifelse(lgb_pred_wvlnage >= 0.5, 1, 0)
    lgb_pred_wvlnage_res <- ifelse(lgb_pred_wvlnage == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_wvlnage <- table(lgb_pred_wvlnage_res, test_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_wvlnage <- sum(cfm_lgb_wvlnage["Severe", "Severe"], cfm_lgb_wvlnage["Non severe", "Non severe"])/sum(cfm_lgb_wvlnage)
    
    # Make prediction on the training set
    lgb_pred_wvlnage_train <- predict(lgb_model_wvlnage, newdata = train_x_wvlnage, type = "response")
    lgb_pred_wvlnage_train <- ifelse(lgb_pred_wvlnage_train >= 0.5, 1, 0)
    lgb_pred_wvlnage_train_res <- ifelse(lgb_pred_wvlnage_train == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_wvlnage_train <- table(lgb_pred_wvlnage_train_res, train_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_wvlnage_train <- sum(cfm_lgb_wvlnage_train["Severe", "Severe"], cfm_lgb_wvlnage_train["Non severe", "Non severe"])/sum(cfm_lgb_wvlnage_train)

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_lgb_wvlnage["Severe", "Severe"]
    FP <- cfm_lgb_wvlnage["Severe", "Non severe"]
    TN <- cfm_lgb_wvlnage["Non severe", "Non severe"]
    FN <- cfm_lgb_wvlnage["Non severe", "Severe"]

    sensitivity_lgb_wvlnage <- TP / (TP + FN)
    specificity_lgb_wvlnage <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_lgb_wvlnage <- TP / (TP + FP)
    f1_sc_lgb_wvlnage <- 2 * ((prec_lgb_wvlnage * sensitivity_lgb_wvlnage) / (prec_lgb_wvlnage + sensitivity_lgb_wvlnage))

    # Compute AUROC
    roc_lgb_wvlnage <- roc(test_df$outcome, lgb_pred_wvlnage)
    auc_val_lgb_wvlnage <- auc(roc_lgb_wvlnage)
    
    ## SHAP Summary
    shp_lgb_wvlnage <- shapviz(lgb_model_wvlnage, X_pred = train_x_wvlnage, X = as.data.frame(train_x_wvlnage))
    
    list(model = lgb_model_wvlnage, confusion_matrix = cfm_lgb_wvlnage, accuracy_training = accuracy_lgb_wvlnage_train,
         accuracy_testing = accuracy_lgb_wvlnage, sensitivity = sensitivity_lgb_wvlnage, specificity = specificity_lgb_wvlnage,
         precision = prec_lgb_wvlnage, F1_score = f1_sc_lgb_wvlnage, AUC_value = auc_val_lgb_wvlnage, SHAP_values = shp_lgb_wvlnage,
         prediction = lgb_pred_wvlnage_res)
}
```

```{r, Stop CPU clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
lgb_wvlnage_metrics_df <- map_dfr(seq_along(lightgbm_wvlnage_list), function(i) {
  result <- lightgbm_wvlnage_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
lgb_wvlnage_metrics_df <- as.data.frame(lgb_wvlnage_metrics_df)

lgb_wvlnage_metrics_summary <- lgb_wvlnage_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(lgb_wvlnage_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(lgb_wvlnage_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(lgb_wvlnage_metrics_df$sensitivity, 0.025)
low_spec <- quantile(lgb_wvlnage_metrics_df$specificity, 0.025)
low_prec <- quantile(lgb_wvlnage_metrics_df$precision, 0.025)
low_f1_sc <- quantile(lgb_wvlnage_metrics_df$F1_score, 0.025)
low_auc <- quantile(lgb_wvlnage_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(lgb_wvlnage_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(lgb_wvlnage_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(lgb_wvlnage_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(lgb_wvlnage_metrics_df$specificity, 0.975)
upp_prec <- quantile(lgb_wvlnage_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(lgb_wvlnage_metrics_df$F1_score, 0.975)
upp_auc <- quantile(lgb_wvlnage_metrics_df$AUC_value, 0.975)

lgb_wvlnage_metrics_summary['low_acc_train'] <- low_acc_train
lgb_wvlnage_metrics_summary['low_acc_test'] <- low_acc_test
lgb_wvlnage_metrics_summary['low_sens'] <- low_sens
lgb_wvlnage_metrics_summary['low_spec'] <- low_spec
lgb_wvlnage_metrics_summary['low_prec'] <- low_prec
lgb_wvlnage_metrics_summary['low_f1_sc'] <- low_f1_sc
lgb_wvlnage_metrics_summary['low_auc'] <- low_auc

lgb_wvlnage_metrics_summary['upp_acc_train'] <- upp_acc_train
lgb_wvlnage_metrics_summary['upp_acc_test'] <- upp_acc_test
lgb_wvlnage_metrics_summary['upp_sens'] <- upp_sens
lgb_wvlnage_metrics_summary['upp_spec'] <- upp_spec
lgb_wvlnage_metrics_summary['upp_prec'] <- upp_prec
lgb_wvlnage_metrics_summary['upp_f1_sc'] <- upp_f1_sc
lgb_wvlnage_metrics_summary['upp_auc'] <- upp_auc

lgb_wvlnage_metrics_summary
```

## Fitting data with VL since symptom onset
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Dataframe excluding Age & with VL since symptom onset}
lightgbm_vlsymp_wage_list <- foreach(i = 1: 100, .packages = c("lightgbm", "pROC", "shapviz")) %dopar% {
    split <- split_list_vlsim_symp_wage[[i]]
    train_df <- split$train
    test_df <- split$test

    # Convert categorical variables to numeric format using one-hot encoding
    train_x_vlsymp_wage <- model.matrix(outcome ~ ., data = train_df) [, -1]
    test_x_vlsymp_wage <- model.matrix(outcome ~ ., data = test_df) [, -1]

    # Convert data to XGBoost matrix format
    dtrain_vlsymp_wage <- lgb.Dataset(data = train_x_vlsymp_wage, label = as.numeric(as.factor(train_df$outcome)) - 1)
    dtest_vlsymp_wage <- lgb.Dataset(data = test_x_vlsymp_wage, label = as.numeric(as.factor(test_df$outcome)) - 1)

    lgb_model_vlsymp_wage <- lgb.train(data = dtrain_vlsymp_wage,
                      nrounds = 1000,
                      verbose = 0,
                      params = list(
                        objective = "binary")
                      )

    # Make prediction on the testing set
    lgb_pred_vlsymp_wage <- predict(lgb_model_vlsymp_wage, newdata = test_x_vlsymp_wage, type = "response")
    lgb_pred_vlsymp_wage <- ifelse(lgb_pred_vlsymp_wage >= 0.5, 1, 0)
    lgb_pred_vlsymp_wage_res <- ifelse(lgb_pred_vlsymp_wage == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_vlsymp_wage <- table(lgb_pred_vlsymp_wage_res, test_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_vlsymp_wage <- sum(cfm_lgb_vlsymp_wage["Severe", "Severe"], cfm_lgb_vlsymp_wage["Non severe", "Non severe"])/sum(cfm_lgb_vlsymp_wage)
    
    # Make prediction on the training set
    lgb_pred_vlsymp_wage_train <- predict(lgb_model_vlsymp_wage, newdata = train_x_vlsymp_wage, type = "response")
    lgb_pred_vlsymp_wage_train <- ifelse(lgb_pred_vlsymp_wage_train >= 0.5, 1, 0)
    lgb_pred_vlsymp_wage_train_res <- ifelse(lgb_pred_vlsymp_wage_train == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_vlsymp_wage_train <- table(lgb_pred_vlsymp_wage_train_res, train_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_vlsymp_wage_train <- sum(cfm_lgb_vlsymp_wage_train["Severe", "Severe"], cfm_lgb_vlsymp_wage_train["Non severe", "Non severe"])/sum(cfm_lgb_vlsymp_wage_train)

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_lgb_vlsymp_wage["Severe", "Severe"]
    FP <- cfm_lgb_vlsymp_wage["Severe", "Non severe"]
    TN <- cfm_lgb_vlsymp_wage["Non severe", "Non severe"]
    FN <- cfm_lgb_vlsymp_wage["Non severe", "Severe"]

    sensitivity_lgb_vlsymp_wage <- TP / (TP + FN)
    specificity_lgb_vlsymp_wage <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_lgb_vlsymp_wage <- TP / (TP + FP)
    f1_sc_lgb_vlsymp_wage <- 2 * ((prec_lgb_vlsymp_wage * sensitivity_lgb_vlsymp_wage) / (prec_lgb_vlsymp_wage + sensitivity_lgb_vlsymp_wage))

    # Compute AUROC
    roc_lgb_vlsymp_wage <- roc(test_df$outcome, lgb_pred_vlsymp_wage)
    auc_val_lgb_vlsymp_wage <- auc(roc_lgb_vlsymp_wage)
    
    ## SHAP Summary
    shp_lgb_vlsymp_wage <- shapviz(lgb_model_vlsymp_wage, X_pred = train_x_vlsymp_wage, X = as.data.frame(train_x_vlsymp_wage))
    
    list(model = lgb_model_vlsymp_wage, confusion_matrix = cfm_lgb_vlsymp_wage, accuracy_training = accuracy_lgb_vlsymp_wage_train,
         accuracy_testing = accuracy_lgb_vlsymp_wage, sensitivity = sensitivity_lgb_vlsymp_wage, specificity = specificity_lgb_vlsymp_wage,
         precision = prec_lgb_vlsymp_wage, F1_score = f1_sc_lgb_vlsymp_wage, AUC_value = auc_val_lgb_vlsymp_wage,
         SHAP_values = shp_lgb_vlsymp_wage, prediction = lgb_pred_vlsymp_wage_res)
}
```

```{r, Stop CPU clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
lgb_vlsymp_wage_metrics_df <- map_dfr(seq_along(lightgbm_vlsymp_wage_list), function(i) {
  result <- lightgbm_vlsymp_wage_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
lgb_vlsymp_wage_metrics_df <- as.data.frame(lgb_vlsymp_wage_metrics_df)

lgb_vlsymp_wage_metrics_summary <- lgb_vlsymp_wage_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(lgb_vlsymp_wage_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(lgb_vlsymp_wage_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(lgb_vlsymp_wage_metrics_df$sensitivity, 0.025)
low_spec <- quantile(lgb_vlsymp_wage_metrics_df$specificity, 0.025)
low_prec <- quantile(lgb_vlsymp_wage_metrics_df$precision, 0.025)
low_f1_sc <- quantile(lgb_vlsymp_wage_metrics_df$F1_score, 0.025)
low_auc <- quantile(lgb_vlsymp_wage_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(lgb_vlsymp_wage_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(lgb_vlsymp_wage_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(lgb_vlsymp_wage_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(lgb_vlsymp_wage_metrics_df$specificity, 0.975)
upp_prec <- quantile(lgb_vlsymp_wage_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(lgb_vlsymp_wage_metrics_df$F1_score, 0.975)
upp_auc <- quantile(lgb_vlsymp_wage_metrics_df$AUC_value, 0.975)

lgb_vlsymp_wage_metrics_summary['low_acc_train'] <- low_acc_train
lgb_vlsymp_wage_metrics_summary['low_acc_test'] <- low_acc_test
lgb_vlsymp_wage_metrics_summary['low_sens'] <- low_sens
lgb_vlsymp_wage_metrics_summary['low_spec'] <- low_spec
lgb_vlsymp_wage_metrics_summary['low_prec'] <- low_prec
lgb_vlsymp_wage_metrics_summary['low_f1_sc'] <- low_f1_sc
lgb_vlsymp_wage_metrics_summary['low_auc'] <- low_auc

lgb_vlsymp_wage_metrics_summary['upp_acc_train'] <- upp_acc_train
lgb_vlsymp_wage_metrics_summary['upp_acc_test'] <- upp_acc_test
lgb_vlsymp_wage_metrics_summary['upp_sens'] <- upp_sens
lgb_vlsymp_wage_metrics_summary['upp_spec'] <- upp_spec
lgb_vlsymp_wage_metrics_summary['upp_prec'] <- upp_prec
lgb_vlsymp_wage_metrics_summary['upp_f1_sc'] <- upp_f1_sc
lgb_vlsymp_wage_metrics_summary['upp_auc'] <- upp_auc

lgb_vlsymp_wage_metrics_summary
```

## Fitting data with VL at diagnosis
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Dataframe excluding Age & with VL at diagnosis}
lightgbm_vldiag_wage_list <- foreach(i = 1: 100, .packages = c("lightgbm", "pROC", "shapviz")) %dopar% {
    split <- split_list_vldiag_wage[[i]]
    train_df <- split$train
    test_df <- split$test

    # Convert categorical variables to numeric format using one-hot encoding
    train_x_vldiag_wage <- model.matrix(outcome ~ ., data = train_df) [, -1]
    test_x_vldiag_wage <- model.matrix(outcome ~ ., data = test_df) [, -1]

    # Convert data to XGBoost matrix format
    dtrain_vldiag_wage <- lgb.Dataset(data = train_x_vldiag_wage, label = as.numeric(as.factor(train_df$outcome)) - 1)
    dtest_vldiag_wage <- lgb.Dataset(data = test_x_vldiag_wage, label = as.numeric(as.factor(test_df$outcome)) - 1)

    lgb_model_vldiag_wage <- lgb.train(data = dtrain_vldiag_wage,
                      nrounds = 1000,
                      verbose = 0,
                      params = list(
                        objective = "binary")
                      )

    # Make prediction on the testing set
    lgb_pred_vldiag_wage <- predict(lgb_model_vldiag_wage, newdata = test_x_vldiag_wage, type = "response")
    lgb_pred_vldiag_wage <- ifelse(lgb_pred_vldiag_wage >= 0.5, 1, 0)
    lgb_pred_vldiag_wage_res <- ifelse(lgb_pred_vldiag_wage == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_vldiag_wage <- table(lgb_pred_vldiag_wage_res, test_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_vldiag_wage <- sum(cfm_lgb_vldiag_wage["Severe", "Severe"], cfm_lgb_vldiag_wage["Non severe", "Non severe"])/sum(cfm_lgb_vldiag_wage)
    
    # Make prediction on the training set
    lgb_pred_vldiag_wage_train <- predict(lgb_model_vldiag_wage, newdata = train_x_vldiag_wage, type = "response")
    lgb_pred_vldiag_wage_train <- ifelse(lgb_pred_vldiag_wage_train >= 0.5, 1, 0)
    lgb_pred_vldiag_wage_train_res <- ifelse(lgb_pred_vldiag_wage_train == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_vldiag_wage_train <- table(lgb_pred_vldiag_wage_train_res, train_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_vldiag_wage_train <- sum(cfm_lgb_vldiag_wage_train["Severe", "Severe"], cfm_lgb_vldiag_wage_train["Non severe", "Non severe"])/sum(cfm_lgb_vldiag_wage_train)

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_lgb_vldiag_wage["Severe", "Severe"]
    FP <- cfm_lgb_vldiag_wage["Severe", "Non severe"]
    TN <- cfm_lgb_vldiag_wage["Non severe", "Non severe"]
    FN <- cfm_lgb_vldiag_wage["Non severe", "Severe"]

    sensitivity_lgb_vldiag_wage <- TP / (TP + FN)
    specificity_lgb_vldiag_wage <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_lgb_vldiag_wage <- TP / (TP + FP)
    f1_sc_lgb_vldiag_wage <- 2 * ((prec_lgb_vldiag_wage * sensitivity_lgb_vldiag_wage) / (prec_lgb_vldiag_wage + sensitivity_lgb_vldiag_wage))

    # Compute AUROC
    roc_lgb_vldiag_wage <- roc(test_df$outcome, lgb_pred_vldiag_wage)
    auc_val_lgb_vldiag_wage <- auc(roc_lgb_vldiag_wage)
    
    ## SHAP Summary
    shp_lgb_vldiag_wage <- shapviz(lgb_model_vldiag_wage, X_pred = train_x_vldiag_wage, X = as.data.frame(train_x_vldiag_wage))
    
    list(model = lgb_model_vldiag_wage, confusion_matrix = cfm_lgb_vldiag_wage, accuracy_training = accuracy_lgb_vldiag_wage_train,
         accuracy_testing = accuracy_lgb_vldiag_wage, sensitivity = sensitivity_lgb_vldiag_wage, specificity = specificity_lgb_vldiag_wage,
         precision = prec_lgb_vldiag_wage, F1_score = f1_sc_lgb_vldiag_wage, AUC_value = auc_val_lgb_vldiag_wage,
         SHAP_values = shp_lgb_vldiag_wage, prediction = lgb_pred_vldiag_wage_res)
}
```

```{r, Stop CPU clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
lgb_vldiag_wage_metrics_df <- map_dfr(seq_along(lightgbm_vldiag_wage_list), function(i) {
  result <- lightgbm_vldiag_wage_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
lgb_vldiag_wage_metrics_df <- as.data.frame(lgb_vldiag_wage_metrics_df)

lgb_vldiag_wage_metrics_summary <- lgb_vldiag_wage_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(lgb_vldiag_wage_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(lgb_vldiag_wage_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(lgb_vldiag_wage_metrics_df$sensitivity, 0.025)
low_spec <- quantile(lgb_vldiag_wage_metrics_df$specificity, 0.025)
low_prec <- quantile(lgb_vldiag_wage_metrics_df$precision, 0.025)
low_f1_sc <- quantile(lgb_vldiag_wage_metrics_df$F1_score, 0.025)
low_auc <- quantile(lgb_vldiag_wage_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(lgb_vldiag_wage_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(lgb_vldiag_wage_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(lgb_vldiag_wage_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(lgb_vldiag_wage_metrics_df$specificity, 0.975)
upp_prec <- quantile(lgb_vldiag_wage_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(lgb_vldiag_wage_metrics_df$F1_score, 0.975)
upp_auc <- quantile(lgb_vldiag_wage_metrics_df$AUC_value, 0.975)

lgb_vldiag_wage_metrics_summary['low_acc_train'] <- low_acc_train
lgb_vldiag_wage_metrics_summary['low_acc_test'] <- low_acc_test
lgb_vldiag_wage_metrics_summary['low_sens'] <- low_sens
lgb_vldiag_wage_metrics_summary['low_spec'] <- low_spec
lgb_vldiag_wage_metrics_summary['low_prec'] <- low_prec
lgb_vldiag_wage_metrics_summary['low_f1_sc'] <- low_f1_sc
lgb_vldiag_wage_metrics_summary['low_auc'] <- low_auc

lgb_vldiag_wage_metrics_summary['upp_acc_train'] <- upp_acc_train
lgb_vldiag_wage_metrics_summary['upp_acc_test'] <- upp_acc_test
lgb_vldiag_wage_metrics_summary['upp_sens'] <- upp_sens
lgb_vldiag_wage_metrics_summary['upp_spec'] <- upp_spec
lgb_vldiag_wage_metrics_summary['upp_prec'] <- upp_prec
lgb_vldiag_wage_metrics_summary['upp_f1_sc'] <- upp_f1_sc
lgb_vldiag_wage_metrics_summary['upp_auc'] <- upp_auc

lgb_vldiag_wage_metrics_summary
```

# Fitting data excluding Comorbidity & Age
## Fitting data without any VL information
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Dataframe excluding Comorbidity, Age & VL information}
lightgbm_wvlnagecom_list <- foreach(i = 1: 100, .packages = c("lightgbm", "pROC", "shapviz")) %dopar% {
    split <- split_list_wvlnagecom[[i]]
    train_df <- split$train
    test_df <- split$test

    # Convert categorical variables to numeric format using one-hot encoding
    train_x_wvlnagecom <- model.matrix(outcome ~ ., data = train_df) [, -1]
    test_x_wvlnagecom <- model.matrix(outcome ~ ., data = test_df) [, -1]

    # Convert data to XGBoost matrix format
    dtrain_wvlnagecom <- lgb.Dataset(data = train_x_wvlnagecom, label = as.numeric(as.factor(train_df$outcome)) - 1)
    dtest_wvlnagecom <- lgb.Dataset(data = test_x_wvlnagecom, label = as.numeric(as.factor(test_df$outcome)) - 1)

    lgb_model_wvlnagecom <- lgb.train(data = dtrain_wvlnagecom,
                      nrounds = 1000,
                      verbose = 0,
                      params = list(
                        objective = "binary")
                      )

    # Make prediction on the testing set
    lgb_pred_wvlnagecom <- predict(lgb_model_wvlnagecom, newdata = test_x_wvlnagecom, type = "response")
    lgb_pred_wvlnagecom <- ifelse(lgb_pred_wvlnagecom >= 0.5, 1, 0)
    lgb_pred_wvlnagecom_res <- ifelse(lgb_pred_wvlnagecom == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_wvlnagecom <- table(lgb_pred_wvlnagecom_res, test_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_wvlnagecom <- sum(cfm_lgb_wvlnagecom["Severe", "Severe"], cfm_lgb_wvlnagecom["Non severe", "Non severe"])/sum(cfm_lgb_wvlnagecom)
    
    # Make prediction on the training set
    lgb_pred_wvlnagecom_train <- predict(lgb_model_wvlnagecom, newdata = train_x_wvlnagecom, type = "response")
    lgb_pred_wvlnagecom_train <- ifelse(lgb_pred_wvlnagecom_train >= 0.5, 1, 0)
    lgb_pred_wvlnagecom_train_res <- ifelse(lgb_pred_wvlnagecom_train == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_wvlnagecom_train <- table(lgb_pred_wvlnagecom_train_res, train_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_wvlnagecom_train <- sum(cfm_lgb_wvlnagecom_train["Severe", "Severe"], cfm_lgb_wvlnagecom_train["Non severe", "Non severe"])/sum(cfm_lgb_wvlnagecom_train)

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_lgb_wvlnagecom["Severe", "Severe"]
    FP <- cfm_lgb_wvlnagecom["Severe", "Non severe"]
    TN <- cfm_lgb_wvlnagecom["Non severe", "Non severe"]
    FN <- cfm_lgb_wvlnagecom["Non severe", "Severe"]

    sensitivity_lgb_wvlnagecom <- TP / (TP + FN)
    specificity_lgb_wvlnagecom <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_lgb_wvlnagecom <- TP / (TP + FP)
    f1_sc_lgb_wvlnagecom <- 2 * ((prec_lgb_wvlnagecom * sensitivity_lgb_wvlnagecom) / (prec_lgb_wvlnagecom + sensitivity_lgb_wvlnagecom))

    # Compute AUROC
    roc_lgb_wvlnagecom <- roc(test_df$outcome, lgb_pred_wvlnagecom)
    auc_val_lgb_wvlnagecom <- auc(roc_lgb_wvlnagecom)
    
    ## SHAP Summary
    shp_lgb_wvlnagecom <- shapviz(lgb_model_wvlnagecom, X_pred = train_x_wvlnagecom, X = as.data.frame(train_x_wvlnagecom))
    
    list(model = lgb_model_wvlnagecom, confusion_matrix = cfm_lgb_wvlnagecom, accuracy_training = accuracy_lgb_wvlnagecom_train,
         accuracy_testing = accuracy_lgb_wvlnagecom, sensitivity = sensitivity_lgb_wvlnagecom, specificity = specificity_lgb_wvlnagecom,
         precision = prec_lgb_wvlnagecom, F1_score = f1_sc_lgb_wvlnagecom, AUC_value = auc_val_lgb_wvlnagecom, SHAP_values = shp_lgb_wvlnagecom,
         prediction = lgb_pred_wvlnagecom_res)
}
```

```{r, Stop CPU clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
lgb_wvlnagecom_metrics_df <- map_dfr(seq_along(lightgbm_wvlnagecom_list), function(i) {
  result <- lightgbm_wvlnagecom_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
lgb_wvlnagecom_metrics_df <- as.data.frame(lgb_wvlnagecom_metrics_df)

lgb_wvlnagecom_metrics_summary <- lgb_wvlnagecom_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(lgb_wvlnagecom_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(lgb_wvlnagecom_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(lgb_wvlnagecom_metrics_df$sensitivity, 0.025)
low_spec <- quantile(lgb_wvlnagecom_metrics_df$specificity, 0.025)
low_prec <- quantile(lgb_wvlnagecom_metrics_df$precision, 0.025)
low_f1_sc <- quantile(lgb_wvlnagecom_metrics_df$F1_score, 0.025)
low_auc <- quantile(lgb_wvlnagecom_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(lgb_wvlnagecom_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(lgb_wvlnagecom_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(lgb_wvlnagecom_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(lgb_wvlnagecom_metrics_df$specificity, 0.975)
upp_prec <- quantile(lgb_wvlnagecom_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(lgb_wvlnagecom_metrics_df$F1_score, 0.975)
upp_auc <- quantile(lgb_wvlnagecom_metrics_df$AUC_value, 0.975)

lgb_wvlnagecom_metrics_summary['low_acc_train'] <- low_acc_train
lgb_wvlnagecom_metrics_summary['low_acc_test'] <- low_acc_test
lgb_wvlnagecom_metrics_summary['low_sens'] <- low_sens
lgb_wvlnagecom_metrics_summary['low_spec'] <- low_spec
lgb_wvlnagecom_metrics_summary['low_prec'] <- low_prec
lgb_wvlnagecom_metrics_summary['low_f1_sc'] <- low_f1_sc
lgb_wvlnagecom_metrics_summary['low_auc'] <- low_auc

lgb_wvlnagecom_metrics_summary['upp_acc_train'] <- upp_acc_train
lgb_wvlnagecom_metrics_summary['upp_acc_test'] <- upp_acc_test
lgb_wvlnagecom_metrics_summary['upp_sens'] <- upp_sens
lgb_wvlnagecom_metrics_summary['upp_spec'] <- upp_spec
lgb_wvlnagecom_metrics_summary['upp_prec'] <- upp_prec
lgb_wvlnagecom_metrics_summary['upp_f1_sc'] <- upp_f1_sc
lgb_wvlnagecom_metrics_summary['upp_auc'] <- upp_auc

lgb_wvlnagecom_metrics_summary
```

## Fitting data with VL since symptom onset
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Dataframe excluding Comorbidity, Age & with VL since symptom onset}
lightgbm_vlsymp_wagecom_list <- foreach(i = 1: 100, .packages = c("lightgbm", "pROC", "shapviz")) %dopar% {
    split <- split_list_vlsim_symp_wagecom[[i]]
    train_df <- split$train
    test_df <- split$test

    # Convert categorical variables to numeric format using one-hot encoding
    train_x_vlsymp_wagecom <- model.matrix(outcome ~ ., data = train_df) [, -1]
    test_x_vlsymp_wagecom <- model.matrix(outcome ~ ., data = test_df) [, -1]

    # Convert data to XGBoost matrix format
    dtrain_vlsymp_wagecom <- lgb.Dataset(data = train_x_vlsymp_wagecom, label = as.numeric(as.factor(train_df$outcome)) - 1)
    dtest_vlsymp_wagecom <- lgb.Dataset(data = test_x_vlsymp_wagecom, label = as.numeric(as.factor(test_df$outcome)) - 1)

    lgb_model_vlsymp_wagecom <- lgb.train(data = dtrain_vlsymp_wagecom,
                      nrounds = 1000,
                      verbose = 0,
                      params = list(
                        objective = "binary")
                      )

    # Make prediction on the testing set
    lgb_pred_vlsymp_wagecom <- predict(lgb_model_vlsymp_wagecom, newdata = test_x_vlsymp_wagecom, type = "response")
    lgb_pred_vlsymp_wagecom <- ifelse(lgb_pred_vlsymp_wagecom >= 0.5, 1, 0)
    lgb_pred_vlsymp_wagecom_res <- ifelse(lgb_pred_vlsymp_wagecom == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_vlsymp_wagecom <- table(lgb_pred_vlsymp_wagecom_res, test_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_vlsymp_wagecom <- sum(cfm_lgb_vlsymp_wagecom["Severe", "Severe"], cfm_lgb_vlsymp_wagecom["Non severe", "Non severe"])/sum(cfm_lgb_vlsymp_wagecom)
    
    # Make prediction on the training set
    lgb_pred_vlsymp_wagecom_train <- predict(lgb_model_vlsymp_wagecom, newdata = train_x_vlsymp_wagecom, type = "response")
    lgb_pred_vlsymp_wagecom_train <- ifelse(lgb_pred_vlsymp_wagecom_train >= 0.5, 1, 0)
    lgb_pred_vlsymp_wagecom_train_res <- ifelse(lgb_pred_vlsymp_wagecom_train == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_vlsymp_wagecom_train <- table(lgb_pred_vlsymp_wagecom_train_res, train_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_vlsymp_wagecom_train <- sum(cfm_lgb_vlsymp_wagecom_train["Severe", "Severe"], cfm_lgb_vlsymp_wagecom_train["Non severe", "Non severe"])/sum(cfm_lgb_vlsymp_wagecom_train)

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_lgb_vlsymp_wagecom["Severe", "Severe"]
    FP <- cfm_lgb_vlsymp_wagecom["Severe", "Non severe"]
    TN <- cfm_lgb_vlsymp_wagecom["Non severe", "Non severe"]
    FN <- cfm_lgb_vlsymp_wagecom["Non severe", "Severe"]

    sensitivity_lgb_vlsymp_wagecom <- TP / (TP + FN)
    specificity_lgb_vlsymp_wagecom <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_lgb_vlsymp_wagecom <- TP / (TP + FP)
    f1_sc_lgb_vlsymp_wagecom <- 2 * ((prec_lgb_vlsymp_wagecom * sensitivity_lgb_vlsymp_wagecom) / (prec_lgb_vlsymp_wagecom + sensitivity_lgb_vlsymp_wagecom))

    # Compute AUROC
    roc_lgb_vlsymp_wagecom <- roc(test_df$outcome, lgb_pred_vlsymp_wagecom)
    auc_val_lgb_vlsymp_wagecom <- auc(roc_lgb_vlsymp_wagecom)
    
    ## SHAP Summary
    shp_lgb_vlsymp_wagecom <- shapviz(lgb_model_vlsymp_wagecom, X_pred = train_x_vlsymp_wagecom, X = as.data.frame(train_x_vlsymp_wagecom))
    
    list(model = lgb_model_vlsymp_wagecom, confusion_matrix = cfm_lgb_vlsymp_wagecom, accuracy_training = accuracy_lgb_vlsymp_wagecom_train,
         accuracy_testing = accuracy_lgb_vlsymp_wagecom, sensitivity = sensitivity_lgb_vlsymp_wagecom,
         specificity = specificity_lgb_vlsymp_wagecom, precision = prec_lgb_vlsymp_wagecom, F1_score = f1_sc_lgb_vlsymp_wagecom,
         AUC_value = auc_val_lgb_vlsymp_wagecom, SHAP_values = shp_lgb_vlsymp_wagecom, prediction = lgb_pred_vlsymp_wagecom_res)
}
```

```{r, Stop CPU clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
lgb_vlsymp_wagecom_metrics_df <- map_dfr(seq_along(lightgbm_vlsymp_wagecom_list), function(i) {
  result <- lightgbm_vlsymp_wagecom_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
lgb_vlsymp_wagecom_metrics_df <- as.data.frame(lgb_vlsymp_wagecom_metrics_df)

lgb_vlsymp_wagecom_metrics_summary <- lgb_vlsymp_wagecom_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(lgb_vlsymp_wagecom_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(lgb_vlsymp_wagecom_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(lgb_vlsymp_wagecom_metrics_df$sensitivity, 0.025)
low_spec <- quantile(lgb_vlsymp_wagecom_metrics_df$specificity, 0.025)
low_prec <- quantile(lgb_vlsymp_wagecom_metrics_df$precision, 0.025)
low_f1_sc <- quantile(lgb_vlsymp_wagecom_metrics_df$F1_score, 0.025)
low_auc <- quantile(lgb_vlsymp_wagecom_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(lgb_vlsymp_wagecom_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(lgb_vlsymp_wagecom_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(lgb_vlsymp_wagecom_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(lgb_vlsymp_wagecom_metrics_df$specificity, 0.975)
upp_prec <- quantile(lgb_vlsymp_wagecom_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(lgb_vlsymp_wagecom_metrics_df$F1_score, 0.975)
upp_auc <- quantile(lgb_vlsymp_wagecom_metrics_df$AUC_value, 0.975)

lgb_vlsymp_wagecom_metrics_summary['low_acc_train'] <- low_acc_train
lgb_vlsymp_wagecom_metrics_summary['low_acc_test'] <- low_acc_test
lgb_vlsymp_wagecom_metrics_summary['low_sens'] <- low_sens
lgb_vlsymp_wagecom_metrics_summary['low_spec'] <- low_spec
lgb_vlsymp_wagecom_metrics_summary['low_prec'] <- low_prec
lgb_vlsymp_wagecom_metrics_summary['low_f1_sc'] <- low_f1_sc
lgb_vlsymp_wagecom_metrics_summary['low_auc'] <- low_auc

lgb_vlsymp_wagecom_metrics_summary['upp_acc_train'] <- upp_acc_train
lgb_vlsymp_wagecom_metrics_summary['upp_acc_test'] <- upp_acc_test
lgb_vlsymp_wagecom_metrics_summary['upp_sens'] <- upp_sens
lgb_vlsymp_wagecom_metrics_summary['upp_spec'] <- upp_spec
lgb_vlsymp_wagecom_metrics_summary['upp_prec'] <- upp_prec
lgb_vlsymp_wagecom_metrics_summary['upp_f1_sc'] <- upp_f1_sc
lgb_vlsymp_wagecom_metrics_summary['upp_auc'] <- upp_auc

lgb_vlsymp_wagecom_metrics_summary
```

## Fitting data with VL at diagnosis
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Dataframe excluding Comorbidity, Age & with VL at diagnosis}
lightgbm_vldiag_wagecom_list <- foreach(i = 1: 100, .packages = c("lightgbm", "pROC", "shapviz")) %dopar% {
    split <- split_list_vldiag_wagecom[[i]]
    train_df <- split$train
    test_df <- split$test

    # Convert categorical variables to numeric format using one-hot encoding
    train_x_vldiag_wagecom <- model.matrix(outcome ~ ., data = train_df) [, -1]
    test_x_vldiag_wagecom <- model.matrix(outcome ~ ., data = test_df) [, -1]

    # Convert data to XGBoost matrix format
    dtrain_vldiag_wagecom <- lgb.Dataset(data = train_x_vldiag_wagecom, label = as.numeric(as.factor(train_df$outcome)) - 1)
    dtest_vldiag_wagecom <- lgb.Dataset(data = test_x_vldiag_wagecom, label = as.numeric(as.factor(test_df$outcome)) - 1)

    lgb_model_vldiag_wagecom <- lgb.train(data = dtrain_vldiag_wagecom,
                      nrounds = 1000,
                      verbose = 0,
                      params = list(
                        objective = "binary")
                      )

    # Make prediction on the testing set
    lgb_pred_vldiag_wagecom <- predict(lgb_model_vldiag_wagecom, newdata = test_x_vldiag_wagecom, type = "response")
    lgb_pred_vldiag_wagecom <- ifelse(lgb_pred_vldiag_wagecom >= 0.5, 1, 0)
    lgb_pred_vldiag_wagecom_res <- ifelse(lgb_pred_vldiag_wagecom == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_vldiag_wagecom <- table(lgb_pred_vldiag_wagecom_res, test_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_vldiag_wagecom <- sum(cfm_lgb_vldiag_wagecom["Severe", "Severe"], cfm_lgb_vldiag_wagecom["Non severe", "Non severe"])/sum(cfm_lgb_vldiag_wagecom)
    
    # Make prediction on the training set
    lgb_pred_vldiag_wagecom_train <- predict(lgb_model_vldiag_wagecom, newdata = train_x_vldiag_wagecom, type = "response")
    lgb_pred_vldiag_wagecom_train <- ifelse(lgb_pred_vldiag_wagecom_train >= 0.5, 1, 0)
    lgb_pred_vldiag_wagecom_train_res <- ifelse(lgb_pred_vldiag_wagecom_train == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_vldiag_wagecom_train <- table(lgb_pred_vldiag_wagecom_train_res, train_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_vldiag_wagecom_train <- sum(cfm_lgb_vldiag_wagecom_train["Severe", "Severe"], cfm_lgb_vldiag_wagecom_train["Non severe", "Non severe"])/sum(cfm_lgb_vldiag_wagecom_train)

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_lgb_vldiag_wagecom["Severe", "Severe"]
    FP <- cfm_lgb_vldiag_wagecom["Severe", "Non severe"]
    TN <- cfm_lgb_vldiag_wagecom["Non severe", "Non severe"]
    FN <- cfm_lgb_vldiag_wagecom["Non severe", "Severe"]

    sensitivity_lgb_vldiag_wagecom <- TP / (TP + FN)
    specificity_lgb_vldiag_wagecom <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_lgb_vldiag_wagecom <- TP / (TP + FP)
    f1_sc_lgb_vldiag_wagecom <- 2 * ((prec_lgb_vldiag_wagecom * sensitivity_lgb_vldiag_wagecom) / (prec_lgb_vldiag_wagecom + sensitivity_lgb_vldiag_wagecom))

    # Compute AUROC
    roc_lgb_vldiag_wagecom <- roc(test_df$outcome, lgb_pred_vldiag_wagecom)
    auc_val_lgb_vldiag_wagecom <- auc(roc_lgb_vldiag_wagecom)
    
    ## SHAP Summary
    shp_lgb_vldiag_wagecom <- shapviz(lgb_model_vldiag_wagecom, X_pred = train_x_vldiag_wagecom, X = as.data.frame(train_x_vldiag_wagecom))
    
    list(model = lgb_model_vldiag_wagecom, confusion_matrix = cfm_lgb_vldiag_wagecom, accuracy_training = accuracy_lgb_vldiag_wagecom_train,
         accuracy_testing = accuracy_lgb_vldiag_wagecom, sensitivity = sensitivity_lgb_vldiag_wagecom,
         specificity = specificity_lgb_vldiag_wagecom, precision = prec_lgb_vldiag_wagecom, F1_score = f1_sc_lgb_vldiag_wagecom,
         AUC_value = auc_val_lgb_vldiag_wagecom, SHAP_values = shp_lgb_vldiag_wagecom, prediction = lgb_pred_vldiag_wagecom_res)
}
```

```{r, Stop CPU clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
lgb_vldiag_wagecom_metrics_df <- map_dfr(seq_along(lightgbm_vldiag_wagecom_list), function(i) {
  result <- lightgbm_vldiag_wagecom_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
lgb_vldiag_wagecom_metrics_df <- as.data.frame(lgb_vldiag_wagecom_metrics_df)

lgb_vldiag_wagecom_metrics_summary <- lgb_vldiag_wagecom_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(lgb_vldiag_wagecom_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(lgb_vldiag_wagecom_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(lgb_vldiag_wagecom_metrics_df$sensitivity, 0.025)
low_spec <- quantile(lgb_vldiag_wagecom_metrics_df$specificity, 0.025)
low_prec <- quantile(lgb_vldiag_wagecom_metrics_df$precision, 0.025)
low_f1_sc <- quantile(lgb_vldiag_wagecom_metrics_df$F1_score, 0.025)
low_auc <- quantile(lgb_vldiag_wagecom_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(lgb_vldiag_wagecom_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(lgb_vldiag_wagecom_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(lgb_vldiag_wagecom_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(lgb_vldiag_wagecom_metrics_df$specificity, 0.975)
upp_prec <- quantile(lgb_vldiag_wagecom_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(lgb_vldiag_wagecom_metrics_df$F1_score, 0.975)
upp_auc <- quantile(lgb_vldiag_wagecom_metrics_df$AUC_value, 0.975)

lgb_vldiag_wagecom_metrics_summary['low_acc_train'] <- low_acc_train
lgb_vldiag_wagecom_metrics_summary['low_acc_test'] <- low_acc_test
lgb_vldiag_wagecom_metrics_summary['low_sens'] <- low_sens
lgb_vldiag_wagecom_metrics_summary['low_spec'] <- low_spec
lgb_vldiag_wagecom_metrics_summary['low_prec'] <- low_prec
lgb_vldiag_wagecom_metrics_summary['low_f1_sc'] <- low_f1_sc
lgb_vldiag_wagecom_metrics_summary['low_auc'] <- low_auc

lgb_vldiag_wagecom_metrics_summary['upp_acc_train'] <- upp_acc_train
lgb_vldiag_wagecom_metrics_summary['upp_acc_test'] <- upp_acc_test
lgb_vldiag_wagecom_metrics_summary['upp_sens'] <- upp_sens
lgb_vldiag_wagecom_metrics_summary['upp_spec'] <- upp_spec
lgb_vldiag_wagecom_metrics_summary['upp_prec'] <- upp_prec
lgb_vldiag_wagecom_metrics_summary['upp_f1_sc'] <- upp_f1_sc
lgb_vldiag_wagecom_metrics_summary['upp_auc'] <- upp_auc

lgb_vldiag_wagecom_metrics_summary
```

# Fitting data with only VL information
## Fitting data with only VL since symptom onset
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Full dataframe with VL since symptom onset}
lightgbm_vlsymp_only_list <- foreach(i = 1: 100, .packages = c("dplyr", "lightgbm", "pROC", "shapviz")) %dopar% {
    split <- split_list[[i]]
    train_df <- split$train %>% select("0", 'outcome') %>% rename("vl_sim_symp" = "0")
    test_df <- split$test %>% select("0", 'outcome') %>% rename("vl_sim_symp" = "0")

    # Convert categorical variables to numeric format using one-hot encoding
    train_x_vlsymp <- model.matrix(outcome ~ ., data = train_df) [, -1, drop = FALSE]
    test_x_vlsymp <- model.matrix(outcome ~ ., data = test_df) [, -1, drop = FALSE]

    # Convert data to XGBoost matrix format
    dtrain_vlsymp <- lgb.Dataset(data = train_x_vlsymp, label = as.numeric(as.factor(train_df$outcome)) - 1)
    dtest_vlsymp <- lgb.Dataset(data = test_x_vlsymp, label = as.numeric(as.factor(test_df$outcome)) - 1)

    lgb_model_vlsymp <- lgb.train(data = dtrain_vlsymp,
                      nrounds = 1000,
                      verbose = 0,
                      params = list(
                        objective = "binary")
                      )

    # Make prediction on the testing set
    lgb_pred_vlsymp <- predict(lgb_model_vlsymp, newdata = test_x_vlsymp, type = "response")
    lgb_pred_vlsymp <- ifelse(lgb_pred_vlsymp >= 0.5, 1, 0)
    lgb_pred_vlsymp_res <- ifelse(lgb_pred_vlsymp == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_vlsymp <- table(lgb_pred_vlsymp_res, test_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_vlsymp <- sum(cfm_lgb_vlsymp["Severe", "Severe"], cfm_lgb_vlsymp["Non severe", "Non severe"])/sum(cfm_lgb_vlsymp)
    
    # Make prediction on the training set
    lgb_pred_vlsymp_train <- predict(lgb_model_vlsymp, newdata = train_x_vlsymp, type = "response")
    lgb_pred_vlsymp_train <- ifelse(lgb_pred_vlsymp_train >= 0.5, 1, 0)
    lgb_pred_vlsymp_train_res <- ifelse(lgb_pred_vlsymp_train == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_vlsymp_train <- table(lgb_pred_vlsymp_train_res, train_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_vlsymp_train <- sum(cfm_lgb_vlsymp_train["Severe", "Severe"], cfm_lgb_vlsymp_train["Non severe", "Non severe"])/sum(cfm_lgb_vlsymp_train)

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_lgb_vlsymp["Severe", "Severe"]
    FP <- cfm_lgb_vlsymp["Severe", "Non severe"]
    TN <- cfm_lgb_vlsymp["Non severe", "Non severe"]
    FN <- cfm_lgb_vlsymp["Non severe", "Severe"]

    sensitivity_lgb_vlsymp <- TP / (TP + FN)
    specificity_lgb_vlsymp <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_lgb_vlsymp <- TP / (TP + FP)
    f1_sc_lgb_vlsymp <- 2 * ((prec_lgb_vlsymp * sensitivity_lgb_vlsymp) / (prec_lgb_vlsymp + sensitivity_lgb_vlsymp))

    # Compute AUROC
    roc_lgb_vlsymp <- roc(test_df$outcome, lgb_pred_vlsymp)
    auc_val_lgb_vlsymp <- auc(roc_lgb_vlsymp)
    
    ## SHAP Summary
    shp_lgb_vlsymp <- shapviz(lgb_model_vlsymp, X_pred = train_x_vlsymp, X = as.data.frame(train_x_vlsymp))
    
    list(model = lgb_model_vlsymp, confusion_matrix = cfm_lgb_vlsymp, accuracy_training = accuracy_lgb_vlsymp_train, accuracy_testing = accuracy_lgb_vlsymp,
          sensitivity = sensitivity_lgb_vlsymp, specificity = specificity_lgb_vlsymp, precision = prec_lgb_vlsymp,
          F1_score = f1_sc_lgb_vlsymp, AUC_value = auc_val_lgb_vlsymp, SHAP_values = shp_lgb_vlsymp, prediction = lgb_pred_vlsymp_res)
}
```

```{r, Stop CPU clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
lgb_vlsymp_only_metrics_df <- map_dfr(seq_along(lightgbm_vlsymp_only_list), function(i) {
  result <- lightgbm_vlsymp_only_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
lgb_vlsymp_only_metrics_df <- as.data.frame(lgb_vlsymp_only_metrics_df)

lgb_vlsymp_only_metrics_summary <- lgb_vlsymp_only_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(lgb_vlsymp_only_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(lgb_vlsymp_only_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(lgb_vlsymp_only_metrics_df$sensitivity, 0.025)
low_spec <- quantile(lgb_vlsymp_only_metrics_df$specificity, 0.025)
low_prec <- quantile(lgb_vlsymp_only_metrics_df$precision, 0.025)
low_f1_sc <- quantile(lgb_vlsymp_only_metrics_df$F1_score, 0.025)
low_auc <- quantile(lgb_vlsymp_only_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(lgb_vlsymp_only_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(lgb_vlsymp_only_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(lgb_vlsymp_only_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(lgb_vlsymp_only_metrics_df$specificity, 0.975)
upp_prec <- quantile(lgb_vlsymp_only_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(lgb_vlsymp_only_metrics_df$F1_score, 0.975)
upp_auc <- quantile(lgb_vlsymp_only_metrics_df$AUC_value, 0.975)

lgb_vlsymp_only_metrics_summary['low_acc_train'] <- low_acc_train
lgb_vlsymp_only_metrics_summary['low_acc_test'] <- low_acc_test
lgb_vlsymp_only_metrics_summary['low_sens'] <- low_sens
lgb_vlsymp_only_metrics_summary['low_spec'] <- low_spec
lgb_vlsymp_only_metrics_summary['low_prec'] <- low_prec
lgb_vlsymp_only_metrics_summary['low_f1_sc'] <- low_f1_sc
lgb_vlsymp_only_metrics_summary['low_auc'] <- low_auc

lgb_vlsymp_only_metrics_summary['upp_acc_train'] <- upp_acc_train
lgb_vlsymp_only_metrics_summary['upp_acc_test'] <- upp_acc_test
lgb_vlsymp_only_metrics_summary['upp_sens'] <- upp_sens
lgb_vlsymp_only_metrics_summary['upp_spec'] <- upp_spec
lgb_vlsymp_only_metrics_summary['upp_prec'] <- upp_prec
lgb_vlsymp_only_metrics_summary['upp_f1_sc'] <- upp_f1_sc
lgb_vlsymp_only_metrics_summary['upp_auc'] <- upp_auc

lgb_vlsymp_only_metrics_summary
```

## Fitting data with VL at diagnosis
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Full dataframe with VL at diagnosis}
lightgbm_vldiag_only_list <- foreach(i = 1: 100, .packages = c("dplyr", "lightgbm", "pROC", "shapviz")) %dopar% {
    split <- split_list[[i]]
    train_df <- split$train %>% select("vl_sim", "outcome")
    test_df <- split$test %>% select("vl_sim", "outcome")

    # Convert categorical variables to numeric format using one-hot encoding
    train_x_vldiag <- model.matrix(outcome ~ ., data = train_df) [, -1, drop = FALSE]
    test_x_vldiag <- model.matrix(outcome ~ ., data = test_df) [, -1, drop = FALSE]

    # Convert data to XGBoost matrix format
    dtrain_vldiag <- lgb.Dataset(data = train_x_vldiag, label = as.numeric(as.factor(train_df$outcome)) - 1)
    dtest_vldiag <- lgb.Dataset(data = test_x_vldiag, label = as.numeric(as.factor(test_df$outcome)) - 1)

    lgb_model_vldiag <- lgb.train(data = dtrain_vldiag,
                      nrounds = 1000,
                      verbose = 0,
                      params = list(
                        objective = "binary")
                      )

    # Make prediction on the testing set
    lgb_pred_vldiag <- predict(lgb_model_vldiag, newdata = test_x_vldiag, type = "response")
    lgb_pred_vldiag <- ifelse(lgb_pred_vldiag >= 0.5, 1, 0)
    lgb_pred_vldiag_res <- ifelse(lgb_pred_vldiag == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_vldiag <- table(lgb_pred_vldiag_res, test_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_vldiag <- sum(cfm_lgb_vldiag["Severe", "Severe"], cfm_lgb_vldiag["Non severe", "Non severe"])/sum(cfm_lgb_vldiag)
    
    # Make prediction on the training set
    lgb_pred_vldiag_train <- predict(lgb_model_vldiag, newdata = train_x_vldiag, type = "response")
    lgb_pred_vldiag_train <- ifelse(lgb_pred_vldiag_train >= 0.5, 1, 0)
    lgb_pred_vldiag_train_res <- ifelse(lgb_pred_vldiag_train == 0, "Non severe", "Severe")
    # Compute the confusion matrix
    cfm_lgb_vldiag_train <- table(lgb_pred_vldiag_train_res, train_df$outcome)
    # Compute accuracy on the testing set
    accuracy_lgb_vldiag_train <- sum(cfm_lgb_vldiag_train["Severe", "Severe"], cfm_lgb_vldiag_train["Non severe", "Non severe"])/sum(cfm_lgb_vldiag_train)

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_lgb_vldiag["Severe", "Severe"]
    FP <- cfm_lgb_vldiag["Severe", "Non severe"]
    TN <- cfm_lgb_vldiag["Non severe", "Non severe"]
    FN <- cfm_lgb_vldiag["Non severe", "Severe"]

    sensitivity_lgb_vldiag <- TP / (TP + FN)
    specificity_lgb_vldiag <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_lgb_vldiag <- TP / (TP + FP)
    f1_sc_lgb_vldiag <- 2 * ((prec_lgb_vldiag * sensitivity_lgb_vldiag) / (prec_lgb_vldiag + sensitivity_lgb_vldiag))

    # Compute AUROC
    roc_lgb_vldiag <- roc(test_df$outcome, lgb_pred_vldiag)
    auc_val_lgb_vldiag <- auc(roc_lgb_vldiag)
    
    ## SHAP Summary
    shp_lgb_vldiag <- shapviz(lgb_model_vldiag, X_pred = train_x_vldiag, X = as.data.frame(train_x_vldiag))
    
    list(model = lgb_model_vldiag, confusion_matrix = cfm_lgb_vldiag, accuracy_training = accuracy_lgb_vldiag_train, accuracy_testing = accuracy_lgb_vldiag,
          sensitivity = sensitivity_lgb_vldiag, specificity = specificity_lgb_vldiag, precision = prec_lgb_vldiag,
          F1_score = f1_sc_lgb_vldiag, AUC_value = auc_val_lgb_vldiag, SHAP_values = shp_lgb_vldiag, prediction = lgb_pred_vldiag_res)
}
```

```{r, Stop CPU clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
lgb_vldiag_only_metrics_df <- map_dfr(seq_along(lightgbm_vldiag_only_list), function(i) {
  result <- lightgbm_vldiag_only_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
lgb_vldiag_only_metrics_df <- as.data.frame(lgb_vldiag_only_metrics_df)

lgb_vldiag_only_metrics_summary <- lgb_vldiag_only_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(lgb_vldiag_only_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(lgb_vldiag_only_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(lgb_vldiag_only_metrics_df$sensitivity, 0.025)
low_spec <- quantile(lgb_vldiag_only_metrics_df$specificity, 0.025)
low_prec <- quantile(lgb_vldiag_only_metrics_df$precision, 0.025)
low_f1_sc <- quantile(lgb_vldiag_only_metrics_df$F1_score, 0.025)
low_auc <- quantile(lgb_vldiag_only_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(lgb_vldiag_only_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(lgb_vldiag_only_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(lgb_vldiag_only_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(lgb_vldiag_only_metrics_df$specificity, 0.975)
upp_prec <- quantile(lgb_vldiag_only_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(lgb_vldiag_only_metrics_df$F1_score, 0.975)
upp_auc <- quantile(lgb_vldiag_only_metrics_df$AUC_value, 0.975)

lgb_vldiag_only_metrics_summary['low_acc_train'] <- low_acc_train
lgb_vldiag_only_metrics_summary['low_acc_test'] <- low_acc_test
lgb_vldiag_only_metrics_summary['low_sens'] <- low_sens
lgb_vldiag_only_metrics_summary['low_spec'] <- low_spec
lgb_vldiag_only_metrics_summary['low_prec'] <- low_prec
lgb_vldiag_only_metrics_summary['low_f1_sc'] <- low_f1_sc
lgb_vldiag_only_metrics_summary['low_auc'] <- low_auc

lgb_vldiag_only_metrics_summary['upp_acc_train'] <- upp_acc_train
lgb_vldiag_only_metrics_summary['upp_acc_test'] <- upp_acc_test
lgb_vldiag_only_metrics_summary['upp_sens'] <- upp_sens
lgb_vldiag_only_metrics_summary['upp_spec'] <- upp_spec
lgb_vldiag_only_metrics_summary['upp_prec'] <- upp_prec
lgb_vldiag_only_metrics_summary['upp_f1_sc'] <- upp_f1_sc
lgb_vldiag_only_metrics_summary['upp_auc'] <- upp_auc

lgb_vldiag_only_metrics_summary
```

# Saving all data in this session
```{r, Saving RData file}
save.image(file = paste0(getwd(), '/LightGBM.RData'))
```

# Show the session info
```{r, Session Info}
sessionInfo()
```