---
title: "Random_forest"
output: html_document
---

# Setup environment & load data
```{r, Import libraries}
library(foreach)
library(doParallel)
library(dplyr)
library(purrr)
library(randomForest)
library(pROC)
library(fastshap)
library(shapviz)
library(ggplot2)
```

```{r, Load data into environment}
load(paste0(getwd(), "/Data_preparation.RData"))
```

# Fitting data with full dataframe
## Fitting data without any VL information
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Full dataframe without VL information}
rf_fil_list <- foreach(i = 1: 100, .packages = c("randomForest", "pROC", "fastshap", "shapviz", "ggplot2")) %dopar% {
    split <- split_list_fil[[i]]
    train_df <- split$train
    test_df <- split$test

    # Fitting the random forest model
    rf_fil <- randomForest(outcome ~ ., data = train_df, importance = TRUE)

    # Make prediction on the testing set
    prediction_rf_fil <- predict(rf_fil, newdata = test_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_fil <- table(prediction_rf_fil, test_df$outcome)
    # Compute accuracy on the testing set
    acc_rf_test <- sum(diag(cfm_rf_fil) / sum(cfm_rf_fil))

    # Make prediction on the training set
    prediction_rf_train <- predict(rf_fil, newdata = train_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_fil_train <- table(prediction_rf_train, train_df$outcome)
    # Compute accuracy on the training set
    acc_rf_train <- sum(diag(cfm_rf_fil_train) / sum(cfm_rf_fil_train))

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_rf_fil["Severe", "Severe"]
    FP <- cfm_rf_fil["Severe", "Non severe"]
    TN <- cfm_rf_fil["Non severe", "Non severe"]
    FN <- cfm_rf_fil["Non severe", "Severe"]

    sensitivity_rf_fil <- TP / (TP + FN)
    specificity_rf_fil <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_rf_fil <- TP / (TP + FP)
    f1_sc_rf_fil <- 2 * ((prec_rf_fil * sensitivity_rf_fil) / (prec_rf_fil + sensitivity_rf_fil))

    # Compute & plot AUROC plot
    pred_rf_fil_res <- ifelse(prediction_rf_fil == "Severe", 1, 0)
    roc_rf_fil <- roc(test_df$outcome, pred_rf_fil_res)
    auc_val_rf_fil <- auc(roc_rf_fil)

    # Compute & plot SHAP values
    xvars <- colnames(train_df)[-5]
    pfun_rf <- function(object, newdata) predict(object, newdata, type = "prob")[, 2]
    shap_values_rf_fil <- fastshap::explain(rf_fil, X = train_df[, -5], pred_wrapper = pfun_rf)
    shp_rf_fil <- shapviz(shap_values_rf_fil, X = train_df[, -which(names(train_df) == "outcome")])

    list(model = rf_fil, confusion_matrix = cfm_rf_fil, accuracy_training = acc_rf_train, accuracy_testing = acc_rf_test,
          sensitivity = sensitivity_rf_fil, specificity = specificity_rf_fil, precision = prec_rf_fil,
          F1_score = f1_sc_rf_fil, AUC_value = auc_val_rf_fil, SHAP_values = shp_rf_fil, prediction = prediction_rf_fil)
}
```

```{r, Stop clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
rf_fil_metrics_df <- map_dfr(seq_along(rf_fil_list), function(i) {
  result <- rf_fil_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
rf_fil_metrics_df <- as.data.frame(rf_fil_metrics_df)

rf_fil_metrics_summary <- rf_fil_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(rf_fil_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(rf_fil_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(rf_fil_metrics_df$sensitivity, 0.025)
low_spec <- quantile(rf_fil_metrics_df$specificity, 0.025)
low_prec <- quantile(rf_fil_metrics_df$precision, 0.025)
low_f1_sc <- quantile(rf_fil_metrics_df$F1_score, 0.025)
low_auc <- quantile(rf_fil_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(rf_fil_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(rf_fil_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(rf_fil_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(rf_fil_metrics_df$specificity, 0.975)
upp_prec <- quantile(rf_fil_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(rf_fil_metrics_df$F1_score, 0.975)
upp_auc <- quantile(rf_fil_metrics_df$AUC_value, 0.975)

rf_fil_metrics_summary['low_acc_train'] <- low_acc_train
rf_fil_metrics_summary['low_acc_test'] <- low_acc_test
rf_fil_metrics_summary['low_sens'] <- low_sens
rf_fil_metrics_summary['low_spec'] <- low_spec
rf_fil_metrics_summary['low_prec'] <- low_prec
rf_fil_metrics_summary['low_f1_sc'] <- low_f1_sc
rf_fil_metrics_summary['low_auc'] <- low_auc

rf_fil_metrics_summary['upp_acc_train'] <- upp_acc_train
rf_fil_metrics_summary['upp_acc_test'] <- upp_acc_test
rf_fil_metrics_summary['upp_sens'] <- upp_sens
rf_fil_metrics_summary['upp_spec'] <- upp_spec
rf_fil_metrics_summary['upp_prec'] <- upp_prec
rf_fil_metrics_summary['upp_f1_sc'] <- upp_f1_sc
rf_fil_metrics_summary['upp_auc'] <- upp_auc

rf_fil_metrics_summary
```

## Fitting data with VL since symptom onset
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Full dataframe with VL since symptom onset}
rf_vlsymp_list <- foreach(i = 1: 100, .packages = c("dplyr", "randomForest", "pROC", "fastshap", "shapviz")) %dopar% {
    split <- split_list_vlsim_symp[[i]]
    train_df <- split$train
    test_df <- split$test

    # Fitting the random forest model
    rf_vlsymp <- randomForest(outcome ~ ., data = train_df, importance = TRUE)

    # Make prediction on the testing set
    prediction_rf_vlsymp <- predict(rf_vlsymp, newdata = test_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_vlsymp <- table(prediction_rf_vlsymp, test_df$outcome)
    # Compute accuracy on the testing set
    acc_rf_test <- sum(diag(cfm_rf_vlsymp) / sum(cfm_rf_vlsymp))

    # Make prediction on the training set
    prediction_rf_train <- predict(rf_vlsymp, newdata = train_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_vlsymp_train <- table(prediction_rf_train, train_df$outcome)
    # Compute accuracy on the training set
    acc_rf_train <- sum(diag(cfm_rf_vlsymp_train) / sum(cfm_rf_vlsymp_train))

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_rf_vlsymp["Severe", "Severe"]
    FP <- cfm_rf_vlsymp["Severe", "Non severe"]
    TN <- cfm_rf_vlsymp["Non severe", "Non severe"]
    FN <- cfm_rf_vlsymp["Non severe", "Severe"]

    sensitivity_rf_vlsymp <- TP / (TP + FN)
    specificity_rf_vlsymp <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_rf_vlsymp <- TP / (TP + FP)
    f1_sc_rf_vlsymp <- 2 * ((prec_rf_vlsymp * sensitivity_rf_vlsymp) / (prec_rf_vlsymp + sensitivity_rf_vlsymp))

    # Compute & plot AUROC plot
    pred_rf_vlsymp_res <- ifelse(prediction_rf_vlsymp == "Severe", 1, 0)
    roc_rf_vlsymp <- roc(test_df$outcome, pred_rf_vlsymp_res)
    auc_val_rf_vlsymp <- auc(roc_rf_vlsymp)

    rocplot_rf_vlsymp <- plot.roc(test_df$outcome, pred_rf_vlsymp_res, main = "ROC Curve for Random Forest Model",
                              ci = TRUE, print.auc = TRUE, percent = TRUE, col = "blue")
    
    # Compute & plot SHAP values
    xvars <- colnames(train_df)[-6]
    pfun_rf <- function(object, newdata) predict(object, newdata, type = "prob")[, 2]
    shap_values_rf_vlsymp <- fastshap::explain(rf_vlsymp, X = train_df[, -6], pred_wrapper = pfun_rf)
    shp_rf_vlsymp <- shapviz(shap_values_rf_vlsymp, X = train_df[, -which(names(train_df) == "outcome")])

    # Rename variable
    shp_rf_vlsymp$X <- shp_rf_vlsymp$X %>% rename("Viral load at symptom onset" = "vl_sim_symp")
    colnames(shp_rf_vlsymp$S) <- c("age", "gender", "vaccination", "comorbidity", "Viral load at symptom onset")

    list(model = rf_vlsymp, confusion_matrix = cfm_rf_vlsymp, accuracy_training = acc_rf_train, accuracy_testing = acc_rf_test,
          sensitivity = sensitivity_rf_vlsymp, specificity = specificity_rf_vlsymp, precision = prec_rf_vlsymp,
          F1_score = f1_sc_rf_vlsymp, AUC_value = auc_val_rf_vlsymp, SHAP_values = shp_rf_vlsymp, prediction = prediction_rf_vlsymp)
}
```

```{r, Stop clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
rf_vlsymp_metrics_df <- map_dfr(seq_along(rf_vlsymp_list), function(i) {
  result <- rf_vlsymp_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
rf_vlsymp_metrics_df <- as.data.frame(rf_vlsymp_metrics_df)

rf_vlsymp_metrics_summary <- rf_vlsymp_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(rf_vlsymp_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(rf_vlsymp_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(rf_vlsymp_metrics_df$sensitivity, 0.025)
low_spec <- quantile(rf_vlsymp_metrics_df$specificity, 0.025)
low_prec <- quantile(rf_vlsymp_metrics_df$precision, 0.025)
low_f1_sc <- quantile(rf_vlsymp_metrics_df$F1_score, 0.025)
low_auc <- quantile(rf_vlsymp_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(rf_vlsymp_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(rf_vlsymp_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(rf_vlsymp_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(rf_vlsymp_metrics_df$specificity, 0.975)
upp_prec <- quantile(rf_vlsymp_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(rf_vlsymp_metrics_df$F1_score, 0.975)
upp_auc <- quantile(rf_vlsymp_metrics_df$AUC_value, 0.975)

rf_vlsymp_metrics_summary['low_acc_train'] <- low_acc_train
rf_vlsymp_metrics_summary['low_acc_test'] <- low_acc_test
rf_vlsymp_metrics_summary['low_sens'] <- low_sens
rf_vlsymp_metrics_summary['low_spec'] <- low_spec
rf_vlsymp_metrics_summary['low_prec'] <- low_prec
rf_vlsymp_metrics_summary['low_f1_sc'] <- low_f1_sc
rf_vlsymp_metrics_summary['low_auc'] <- low_auc

rf_vlsymp_metrics_summary['upp_acc_train'] <- upp_acc_train
rf_vlsymp_metrics_summary['upp_acc_test'] <- upp_acc_test
rf_vlsymp_metrics_summary['upp_sens'] <- upp_sens
rf_vlsymp_metrics_summary['upp_spec'] <- upp_spec
rf_vlsymp_metrics_summary['upp_prec'] <- upp_prec
rf_vlsymp_metrics_summary['upp_f1_sc'] <- upp_f1_sc
rf_vlsymp_metrics_summary['upp_auc'] <- upp_auc

rf_vlsymp_metrics_summary
```

## Fitting data with VL at diagnosis
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Full dataframe with VL at diagnosis}
rf_vldiag_list <- foreach(i = 1: 100, .packages = c("dplyr", "randomForest", "pROC", "fastshap", "shapviz")) %dopar% {
    split <- split_list_vldiag[[i]]
    train_df <- split$train
    test_df <- split$test

    # Fitting the random forest model
    rf_vldiag <- randomForest(outcome ~ ., data = train_df, importance = TRUE)

    # Make prediction on the testing set
    prediction_rf_vldiag <- predict(rf_vldiag, newdata = test_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_vldiag <- table(prediction_rf_vldiag, test_df$outcome)
    # Compute accuracy on the testing set
    acc_rf_test <- sum(diag(cfm_rf_vldiag) / sum(cfm_rf_vldiag))

    # Make prediction on the training set
    prediction_rf_train <- predict(rf_vldiag, newdata = train_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_vldiag_train <- table(prediction_rf_train, train_df$outcome)
    # Compute accuracy on the training set
    acc_rf_train <- sum(diag(cfm_rf_vldiag_train) / sum(cfm_rf_vldiag_train))

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_rf_vldiag["Severe", "Severe"]
    FP <- cfm_rf_vldiag["Severe", "Non severe"]
    TN <- cfm_rf_vldiag["Non severe", "Non severe"]
    FN <- cfm_rf_vldiag["Non severe", "Severe"]

    sensitivity_rf_vldiag <- TP / (TP + FN)
    specificity_rf_vldiag <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_rf_vldiag <- TP / (TP + FP)
    f1_sc_rf_vldiag <- 2 * ((prec_rf_vldiag * sensitivity_rf_vldiag) / (prec_rf_vldiag + sensitivity_rf_vldiag))

    # Compute AUROC plot
    pred_rf_vldiag_res <- ifelse(prediction_rf_vldiag == "Severe", 1, 0)
    roc_rf_vldiag <- roc(test_df$outcome, pred_rf_vldiag_res)
    auc_val_rf_vldiag <- auc(roc_rf_vldiag)
    
    # Compute SHAP values
    xvars <- colnames(train_df)[-6]
    pfun_rf <- function(object, newdata) predict(object, newdata, type = "prob")[, 2]
    shap_values_rf_vldiag <- fastshap::explain(rf_vldiag, X = train_df[, -6], pred_wrapper = pfun_rf)
    shp_rf_vldiag <- shapviz(shap_values_rf_vldiag, X = train_df[, -which(names(train_df) == "outcome")])

    # Rename variable
    shp_rf_vldiag$X <- shp_rf_vldiag$X %>% rename("Viral load at diagnosis" = "vl_sim")
    colnames(shp_rf_vldiag$S) <- c("age", "gender", "vaccination", "comorbidity", "Viral load at diagnosis")
    
    list(model = rf_vldiag, confusion_matrix = cfm_rf_vldiag, accuracy_training = acc_rf_train, accuracy_testing = acc_rf_test,
          sensitivity = sensitivity_rf_vldiag, specificity = specificity_rf_vldiag, precision = prec_rf_vldiag,
          F1_score = f1_sc_rf_vldiag, AUC_value = auc_val_rf_vldiag, SHAP_values = shp_rf_vldiag, prediction = prediction_rf_vldiag)
}
```

```{r, Stop clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
rf_vldiag_metrics_df <- map_dfr(seq_along(rf_vldiag_list), function(i) {
  result <- rf_vldiag_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
rf_vldiag_metrics_df <- as.data.frame(rf_vldiag_metrics_df)

rf_vldiag_metrics_summary <- rf_vldiag_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(rf_vldiag_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(rf_vldiag_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(rf_vldiag_metrics_df$sensitivity, 0.025)
low_spec <- quantile(rf_vldiag_metrics_df$specificity, 0.025)
low_prec <- quantile(rf_vldiag_metrics_df$precision, 0.025)
low_f1_sc <- quantile(rf_vldiag_metrics_df$F1_score, 0.025)
low_auc <- quantile(rf_vldiag_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(rf_vldiag_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(rf_vldiag_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(rf_vldiag_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(rf_vldiag_metrics_df$specificity, 0.975)
upp_prec <- quantile(rf_vldiag_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(rf_vldiag_metrics_df$F1_score, 0.975)
upp_auc <- quantile(rf_vldiag_metrics_df$AUC_value, 0.975)

rf_vldiag_metrics_summary['low_acc_train'] <- low_acc_train
rf_vldiag_metrics_summary['low_acc_test'] <- low_acc_test
rf_vldiag_metrics_summary['low_sens'] <- low_sens
rf_vldiag_metrics_summary['low_spec'] <- low_spec
rf_vldiag_metrics_summary['low_prec'] <- low_prec
rf_vldiag_metrics_summary['low_f1_sc'] <- low_f1_sc
rf_vldiag_metrics_summary['low_auc'] <- low_auc

rf_vldiag_metrics_summary['upp_acc_train'] <- upp_acc_train
rf_vldiag_metrics_summary['upp_acc_test'] <- upp_acc_test
rf_vldiag_metrics_summary['upp_sens'] <- upp_sens
rf_vldiag_metrics_summary['upp_spec'] <- upp_spec
rf_vldiag_metrics_summary['upp_prec'] <- upp_prec
rf_vldiag_metrics_summary['upp_f1_sc'] <- upp_f1_sc
rf_vldiag_metrics_summary['upp_auc'] <- upp_auc

rf_vldiag_metrics_summary
```

# Fitting data excluding Comorbidity
## Fitting data without any VL information
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Dataframe excluding Comorbidity & VL information}
rf_wvlncom_list <- foreach(i = 1: 100, .packages = c("randomForest", "pROC", "fastshap", "shapviz")) %dopar% {
    split <- split_list_wvlncom[[i]]
    train_df <- split$train
    test_df <- split$test

    # Fitting the random forest model
    rf_wvlncom <- randomForest(outcome ~ ., data = train_df, importance = TRUE)

    # Make prediction on the testing set
    prediction_rf_wvlncom <- predict(rf_wvlncom, newdata = test_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_wvlncom <- table(prediction_rf_wvlncom, test_df$outcome)
    # Compute accuracy on the testing set
    acc_rf_test <- sum(diag(cfm_rf_wvlncom) / sum(cfm_rf_wvlncom))

    # Make prediction on the training set
    prediction_rf_train <- predict(rf_wvlncom, newdata = train_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_wvlncom_train <- table(prediction_rf_train, train_df$outcome)
    # Compute accuracy on the training set
    acc_rf_train <- sum(diag(cfm_rf_wvlncom_train) / sum(cfm_rf_wvlncom_train))

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_rf_wvlncom["Severe", "Severe"]
    FP <- cfm_rf_wvlncom["Severe", "Non severe"]
    TN <- cfm_rf_wvlncom["Non severe", "Non severe"]
    FN <- cfm_rf_wvlncom["Non severe", "Severe"]

    sensitivity_rf_wvlncom <- TP / (TP + FN)
    specificity_rf_wvlncom <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_rf_wvlncom <- TP / (TP + FP)
    f1_sc_rf_wvlncom <- 2 * ((prec_rf_wvlncom * sensitivity_rf_wvlncom) / (prec_rf_wvlncom + sensitivity_rf_wvlncom))

    # Compute AUROC
    pred_rf_wvlncom_res <- ifelse(prediction_rf_wvlncom == "Severe", 1, 0)
    roc_rf_wvlncom <- roc(test_df$outcome, pred_rf_wvlncom_res)
    auc_val_rf_wvlncom <- auc(roc_rf_wvlncom)
    
    # Compute SHAP values
    xvars <- colnames(train_df)[-4]
    pfun_rf <- function(object, newdata) predict(object, newdata, type = "prob")[, 2]
    shap_values_rf_wvlncom <- fastshap::explain(rf_wvlncom, X = train_df[, -4], pred_wrapper = pfun_rf)
    shp_rf_wvlncom <- shapviz(shap_values_rf_wvlncom, X = train_df[, -which(names(train_df) == "outcome")])

    list(model = rf_wvlncom, confusion_matrix = cfm_rf_wvlncom, accuracy_training = acc_rf_train, accuracy_testing = acc_rf_test,
          sensitivity = sensitivity_rf_wvlncom, specificity = specificity_rf_wvlncom, precision = prec_rf_wvlncom,
          F1_score = f1_sc_rf_wvlncom, AUC_value = auc_val_rf_wvlncom, SHAP_values = shp_rf_wvlncom, prediction = prediction_rf_wvlncom)
}
```

```{r, Stop clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
rf_wvlncom_metrics_df <- map_dfr(seq_along(rf_wvlncom_list), function(i) {
  result <- rf_wvlncom_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
rf_wvlncom_metrics_df <- as.data.frame(rf_wvlncom_metrics_df)

rf_wvlncom_metrics_summary <- rf_wvlncom_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(rf_wvlncom_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(rf_wvlncom_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(rf_wvlncom_metrics_df$sensitivity, 0.025)
low_spec <- quantile(rf_wvlncom_metrics_df$specificity, 0.025)
low_prec <- quantile(rf_wvlncom_metrics_df$precision, 0.025)
low_f1_sc <- quantile(rf_wvlncom_metrics_df$F1_score, 0.025)
low_auc <- quantile(rf_wvlncom_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(rf_wvlncom_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(rf_wvlncom_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(rf_wvlncom_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(rf_wvlncom_metrics_df$specificity, 0.975)
upp_prec <- quantile(rf_wvlncom_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(rf_wvlncom_metrics_df$F1_score, 0.975)
upp_auc <- quantile(rf_wvlncom_metrics_df$AUC_value, 0.975)

rf_wvlncom_metrics_summary['low_acc_train'] <- low_acc_train
rf_wvlncom_metrics_summary['low_acc_test'] <- low_acc_test
rf_wvlncom_metrics_summary['low_sens'] <- low_sens
rf_wvlncom_metrics_summary['low_spec'] <- low_spec
rf_wvlncom_metrics_summary['low_prec'] <- low_prec
rf_wvlncom_metrics_summary['low_f1_sc'] <- low_f1_sc
rf_wvlncom_metrics_summary['low_auc'] <- low_auc

rf_wvlncom_metrics_summary['upp_acc_train'] <- upp_acc_train
rf_wvlncom_metrics_summary['upp_acc_test'] <- upp_acc_test
rf_wvlncom_metrics_summary['upp_sens'] <- upp_sens
rf_wvlncom_metrics_summary['upp_spec'] <- upp_spec
rf_wvlncom_metrics_summary['upp_prec'] <- upp_prec
rf_wvlncom_metrics_summary['upp_f1_sc'] <- upp_f1_sc
rf_wvlncom_metrics_summary['upp_auc'] <- upp_auc

rf_wvlncom_metrics_summary
```

## Fitting data with VL since symptom onset
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Dataframe excluding Comorbidity & with VL since symptom onset}
rf_vlsymp_wcom_list <- foreach(i = 1: 100, .packages = c("dplyr", "randomForest", "pROC", "fastshap", "shapviz")) %dopar% {
    split <- split_list_vlsim_symp_wcom[[i]]
    train_df <- split$train
    test_df <- split$test

    # Fitting the random forest model
    rf_vlsymp_wcom <- randomForest(outcome ~ ., data = train_df, importance = TRUE)

    # Make prediction on the testing set
    prediction_rf_vlsymp_wcom <- predict(rf_vlsymp_wcom, newdata = test_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_vlsymp_wcom <- table(prediction_rf_vlsymp_wcom, test_df$outcome)
    # Compute accuracy on the testing set
    acc_rf_test <- sum(diag(cfm_rf_vlsymp_wcom) / sum(cfm_rf_vlsymp_wcom))

    # Make prediction on the training set
    prediction_rf_train <- predict(rf_vlsymp_wcom, newdata = train_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_vlsymp_wcom_train <- table(prediction_rf_train, train_df$outcome)
    # Compute accuracy on the training set
    acc_rf_train <- sum(diag(cfm_rf_vlsymp_wcom_train) / sum(cfm_rf_vlsymp_wcom_train))

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_rf_vlsymp_wcom["Severe", "Severe"]
    FP <- cfm_rf_vlsymp_wcom["Severe", "Non severe"]
    TN <- cfm_rf_vlsymp_wcom["Non severe", "Non severe"]
    FN <- cfm_rf_vlsymp_wcom["Non severe", "Severe"]

    sensitivity_rf_vlsymp_wcom <- TP / (TP + FN)
    specificity_rf_vlsymp_wcom <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_rf_vlsymp_wcom <- TP / (TP + FP)
    f1_sc_rf_vlsymp_wcom <- 2 * ((prec_rf_vlsymp_wcom * sensitivity_rf_vlsymp_wcom) / (prec_rf_vlsymp_wcom + sensitivity_rf_vlsymp_wcom))

    # Compute AUROC
    pred_rf_vlsymp_wcom_res <- ifelse(prediction_rf_vlsymp_wcom == "Severe", 1, 0)
    roc_rf_vlsymp_wcom <- roc(test_df$outcome, pred_rf_vlsymp_wcom_res)
    auc_val_rf_vlsymp_wcom <- auc(roc_rf_vlsymp_wcom)
    
    # Compute SHAP values
    xvars <- colnames(train_df)[-5]
    pfun_rf <- function(object, newdata) predict(object, newdata, type = "prob")[, 2]
    shap_values_rf_vlsymp_wcom <- fastshap::explain(rf_vlsymp_wcom, X = train_df[, -5], pred_wrapper = pfun_rf)
    shp_rf_vlsymp_wcom <- shapviz(shap_values_rf_vlsymp_wcom, X = train_df[, -which(names(train_df) == "outcome")])

    # Rename variable
    shp_rf_vlsymp_wcom$X <- shp_rf_vlsymp_wcom$X %>% rename("Viral load at symptom onset" = "vl_sim_symp")
    colnames(shp_rf_vlsymp_wcom$S) <- c("age", "gender", "vaccination", "Viral load at symptom onset")
    
    list(model = rf_vlsymp_wcom, confusion_matrix = cfm_rf_vlsymp_wcom, accuracy_training = acc_rf_train, accuracy_testing = acc_rf_test,
          sensitivity = sensitivity_rf_vlsymp_wcom, specificity = specificity_rf_vlsymp_wcom, precision = prec_rf_vlsymp_wcom,
          F1_score = f1_sc_rf_vlsymp_wcom, AUC_value = auc_val_rf_vlsymp_wcom, SHAP_values = shp_rf_vlsymp_wcom, prediction = prediction_rf_vlsymp_wcom)
}
```

```{r, Stop clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
rf_vlsymp_wcom_metrics_df <- map_dfr(seq_along(rf_vlsymp_wcom_list), function(i) {
  result <- rf_vlsymp_wcom_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
rf_vlsymp_wcom_metrics_df <- as.data.frame(rf_vlsymp_wcom_metrics_df)

rf_vlsymp_wcom_metrics_summary <- rf_vlsymp_wcom_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(rf_vlsymp_wcom_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(rf_vlsymp_wcom_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(rf_vlsymp_wcom_metrics_df$sensitivity, 0.025)
low_spec <- quantile(rf_vlsymp_wcom_metrics_df$specificity, 0.025)
low_prec <- quantile(rf_vlsymp_wcom_metrics_df$precision, 0.025)
low_f1_sc <- quantile(rf_vlsymp_wcom_metrics_df$F1_score, 0.025)
low_auc <- quantile(rf_vlsymp_wcom_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(rf_vlsymp_wcom_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(rf_vlsymp_wcom_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(rf_vlsymp_wcom_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(rf_vlsymp_wcom_metrics_df$specificity, 0.975)
upp_prec <- quantile(rf_vlsymp_wcom_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(rf_vlsymp_wcom_metrics_df$F1_score, 0.975)
upp_auc <- quantile(rf_vlsymp_wcom_metrics_df$AUC_value, 0.975)

rf_vlsymp_wcom_metrics_summary['low_acc_train'] <- low_acc_train
rf_vlsymp_wcom_metrics_summary['low_acc_test'] <- low_acc_test
rf_vlsymp_wcom_metrics_summary['low_sens'] <- low_sens
rf_vlsymp_wcom_metrics_summary['low_spec'] <- low_spec
rf_vlsymp_wcom_metrics_summary['low_prec'] <- low_prec
rf_vlsymp_wcom_metrics_summary['low_f1_sc'] <- low_f1_sc
rf_vlsymp_wcom_metrics_summary['low_auc'] <- low_auc

rf_vlsymp_wcom_metrics_summary['upp_acc_train'] <- upp_acc_train
rf_vlsymp_wcom_metrics_summary['upp_acc_test'] <- upp_acc_test
rf_vlsymp_wcom_metrics_summary['upp_sens'] <- upp_sens
rf_vlsymp_wcom_metrics_summary['upp_spec'] <- upp_spec
rf_vlsymp_wcom_metrics_summary['upp_prec'] <- upp_prec
rf_vlsymp_wcom_metrics_summary['upp_f1_sc'] <- upp_f1_sc
rf_vlsymp_wcom_metrics_summary['upp_auc'] <- upp_auc

rf_vlsymp_wcom_metrics_summary
```

## Fitting data with VL at diagnosis
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Dataframe excluding Comorbidity & with VL at diagnosis}
rf_vldiag_wcom_list <- foreach(i = 1: 100, .packages = c("dplyr", "randomForest", "pROC", "fastshap", "shapviz")) %dopar% {
    split <- split_list_vldiag_wcom[[i]]
    train_df <- split$train
    test_df <- split$test

    # Fitting the random forest model
    rf_vldiag_wcom <- randomForest(outcome ~ ., data = train_df, importance = TRUE)

    # Make prediction on the testing set
    prediction_rf_vldiag_wcom <- predict(rf_vldiag_wcom, newdata = test_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_vldiag_wcom <- table(prediction_rf_vldiag_wcom, test_df$outcome)
    # Compute accuracy on the testing set
    acc_rf_test <- sum(diag(cfm_rf_vldiag_wcom) / sum(cfm_rf_vldiag_wcom))

    # Make prediction on the training set
    prediction_rf_train <- predict(rf_vldiag_wcom, newdata = train_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_vldiag_wcom_train <- table(prediction_rf_train, train_df$outcome)
    # Compute accuracy on the training set
    acc_rf_train <- sum(diag(cfm_rf_vldiag_wcom_train) / sum(cfm_rf_vldiag_wcom_train))

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_rf_vldiag_wcom["Severe", "Severe"]
    FP <- cfm_rf_vldiag_wcom["Severe", "Non severe"]
    TN <- cfm_rf_vldiag_wcom["Non severe", "Non severe"]
    FN <- cfm_rf_vldiag_wcom["Non severe", "Severe"]

    sensitivity_rf_vldiag_wcom <- TP / (TP + FN)
    specificity_rf_vldiag_wcom <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_rf_vldiag_wcom <- TP / (TP + FP)
    f1_sc_rf_vldiag_wcom <- 2 * ((prec_rf_vldiag_wcom * sensitivity_rf_vldiag_wcom) / (prec_rf_vldiag_wcom + sensitivity_rf_vldiag_wcom))

    # Compute AUROC
    pred_rf_vldiag_wcom_res <- ifelse(prediction_rf_vldiag_wcom == "Severe", 1, 0)
    roc_rf_vldiag_wcom <- roc(test_df$outcome, pred_rf_vldiag_wcom_res)
    auc_val_rf_vldiag_wcom <- auc(roc_rf_vldiag_wcom)
    
    # Compute SHAP values
    xvars <- colnames(train_df)[-5]
    pfun_rf <- function(object, newdata) predict(object, newdata, type = "prob")[, 2]
    shap_values_rf_vldiag_wcom <- fastshap::explain(rf_vldiag_wcom, X = train_df[, -5], pred_wrapper = pfun_rf)
    shp_rf_vldiag_wcom <- shapviz(shap_values_rf_vldiag_wcom, X = train_df[, -which(names(train_df) == "outcome")])

    # Rename variable
    shp_rf_vldiag_wcom$X <- shp_rf_vldiag_wcom$X %>% rename("Viral load at diagnosis" = "vl_sim")
    colnames(shp_rf_vldiag_wcom$S) <- c("age", "gender", "vaccination", "Viral load at diagnosis")
    
    list(model = rf_vldiag_wcom, confusion_matrix = cfm_rf_vldiag_wcom, accuracy_training = acc_rf_train, accuracy_testing = acc_rf_test,
          sensitivity = sensitivity_rf_vldiag_wcom, specificity = specificity_rf_vldiag_wcom, precision = prec_rf_vldiag_wcom,
          F1_score = f1_sc_rf_vldiag_wcom, AUC_value = auc_val_rf_vldiag_wcom, SHAP_values = shp_rf_vldiag_wcom, prediction = prediction_rf_vldiag_wcom)
}
```

```{r, Stop clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
rf_vldiag_wcom_metrics_df <- map_dfr(seq_along(rf_vldiag_wcom_list), function(i) {
  result <- rf_vldiag_wcom_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
rf_vldiag_wcom_metrics_df <- as.data.frame(rf_vldiag_wcom_metrics_df)

rf_vldiag_wcom_metrics_summary <- rf_vldiag_wcom_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(rf_vldiag_wcom_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(rf_vldiag_wcom_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(rf_vldiag_wcom_metrics_df$sensitivity, 0.025)
low_spec <- quantile(rf_vldiag_wcom_metrics_df$specificity, 0.025)
low_prec <- quantile(rf_vldiag_wcom_metrics_df$precision, 0.025)
low_f1_sc <- quantile(rf_vldiag_wcom_metrics_df$F1_score, 0.025)
low_auc <- quantile(rf_vldiag_wcom_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(rf_vldiag_wcom_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(rf_vldiag_wcom_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(rf_vldiag_wcom_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(rf_vldiag_wcom_metrics_df$specificity, 0.975)
upp_prec <- quantile(rf_vldiag_wcom_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(rf_vldiag_wcom_metrics_df$F1_score, 0.975)
upp_auc <- quantile(rf_vldiag_wcom_metrics_df$AUC_value, 0.975)

rf_vldiag_wcom_metrics_summary['low_acc_train'] <- low_acc_train
rf_vldiag_wcom_metrics_summary['low_acc_test'] <- low_acc_test
rf_vldiag_wcom_metrics_summary['low_sens'] <- low_sens
rf_vldiag_wcom_metrics_summary['low_spec'] <- low_spec
rf_vldiag_wcom_metrics_summary['low_prec'] <- low_prec
rf_vldiag_wcom_metrics_summary['low_f1_sc'] <- low_f1_sc
rf_vldiag_wcom_metrics_summary['low_auc'] <- low_auc

rf_vldiag_wcom_metrics_summary['upp_acc_train'] <- upp_acc_train
rf_vldiag_wcom_metrics_summary['upp_acc_test'] <- upp_acc_test
rf_vldiag_wcom_metrics_summary['upp_sens'] <- upp_sens
rf_vldiag_wcom_metrics_summary['upp_spec'] <- upp_spec
rf_vldiag_wcom_metrics_summary['upp_prec'] <- upp_prec
rf_vldiag_wcom_metrics_summary['upp_f1_sc'] <- upp_f1_sc
rf_vldiag_wcom_metrics_summary['upp_auc'] <- upp_auc

rf_vldiag_wcom_metrics_summary
```

# Fitting data excluding Age
## Fitting data without any VL information
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Dataframe excluding Age & VL information}
rf_wvlnage_list <- foreach(i = 1: 100, .packages = c("randomForest", "pROC", "fastshap", "shapviz")) %dopar% {
    split <- split_list_wvlnage[[i]]
    train_df <- split$train
    test_df <- split$test

    # Fitting the random forest model
    rf_wvlnage <- randomForest(outcome ~ ., data = train_df, importance = TRUE)

    # Make prediction on the testing set
    prediction_rf_wvlnage <- predict(rf_wvlnage, newdata = test_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_wvlnage <- table(prediction_rf_wvlnage, test_df$outcome)
    # Compute accuracy on the testing set
    acc_rf_test <- sum(diag(cfm_rf_wvlnage) / sum(cfm_rf_wvlnage))

    # Make prediction on the training set
    prediction_rf_train <- predict(rf_wvlnage, newdata = train_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_wvlnage_train <- table(prediction_rf_train, train_df$outcome)
    # Compute accuracy on the training set
    acc_rf_train <- sum(diag(cfm_rf_wvlnage_train) / sum(cfm_rf_wvlnage_train))

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_rf_wvlnage["Severe", "Severe"]
    FP <- cfm_rf_wvlnage["Severe", "Non severe"]
    TN <- cfm_rf_wvlnage["Non severe", "Non severe"]
    FN <- cfm_rf_wvlnage["Non severe", "Severe"]

    sensitivity_rf_wvlnage <- TP / (TP + FN)
    specificity_rf_wvlnage <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_rf_wvlnage <- TP / (TP + FP)
    f1_sc_rf_wvlnage <- 2 * ((prec_rf_wvlnage * sensitivity_rf_wvlnage) / (prec_rf_wvlnage + sensitivity_rf_wvlnage))

    # Compute AUROC
    pred_rf_wvlnage_res <- ifelse(prediction_rf_wvlnage == "Severe", 1, 0)
    roc_rf_wvlnage <- roc(test_df$outcome, pred_rf_wvlnage_res)
    auc_val_rf_wvlnage <- auc(roc_rf_wvlnage)
    
    # Compute SHAP values
    xvars <- colnames(train_df)[-4]
    pfun_rf <- function(object, newdata) predict(object, newdata, type = "prob")[, 2]
    shap_values_rf_wvlnage <- fastshap::explain(rf_wvlnage, X = train_df[, -4], pred_wrapper = pfun_rf)
    shp_rf_wvlnage <- shapviz(shap_values_rf_wvlnage, X = train_df[, -which(names(train_df) == "outcome")])
    
    list(model = rf_wvlnage, confusion_matrix = cfm_rf_wvlnage, accuracy_training = acc_rf_train, accuracy_testing = acc_rf_test,
          sensitivity = sensitivity_rf_wvlnage, specificity = specificity_rf_wvlnage, precision = prec_rf_wvlnage,
          F1_score = f1_sc_rf_wvlnage, AUC_value = auc_val_rf_wvlnage, SHAP_values = shp_rf_wvlnage, prediction = prediction_rf_wvlnage)
}
```

```{r, Stop clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
rf_wvlnage_metrics_df <- map_dfr(seq_along(rf_wvlnage_list), function(i) {
  result <- rf_wvlnage_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
rf_wvlnage_metrics_df <- as.data.frame(rf_wvlnage_metrics_df)

rf_wvlnage_metrics_summary <- rf_wvlnage_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(rf_wvlnage_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(rf_wvlnage_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(rf_wvlnage_metrics_df$sensitivity, 0.025)
low_spec <- quantile(rf_wvlnage_metrics_df$specificity, 0.025)
low_prec <- quantile(rf_wvlnage_metrics_df$precision, 0.025)
low_f1_sc <- quantile(rf_wvlnage_metrics_df$F1_score, 0.025)
low_auc <- quantile(rf_wvlnage_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(rf_wvlnage_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(rf_wvlnage_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(rf_wvlnage_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(rf_wvlnage_metrics_df$specificity, 0.975)
upp_prec <- quantile(rf_wvlnage_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(rf_wvlnage_metrics_df$F1_score, 0.975)
upp_auc <- quantile(rf_wvlnage_metrics_df$AUC_value, 0.975)

rf_wvlnage_metrics_summary['low_acc_train'] <- low_acc_train
rf_wvlnage_metrics_summary['low_acc_test'] <- low_acc_test
rf_wvlnage_metrics_summary['low_sens'] <- low_sens
rf_wvlnage_metrics_summary['low_spec'] <- low_spec
rf_wvlnage_metrics_summary['low_prec'] <- low_prec
rf_wvlnage_metrics_summary['low_f1_sc'] <- low_f1_sc
rf_wvlnage_metrics_summary['low_auc'] <- low_auc

rf_wvlnage_metrics_summary['upp_acc_train'] <- upp_acc_train
rf_wvlnage_metrics_summary['upp_acc_test'] <- upp_acc_test
rf_wvlnage_metrics_summary['upp_sens'] <- upp_sens
rf_wvlnage_metrics_summary['upp_spec'] <- upp_spec
rf_wvlnage_metrics_summary['upp_prec'] <- upp_prec
rf_wvlnage_metrics_summary['upp_f1_sc'] <- upp_f1_sc
rf_wvlnage_metrics_summary['upp_auc'] <- upp_auc

rf_wvlnage_metrics_summary
```

## Fitting data with VL since symptom onset
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Dataframe excluding Age & with VL since symptom onset}
rf_vlsymp_wage_list <- foreach(i = 1: 100, .packages = c("dplyr", "randomForest", "pROC", "fastshap", "shapviz")) %dopar% {
    split <- split_list_vlsim_symp_wage[[i]]
    train_df <- split$train
    test_df <- split$test

    # Fitting the random forest model
    rf_vlsymp_wage <- randomForest(outcome ~ ., data = train_df, importance = TRUE)

    # Make prediction on the testing set
    prediction_rf_vlsymp_wage <- predict(rf_vlsymp_wage, newdata = test_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_vlsymp_wage <- table(prediction_rf_vlsymp_wage, test_df$outcome)
    # Compute accuracy on the testing set
    acc_rf_test <- sum(diag(cfm_rf_vlsymp_wage) / sum(cfm_rf_vlsymp_wage))

    # Make prediction on the training set
    prediction_rf_train <- predict(rf_vlsymp_wage, newdata = train_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_vlsymp_wage_train <- table(prediction_rf_train, train_df$outcome)
    # Compute accuracy on the training set
    acc_rf_train <- sum(diag(cfm_rf_vlsymp_wage_train) / sum(cfm_rf_vlsymp_wage_train))

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_rf_vlsymp_wage["Severe", "Severe"]
    FP <- cfm_rf_vlsymp_wage["Severe", "Non severe"]
    TN <- cfm_rf_vlsymp_wage["Non severe", "Non severe"]
    FN <- cfm_rf_vlsymp_wage["Non severe", "Severe"]

    sensitivity_rf_vlsymp_wage <- TP / (TP + FN)
    specificity_rf_vlsymp_wage <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_rf_vlsymp_wage <- TP / (TP + FP)
    f1_sc_rf_vlsymp_wage <- 2 * ((prec_rf_vlsymp_wage * sensitivity_rf_vlsymp_wage) / (prec_rf_vlsymp_wage + sensitivity_rf_vlsymp_wage))

    # Compute AUROC
    pred_rf_vlsymp_wage_res <- ifelse(prediction_rf_vlsymp_wage == "Severe", 1, 0)
    roc_rf_vlsymp_wage <- roc(test_df$outcome, pred_rf_vlsymp_wage_res)
    auc_val_rf_vlsymp_wage <- auc(roc_rf_vlsymp_wage)
    
    # Compute SHAP values
    xvars <- colnames(train_df)[-5]
    pfun_rf <- function(object, newdata) predict(object, newdata, type = "prob")[, 2]
    shap_values_rf_vlsymp_wage <- fastshap::explain(rf_vlsymp_wage, X = train_df[, -5], pred_wrapper = pfun_rf)
    shp_rf_vlsymp_wage <- shapviz(shap_values_rf_vlsymp_wage, X = train_df[, -which(names(train_df) == "outcome")])

    # Rename variable
    shp_rf_vlsymp_wage$X <- shp_rf_vlsymp_wage$X %>% rename("Viral load at symptom onset" = "vl_sim_symp")
    colnames(shp_rf_vlsymp_wage$S) <- c("gender", "vaccination", "comorbidity", "Viral load at symptom onset")
    
    list(model = rf_vlsymp_wage, confusion_matrix = cfm_rf_vlsymp_wage, accuracy_training = acc_rf_train, accuracy_testing = acc_rf_test,
          sensitivity = sensitivity_rf_vlsymp_wage, specificity = specificity_rf_vlsymp_wage, precision = prec_rf_vlsymp_wage,
          F1_score = f1_sc_rf_vlsymp_wage, AUC_value = auc_val_rf_vlsymp_wage, SHAP_values = shp_rf_vlsymp_wage, prediction = prediction_rf_vlsymp_wage)
}
```

```{r, Stop clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
rf_vlsymp_wage_metrics_df <- map_dfr(seq_along(rf_vlsymp_wage_list), function(i) {
  result <- rf_vlsymp_wage_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
rf_vlsymp_wage_metrics_df <- as.data.frame(rf_vlsymp_wage_metrics_df)

rf_vlsymp_wage_metrics_summary <- rf_vlsymp_wage_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(rf_vlsymp_wage_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(rf_vlsymp_wage_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(rf_vlsymp_wage_metrics_df$sensitivity, 0.025)
low_spec <- quantile(rf_vlsymp_wage_metrics_df$specificity, 0.025)
low_prec <- quantile(rf_vlsymp_wage_metrics_df$precision, 0.025)
low_f1_sc <- quantile(rf_vlsymp_wage_metrics_df$F1_score, 0.025)
low_auc <- quantile(rf_vlsymp_wage_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(rf_vlsymp_wage_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(rf_vlsymp_wage_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(rf_vlsymp_wage_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(rf_vlsymp_wage_metrics_df$specificity, 0.975)
upp_prec <- quantile(rf_vlsymp_wage_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(rf_vlsymp_wage_metrics_df$F1_score, 0.975)
upp_auc <- quantile(rf_vlsymp_wage_metrics_df$AUC_value, 0.975)

rf_vlsymp_wage_metrics_summary['low_acc_train'] <- low_acc_train
rf_vlsymp_wage_metrics_summary['low_acc_test'] <- low_acc_test
rf_vlsymp_wage_metrics_summary['low_sens'] <- low_sens
rf_vlsymp_wage_metrics_summary['low_spec'] <- low_spec
rf_vlsymp_wage_metrics_summary['low_prec'] <- low_prec
rf_vlsymp_wage_metrics_summary['low_f1_sc'] <- low_f1_sc
rf_vlsymp_wage_metrics_summary['low_auc'] <- low_auc

rf_vlsymp_wage_metrics_summary['upp_acc_train'] <- upp_acc_train
rf_vlsymp_wage_metrics_summary['upp_acc_test'] <- upp_acc_test
rf_vlsymp_wage_metrics_summary['upp_sens'] <- upp_sens
rf_vlsymp_wage_metrics_summary['upp_spec'] <- upp_spec
rf_vlsymp_wage_metrics_summary['upp_prec'] <- upp_prec
rf_vlsymp_wage_metrics_summary['upp_f1_sc'] <- upp_f1_sc
rf_vlsymp_wage_metrics_summary['upp_auc'] <- upp_auc

rf_vlsymp_wage_metrics_summary
```

## Fitting data with VL at diagnosis
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Dataframe excluding Age & with VL at diagnosis}
rf_vldiag_wage_list <- foreach(i = 1: 100, .packages = c("dplyr", "randomForest", "pROC", "fastshap", "shapviz")) %dopar% {
    split <- split_list_vldiag_wage[[i]]
    train_df <- split$train
    test_df <- split$test

    # Fitting the random forest model
    rf_vldiag_wage <- randomForest(outcome ~ ., data = train_df, importance = TRUE)

    # Make prediction on the testing set
    prediction_rf_vldiag_wage <- predict(rf_vldiag_wage, newdata = test_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_vldiag_wage <- table(prediction_rf_vldiag_wage, test_df$outcome)
    # Compute accuracy on the testing set
    acc_rf_test <- sum(diag(cfm_rf_vldiag_wage) / sum(cfm_rf_vldiag_wage))

    # Make prediction on the training set
    prediction_rf_train <- predict(rf_vldiag_wage, newdata = train_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_vldiag_wage_train <- table(prediction_rf_train, train_df$outcome)
    # Compute accuracy on the training set
    acc_rf_train <- sum(diag(cfm_rf_vldiag_wage_train) / sum(cfm_rf_vldiag_wage_train))

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_rf_vldiag_wage["Severe", "Severe"]
    FP <- cfm_rf_vldiag_wage["Severe", "Non severe"]
    TN <- cfm_rf_vldiag_wage["Non severe", "Non severe"]
    FN <- cfm_rf_vldiag_wage["Non severe", "Severe"]

    sensitivity_rf_vldiag_wage <- TP / (TP + FN)
    specificity_rf_vldiag_wage <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_rf_vldiag_wage <- TP / (TP + FP)
    f1_sc_rf_vldiag_wage <- 2 * ((prec_rf_vldiag_wage * sensitivity_rf_vldiag_wage) / (prec_rf_vldiag_wage + sensitivity_rf_vldiag_wage))

    # Compute AUROC
    pred_rf_vldiag_wage_res <- ifelse(prediction_rf_vldiag_wage == "Severe", 1, 0)
    roc_rf_vldiag_wage <- roc(test_df$outcome, pred_rf_vldiag_wage_res)
    auc_val_rf_vldiag_wage <- auc(roc_rf_vldiag_wage)
    
    # Compute SHAP values
    xvars <- colnames(train_df)[-5]
    pfun_rf <- function(object, newdata) predict(object, newdata, type = "prob")[, 2]
    shap_values_rf_vldiag_wage <- fastshap::explain(rf_vldiag_wage, X = train_df[, -5], pred_wrapper = pfun_rf)
    shp_rf_vldiag_wage <- shapviz(shap_values_rf_vldiag_wage, X = train_df[, -which(names(train_df) == "outcome")])

    # Rename variable
    shp_rf_vldiag_wage$X <- shp_rf_vldiag_wage$X %>% rename("Viral load at diagnosis" = "vl_sim")
    colnames(shp_rf_vldiag_wage$S) <- c("gender", "vaccination", "comorbidity", "Viral load at diagnosis")
    
    list(model = rf_vldiag_wage, confusion_matrix = cfm_rf_vldiag_wage, accuracy_training = acc_rf_train, accuracy_testing = acc_rf_test,
          sensitivity = sensitivity_rf_vldiag_wage, specificity = specificity_rf_vldiag_wage, precision = prec_rf_vldiag_wage,
          F1_score = f1_sc_rf_vldiag_wage, AUC_value = auc_val_rf_vldiag_wage, SHAP_values = shp_rf_vldiag_wage, prediction = prediction_rf_vldiag_wage)
}
```

```{r, Stop clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
rf_vldiag_wage_metrics_df <- map_dfr(seq_along(rf_vldiag_wage_list), function(i) {
  result <- rf_vldiag_wage_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
rf_vldiag_wage_metrics_df <- as.data.frame(rf_vldiag_wage_metrics_df)

rf_vldiag_wage_metrics_summary <- rf_vldiag_wage_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(rf_vldiag_wage_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(rf_vldiag_wage_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(rf_vldiag_wage_metrics_df$sensitivity, 0.025)
low_spec <- quantile(rf_vldiag_wage_metrics_df$specificity, 0.025)
low_prec <- quantile(rf_vldiag_wage_metrics_df$precision, 0.025)
low_f1_sc <- quantile(rf_vldiag_wage_metrics_df$F1_score, 0.025)
low_auc <- quantile(rf_vldiag_wage_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(rf_vldiag_wage_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(rf_vldiag_wage_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(rf_vldiag_wage_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(rf_vldiag_wage_metrics_df$specificity, 0.975)
upp_prec <- quantile(rf_vldiag_wage_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(rf_vldiag_wage_metrics_df$F1_score, 0.975)
upp_auc <- quantile(rf_vldiag_wage_metrics_df$AUC_value, 0.975)

rf_vldiag_wage_metrics_summary['low_acc_train'] <- low_acc_train
rf_vldiag_wage_metrics_summary['low_acc_test'] <- low_acc_test
rf_vldiag_wage_metrics_summary['low_sens'] <- low_sens
rf_vldiag_wage_metrics_summary['low_spec'] <- low_spec
rf_vldiag_wage_metrics_summary['low_prec'] <- low_prec
rf_vldiag_wage_metrics_summary['low_f1_sc'] <- low_f1_sc
rf_vldiag_wage_metrics_summary['low_auc'] <- low_auc

rf_vldiag_wage_metrics_summary['upp_acc_train'] <- upp_acc_train
rf_vldiag_wage_metrics_summary['upp_acc_test'] <- upp_acc_test
rf_vldiag_wage_metrics_summary['upp_sens'] <- upp_sens
rf_vldiag_wage_metrics_summary['upp_spec'] <- upp_spec
rf_vldiag_wage_metrics_summary['upp_prec'] <- upp_prec
rf_vldiag_wage_metrics_summary['upp_f1_sc'] <- upp_f1_sc
rf_vldiag_wage_metrics_summary['upp_auc'] <- upp_auc

rf_vldiag_wage_metrics_summary
```

# Fitting data excluding Comorbidity & Age
## Fitting data without any VL information
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Dataframe excluding Comorbidity, Age & VL information}
rf_wvlnagecom_list <- foreach(i = 1: 100, .packages = c("randomForest", "pROC", "fastshap", "shapviz")) %dopar% {
    split <- split_list_wvlnagecom[[i]]
    train_df <- split$train
    test_df <- split$test

    # Fitting the random forest model
    rf_wvlnagecom <- randomForest(outcome ~ ., data = train_df, importance = TRUE)

    # Make prediction on the testing set
    prediction_rf_wvlnagecom <- predict(rf_wvlnagecom, newdata = test_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_wvlnagecom <- table(prediction_rf_wvlnagecom, test_df$outcome)
    # Compute accuracy on the testing set
    acc_rf_test <- sum(diag(cfm_rf_wvlnagecom) / sum(cfm_rf_wvlnagecom))

    # Make prediction on the training set
    prediction_rf_train <- predict(rf_wvlnagecom, newdata = train_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_wvlnagecom_train <- table(prediction_rf_train, train_df$outcome)
    # Compute accuracy on the training set
    acc_rf_train <- sum(diag(cfm_rf_wvlnagecom_train) / sum(cfm_rf_wvlnagecom_train))

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_rf_wvlnagecom["Severe", "Severe"]
    FP <- cfm_rf_wvlnagecom["Severe", "Non severe"]
    TN <- cfm_rf_wvlnagecom["Non severe", "Non severe"]
    FN <- cfm_rf_wvlnagecom["Non severe", "Severe"]

    sensitivity_rf_wvlnagecom <- TP / (TP + FN)
    specificity_rf_wvlnagecom <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_rf_wvlnagecom <- TP / (TP + FP)
    f1_sc_rf_wvlnagecom <- 2 * ((prec_rf_wvlnagecom * sensitivity_rf_wvlnagecom) / (prec_rf_wvlnagecom + sensitivity_rf_wvlnagecom))

    # Compute AUROC
    pred_rf_wvlnagecom_res <- ifelse(prediction_rf_wvlnagecom == "Severe", 1, 0)
    roc_rf_wvlnagecom <- roc(test_df$outcome, pred_rf_wvlnagecom_res)
    auc_val_rf_wvlnagecom <- auc(roc_rf_wvlnagecom)
    
    # Compute SHAP values
    xvars <- colnames(train_df)[-3]
    pfun_rf <- function(object, newdata) predict(object, newdata, type = "prob")[, 2]
    shap_values_rf_wvlnagecom <- fastshap::explain(rf_wvlnagecom, X = train_df[, -3], pred_wrapper = pfun_rf)
    shp_rf_wvlnagecom <- shapviz(shap_values_rf_wvlnagecom, X = train_df[, -which(names(train_df) == "outcome")])
    
    list(model = rf_wvlnagecom, confusion_matrix = cfm_rf_wvlnagecom, accuracy_training = acc_rf_train, accuracy_testing = acc_rf_test,
          sensitivity = sensitivity_rf_wvlnagecom, specificity = specificity_rf_wvlnagecom, precision = prec_rf_wvlnagecom,
          F1_score = f1_sc_rf_wvlnagecom, AUC_value = auc_val_rf_wvlnagecom, SHAP_values = shp_rf_wvlnagecom, prediction = prediction_rf_wvlnagecom)
}
```

```{r, Stop clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
rf_wvlnagecom_metrics_df <- map_dfr(seq_along(rf_wvlnagecom_list), function(i) {
  result <- rf_wvlnagecom_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
rf_wvlnagecom_metrics_df <- as.data.frame(rf_wvlnagecom_metrics_df)

rf_wvlnagecom_metrics_summary <- rf_wvlnagecom_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(rf_wvlnagecom_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(rf_wvlnagecom_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(rf_wvlnagecom_metrics_df$sensitivity, 0.025)
low_spec <- quantile(rf_wvlnagecom_metrics_df$specificity, 0.025)
low_prec <- quantile(rf_wvlnagecom_metrics_df$precision, 0.025)
low_f1_sc <- quantile(rf_wvlnagecom_metrics_df$F1_score, 0.025)
low_auc <- quantile(rf_wvlnagecom_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(rf_wvlnagecom_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(rf_wvlnagecom_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(rf_wvlnagecom_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(rf_wvlnagecom_metrics_df$specificity, 0.975)
upp_prec <- quantile(rf_wvlnagecom_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(rf_wvlnagecom_metrics_df$F1_score, 0.975)
upp_auc <- quantile(rf_wvlnagecom_metrics_df$AUC_value, 0.975)

rf_wvlnagecom_metrics_summary['low_acc_train'] <- low_acc_train
rf_wvlnagecom_metrics_summary['low_acc_test'] <- low_acc_test
rf_wvlnagecom_metrics_summary['low_sens'] <- low_sens
rf_wvlnagecom_metrics_summary['low_spec'] <- low_spec
rf_wvlnagecom_metrics_summary['low_prec'] <- low_prec
rf_wvlnagecom_metrics_summary['low_f1_sc'] <- low_f1_sc
rf_wvlnagecom_metrics_summary['low_auc'] <- low_auc

rf_wvlnagecom_metrics_summary['upp_acc_train'] <- upp_acc_train
rf_wvlnagecom_metrics_summary['upp_acc_test'] <- upp_acc_test
rf_wvlnagecom_metrics_summary['upp_sens'] <- upp_sens
rf_wvlnagecom_metrics_summary['upp_spec'] <- upp_spec
rf_wvlnagecom_metrics_summary['upp_prec'] <- upp_prec
rf_wvlnagecom_metrics_summary['upp_f1_sc'] <- upp_f1_sc
rf_wvlnagecom_metrics_summary['upp_auc'] <- upp_auc

rf_wvlnagecom_metrics_summary
```

## Fitting data with VL since symptom onset
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Dataframe excluding Comorbidity, Age & with VL since symptom onset}
rf_vlsymp_wagecom_list <- foreach(i = 1: 100, .packages = c("dplyr", "randomForest", "pROC", "fastshap", "shapviz")) %dopar% {
    split <- split_list_vlsim_symp_wagecom[[i]]
    train_df <- split$train
    test_df <- split$test

    # Fitting the random forest model
    rf_vlsymp_wagecom <- randomForest(outcome ~ ., data = train_df, importance = TRUE)

    # Make prediction on the testing set
    prediction_rf_vlsymp_wagecom <- predict(rf_vlsymp_wagecom, newdata = test_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_vlsymp_wagecom <- table(prediction_rf_vlsymp_wagecom, test_df$outcome)
    # Compute accuracy on the testing set
    acc_rf_test <- sum(diag(cfm_rf_vlsymp_wagecom) / sum(cfm_rf_vlsymp_wagecom))

    # Make prediction on the training set
    prediction_rf_train <- predict(rf_vlsymp_wagecom, newdata = train_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_vlsymp_wagecom_train <- table(prediction_rf_train, train_df$outcome)
    # Compute accuracy on the training set
    acc_rf_train <- sum(diag(cfm_rf_vlsymp_wagecom_train) / sum(cfm_rf_vlsymp_wagecom_train))

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_rf_vlsymp_wagecom["Severe", "Severe"]
    FP <- cfm_rf_vlsymp_wagecom["Severe", "Non severe"]
    TN <- cfm_rf_vlsymp_wagecom["Non severe", "Non severe"]
    FN <- cfm_rf_vlsymp_wagecom["Non severe", "Severe"]

    sensitivity_rf_vlsymp_wagecom <- TP / (TP + FN)
    specificity_rf_vlsymp_wagecom <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_rf_vlsymp_wagecom <- TP / (TP + FP)
    f1_sc_rf_vlsymp_wagecom <- 2 * ((prec_rf_vlsymp_wagecom * sensitivity_rf_vlsymp_wagecom) / (prec_rf_vlsymp_wagecom + sensitivity_rf_vlsymp_wagecom))

    # Compute AUROC
    pred_rf_vlsymp_wagecom_res <- ifelse(prediction_rf_vlsymp_wagecom == "Severe", 1, 0)
    roc_rf_vlsymp_wagecom <- roc(test_df$outcome, pred_rf_vlsymp_wagecom_res)
    auc_val_rf_vlsymp_wagecom <- auc(roc_rf_vlsymp_wagecom)
    
    # Compute SHAP values
    xvars <- colnames(train_df)[-4]
    pfun_rf <- function(object, newdata) predict(object, newdata, type = "prob")[, 2]
    shap_values_rf_vlsymp_wagecom <- fastshap::explain(rf_vlsymp_wagecom, X = train_df[, -4], pred_wrapper = pfun_rf)
    shp_rf_vlsymp_wagecom <- shapviz(shap_values_rf_vlsymp_wagecom, X = train_df[, -which(names(train_df) == "outcome")])

    # Rename variable
    shp_rf_vlsymp_wagecom$X <- shp_rf_vlsymp_wagecom$X %>% rename("Viral load at symptom onset" = "vl_sim_symp")
    colnames(shp_rf_vlsymp_wagecom$S) <- c("gender", "vaccination", "Viral load at symptom onset")
    
    list(model = rf_vlsymp_wagecom, confusion_matrix = cfm_rf_vlsymp_wagecom, accuracy_training = acc_rf_train, accuracy_testing = acc_rf_test,
          sensitivity = sensitivity_rf_vlsymp_wagecom, specificity = specificity_rf_vlsymp_wagecom, precision = prec_rf_vlsymp_wagecom,
          F1_score = f1_sc_rf_vlsymp_wagecom, AUC_value = auc_val_rf_vlsymp_wagecom, SHAP_values = shp_rf_vlsymp_wagecom, prediction = prediction_rf_vlsymp_wagecom)
}
```

```{r, Stop clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
rf_vlsymp_wagecom_metrics_df <- map_dfr(seq_along(rf_vlsymp_wagecom_list), function(i) {
  result <- rf_vlsymp_wagecom_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
rf_vlsymp_wagecom_metrics_df <- as.data.frame(rf_vlsymp_wagecom_metrics_df)

rf_vlsymp_wagecom_metrics_summary <- rf_vlsymp_wagecom_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(rf_vlsymp_wagecom_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(rf_vlsymp_wagecom_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(rf_vlsymp_wagecom_metrics_df$sensitivity, 0.025)
low_spec <- quantile(rf_vlsymp_wagecom_metrics_df$specificity, 0.025)
low_prec <- quantile(rf_vlsymp_wagecom_metrics_df$precision, 0.025)
low_f1_sc <- quantile(rf_vlsymp_wagecom_metrics_df$F1_score, 0.025)
low_auc <- quantile(rf_vlsymp_wagecom_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(rf_vlsymp_wagecom_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(rf_vlsymp_wagecom_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(rf_vlsymp_wagecom_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(rf_vlsymp_wagecom_metrics_df$specificity, 0.975)
upp_prec <- quantile(rf_vlsymp_wagecom_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(rf_vlsymp_wagecom_metrics_df$F1_score, 0.975)
upp_auc <- quantile(rf_vlsymp_wagecom_metrics_df$AUC_value, 0.975)

rf_vlsymp_wagecom_metrics_summary['low_acc_train'] <- low_acc_train
rf_vlsymp_wagecom_metrics_summary['low_acc_test'] <- low_acc_test
rf_vlsymp_wagecom_metrics_summary['low_sens'] <- low_sens
rf_vlsymp_wagecom_metrics_summary['low_spec'] <- low_spec
rf_vlsymp_wagecom_metrics_summary['low_prec'] <- low_prec
rf_vlsymp_wagecom_metrics_summary['low_f1_sc'] <- low_f1_sc
rf_vlsymp_wagecom_metrics_summary['low_auc'] <- low_auc

rf_vlsymp_wagecom_metrics_summary['upp_acc_train'] <- upp_acc_train
rf_vlsymp_wagecom_metrics_summary['upp_acc_test'] <- upp_acc_test
rf_vlsymp_wagecom_metrics_summary['upp_sens'] <- upp_sens
rf_vlsymp_wagecom_metrics_summary['upp_spec'] <- upp_spec
rf_vlsymp_wagecom_metrics_summary['upp_prec'] <- upp_prec
rf_vlsymp_wagecom_metrics_summary['upp_f1_sc'] <- upp_f1_sc
rf_vlsymp_wagecom_metrics_summary['upp_auc'] <- upp_auc

rf_vlsymp_wagecom_metrics_summary
```

## Fitting data with VL at diagnosis
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Dataframe excluding Comorbidity, Age & with VL at diagnosis}
rf_vldiag_wagecom_list <- foreach(i = 1: 100, .packages = c("dplyr", "randomForest", "pROC", "fastshap", "shapviz")) %dopar% {
    split <- split_list_vldiag_wagecom[[i]]
    train_df <- split$train
    test_df <- split$test

    # Fitting the random forest model
    rf_vldiag_wagecom <- randomForest(outcome ~ ., data = train_df, importance = TRUE)

    # Make prediction on the testing set
    prediction_rf_vldiag_wagecom <- predict(rf_vldiag_wagecom, newdata = test_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_vldiag_wagecom <- table(prediction_rf_vldiag_wagecom, test_df$outcome)
    # Compute accuracy on the testing set
    acc_rf_test <- sum(diag(cfm_rf_vldiag_wagecom) / sum(cfm_rf_vldiag_wagecom))

    # Make prediction on the training set
    prediction_rf_train <- predict(rf_vldiag_wagecom, newdata = train_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_vldiag_wagecom_train <- table(prediction_rf_train, train_df$outcome)
    # Compute accuracy on the training set
    acc_rf_train <- sum(diag(cfm_rf_vldiag_wagecom_train) / sum(cfm_rf_vldiag_wagecom_train))

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_rf_vldiag_wagecom["Severe", "Severe"]
    FP <- cfm_rf_vldiag_wagecom["Severe", "Non severe"]
    TN <- cfm_rf_vldiag_wagecom["Non severe", "Non severe"]
    FN <- cfm_rf_vldiag_wagecom["Non severe", "Severe"]

    sensitivity_rf_vldiag_wagecom <- TP / (TP + FN)
    specificity_rf_vldiag_wagecom <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_rf_vldiag_wagecom <- TP / (TP + FP)
    f1_sc_rf_vldiag_wagecom <- 2 * ((prec_rf_vldiag_wagecom * sensitivity_rf_vldiag_wagecom) / (prec_rf_vldiag_wagecom + sensitivity_rf_vldiag_wagecom))

    # Compute AUROC
    pred_rf_vldiag_wagecom_res <- ifelse(prediction_rf_vldiag_wagecom == "Severe", 1, 0)
    roc_rf_vldiag_wagecom <- roc(test_df$outcome, pred_rf_vldiag_wagecom_res)
    auc_val_rf_vldiag_wagecom <- auc(roc_rf_vldiag_wagecom)
    
    # Compute SHAP values
    xvars <- colnames(train_df)[-4]
    pfun_rf <- function(object, newdata) predict(object, newdata, type = "prob")[, 2]
    shap_values_rf_vldiag_wagecom <- fastshap::explain(rf_vldiag_wagecom, X = train_df[, -4], pred_wrapper = pfun_rf)
    shp_rf_vldiag_wagecom <- shapviz(shap_values_rf_vldiag_wagecom, X = train_df[, -which(names(train_df) == "outcome")])

    # Rename variable
    shp_rf_vldiag_wagecom$X <- shp_rf_vldiag_wagecom$X %>% rename("Viral load at diagnosis" = "vl_sim")
    colnames(shp_rf_vldiag_wagecom$S) <- c("gender", "vaccination", "Viral load at diagnosis")
    
    list(model = rf_vldiag_wagecom, confusion_matrix = cfm_rf_vldiag_wagecom, accuracy_training = acc_rf_train, accuracy_testing = acc_rf_test,
          sensitivity = sensitivity_rf_vldiag_wagecom, specificity = specificity_rf_vldiag_wagecom, precision = prec_rf_vldiag_wagecom,
          F1_score = f1_sc_rf_vldiag_wagecom, AUC_value = auc_val_rf_vldiag_wagecom, SHAP_values = shp_rf_vldiag_wagecom, prediction = prediction_rf_vldiag_wagecom)
}
```

```{r, Stop clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
rf_vldiag_wagecom_metrics_df <- map_dfr(seq_along(rf_vldiag_wagecom_list), function(i) {
  result <- rf_vldiag_wagecom_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
rf_vldiag_wagecom_metrics_df <- as.data.frame(rf_vldiag_wagecom_metrics_df)

rf_vldiag_wagecom_metrics_summary <- rf_vldiag_wagecom_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(rf_vldiag_wagecom_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(rf_vldiag_wagecom_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(rf_vldiag_wagecom_metrics_df$sensitivity, 0.025)
low_spec <- quantile(rf_vldiag_wagecom_metrics_df$specificity, 0.025)
low_prec <- quantile(rf_vldiag_wagecom_metrics_df$precision, 0.025)
low_f1_sc <- quantile(rf_vldiag_wagecom_metrics_df$F1_score, 0.025)
low_auc <- quantile(rf_vldiag_wagecom_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(rf_vldiag_wagecom_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(rf_vldiag_wagecom_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(rf_vldiag_wagecom_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(rf_vldiag_wagecom_metrics_df$specificity, 0.975)
upp_prec <- quantile(rf_vldiag_wagecom_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(rf_vldiag_wagecom_metrics_df$F1_score, 0.975)
upp_auc <- quantile(rf_vldiag_wagecom_metrics_df$AUC_value, 0.975)

rf_vldiag_wagecom_metrics_summary['low_acc_train'] <- low_acc_train
rf_vldiag_wagecom_metrics_summary['low_acc_test'] <- low_acc_test
rf_vldiag_wagecom_metrics_summary['low_sens'] <- low_sens
rf_vldiag_wagecom_metrics_summary['low_spec'] <- low_spec
rf_vldiag_wagecom_metrics_summary['low_prec'] <- low_prec
rf_vldiag_wagecom_metrics_summary['low_f1_sc'] <- low_f1_sc
rf_vldiag_wagecom_metrics_summary['low_auc'] <- low_auc

rf_vldiag_wagecom_metrics_summary['upp_acc_train'] <- upp_acc_train
rf_vldiag_wagecom_metrics_summary['upp_acc_test'] <- upp_acc_test
rf_vldiag_wagecom_metrics_summary['upp_sens'] <- upp_sens
rf_vldiag_wagecom_metrics_summary['upp_spec'] <- upp_spec
rf_vldiag_wagecom_metrics_summary['upp_prec'] <- upp_prec
rf_vldiag_wagecom_metrics_summary['upp_f1_sc'] <- upp_f1_sc
rf_vldiag_wagecom_metrics_summary['upp_auc'] <- upp_auc

rf_vldiag_wagecom_metrics_summary
```

# Fitting data with only VL information
## Fitting data with only VL since symptom onset
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Full dataframe with VL since symptom onset}
rf_vlsymp_only_list <- foreach(i = 1: 100, .packages = c("dplyr", "randomForest", "pROC", "fastshap", "shapviz")) %dopar% {
    split <- split_list[[i]]
    train_df <- split$train %>% select("0", 'outcome') %>% rename("vl_sim_symp" = "0")
    test_df <- split$test %>% select("0", 'outcome') %>% rename("vl_sim_symp" = "0")

    # Fitting the random forest model
    rf_vlsymp <- randomForest(outcome ~ ., data = train_df, importance = TRUE)

    # Make prediction on the testing set
    prediction_rf_vlsymp <- predict(rf_vlsymp, newdata = test_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_vlsymp <- table(prediction_rf_vlsymp, test_df$outcome)
    # Compute accuracy on the testing set
    acc_rf_test <- sum(diag(cfm_rf_vlsymp) / sum(cfm_rf_vlsymp))

    # Make prediction on the training set
    prediction_rf_train <- predict(rf_vlsymp, newdata = train_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_vlsymp_train <- table(prediction_rf_train, train_df$outcome)
    # Compute accuracy on the training set
    acc_rf_train <- sum(diag(cfm_rf_vlsymp_train) / sum(cfm_rf_vlsymp_train))

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_rf_vlsymp["Severe", "Severe"]
    FP <- cfm_rf_vlsymp["Severe", "Non severe"]
    TN <- cfm_rf_vlsymp["Non severe", "Non severe"]
    FN <- cfm_rf_vlsymp["Non severe", "Severe"]

    sensitivity_rf_vlsymp <- TP / (TP + FN)
    specificity_rf_vlsymp <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_rf_vlsymp <- TP / (TP + FP)
    f1_sc_rf_vlsymp <- 2 * ((prec_rf_vlsymp * sensitivity_rf_vlsymp) / (prec_rf_vlsymp + sensitivity_rf_vlsymp))

    # Compute & plot AUROC plot
    pred_rf_vlsymp_res <- ifelse(prediction_rf_vlsymp == "Severe", 1, 0)
    roc_rf_vlsymp <- roc(test_df$outcome, pred_rf_vlsymp_res)
    auc_val_rf_vlsymp <- auc(roc_rf_vlsymp)

    rocplot_rf_vlsymp <- plot.roc(test_df$outcome, pred_rf_vlsymp_res, main = "ROC Curve for Random Forest Model",
                              ci = TRUE, print.auc = TRUE, percent = TRUE, col = "blue")
    
    # Compute & plot SHAP values
    xvars <- colnames(train_df)[-2]
    pfun_rf <- function(object, newdata) predict(object, newdata, type = "prob")[, 2]
    shap_values_rf_vlsymp <- fastshap::explain(rf_vlsymp, X = train_df[, -2, drop = FALSE], pred_wrapper = pfun_rf)
    shp_rf_vlsymp <- shapviz(shap_values_rf_vlsymp, X = train_df[, -which(names(train_df) == "outcome"), drop = FALSE])

    # Rename variable
    shp_rf_vlsymp$X <- shp_rf_vlsymp$X %>% rename("Viral load at symptom onset" = "vl_sim_symp")
    colnames(shp_rf_vlsymp$S) <- c("Viral load at symptom onset")

    list(#model = rf_vlsymp, 
         confusion_matrix = cfm_rf_vlsymp, accuracy_training = acc_rf_train, accuracy_testing = acc_rf_test,
          sensitivity = sensitivity_rf_vlsymp, specificity = specificity_rf_vlsymp, precision = prec_rf_vlsymp,
          F1_score = f1_sc_rf_vlsymp, AUC_value = auc_val_rf_vlsymp, SHAP_values = shp_rf_vlsymp, prediction = prediction_rf_vlsymp)
}
```

```{r, Stop clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
rf_vlsymp_only_metrics_df <- map_dfr(seq_along(rf_vlsymp_only_list), function(i) {
  result <- rf_vlsymp_only_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
rf_vlsymp_only_metrics_df <- as.data.frame(rf_vlsymp_only_metrics_df)

rf_vlsymp_only_metrics_summary <- rf_vlsymp_only_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(rf_vlsymp_only_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(rf_vlsymp_only_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(rf_vlsymp_only_metrics_df$sensitivity, 0.025)
low_spec <- quantile(rf_vlsymp_only_metrics_df$specificity, 0.025)
low_prec <- quantile(rf_vlsymp_only_metrics_df$precision, 0.025)
low_f1_sc <- quantile(rf_vlsymp_only_metrics_df$F1_score, 0.025)
low_auc <- quantile(rf_vlsymp_only_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(rf_vlsymp_only_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(rf_vlsymp_only_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(rf_vlsymp_only_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(rf_vlsymp_only_metrics_df$specificity, 0.975)
upp_prec <- quantile(rf_vlsymp_only_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(rf_vlsymp_only_metrics_df$F1_score, 0.975)
upp_auc <- quantile(rf_vlsymp_only_metrics_df$AUC_value, 0.975)

rf_vlsymp_only_metrics_summary['low_acc_train'] <- low_acc_train
rf_vlsymp_only_metrics_summary['low_acc_test'] <- low_acc_test
rf_vlsymp_only_metrics_summary['low_sens'] <- low_sens
rf_vlsymp_only_metrics_summary['low_spec'] <- low_spec
rf_vlsymp_only_metrics_summary['low_prec'] <- low_prec
rf_vlsymp_only_metrics_summary['low_f1_sc'] <- low_f1_sc
rf_vlsymp_only_metrics_summary['low_auc'] <- low_auc

rf_vlsymp_only_metrics_summary['upp_acc_train'] <- upp_acc_train
rf_vlsymp_only_metrics_summary['upp_acc_test'] <- upp_acc_test
rf_vlsymp_only_metrics_summary['upp_sens'] <- upp_sens
rf_vlsymp_only_metrics_summary['upp_spec'] <- upp_spec
rf_vlsymp_only_metrics_summary['upp_prec'] <- upp_prec
rf_vlsymp_only_metrics_summary['upp_f1_sc'] <- upp_f1_sc
rf_vlsymp_metrics_summary['upp_auc'] <- upp_auc

rf_vlsymp_only_metrics_summary
```

## Fitting data with only VL at diagnosis
```{r, Setup clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

```{r, Full dataframe with VL at diagnosis}
rf_vldiag_only_list <- foreach(i = 1: 100, .packages = c("dplyr", "randomForest", "pROC", "fastshap", "shapviz")) %dopar% {
    split <- split_list[[i]]
    train_df <- split$train %>% select("vl_sim", "outcome")
    test_df <- split$test %>% select("vl_sim", "outcome")

    # Fitting the random forest model
    rf_vldiag <- randomForest(outcome ~ ., data = train_df, importance = TRUE)

    # Make prediction on the testing set
    prediction_rf_vldiag <- predict(rf_vldiag, newdata = test_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_vldiag <- table(prediction_rf_vldiag, test_df$outcome)
    # Compute accuracy on the testing set
    acc_rf_test <- sum(diag(cfm_rf_vldiag) / sum(cfm_rf_vldiag))

    # Make prediction on the training set
    prediction_rf_train <- predict(rf_vldiag, newdata = train_df, type = "class")
    # Compute the confusion matrix
    cfm_rf_vldiag_train <- table(prediction_rf_train, train_df$outcome)
    # Compute accuracy on the training set
    acc_rf_train <- sum(diag(cfm_rf_vldiag_train) / sum(cfm_rf_vldiag_train))

    # Extract elements from the confusion matrix & compute sensitivity and specificity
    TP <- cfm_rf_vldiag["Severe", "Severe"]
    FP <- cfm_rf_vldiag["Severe", "Non severe"]
    TN <- cfm_rf_vldiag["Non severe", "Non severe"]
    FN <- cfm_rf_vldiag["Non severe", "Severe"]

    sensitivity_rf_vldiag <- TP / (TP + FN)
    specificity_rf_vldiag <- TN / (TN + FP)

    # Compute the precision and F1-Score
    prec_rf_vldiag <- TP / (TP + FP)
    f1_sc_rf_vldiag <- 2 * ((prec_rf_vldiag * sensitivity_rf_vldiag) / (prec_rf_vldiag + sensitivity_rf_vldiag))

    # Compute AUROC plot
    pred_rf_vldiag_res <- ifelse(prediction_rf_vldiag == "Severe", 1, 0)
    roc_rf_vldiag <- roc(test_df$outcome, pred_rf_vldiag_res)
    auc_val_rf_vldiag <- auc(roc_rf_vldiag)
    
    # Compute SHAP values
    #xvars <- colnames(train_df)[-2]
    pfun_rf <- function(object, newdata) predict(object, newdata, type = "prob")[, 2]
    shap_values_rf_vldiag <- fastshap::explain(rf_vldiag, X = train_df[, -2, drop = FALSE], pred_wrapper = pfun_rf)
    shp_rf_vldiag <- shapviz(shap_values_rf_vldiag, X = train_df[, -which(names(train_df) == "outcome"), drop = FALSE])

    # Rename variable
    shp_rf_vldiag$X <- shp_rf_vldiag$X %>% rename("Viral load at diagnosis" = "vl_sim")
    colnames(shp_rf_vldiag$S) <- c("Viral load at diagnosis")
    
    list(#model = rf_vldiag, 
         confusion_matrix = cfm_rf_vldiag, accuracy_training = acc_rf_train, accuracy_testing = acc_rf_test,
          sensitivity = sensitivity_rf_vldiag, specificity = specificity_rf_vldiag, precision = prec_rf_vldiag,
          F1_score = f1_sc_rf_vldiag, AUC_value = auc_val_rf_vldiag, SHAP_values = shp_rf_vldiag, prediction = prediction_rf_vldiag)
}
```

```{r, Stop clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
rf_vldiag_only_metrics_df <- map_dfr(seq_along(rf_vldiag_only_list), function(i) {
  result <- rf_vldiag_only_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
rf_vldiag_only_metrics_df <- as.data.frame(rf_vldiag_only_metrics_df)

rf_vldiag_only_metrics_summary <- rf_vldiag_only_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(rf_vldiag_only_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(rf_vldiag_only_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(rf_vldiag_only_metrics_df$sensitivity, 0.025)
low_spec <- quantile(rf_vldiag_only_metrics_df$specificity, 0.025)
low_prec <- quantile(rf_vldiag_only_metrics_df$precision, 0.025)
low_f1_sc <- quantile(rf_vldiag_only_metrics_df$F1_score, 0.025)
low_auc <- quantile(rf_vldiag_only_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(rf_vldiag_only_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(rf_vldiag_only_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(rf_vldiag_only_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(rf_vldiag_only_metrics_df$specificity, 0.975)
upp_prec <- quantile(rf_vldiag_only_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(rf_vldiag_only_metrics_df$F1_score, 0.975)
upp_auc <- quantile(rf_vldiag_only_metrics_df$AUC_value, 0.975)

rf_vldiag_only_metrics_summary['low_acc_train'] <- low_acc_train
rf_vldiag_only_metrics_summary['low_acc_test'] <- low_acc_test
rf_vldiag_only_metrics_summary['low_sens'] <- low_sens
rf_vldiag_only_metrics_summary['low_spec'] <- low_spec
rf_vldiag_only_metrics_summary['low_prec'] <- low_prec
rf_vldiag_only_metrics_summary['low_f1_sc'] <- low_f1_sc
rf_vldiag_only_metrics_summary['low_auc'] <- low_auc

rf_vldiag_only_metrics_summary['upp_acc_train'] <- upp_acc_train
rf_vldiag_only_metrics_summary['upp_acc_test'] <- upp_acc_test
rf_vldiag_only_metrics_summary['upp_sens'] <- upp_sens
rf_vldiag_only_metrics_summary['upp_spec'] <- upp_spec
rf_vldiag_only_metrics_summary['upp_prec'] <- upp_prec
rf_vldiag_only_metrics_summary['upp_f1_sc'] <- upp_f1_sc
rf_vldiag_only_metrics_summary['upp_auc'] <- upp_auc

rf_vldiag_only_metrics_summary
```

# Saving all data in this session
```{r, Saving RData file}
save.image(file = paste0(getwd(), '/Random_forest.RData'))
```

# Show the session info
```{r, Session Info}
sessionInfo()
```