---
title: "Supplementary_figures3_4_5"
output: html_document
---

# Setup environment & load data
```{r, Import libraries}
library(dplyr)
library(ggplot2)
library(stringr)
library(tidyr)
library(shapviz)
library(fastshap)
library(SHAPforxgboost)
library(purrr)
library(ggpubr)
library(cowplot)
```

```{r, Load data into environment}
load(paste0(path, '/Random_forest.RData'))
load(paste0(path, '/XGBoost.RData'))
load(paste0(path, '/LightGBM.RData'))
```

# Define functions
```{r, Define functions}
# Function for SHAP summary plot
shap_plot_func <- function(data) {
  sv_importance(data$SHAP_values, kind = "beeswarm", size = rel(1)) +
    scale_color_viridis_c(name = "Values")  + #,trans = "reverse")  +
    theme(axis.line = element_line(color = "black"),
          axis.text.x = element_text(size = rel(1)),
          axis.text.y = element_text(size = rel(1)),
          axis.title.x = element_text(family = "Helvetica", size = rel(1)),
          axis.title.y = element_text(family = "Helvetica"),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_blank(),
          legend.title = element_text(size = rel(1)),
          legend.text = element_text(size = rel(1)),
          legend.key.size = unit(3, "cm"))
}

# Function to extract and compute the mean and 95% confidence interval of SHAP values over 100 simulation runs
mean_shap <- function(data) {
  # Grab the shapviz objects
  sv_list <- map(data, \(x) x$SHAP_values)

  # Pooled |SHAP| across all runs (observation-level), then summarize
  shap_long <- imap_dfr(sv_list, \(sv, run) 
                {
                  as_tibble(abs(sv$S)) %>%
                  mutate(.run = as.integer(run)) %>%
                  pivot_longer(
                    cols = - .run,
                    names_to = "feature",
                    values_to = "abs_shap")
                })

  imp_avg <- shap_long %>%
              group_by(feature) %>%
              summarise(
                mean_abs_shap = mean(abs_shap, na.rm = TRUE),
                lower = quantile(abs_shap, probs = 0.025, na.rm = TRUE),
                upper = quantile(abs_shap, probs = 0.975, na.rm = TRUE),
                .groups = "drop") %>%
              arrange(desc(mean_abs_shap))
  return(imp_avg)
}

# Function for Rank of mean SHAP value over 100 simulation runs
rank_plot <- function(data) {
  ggplot(data, aes(x = reorder(feature, mean_abs_shap), y = mean_abs_shap, color = feature)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.1, linewidth = 1.2) +
  geom_point(size = 1.5, shape = 21, stroke = 1.2) +
  #scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.25)) +
  coord_flip() +
  labs(
    title = "Average SHAP feature importance across 100 runs",
    x = NULL,
    y = "Mean |SHAP|"
  ) +
  theme_classic() +
    theme(legend.position = "none")
}
```

## Compile & plot the SHAP values plot for each models
### Random forest
#### Viral load at symptom onset
```{r, SHAP values plot for Random forest with viral load at symptom onset}
# Fetching the model with the highest accuracy
rf_vlsymp_run <- as.integer(rf_vlsymp_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_rf_vlsymp <- shap_plot_func(rf_vlsymp_list[[rf_vlsymp_run]])
shp_rf_vlsymp
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_rf_vlsymp <- mean_shap(rf_vlsymp_list)

# Plot of average importance
rank_rf_vlsymp <- rank_plot(mean_rf_vlsymp)
rank_rf_vlsymp
```

#### Viral load at diagnosis
```{r, SHAP values plot for Random forest with viral load at diagnosis}
# Fetching the model with the highest accuracy
rf_vldiag_run <- as.integer(rf_vldiag_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_rf_vldiag <- shap_plot_func(rf_vldiag_list[[rf_vldiag_run]])
shp_rf_vldiag
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_rf_vldiag <- mean_shap(rf_vldiag_list)

# Plot of average importance
rank_rf_vldiag <- rank_plot(mean_rf_vldiag)
rank_rf_vldiag
```

#### Without viral load point
```{r, SHAP values plot for Random forest without viral load point}
# Fetching the model with the highest accuracy
rf_fil_run <- as.integer(rf_fil_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_rf_fil <- shap_plot_func(rf_fil_list[[rf_fil_run]])
shp_rf_fil
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_rf_fil <- mean_shap(rf_fil_list)

# Plot of average importance
rank_rf_fil <- rank_plot(mean_rf_fil)
rank_rf_fil
```

#### Without comorbidity
##### Without comorbidity & with viral load since symptom onset
```{r, SHAP values plot for Random forest without comorbidity & with viral load at symptom onset}
rf_vlsymp_wcom_run <- as.integer(rf_vlsymp_wcom_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_rf_vlsymp_wcom <- shap_plot_func(rf_vlsymp_wcom_list[[rf_vlsymp_wcom_run]])
shp_rf_vlsymp_wcom
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_rf_vlsymp_wcom <- mean_shap(rf_vlsymp_wcom_list)

# Plot of average importance
rank_rf_vlsymp_wcom <- rank_plot(mean_rf_vlsymp_wcom)
rank_rf_vlsymp_wcom
```

##### Withou comorbidity & with viral load at diagnosis
```{r, SHAP values plot for Random forest without comorbidity & with viral load at diagnosis}
# Fetching the model with the highest accuracy
rf_vldiag_wcom_run <- as.integer(rf_vldiag_wcom_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_rf_vldiag_wcom <- shap_plot_func(rf_vldiag_wcom_list[[rf_vldiag_wcom_run]])
shp_rf_vldiag_wcom
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_rf_vldiag_wcom <- mean_shap(rf_vldiag_wcom_list)

# Plot of average importance
rank_rf_vldiag_wcom <- rank_plot(mean_rf_vldiag_wcom)
rank_rf_vldiag_wcom
```

##### Without comorbidity & viral load point
```{r, SHAP values plot for Random forest without comorbidity & viral load point}
# Fetching the model with the highest accuracy
rf_wvlncom_run <- as.integer(rf_wvlncom_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_rf_wvlncom <- shap_plot_func(rf_wvlncom_list[[rf_wvlncom_run]])
shp_rf_wvlncom
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_rf_wvlncom <- mean_shap(rf_wvlncom_list)

# Plot of average importance
rank_rf_wvlncom <- rank_plot(mean_rf_wvlncom)
rank_rf_wvlncom
```

#### Without Age
##### Without age & with viral load since symptom onset
```{r, SHAP values plot for Random forest without age & with viral load at symptom onset}
rf_vlsymp_wage_run <- as.integer(rf_vlsymp_wage_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_rf_vlsymp_wage <- shap_plot_func(rf_vlsymp_wage_list[[rf_vlsymp_wage_run]])
shp_rf_vlsymp_wage
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_rf_vlsymp_wage <- mean_shap(rf_vlsymp_wage_list)

# Plot of average importance
rank_rf_vlsymp_wage <- rank_plot(mean_rf_vlsymp_wage)
rank_rf_vlsymp_wage
```

##### Withou age & with viral load at diagnosis
```{r, SHAP values plot for Random forest without age & with viral load at diagnosis}
# Fetching the model with the highest accuracy
rf_vldiag_wage_run <- as.integer(rf_vldiag_wage_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_rf_vldiag_wage <- shap_plot_func(rf_vldiag_wage_list[[rf_vldiag_wage_run]])
shp_rf_vldiag_wage
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_rf_vldiag_wage <- mean_shap(rf_vldiag_wage_list)

# Plot of average importance
rank_rf_vldiag_wage <- rank_plot(mean_rf_vldiag_wage)
rank_rf_vldiag_wage
```

##### Without age & viral load point
```{r, SHAP values plot for Random forest without age & viral load point}
# Fetching the model with the highest accuracy
rf_wvlnage_run <- as.integer(rf_wvlnage_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_rf_wvlnage <- shap_plot_func(rf_wvlnage_list[[rf_wvlnage_run]])
shp_rf_wvlnage
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_rf_wvlnage <- mean_shap(rf_wvlnage_list)

# Plot of average importance
rank_rf_wvlnage <- rank_plot(mean_rf_wvlnage)
rank_rf_wvlnage
```

#### Without comorbidity and age
##### Without comorbidity & age with viral load since symptom onset
```{r, SHAP values plot for Random forest without comorbidity & age with viral load at symptom onset}
rf_vlsymp_wagecom_run <- as.integer(rf_vlsymp_wagecom_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_rf_vlsymp_wagecom <- shap_plot_func(rf_vlsymp_wagecom_list[[rf_vlsymp_wagecom_run]])
shp_rf_vlsymp_wagecom
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_rf_vlsymp_wagecom <- mean_shap(rf_vlsymp_wagecom_list)

# Plot of average importance
rank_rf_vlsymp_wagecom <- rank_plot(mean_rf_vlsymp_wagecom)
rank_rf_vlsymp_wagecom
```

##### Withou comorbidity & age with viral load at diagnosis
```{r, SHAP values plot for Random forest without comorbidity & age with viral load at diagnosis}
# Fetching the model with the highest accuracy
rf_vldiag_wagecom_run <- as.integer(rf_vldiag_wagecom_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_rf_vldiag_wagecom <- shap_plot_func(rf_vldiag_wagecom_list[[rf_vldiag_wagecom_run]])
shp_rf_vldiag_wagecom
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_rf_vldiag_wagecom <- mean_shap(rf_vldiag_wagecom_list)

# Plot of average importance
rank_rf_vldiag_wagecom <- rank_plot(mean_rf_vldiag_wagecom)
rank_rf_vldiag_wagecom
```

##### Without comorbidity & age viral load point
```{r, SHAP values plot for Random forest without comorbidity & age viral load point}
# Fetching the model with the highest accuracy
rf_wvlnagecom_run <- as.integer(rf_wvlnagecom_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_rf_wvlnagecom <- shap_plot_func(rf_wvlnagecom_list[[rf_wvlnagecom_run]])
shp_rf_wvlnagecom
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_rf_wvlnagecom <- mean_shap(rf_wvlnagecom_list)

# Plot of average importance
rank_rf_wvlnagecom <- rank_plot(mean_rf_wvlnagecom)
rank_rf_wvlnagecom
```

### XGBoost
```{r, Rename variables for XGBoost}
for (i in 1:100) {
  # Rename variable
  xgb_vlsymp_list[[i]]$SHAP_values$X <- xgb_vlsymp_list[[i]]$SHAP_values$X %>% rename("Viral load at symptom onset" = "vl_sim_symp")
  colnames(xgb_vlsymp_list[[i]]$SHAP_values$S) <- c("age>=80", "age60-79", "genderFemale", "vaccinationBooster", "vaccinationFull", "comorbidity>=3", "comorbidity1-2",
                                                         "Viral load at symptom onset")
  
  # Rename variable
  xgb_vldiag_list[[i]]$SHAP_values$X <- xgb_vldiag_list[[i]]$SHAP_values$X %>% rename("Viral load at diagnosis" = "vl_sim")
  colnames(xgb_vldiag_list[[i]]$SHAP_values$S) <- c("age>=80", "age60-79", "genderFemale", "vaccinationBooster", "vaccinationFull", "comorbidity>=3", "comorbidity1-2",
                                                         "Viral load at diagnosis")
  
  # Rename variable
  xgb_vlsymp_wcom_list[[i]]$SHAP_values$X <- xgb_vlsymp_wcom_list[[i]]$SHAP_values$X %>% rename("Viral load at symptom onset" = "vl_sim_symp")
  colnames(xgb_vlsymp_wcom_list[[i]]$SHAP_values$S) <- c("age>=80", "age60-79", "genderFemale", "vaccinationBooster", "vaccinationFull", "Viral load at symptom onset")
  
  # Rename variable
  xgb_vldiag_wcom_list[[i]]$SHAP_values$X <- xgb_vldiag_wcom_list[[i]]$SHAP_values$X %>% rename("Viral load at diagnosis" = "vl_sim")
  colnames(xgb_vldiag_wcom_list[[i]]$SHAP_values$S) <- c("age>=80", "age60-79", "genderFemale", "vaccinationBooster", "vaccinationFull", "Viral load at diagnosis")
  
  # Rename variable
  xgb_vlsymp_wage_list[[i]]$SHAP_values$X <- xgb_vlsymp_wage_list[[i]]$SHAP_values$X %>% rename("Viral load at symptom onset" = "vl_sim_symp")
  colnames(xgb_vlsymp_wage_list[[i]]$SHAP_values$S) <- c("genderFemale", "vaccinationBooster", "vaccinationFull", "comorbidity>=3", "comorbidity1-2", "Viral load at symptom onset")
  
  # Rename variable
  xgb_vldiag_wage_list[[i]]$SHAP_values$X <- xgb_vldiag_wage_list[[i]]$SHAP_values$X %>% rename("Viral load at diagnosis" = "vl_sim")
  colnames(xgb_vldiag_wage_list[[i]]$SHAP_values$S) <- c("genderFemale", "vaccinationBooster", "vaccinationFull", "comorbidity>=3", "comorbidity1-2", "Viral load at diagnosis")
  
  # Rename variable
  xgb_vlsymp_wagecom_list[[i]]$SHAP_values$X <- xgb_vlsymp_wagecom_list[[i]]$SHAP_values$X %>% rename("Viral load at symptom onset" = "vl_sim_symp")
  colnames(xgb_vlsymp_wagecom_list[[i]]$SHAP_values$S) <- c("genderFemale", "vaccinationBooster", "vaccinationFull", "Viral load at symptom onset")
  
  # Rename variable
  xgb_vldiag_wagecom_list[[i]]$SHAP_values$X <- xgb_vldiag_wagecom_list[[i]]$SHAP_values$X %>% rename("Viral load at diagnosis" = "vl_sim")
  colnames(xgb_vldiag_wagecom_list[[i]]$SHAP_values$S) <- c("genderFemale", "vaccinationBooster", "vaccinationFull", "Viral load at diagnosis")
}
```

#### Viral load at symptom onset
```{r, SHAP values plot for XGBoost with viral load at symptom onset}
# Fetching the model with the highest accuracy
xgb_vlsymp_run <- as.integer(xgb_vlsymp_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_xgb_vlsymp <- shap_plot_func(xgb_vlsymp_list[[xgb_vlsymp_run]])
shp_xgb_vlsymp
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_xgb_vlsymp <- mean_shap(xgb_vlsymp_list)

# Plot of average importance
rank_xgb_vlsymp <- rank_plot(mean_xgb_vlsymp)
rank_xgb_vlsymp
```

#### Viral load at diagnosis
```{r, SHAP values plot for XGBoost with viral load at diagnosis}
# Fetching the model with the highest accuracy
xgb_vldiag_run <- as.integer(xgb_vldiag_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_xgb_vldiag <- shap_plot_func(xgb_vldiag_list[[xgb_vldiag_run]])
shp_xgb_vldiag
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_xgb_vldiag <- mean_shap(xgb_vldiag_list)

# Plot of average importance
rank_xgb_vldiag <- rank_plot(mean_xgb_vldiag)
rank_xgb_vldiag
```

#### Without viral load point
```{r, SHAP values plot for XGBoost without viral load point}
# Fetching the model with the highest accuracy
xgb_fil_run <- as.integer(xgb_fil_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_xgb_fil <- shap_plot_func(xgb_fil_list[[xgb_fil_run]])
shp_xgb_fil
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_xgb_fil <- mean_shap(xgb_fil_list)

# Plot of average importance
rank_xgb_fil <- rank_plot(mean_xgb_fil)
rank_xgb_fil
```

#### Without comorbidity
##### Without comorbidity & with viral load since symptom onset
```{r, SHAP values plot for XGBoost without comorbidity & with viral load at symptom onset}
xgb_vlsymp_wcom_run <- as.integer(xgb_vlsymp_wcom_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_xgb_vlsymp_wcom <- shap_plot_func(xgb_vlsymp_wcom_list[[xgb_vlsymp_wcom_run]])
shp_xgb_vlsymp_wcom
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_xgb_vlsymp_wcom <- mean_shap(xgb_vlsymp_wcom_list)

# Plot of average importance
rank_xgb_vlsymp_wcom <- rank_plot(mean_xgb_vlsymp_wcom)
rank_xgb_vlsymp_wcom
```

##### Withou comorbidity & with viral load at diagnosis
```{r, SHAP values plot for XGBoost without comorbidity & with viral load at diagnosis}
# Fetching the model with the highest accuracy
xgb_vldiag_wcom_run <- as.integer(xgb_vldiag_wcom_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_xgb_vldiag_wcom <- shap_plot_func(xgb_vldiag_wcom_list[[xgb_vldiag_wcom_run]])
shp_xgb_vldiag_wcom
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_xgb_vldiag_wcom <- mean_shap(xgb_vldiag_wcom_list)

# Plot of average importance
rank_xgb_vldiag_wcom <- rank_plot(mean_xgb_vldiag_wcom)
rank_xgb_vldiag_wcom
```

##### Without comorbidity & viral load point
```{r, SHAP values plot for XGBoost without comorbidity & viral load point}
# Fetching the model with the highest accuracy
xgb_wvlncom_run <- as.integer(xgb_wvlncom_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_xgb_wvlncom <- shap_plot_func(xgb_wvlncom_list[[xgb_wvlncom_run]])
shp_xgb_wvlncom
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_xgb_wvlncom <- mean_shap(xgb_wvlncom_list)

# Plot of average importance
rank_xgb_wvlncom <- rank_plot(mean_xgb_wvlncom)
rank_xgb_wvlncom
```

#### Without Age
##### Without age & with viral load since symptom onset
```{r, SHAP values plot for XGBoost without age & with viral load at symptom onset}
xgb_vlsymp_wage_run <- as.integer(xgb_vlsymp_wage_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_xgb_vlsymp_wage <- shap_plot_func(xgb_vlsymp_wage_list[[xgb_vlsymp_wage_run]])
shp_xgb_vlsymp_wage
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_xgb_vlsymp_wage <- mean_shap(xgb_vlsymp_wage_list)

# Plot of average importance
rank_xgb_vlsymp_wage <- rank_plot(mean_xgb_vlsymp_wage)
rank_xgb_vlsymp_wage
```

##### Withou age & with viral load at diagnosis
```{r, SHAP values plot for XGBoost without age & with viral load at diagnosis}
# Fetching the model with the highest accuracy
xgb_vldiag_wage_run <- as.integer(xgb_vldiag_wage_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_xgb_vldiag_wage <- shap_plot_func(xgb_vldiag_wage_list[[xgb_vldiag_wage_run]])
shp_xgb_vldiag_wage
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_xgb_vldiag_wage <- mean_shap(xgb_vldiag_wage_list)

# Plot of average importance
rank_xgb_vldiag_wage <- rank_plot(mean_xgb_vldiag_wage)
rank_xgb_vldiag_wage
```

##### Without age & viral load point
```{r, SHAP values plot for XGBoost without age & viral load point}
# Fetching the model with the highest accuracy
xgb_wvlnage_run <- as.integer(xgb_wvlnage_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_xgb_wvlnage <- shap_plot_func(xgb_wvlnage_list[[xgb_wvlnage_run]])
shp_xgb_wvlnage
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_xgb_wvlnage <- mean_shap(xgb_wvlnage_list)

# Plot of average importance
rank_xgb_wvlnage <- rank_plot(mean_xgb_wvlnage)
rank_xgb_wvlnage
```

#### Without comorbidity and age
##### Without comorbidity & age with viral load since symptom onset
```{r, SHAP values plot for XGBoost without comorbidity & age with viral load at symptom onset}
xgb_vlsymp_wagecom_run <- as.integer(xgb_vlsymp_wagecom_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_xgb_vlsymp_wagecom <- shap_plot_func(xgb_vlsymp_wagecom_list[[xgb_vlsymp_wagecom_run]])
shp_xgb_vlsymp_wagecom
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_xgb_vlsymp_wagecom <- mean_shap(xgb_vlsymp_wagecom_list)

# Plot of average importance
rank_xgb_vlsymp_wagecom <- rank_plot(mean_xgb_vlsymp_wagecom)
rank_xgb_vlsymp_wagecom
```

##### Withou comorbidity & age with viral load at diagnosis
```{r, SHAP values plot for XGBoost without comorbidity & age with viral load at diagnosis}
# Fetching the model with the highest accuracy
xgb_vldiag_wagecom_run <- as.integer(xgb_vldiag_wagecom_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_xgb_vldiag_wagecom <- shap_plot_func(xgb_vldiag_wagecom_list[[xgb_vldiag_wagecom_run]])
shp_xgb_vldiag_wagecom
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_xgb_vldiag_wagecom <- mean_shap(xgb_vldiag_wagecom_list)

# Plot of average importance
rank_xgb_vldiag_wagecom <- rank_plot(mean_xgb_vldiag_wagecom)
rank_xgb_vldiag_wagecom
```

##### Without comorbidity & age viral load point
```{r, SHAP values plot for XGBoost without comorbidity & age viral load point}
# Fetching the model with the highest accuracy
xgb_wvlnagecom_run <- as.integer(xgb_wvlnagecom_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_xgb_wvlnagecom <- shap_plot_func(xgb_wvlnagecom_list[[xgb_wvlnagecom_run]])
shp_xgb_wvlnagecom
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_xgb_wvlnagecom <- mean_shap(xgb_wvlnagecom_list)

# Plot of average importance
rank_xgb_wvlnagecom <- rank_plot(mean_xgb_wvlnagecom)
rank_xgb_wvlnagecom
```

### LightGBM
```{r, Rename variables for lightgbm}
for (i in 1:100) {
  # Rename variable
  lightgbm_vlsymp_list[[i]]$SHAP_values$X <- lightgbm_vlsymp_list[[i]]$SHAP_values$X %>% rename("Viral load at symptom onset" = "vl_sim_symp")
  colnames(lightgbm_vlsymp_list[[i]]$SHAP_values$S) <- c("age>=80", "age60-79", "genderFemale", "vaccinationBooster", "vaccinationFull", "comorbidity>=3", "comorbidity1-2",
                                                         "Viral load at symptom onset")
  
  # Rename variable
  lightgbm_vldiag_list[[i]]$SHAP_values$X <- lightgbm_vldiag_list[[i]]$SHAP_values$X %>% rename("Viral load at diagnosis" = "vl_sim")
  colnames(lightgbm_vldiag_list[[i]]$SHAP_values$S) <- c("age>=80", "age60-79", "genderFemale", "vaccinationBooster", "vaccinationFull", "comorbidity>=3", "comorbidity1-2",
                                                         "Viral load at diagnosis")
  
  # Rename variable
  lightgbm_vlsymp_wcom_list[[i]]$SHAP_values$X <- lightgbm_vlsymp_wcom_list[[i]]$SHAP_values$X %>% rename("Viral load at symptom onset" = "vl_sim_symp")
  colnames(lightgbm_vlsymp_wcom_list[[i]]$SHAP_values$S) <- c("age>=80", "age60-79", "genderFemale", "vaccinationBooster", "vaccinationFull", "Viral load at symptom onset")
  
  # Rename variable
  lightgbm_vldiag_wcom_list[[i]]$SHAP_values$X <- lightgbm_vldiag_wcom_list[[i]]$SHAP_values$X %>% rename("Viral load at diagnosis" = "vl_sim")
  colnames(lightgbm_vldiag_wcom_list[[i]]$SHAP_values$S) <- c("age>=80", "age60-79", "genderFemale", "vaccinationBooster", "vaccinationFull", "Viral load at diagnosis")
  
  # Rename variable
  lightgbm_vlsymp_wage_list[[i]]$SHAP_values$X <- lightgbm_vlsymp_wage_list[[i]]$SHAP_values$X %>% rename("Viral load at symptom onset" = "vl_sim_symp")
  colnames(lightgbm_vlsymp_wage_list[[i]]$SHAP_values$S) <- c("genderFemale", "vaccinationBooster", "vaccinationFull", "comorbidity>=3", "comorbidity1-2", "Viral load at symptom onset")
  
  # Rename variable
  lightgbm_vldiag_wage_list[[i]]$SHAP_values$X <- lightgbm_vldiag_wage_list[[i]]$SHAP_values$X %>% rename("Viral load at diagnosis" = "vl_sim")
  colnames(lightgbm_vldiag_wage_list[[i]]$SHAP_values$S) <- c("genderFemale", "vaccinationBooster", "vaccinationFull", "comorbidity>=3", "comorbidity1-2", "Viral load at diagnosis")
  
  # Rename variable
  lightgbm_vlsymp_wagecom_list[[i]]$SHAP_values$X <- lightgbm_vlsymp_wagecom_list[[i]]$SHAP_values$X %>% rename("Viral load at symptom onset" = "vl_sim_symp")
  colnames(lightgbm_vlsymp_wagecom_list[[i]]$SHAP_values$S) <- c("genderFemale", "vaccinationBooster", "vaccinationFull", "Viral load at symptom onset")
  
  # Rename variable
  lightgbm_vldiag_wagecom_list[[i]]$SHAP_values$X <- lightgbm_vldiag_wagecom_list[[i]]$SHAP_values$X %>% rename("Viral load at diagnosis" = "vl_sim")
  colnames(lightgbm_vldiag_wagecom_list[[i]]$SHAP_values$S) <- c("genderFemale", "vaccinationBooster", "vaccinationFull", "Viral load at diagnosis")
}
```

#### Viral load at symptom onset
```{r, SHAP values plot for LightGBM with viral load at symptom onset}
# Fetching the model with the highest accuracy
lgb_vlsymp_run <- as.integer(lgb_vlsymp_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_lgb_vlsymp <- shap_plot_func(lightgbm_vlsymp_list[[lgb_vlsymp_run]])
shp_lgb_vlsymp
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_lgb_vlsymp <- mean_shap(lightgbm_vlsymp_list)

# Plot of average importance
rank_lgb_vlsymp <- rank_plot(mean_lgb_vlsymp)
rank_lgb_vlsymp
```

#### Viral load at diagnosis
```{r, SHAP values plot for LightGBM with viral load at diagnosis}
# Fetching the model with the highest accuracy
lgb_vldiag_run <- as.integer(lgb_vldiag_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_lgb_vldiag <- shap_plot_func(lightgbm_vldiag_list[[lgb_vldiag_run]])
shp_lgb_vldiag
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_lgb_vldiag <- mean_shap(lightgbm_vldiag_list)

# Plot of average importance
rank_lgb_vldiag <- rank_plot(mean_lgb_vldiag)
rank_lgb_vldiag
```

#### Without viral load point
```{r, SHAP values plot for LightGBM without viral load point}
# Fetching the model with the highest accuracy
lgb_fil_run <- as.integer(lgb_fil_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_lgb_fil <- shap_plot_func(lightgbm_fil_list[[lgb_fil_run]])
shp_lgb_fil
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_lgb_fil <- mean_shap(lightgbm_fil_list)

# Plot of average importance
rank_lgb_fil <- rank_plot(mean_lgb_fil)
rank_lgb_fil
```

#### Without comorbidity
##### Without comorbidity & with viral load since symptom onset
```{r, SHAP values plot for LightGBM without comorbidity & with viral load at symptom onset}
lgb_vlsymp_wcom_run <- as.integer(lgb_vlsymp_wcom_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_lgb_vlsymp_wcom <- shap_plot_func(lightgbm_vlsymp_wcom_list[[lgb_vlsymp_wcom_run]])
shp_lgb_vlsymp_wcom
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_lgb_vlsymp_wcom <- mean_shap(lightgbm_vlsymp_wcom_list)

# Plot of average importance
rank_lgb_vlsymp_wcom <- rank_plot(mean_lgb_vlsymp_wcom)
rank_lgb_vlsymp_wcom
```

##### Withou comorbidity & with viral load at diagnosis
```{r, SHAP values plot for LightGBM without comorbidity & with viral load at diagnosis}
# Fetching the model with the highest accuracy
lgb_vldiag_wcom_run <- as.integer(lgb_vldiag_wcom_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_lgb_vldiag_wcom <- shap_plot_func(lightgbm_vldiag_wcom_list[[lgb_vldiag_wcom_run]])
shp_lgb_vldiag_wcom
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_lgb_vldiag_wcom <- mean_shap(lightgbm_vldiag_wcom_list)

# Plot of average importance
rank_lgb_vldiag_wcom <- rank_plot(mean_lgb_vldiag_wcom)
rank_lgb_vldiag_wcom
```

##### Without comorbidity & viral load point
```{r, SHAP values plot for LightGBM without comorbidity & viral load point}
# Fetching the model with the highest accuracy
lgb_wvlncom_run <- as.integer(lgb_wvlncom_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_lgb_wvlncom <- shap_plot_func(lightgbm_wvlncom_list[[lgb_wvlncom_run]])
shp_lgb_wvlncom
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_lgb_wvlncom <- mean_shap(lightgbm_wvlncom_list)

# Plot of average importance
rank_lgb_wvlncom <- rank_plot(mean_lgb_wvlncom)
rank_lgb_wvlncom
```

#### Without Age
##### Without age & with viral load since symptom onset
```{r, SHAP values plot for LightGBM without age & with viral load at symptom onset}
lgb_vlsymp_wage_run <- as.integer(lgb_vlsymp_wage_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_lgb_vlsymp_wage <- shap_plot_func(lightgbm_vlsymp_wage_list[[lgb_vlsymp_wage_run]])
shp_lgb_vlsymp_wage
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_lgb_vlsymp_wage <- mean_shap(lightgbm_vlsymp_wage_list)

# Plot of average importance
rank_lgb_vlsymp_wage <- rank_plot(mean_lgb_vlsymp_wage)
rank_lgb_vlsymp_wage
```

##### Withou age & with viral load at diagnosis
```{r, SHAP values plot for LightGBM without age & with viral load at diagnosis}
# Fetching the model with the highest accuracy
lgb_vldiag_wage_run <- as.integer(lgb_vldiag_wage_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_lgb_vldiag_wage <- shap_plot_func(lightgbm_vldiag_wage_list[[lgb_vldiag_wage_run]])
shp_lgb_vldiag_wage
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_lgb_vldiag_wage <- mean_shap(lightgbm_vldiag_wage_list)

# Plot of average importance
rank_lgb_vldiag_wage <- rank_plot(mean_lgb_vldiag_wage)
rank_lgb_vldiag_wage
```

##### Without age & viral load point
```{r, SHAP values plot for LightGBM without age & viral load point}
# Fetching the model with the highest accuracy
lgb_wvlnage_run <- as.integer(lgb_wvlnage_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_lgb_wvlnage <- shap_plot_func(lightgbm_wvlnage_list[[lgb_wvlnage_run]])
shp_lgb_wvlnage
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_lgb_wvlnage <- mean_shap(lightgbm_wvlnage_list)

# Plot of average importance
rank_lgb_wvlnage <- rank_plot(mean_lgb_wvlnage)
rank_lgb_wvlnage
```

#### Without comorbidity and age
##### Without comorbidity & age with viral load since symptom onset
```{r, SHAP values plot for LightGBM without comorbidity & age with viral load at symptom onset}
lgb_vlsymp_wagecom_run <- as.integer(lgb_vlsymp_wagecom_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_lgb_vlsymp_wagecom <- shap_plot_func(lightgbm_vlsymp_wagecom_list[[lgb_vlsymp_wagecom_run]])
shp_lgb_vlsymp_wagecom
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_lgb_vlsymp_wagecom <- mean_shap(lightgbm_vlsymp_wagecom_list)

# Plot of average importance
rank_lgb_vlsymp_wagecom <- rank_plot(mean_lgb_vlsymp_wagecom)
rank_lgb_vlsymp_wagecom
```

##### Withou comorbidity & age with viral load at diagnosis
```{r, SHAP values plot for LightGBM without comorbidity & age with viral load at diagnosis}
# Fetching the model with the highest accuracy
lgb_vldiag_wagecom_run <- as.integer(lgb_vldiag_wagecom_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_lgb_vldiag_wagecom <- shap_plot_func(lightgbm_vldiag_wagecom_list[[lgb_vldiag_wagecom_run]])
shp_lgb_vldiag_wagecom
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_lgb_vldiag_wagecom <- mean_shap(lightgbm_vldiag_wagecom_list)

# Plot of average importance
rank_lgb_vldiag_wagecom <- rank_plot(mean_lgb_vldiag_wagecom)
rank_lgb_vldiag_wagecom
```

##### Without comorbidity & age viral load point
```{r, SHAP values plot for LightGBM without comorbidity & age viral load point}
# Fetching the model with the highest accuracy
lgb_wvlnagecom_run <- as.integer(lgb_wvlnagecom_metrics_df %>% filter(accuracy_test == max(accuracy_test)) %>% select(run) %>% slice_head(n =1))

# Plotting the SHAP value plot for the model with the highest accuracy
shp_lgb_wvlnagecom <- shap_plot_func(lightgbm_wvlnagecom_list[[lgb_wvlnagecom_run]])
shp_lgb_wvlnagecom
```

```{r, Aggregate the mean of the SHAP value importance over all simulation runs}
# Compute the mean SHAP value over 100 simulation runs
mean_lgb_wvlnagecom <- mean_shap(lightgbm_wvlnagecom_list)

# Plot of average importance
rank_lgb_wvlnagecom <- rank_plot(mean_lgb_wvlnagecom)
rank_lgb_wvlnagecom
```

# Supplementary figures
```{r, Compile & arrange the plots}
# Compilation for Random forest
SHAP_plot_rf_full2 <- ggarrange(shp_rf_fil + theme(legend.key.size = unit(1.3, "cm")), rank_rf_fil + theme(plot.title = element_blank()),
                                shp_rf_vlsymp + theme(legend.key.size = unit(1.3, "cm")), rank_rf_vlsymp + theme(plot.title = element_blank()),
                                shp_rf_vldiag + theme(legend.key.size = unit(1.3, "cm")), rank_rf_vldiag + theme(plot.title = element_blank()),
                                ncol = 2, nrow = 3, widths = c(1, 1), heights = rep(0.8, 3), align = "hv")
SHAP_plot_rf_full2

SHAP_plot_rf_wcom2 <- ggarrange(shp_rf_wvlncom + theme(legend.key.size = unit(1.3, "cm")), rank_rf_wvlncom + theme(plot.title = element_blank()),
                                shp_rf_vlsymp_wcom + theme(legend.key.size = unit(1.3, "cm")), rank_rf_vlsymp_wcom + theme(plot.title = element_blank()),
                                shp_rf_vldiag_wcom + theme(legend.key.size = unit(1.3, "cm")), rank_rf_vldiag_wcom + theme(plot.title = element_blank()),
                                ncol = 2, nrow = 3, widths = c(1, 1), heights = rep(0.8, 3), align = "hv")
SHAP_plot_rf_wcom2

SHAP_plot_rf_wage2 <- ggarrange(shp_rf_wvlnage + theme(legend.key.size = unit(1.3, "cm")), rank_rf_wvlnage + theme(plot.title = element_blank()),
                                shp_rf_vlsymp_wage + theme(legend.key.size = unit(1.3, "cm")), rank_rf_vlsymp_wage + theme(plot.title = element_blank()),
                                shp_rf_vldiag_wage + theme(legend.key.size = unit(1.3, "cm")), rank_rf_vldiag_wage + theme(plot.title = element_blank()),
                                ncol = 2, nrow = 3, widths = c(1, 1), heights = rep(0.8, 3), align = "hv")
SHAP_plot_rf_wage2

SHAP_plot_rf_wagecom2 <- ggarrange(shp_rf_wvlnagecom + theme(legend.key.size = unit(1.3, "cm")), rank_rf_wvlnagecom + theme(plot.title = element_blank()),
                                   shp_rf_vlsymp_wagecom + theme(legend.key.size = unit(1.3, "cm")), rank_rf_vlsymp_wagecom + theme(plot.title = element_blank()),
                                   shp_rf_vldiag_wagecom + theme(legend.key.size = unit(1.3, "cm")), rank_rf_vldiag_wagecom + theme(plot.title = element_blank()),
                                   ncol = 2, nrow = 3, widths = c(1, 1), heights = rep(0.8, 3), align = "hv")
SHAP_plot_rf_wagecom2

# Compilation for XGBoost
SHAP_plot_xgb_full2 <- ggarrange( shp_xgb_fil + theme(legend.key.size = unit(1.3, "cm")), rank_xgb_fil + theme(plot.title = element_blank()),
                                  shp_xgb_vlsymp + theme(legend.key.size = unit(1.3, "cm")), rank_xgb_vlsymp + theme(plot.title = element_blank()),
                                  shp_xgb_vldiag + theme(legend.key.size = unit(1.3, "cm")), rank_xgb_vldiag + theme(plot.title = element_blank()),
                                  ncol = 2, nrow = 3, widths = c(1, 1), heights = rep(0.8, 3), align = "hv")
SHAP_plot_xgb_full2

SHAP_plot_xgb_wcom2 <- ggarrange(shp_xgb_wvlncom + theme(legend.key.size = unit(1.3, "cm")), rank_xgb_wvlncom + theme(plot.title = element_blank()),
                                 shp_xgb_vlsymp_wcom + theme(legend.key.size = unit(1.3, "cm")), rank_xgb_vlsymp_wcom + theme(plot.title = element_blank()),
                                 shp_xgb_vldiag_wcom + theme(legend.key.size = unit(1.3, "cm")), rank_xgb_vldiag_wcom + theme(plot.title = element_blank()),
                                 ncol = 2, nrow = 3, widths = c(1, 1), heights = rep(0.8, 3), align = "hv")
SHAP_plot_xgb_wcom2

SHAP_plot_xgb_wage2 <- ggarrange( shp_xgb_wvlnage + theme(legend.key.size = unit(1.3, "cm")), rank_xgb_wvlnage + theme(plot.title = element_blank()),
                                  shp_xgb_vlsymp_wage + theme(legend.key.size = unit(1.3, "cm")), rank_xgb_vlsymp_wage + theme(plot.title = element_blank()),
                                  shp_xgb_vldiag_wage + theme(legend.key.size = unit(1.3, "cm")), rank_xgb_vldiag_wage + theme(plot.title = element_blank()),
                                  ncol = 2, nrow = 3, widths = c(1, 1), heights = rep(0.8, 3), align = "hv")
SHAP_plot_xgb_wage2

SHAP_plot_xgb_wagecom2 <- ggarrange(shp_xgb_wvlnagecom + theme(legend.key.size = unit(1.3, "cm")), rank_xgb_wvlnagecom + theme(plot.title = element_blank()),
                                    shp_xgb_vlsymp_wagecom + theme(legend.key.size = unit(1.3, "cm")), rank_xgb_vlsymp_wagecom + theme(plot.title = element_blank()),
                                    shp_xgb_vldiag_wagecom + theme(legend.key.size = unit(1.3, "cm")), rank_xgb_vldiag_wagecom + theme(plot.title = element_blank()),
                                    ncol = 2, nrow = 3, widths = c(1, 1), heights = rep(0.8, 3), align = "hv")
SHAP_plot_xgb_wagecom2

# Compilation for LightGBM
SHAP_plot_lgb_full2 <- ggarrange(shp_lgb_fil + theme(legend.key.size = unit(1.3, "cm")), rank_lgb_fil + theme(plot.title = element_blank()),
                                 shp_lgb_vlsymp + theme(legend.key.size = unit(1.3, "cm")), rank_lgb_vlsymp + theme(plot.title = element_blank()),
                                 shp_lgb_vldiag + theme(legend.key.size = unit(1.3, "cm")), rank_lgb_vldiag + theme(plot.title = element_blank()),
                                 ncol = 2, nrow = 3, widths = c(1, 1), heights = rep(0.8, 3), align = "hv")
SHAP_plot_lgb_full2

SHAP_plot_lgb_wcom2 <- ggarrange(shp_lgb_wvlncom + theme(legend.key.size = unit(1.3, "cm")), rank_lgb_wvlncom + theme(plot.title = element_blank()),
                                 shp_lgb_vlsymp_wcom + theme(legend.key.size = unit(1.3, "cm")), rank_lgb_vlsymp_wcom + theme(plot.title = element_blank()),
                                 shp_lgb_vldiag_wcom + theme(legend.key.size = unit(1.3, "cm")), rank_lgb_vldiag_wcom + theme(plot.title = element_blank()),
                                 ncol = 2, nrow = 3, widths = c(1, 1), heights = rep(0.8, 3), align = "hv")
SHAP_plot_lgb_wcom2

SHAP_plot_lgb_wage2 <- ggarrange(shp_lgb_wvlnage + theme(legend.key.size = unit(1.3, "cm")), rank_lgb_wvlnage + theme(plot.title = element_blank()),
                                 shp_lgb_vlsymp_wage + theme(legend.key.size = unit(1.3, "cm")), rank_lgb_vlsymp_wage + theme(plot.title = element_blank()),
                                 shp_lgb_vldiag_wage + theme(legend.key.size = unit(1.3, "cm")), rank_lgb_vldiag_wage + theme(plot.title = element_blank()),
                                 ncol = 2, nrow = 3, widths = c(1, 1), heights = rep(0.8, 3), align = "hv")
SHAP_plot_lgb_wage2

SHAP_plot_lgb_wagecom2 <- ggarrange(shp_lgb_wvlnagecom + theme(legend.key.size = unit(1.3, "cm")), rank_lgb_wvlnagecom + theme(plot.title = element_blank()),
                                    shp_lgb_vlsymp_wagecom + theme(legend.key.size = unit(1.3, "cm")), rank_lgb_vlsymp_wagecom + theme(plot.title = element_blank()),
                                    shp_lgb_vldiag_wagecom + theme(legend.key.size = unit(1.3, "cm")), rank_lgb_vldiag_wagecom + theme(plot.title = element_blank()),
                                    ncol = 2, nrow = 3, widths = c(1, 1), heights = rep(0.8, 3), align = "hv")
SHAP_plot_lgb_wagecom2
```

```{r, Saving session data}
save.image(file = paste0(getwd(), '/SHAP_plots.RData'))
```

```{r, Session Info}
sessionInfo()
```