---
title: "Supplementary_figure6"
output: html_document
---

# Import library & Setup environment
```{r, Import libraries}
library(dplyr)
library(stringr)
library(tidyr)
library(ggpubr)
library(doParallel)
library(foreach)
library(randomForest)
library(fastshap)
library(shapviz)
library(lightgbm)
library(pROC)
library(purrr)
library(ggplot2)
library(ggpattern)
library(tidymodels)
library(grid)
```

```{r, Load data into environment}
load(paste0(getwd(), "/Data_preparation.RData"))
load(paste0(getwd(), '/Random_forest.RData'))
```

# Retrieve Random forest performance with VL at symptom onset & VL at diagnosis
```{r, Compile models performance}
rf_acc_vlsymp <- rf_vlsymp_metrics_summary$accuracy_test_mean
rf_acc_low_vlsymp <- rf_vlsymp_metrics_summary$low_acc_test
rf_acc_upp_vlsymp <- rf_vlsymp_metrics_summary$upp_acc_test
rf_sens_vlsymp <- rf_vlsymp_metrics_summary$sensitivity_mean
rf_sens_low_vlsymp <- rf_vlsymp_metrics_summary$low_sens
rf_sens_upp_vlsymp <- rf_vlsymp_metrics_summary$upp_sens
rf_spec_vlsymp <- rf_vlsymp_metrics_summary$specificity_mean
rf_spec_low_vlsymp <- rf_vlsymp_metrics_summary$low_spec
rf_spec_upp_vlsymp <- rf_vlsymp_metrics_summary$upp_spec
rf_prec_vlsymp <- rf_vlsymp_metrics_summary$precision_mean
rf_prec_low_vlsymp <- rf_vlsymp_metrics_summary$low_prec
rf_prec_upp_vlsymp <- rf_vlsymp_metrics_summary$upp_prec
rf_f1_vlsymp <- rf_vlsymp_metrics_summary$F1_score_mean
rf_f1_low_vlsymp <- rf_vlsymp_metrics_summary$low_f1_sc
rf_f1_upp_vlsymp <- rf_vlsymp_metrics_summary$upp_f1_sc
rf_auc_vlsymp <- rf_vlsymp_metrics_summary$AUC_mean
rf_auc_low_vlsymp <- rf_vlsymp_metrics_summary$low_auc
rf_auc_upp_vlsymp <- rf_vlsymp_metrics_summary$upp_auc

rf_acc_vldiag <- rf_vldiag_metrics_summary$accuracy_test_mean
rf_acc_low_vldiag <- rf_vldiag_metrics_summary$low_acc_test
rf_acc_upp_vldiag <- rf_vldiag_metrics_summary$upp_acc_test
rf_sens_vldiag <- rf_vldiag_metrics_summary$sensitivity_mean
rf_sens_low_vldiag <- rf_vldiag_metrics_summary$low_sens
rf_sens_upp_vldiag <- rf_vldiag_metrics_summary$upp_sens
rf_spec_vldiag <- rf_vldiag_metrics_summary$specificity_mean
rf_spec_low_vldiag <- rf_vldiag_metrics_summary$low_spec
rf_spec_upp_vldiag <- rf_vldiag_metrics_summary$upp_spec
rf_prec_vldiag <- rf_vldiag_metrics_summary$precision_mean
rf_prec_low_vldiag <- rf_vldiag_metrics_summary$low_prec
rf_prec_upp_vldiag <- rf_vldiag_metrics_summary$upp_prec
rf_f1_vldiag <- rf_vldiag_metrics_summary$F1_score_mean
rf_f1_low_vldiag <- rf_vldiag_metrics_summary$low_f1_sc
rf_f1_upp_vldiag <- rf_vldiag_metrics_summary$upp_f1_sc
rf_auc_vldiag <- rf_vldiag_metrics_summary$AUC_mean
rf_auc_low_vldiag <- rf_vldiag_metrics_summary$low_auc
rf_auc_upp_vldiag <- rf_vldiag_metrics_summary$upp_auc

df_perf_summary <- data.frame(
    models = c("Random forest (Viral load at symptom onset)", "Random forest (Viral load at diagnosis)"),
    Accuracy = c(rf_acc_vlsymp, rf_acc_vldiag),
    acc_low = c(rf_acc_low_vlsymp, rf_acc_low_vldiag),
    acc_upp = c(rf_acc_upp_vlsymp, rf_acc_upp_vldiag),
    Sensitivity = c(rf_sens_vlsymp, rf_sens_vldiag),
    sens_low = c(rf_sens_low_vlsymp, rf_sens_low_vldiag),
    sens_upp = c(rf_sens_upp_vlsymp, rf_sens_upp_vldiag),
    Specificity = c(rf_spec_vlsymp, rf_spec_vldiag),
    spec_low = c(rf_spec_low_vlsymp, rf_spec_low_vldiag),
    spec_upp = c(rf_spec_upp_vlsymp, rf_spec_upp_vldiag),
    Precision = c(rf_prec_vlsymp, rf_prec_vldiag),
    prec_low = c(rf_prec_low_vlsymp, rf_prec_low_vldiag),
    prec_upp = c(rf_prec_upp_vlsymp, rf_prec_upp_vldiag),
    `F1-Score` = c(rf_f1_vlsymp, rf_f1_vldiag),
    f1_low = c(rf_f1_low_vlsymp, rf_f1_low_vldiag),
    f1_upp = c(rf_f1_upp_vlsymp, rf_f1_upp_vldiag),
    AUROC = c(rf_auc_vlsymp, rf_auc_vldiag),
    auc_low = c(rf_auc_low_vlsymp, rf_auc_low_vldiag),
    auc_upp = c(rf_auc_upp_vlsymp, rf_auc_upp_vldiag)
)
```

# Random forest with VL at sequential days after diagnosis
## Setup CPU clusters
```{r, Setup CPU clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

## Fitting data into Random Forest
```{r}
rf_seq_diag_list <- foreach(i = 1:100, .packages = c("dplyr", "randomForest", "pROC", "fastshap", "shapviz")) %dopar% {
  split <- split_list_p[[i]]
  
  lapply(1:10, function(j) {
    col_nm <- paste0("vl_dp", j)
    
    train_df <- split$train %>% select(age, gender, vaccination, comorbidity, col_nm, outcome)
    test_df <- split$test %>% select(age, gender, vaccination, comorbidity, col_nm, outcome)
    
    rf_model <- randomForest(outcome ~ ., data = train_df, importance = TRUE)
    
    rf_pred <- predict(rf_model, newdata = test_df, type = "class")
    
    cfm_rf <- table(Predicted = rf_pred, Actual = test_df$outcome)
    accuracy_rf <- sum(cfm_rf["Severe", "Severe"], cfm_rf["Non severe", "Non severe"]) / sum(cfm_rf)
    
    rf_pred_train <- predict(rf_model, newdata = train_df, type = "class")
    cfm_rf_train <- table(Predicted = rf_pred_train, Actual = train_df$outcome)
    accuracy_rf_train <- sum(cfm_rf_train["Severe", "Severe"], cfm_rf_train["Non severe", "Non severe"]) / sum(cfm_rf_train)

    TP <- cfm_rf["Severe", "Severe"]
    FP <- cfm_rf["Severe", "Non severe"]
    TN <- cfm_rf["Non severe", "Non severe"]
    FN <- cfm_rf["Non severe", "Severe"]
    
    sensitivity_rf <- TP / (TP + FN)
    specificity_rf <- TN / (TN + FP)
    prec_rf <- TP / (TP + FP)
    f1_sc_rf <- 2 * ((prec_rf * sensitivity_rf) / (prec_rf + sensitivity_rf))
    
    rf_pred_res <- ifelse(rf_pred == "Severe", 1, 0)
    roc_rf <- roc(test_df$outcome, rf_pred_res)
    auc_val_rf <- auc(roc_rf)
    
    xvars <- colnames(train_df)[-6]
    pfun_rf <- function(object, newdata) predict(object, newdata, type = "prob")[, 2]
    shap_values_rf <- fastshap::explain(rf_model, X = train_df[, -6], pred_wrapper = pfun_rf)
    shp_rf <- shapviz(shap_values_rf, X = train_df[, -which(names(train_df) == "outcome")])
    
    list(
      #model = rf_model,
      confusion_matrix = cfm_rf,
      accuracy_training = accuracy_rf_train,
      accuracy_testing = accuracy_rf,
      sensitivity = sensitivity_rf,
      specificity = specificity_rf,
      precision = prec_rf,
      F1_score = f1_sc_rf,
      AUC_value = auc_val_rf,
      #SHAP_values = shp_rf,
      prediction = rf_pred
    )
  })
}
```

## Stop CPU clusters
```{r, Stop CPU clusters}
stopCluster(cl)
```

```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
rf_seq_diag_metrics_df <- map2_dfr(
  .x = rf_seq_diag_list,
  .y = seq_along(rf_seq_diag_list),
  .f = function(model_list, run_index) {
    map2_dfr(model_list, 1:10, function(model_result, var_index) {
      tibble(
        run = run_index,
        variable = var_index,
        accuracy_train = round(model_result$accuracy_training * 100, 4),
        accuracy_test = round(model_result$accuracy_testing * 100, 4),
        sensitivity = round(model_result$sensitivity * 100, 4),
        specificity = round(model_result$specificity * 100, 4),
        precision = round(model_result$precision * 100, 4),
        F1_score = round(model_result$F1_score, 4),
        AUC_value = round(model_result$AUC_value * 100, 4)
      )
    })
  }
)

rf_seq_diag_metrics_df

rf_seq_diag_metrics_summary <- rf_seq_diag_metrics_df %>%
  group_by(variable) %>%
  summarise(
    across(
      .cols = c(accuracy_train, accuracy_test, sensitivity, specificity, precision, F1_score, AUC_value),
      .fns = list(mean = mean, sd = sd, low = ~ quantile(.x, 0.025), upp = ~ quantile(.x, 0.975)),
      .names = "{.col}_{.fn}"
    )
  ) %>%
  ungroup()

rf_seq_diag_metrics_summary
```

```{r, Model performance visualisation}
rf_perf_viz_diag_df <- rf_seq_diag_metrics_summary %>%
  select(-c("accuracy_train_mean", "accuracy_train_sd", "accuracy_train_upp", "accuracy_train_low")) %>%
  pivot_longer(
    cols = -variable,
    names_to = "metrics",
    values_to = "perf"
  ) %>%
  mutate(
    Metrics = case_when(
      str_starts(metrics, "accuracy_") ~ "Accuracy",
      str_starts(metrics, "sensitivity") ~ "Sensitivity",
      str_starts(metrics, "specificity") ~ "Specificity",
      str_starts(metrics, "precision") ~ "Precision",
      str_starts(metrics, "F1_score") ~ "F1_score",
      str_starts(metrics, "AUC_value") ~ "AUROC_value"
    ),
    bound = case_when(
      str_ends(metrics, "_low") ~ "lower",
      str_ends(metrics, "_upp") ~ "upper",
      str_ends(metrics, "_sd") ~ "sd",
      TRUE ~ "estimate"
    )
  ) %>%
  select(c("variable", "Metrics", "bound", "perf")) %>%
  pivot_wider(names_from = bound, values_from = perf) %>%
  select(-sd)

rf_perf_viz_diag_df2 <- df_perf_summary %>%
  filter(models == "Random forest (Viral load at diagnosis)") %>%
  pivot_longer(
    cols = -models,
    names_to = "metrics",
    values_to = "Perf"
    ) %>%
  mutate(Metrics = case_when(
    str_starts(metrics, 'acc_') ~ "Accuracy",
    str_starts(metrics, "sens_") ~ "Sensitivity",
    str_starts(metrics, "spec_") ~ "Specificity",
    str_starts(metrics, "prec_") ~ "Precision",
    str_starts(metrics, "f1_") ~ "F1_score",
    str_starts(metrics, "auc_") ~ "AUROC_value",
    metrics == "Accuracy" ~ "Accuracy",
    metrics == "Sensitivity" ~ "Sensitivity",
    metrics == "Specificity" ~ "Specificity",
    metrics == "Precision" ~ "Precision",
    metrics == "F1.Score" ~ "F1_score",
    metrics == "AUROC" ~ "AUROC_value"
    ),
    bound = case_when(
      str_ends(metrics, "_low") ~ "lower",
      str_ends(metrics, "_upp") ~ "upper",
      TRUE ~ "estimate"
      )) %>%
  select(c("models", "Metrics", "bound", "Perf")) %>%
  rename("variable" = "models") %>%
  pivot_wider(names_from = bound, values_from = Perf) %>%
  mutate(variable = 0)

rf_perf_viz_df_all2 <- dplyr::bind_rows(rf_perf_viz_diag_df, rf_perf_viz_diag_df2) %>%
  dplyr::arrange(Metrics, variable)
```

## Figure 4A
```{r, Fig4A_rf}
SF6A_Sen <- subset(rf_perf_viz_df_all2, Metrics == "Sensitivity")
SF6A_Acc <- subset(rf_perf_viz_df_all2, Metrics == "Accuracy")
SF6A_AUC <- subset(rf_perf_viz_df_all2, Metrics == "AUROC_value")

lb_A <- 85

theme_set(theme_classic(base_size = 50, base_family = "Helvetica"))
fig4a_rf_diag <- ggplot() +
  geom_bar(data = SF6A_Sen, aes(x = variable, y = pmax(estimate - lb_A, 0)), fill = "#348EC2", position = "dodge", stat = "identity", width = 0.6) + 
  geom_errorbar(data = SF6A_Sen, aes(x = variable, ymin = pmax(lower - lb_A, 0), ymax = pmax(upper - lb_A, 0)), width = 0.3, position = position_dodge(0.6), linewidth = 1.0) +
  
  geom_point(data = SF6A_Acc, aes(x = variable, y = pmax(estimate - lb_A, 0)), color = "#FA766E", size = 7) + 
  geom_line(data = SF6A_Acc, aes(x = variable, y = pmax(estimate - lb_A, 0)), color = "#FA766E", linewidth = 2, linetype = "dashed") + 
  
  geom_point(data = SF6A_AUC, aes(x = variable, y = pmax(estimate - lb_A, 0)), color = "#FFC001", size = 7) + 
  geom_line(data = SF6A_AUC, aes(x = variable, y = pmax(estimate - lb_A, 0)), color = "#FFC001", linewidth = 2, linetype = "solid") + 

  scale_x_continuous(breaks=seq(0, 100 - lb_A, by = 1)) +
  scale_y_continuous(
    limits = c(0, 100 - lb_A),
    breaks  = seq(0, 100 - lb_A, by = 5),
    labels  = function(b) sprintf("%d", b + lb_A)) +
  xlab("Time since diagnosis (days)") +
  ylab("Metrics (%)") +
  theme(plot.title = element_text(colour = "black", size=36),
        axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_line(colour = "black"),
        axis.line = element_line(colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        legend.position='none',
        axis.title.x = element_text(colour = "black"),
        axis.title.y = element_text(colour = "black"))
  
fig4a_rf_diag
```

# Comparison between model with viral load point at different time point
```{r, McNemar Test}
# Function for getting the contigency table
mc_tab <- function(list1, list2) {
  table(
    list1 = factor(list1, levels = c(TRUE, FALSE)),
    list2 = factor(list2, levels = c(TRUE, FALSE))
  )
}

mc_rf_seqcomp_diag_list <- list()
for(i in 1:100) {
  # Normalize all factors
  actual_rf_vldiag <- factor(split_list_vldiag[[i]]$test$outcome)
  actual_rf <- factor(split_list[[i]]$test$outcome)

  pred_rf_vldiag <- factor(rf_vldiag_list[[i]]$prediction, levels = levels(actual_rf_vldiag))
  pred_rf_day1 <- factor(rf_seq_diag_list[[i]][[1]]$prediction, levels = levels(actual_rf))
  pred_rf_day2 <- factor(rf_seq_diag_list[[i]][[2]]$prediction, levels = levels(actual_rf))
  pred_rf_day5 <- factor(rf_seq_diag_list[[i]][[5]]$prediction, levels = levels(actual_rf))

  pos_case <- "Severe"

  idx_pos_vldiag <- actual_rf_vldiag == pos_case
  idx_pos_rf <- actual_rf == pos_case

  rf_correct_vldiag <- pred_rf_vldiag[idx_pos_vldiag] == actual_rf_vldiag[idx_pos_vldiag]
  rf_correct_day1 <- pred_rf_day1[idx_pos_rf] == actual_rf[idx_pos_rf]
  rf_correct_day2 <- pred_rf_day2[idx_pos_rf] == actual_rf[idx_pos_rf]
  rf_correct_day5 <- pred_rf_day5[idx_pos_rf] == actual_rf[idx_pos_rf]

  # Forming the table for McNemar test
  mc_tab_rf_diagvday1 <- mc_tab(rf_correct_vldiag, rf_correct_day1)
  mc_tab_rf_diagvday2 <- mc_tab(rf_correct_vldiag, rf_correct_day2)
  mc_tab_rf_diagvday5 <- mc_tab(rf_correct_vldiag, rf_correct_day5)
  
  mc_tab_rf_day1vday2 <- mc_tab(rf_correct_day1, rf_correct_day2)
  mc_tab_rf_day1vday5 <- mc_tab(rf_correct_day1, rf_correct_day5)
  
  mc_tab_rf_day2vday5 <- mc_tab(rf_correct_day2, rf_correct_day5)

  # Perform McNemar test
  mc_rf_diagvday1 <- mcnemar.test(mc_tab_rf_diagvday1, correct = FALSE)
  mc_rf_diagvday2 <- mcnemar.test(mc_tab_rf_diagvday2, correct = FALSE)
  mc_rf_diagvday5 <- mcnemar.test(mc_tab_rf_diagvday5, correct = FALSE)
  
  mc_rf_day1vday2 <- mcnemar.test(mc_tab_rf_day1vday2, correct = FALSE)
  mc_rf_day1vday5 <- mcnemar.test(mc_tab_rf_day1vday5, correct = FALSE)
  
  mc_rf_day2vday5 <- mcnemar.test(mc_tab_rf_day2vday5, correct = FALSE)
  
  # Getting the p-value of McNemar test
  mc_rf_diagvday1_p <- tidy(mc_rf_diagvday1)$p.value
  mc_rf_diagvday2_p <- tidy(mc_rf_diagvday2)$p.value
  mc_rf_diagvday5_p <- tidy(mc_rf_diagvday5)$p.value
  
  mc_rf_day1vday2_p <- tidy(mc_rf_day1vday2)$p.value
  mc_rf_day1vday5_p <- tidy(mc_rf_day1vday5)$p.value
  
  mc_rf_day2vday5_p <- tidy(mc_rf_day2vday5)$p.value

  mc_rf_summary <- tibble(
      group1 = c("Random forest (Day 0)", "Random forest (Day 0)", "Random forest (Day 0)", "Random forest (Day 1)", "Random forest (Day 1)", "Random forest (Day 2)",
                 "Random forest (Day 1)", "Random forest (Day 2)", "Random forest (Day 5)", "Random forest (Day 2)", "Random forest (Day 5)", "Random forest (Day 5)",
                 "Random forest (Day 0)", "Random forest (Day 1)", "Random forest (Day 2)", "Random forest (Day 5)"),

      group2 = c("Random forest (Day 1)", "Random forest (Day 2)", "Random forest (Day 5)", "Random forest (Day 2)", "Random forest (Day 5)", "Random forest (Day 5)",
                 "Random forest (Day 0)", "Random forest (Day 0)", "Random forest (Day 0)", "Random forest (Day 1)", "Random forest (Day 1)", "Random forest (Day 2)",
                 "Random forest (Day 0)", "Random forest (Day 1)", "Random forest (Day 2)", "Random forest (Day 5)"),

      p.value = c(mc_rf_diagvday1_p, mc_rf_diagvday2_p, mc_rf_diagvday5_p, mc_rf_day1vday2_p, mc_rf_day1vday5_p, mc_rf_day2vday5_p,
                  mc_rf_diagvday1_p, mc_rf_diagvday2_p, mc_rf_diagvday5_p, mc_rf_day1vday2_p, mc_rf_day1vday5_p, mc_rf_day2vday5_p,
                  2, 2, 2, 2)
  ) %>%
  mutate(label = case_when(
      is.na(p.value) ~ "NS",
      p.value < 0.001 ~ "***",
      p.value < 0.01 ~ "**",
      p.value < 0.05 ~ "*",
      p.value == 2 ~ "NA",
      TRUE ~ "NS"
  ))

  mc_rf_heatmap <- mc_rf_summary %>%
                      select(group1, group2, label) %>%
                      pivot_wider(names_from = group1, values_from = label) %>%
                      column_to_rownames("group2")


  mcnemar_rf_long <- as.data.frame(as.table(as.matrix(mc_rf_heatmap)))
  colnames(mcnemar_rf_long) <- c("Model1", "Model2", "Significance")

  mc_rf_seqcomp_diag_list[[i]] <- mcnemar_rf_long %>%
                        mutate(
                          Model1 = case_when(
                          Model1 == "Random forest (Day 0)" ~ "0",
                          Model1 == "Random forest (Day 1)" ~ "1",
                          Model1 == "Random forest (Day 2)" ~ "2",
                          Model1 == "Random forest (Day 5)" ~ "5"
                          ),
                          Model2 = case_when(
                          Model2 == "Random forest (Day 0)" ~ "0",
                          Model2 == "Random forest (Day 1)" ~ "1",
                          Model2 == "Random forest (Day 2)" ~ "2",
                          Model2 == "Random forest (Day 5)" ~ "5"
                          ),
                          Model1 = factor(Model1, levels = c("5", "2", "1", "0")),
                          Model2 = factor(Model2, levels = c("0", "1", "2", "5"))
                        )
}

# Summarise the percentage of significance in each scenario cases
mc_rf_seqcomp_diag_percent_sum <- dplyr::bind_rows(
  lapply(seq_along(mc_rf_seqcomp_diag_list), function(i) {
    mc_rf_seqcomp_diag_list[[i]] %>% mutate(run = i)
    })
  )

# Define labels of statistically significant
sig_labels <- c("*", "**", "***")

# Summarize the percentage significant for each scenario
sig_rf_seqcomp_diag_sum <- mc_rf_seqcomp_diag_percent_sum %>%
                mutate(is_significant = Significance %in% sig_labels) %>%
                group_by(Model1, Model2) %>%
                summarize(
                  n_sig = sum(is_significant),
                  n_total = n(),
                  percent_sig = 100 * n_sig / n_total,
                  .groups = "drop"
                ) %>%
                mutate(percent_sig = ifelse(Model1 == Model2, NA, percent_sig)) %>%
                mutate(
                  fill = case_when(
                      is.na(percent_sig) ~ "black",
                      percent_sig < 40 ~ "white",
                      percent_sig >= 40 & percent_sig < 60 ~ "grey90",
                      percent_sig >=60 & percent_sig <80 ~ "gold",
                      percent_sig >= 80 ~ "orange"
                    ),
                  percent_label = ifelse(is.na(percent_sig), "", sprintf("%.1f%%", percent_sig))
                )
sig_rf_seqcomp_diag_sum
```

```{r, Heatmap}
# Plot heatmap
mc_plot_rfseq_diag <- ggplot(sig_rf_seqcomp_diag_sum, aes(x = Model2, y = Model1, fill = fill)) +
                  geom_tile(color = "black") +
                  geom_text(aes(label = percent_label), color = "black", size = rel(5), fontface = "bold") +
                  scale_fill_manual(values = c("black"= "black", "white" = "white", "grey90" = "grey90", "orange" = "orange", "gold" = "gold"), guide = "none") +
                  theme_classic() +
                  theme(axis.text.x = element_text(hjust = 0.5, face = "bold", size = rel(2)),
                        axis.text.y = element_text(face = "bold", size = rel(2)),
                        axis.title.x = element_blank(),
                        axis.title.y = element_blank(),
                        legend.position = "none")
mc_plot_rfseq_diag
```

## Figure 4B
```{r, Fig4B_rf_diag}
rf_sens_comp_diag <- rf_perf_viz_df_all2 %>%
                filter(Metrics == "Sensitivity" & variable %in% c("0", "1", "2", "5"))

# Function to convert the percentage of significant to annotation
pct_to_stars <- function(p) dplyr::case_when(
  is.na(p) ~ "NA",
  p >= 80 ~ "****",
  p >= 60 ~ "***",
  p >= 40 ~ "**",
  p >= 20 ~ "*",
  TRUE ~ "NS"
)

# Function to extract the percentage of significant
get_pair_percents <- function(sig_df) {
  sig_df %>%
    filter(!is.na(percent_sig)) %>%
    mutate(
      a = pmin(as.character(Model1), as.character(Model2)),
      b = pmax(as.character(Model1), as.character(Model2)),
      pair = paste0(a, "-", b)
    ) %>%
    distinct(pair, percent_sig) %>%
    select(pair, percent_sig) %>%
    tibble::deframe()
}

# Function to build bracket information for one row facet for each model family
row_signif_2 <- function(sig_df, perf_all) {
  fam_sens <- perf_all
  if (nrow(fam_sens) == 0) {
    return(NULL)
  }
  
  pairs <- list(c("0", "1"), c("0", "2"), c("0", "5"))
  
  pp <- get_pair_percents(sig_df)
  pct_vec <- c(pp[["0-1"]], pp[["0-2"]], pp[["0-5"]])
  ann <- pct_to_stars(pct_vec)
  
  y_top <- max(fam_sens$upper, fam_sens$estimate, na.rm = TRUE)
  gap <- 0.01 * (y_top %||% 1)
  y_pos <- y_top + gap * (1:6)
  
  # Return the list compiled
  list(family = family, pairs = pairs, annotations = ann, y = y_pos)
}

# Compile the results of comparisons
rf_row_3 <- row_signif_2(sig_rf_seqcomp_diag_sum, rf_sens_comp_diag)

# Function to add the row of results of comparisons into plot
add_row_signif_diag <- function(p, row_spec) {
  if (is.null(row_spec)) {
    return(p)
  }
  p + geom_signif(
    data = rf_sens_comp_diag,
    inherit.aes = FALSE,
    aes(x = as.factor(variable), y = estimate),
    comparisons = row_spec$pairs,
    annotations = row_spec$annotations,
    y_position = row_spec$y,
    textsize = 8,
    size = 0.8,
    vjust = -0.1
  )
}

fig4b_rf_diag <- ggplot(data = rf_sens_comp_diag, aes(x = as.factor(variable), y = estimate, group = Metrics, color = Metrics)) +
                geom_col(data = rf_sens_comp_diag, aes(x = as.factor(variable), y = estimate, fill = Metrics), alpha = 0.8) +
                geom_errorbar(aes(ymin = lower, ymax = upper, color = Metrics), width = 0.1, linewidth = 1.2) +
                scale_x_discrete(limits = c("0", "1", "2", "5")) +
                xlab("Time since diagnosis (days)") +
                ylab("Sensitivity (%)") +
                scale_fill_manual(name = "", values = c(Sensitivity = "#0072B2")) +
                scale_color_manual(name = "", values = c(Sensitivity = "black")) +
                coord_cartesian(ylim = c(88, 103)) +
                theme_classic(base_family = "Helvetica") +
                theme(axis.text = element_text(color = "black"),
                      axis.text.x = element_text(vjust = 0.5, hjust = 0.5, face = "bold", size = rel(4)),
                      axis.text.y.left = element_text(face = "bold", size = rel(4)),
                      axis.line = element_line(color = "black"),
                      strip.text.x = element_text(angle = 360, vjust = 0.5, face = "bold", size = rel(4)),
                      strip.text.y = element_text(face = "bold", size = rel(4)),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.background = element_blank(),
                      legend.position = "none",
                      axis.title.y = element_text(size = rel(4)),
                      axis.title.x = element_text(size = rel(4))
                      )
fig4b_rf_diag <- fig4b_rf_diag %>%
        add_row_signif_diag(rf_row_3)
fig4b_rf_diag
#ggsave("Figure4B.png", fig4b_rf_diag, width = 16, height = 12)
```

# Adding one additional viral load to the model
## Day 2
### Setup CPU clusters
```{r, Setup CPU clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

### Fitting data into Random forest
```{r, Inclusion of additional time point into model}
rf_add2_list <- foreach(i = 1:100, .packages = c("dplyr", "randomForest", "pROC", "fastshap", "shapviz")) %dopar% {
  split <- split_list[[i]]
  
  train_df <- split$train %>% select(age, gender, vaccination, comorbidity, vl_sim, vl_sim2, outcome) %>% rename("diagnosis" = "vl_sim", "day2" = "vl_sim2")
  test_df <- split$test %>% select(age, gender, vaccination, comorbidity, vl_sim, vl_sim2, outcome) %>% rename("diagnosis" = "vl_sim", "day2" = "vl_sim2")
  
  rf_model <- randomForest(outcome ~ ., data = train_df, importance = TRUE)
  
  rf_pred <- predict(rf_model, newdata = test_df, type = "class")
  cfm_rf <- table(Predicted = rf_pred, Actual = test_df$outcome)
  accuracy_rf <- sum(cfm_rf["Severe", "Severe"], cfm_rf["Non severe", "Non severe"]) / sum(cfm_rf)
  
  rf_pred_train <- predict(rf_model, newdata = train_df, type = "class")
  cfm_rf_train <- table(Predicted = rf_pred_train, Actual = train_df$outcome)
  accuracy_rf_train <- sum(cfm_rf_train["Severe", "Severe"], cfm_rf_train["Non severe", "Non severe"]) / sum(cfm_rf_train)
  
  TP <- cfm_rf["Severe", "Severe"]
  FP <- cfm_rf["Severe", "Non severe"]
  TN <- cfm_rf["Non severe", "Non severe"]
  FN <- cfm_rf["Non severe", "Severe"]
    
  sensitivity_rf <- TP / (TP + FN)
  specificity_rf <- TN / (TN + FP)
  prec_rf <- TP / (TP + FP)
  f1_sc_rf <- 2 * ((prec_rf * sensitivity_rf) / (prec_rf + sensitivity_rf))
    
  rf_pred_res <- ifelse(rf_pred == "Severe", 1, 0)
  roc_rf <- roc(test_df$outcome, rf_pred_res)
  auc_val_rf <- auc(roc_rf)
    
  xvars <- colnames(train_df)[-7]
  pfun_rf <- function(object, newdata) predict(object, newdata, type = "prob")[, 2]
  shap_values_rf <- fastshap::explain(rf_model, X = train_df[, -7], pred_wrapper = pfun_rf)
  shp_rf <- shapviz(shap_values_rf, X = train_df[, -which(names(train_df) == "outcome")])
    
  list(#model = rf_model,
       confusion_matrix = cfm_rf, accuracy_training = accuracy_rf_train, accuracy_testing = accuracy_rf, sensitivity = sensitivity_rf,
       specificity = specificity_rf, precision = prec_rf, F1_score = f1_sc_rf, AUC_value = auc_val_rf,
       #SHAP_values = shp_rf,
       prediction = rf_pred, roc = roc_rf)
}
```

### Stop CPU clusters
```{r, Stop CPU clusters}
stopCluster(cl)
```

### Compile model performance metrics 
```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
rf_add2_metrics_df <- map_dfr(seq_along(rf_add2_list), function(i) {
  result <- rf_add2_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
rf_add2_metrics_df <- as.data.frame(rf_add2_metrics_df)

rf_add2_metrics_summary <- rf_add2_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(rf_add2_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(rf_add2_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(rf_add2_metrics_df$sensitivity, 0.025)
low_spec <- quantile(rf_add2_metrics_df$specificity, 0.025)
low_prec <- quantile(rf_add2_metrics_df$precision, 0.025)
low_f1_sc <- quantile(rf_add2_metrics_df$F1_score, 0.025)
low_auc <- quantile(rf_add2_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(rf_add2_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(rf_add2_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(rf_add2_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(rf_add2_metrics_df$specificity, 0.975)
upp_prec <- quantile(rf_add2_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(rf_add2_metrics_df$F1_score, 0.975)
upp_auc <- quantile(rf_add2_metrics_df$AUC_value, 0.975)

rf_add2_metrics_summary['low_acc_train'] <- low_acc_train
rf_add2_metrics_summary['low_acc_test'] <- low_acc_test
rf_add2_metrics_summary['low_sens'] <- low_sens
rf_add2_metrics_summary['low_spec'] <- low_spec
rf_add2_metrics_summary['low_prec'] <- low_prec
rf_add2_metrics_summary['low_f1_sc'] <- low_f1_sc
rf_add2_metrics_summary['low_auc'] <- low_auc

rf_add2_metrics_summary['upp_acc_train'] <- upp_acc_train
rf_add2_metrics_summary['upp_acc_test'] <- upp_acc_test
rf_add2_metrics_summary['upp_sens'] <- upp_sens
rf_add2_metrics_summary['upp_spec'] <- upp_spec
rf_add2_metrics_summary['upp_prec'] <- upp_prec
rf_add2_metrics_summary['upp_f1_sc'] <- upp_f1_sc
rf_add2_metrics_summary['upp_auc'] <- upp_auc

rf_add2_metrics_summary
```

## Day 1
### Setup CPU clusters
```{r, Setup CPU clusters}
num_cores <- parallel::detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)
```

### Fitting data into Random forest
```{r, Inclusion of additional time point into model}
rf_add3_list <- foreach(i = 1:100, .packages = c("dplyr", "randomForest", "pROC", "fastshap", "shapviz")) %dopar% {
  split <- split_list_p[[i]]
  
  train_df <- split$train %>% select(age, gender, vaccination, comorbidity, vl_sim, vl_dp1, outcome) %>% rename("diagnosis" = "vl_sim", "day1" = "vl_dp1")
  test_df <- split$test %>% select(age, gender, vaccination, comorbidity, vl_sim, vl_dp1, outcome) %>% rename("diagnosis" = "vl_sim", "day1" = "vl_dp1")
  
  rf_model <- randomForest(outcome ~ ., data = train_df, importance = TRUE)
  
  rf_pred <- predict(rf_model, newdata = test_df, type = "class")
  cfm_rf <- table(Predicted = rf_pred, Actual = test_df$outcome)
  accuracy_rf <- sum(cfm_rf["Severe", "Severe"], cfm_rf["Non severe", "Non severe"]) / sum(cfm_rf)
  
  rf_pred_train <- predict(rf_model, newdata = train_df, type = "class")
  cfm_rf_train <- table(Predicted = rf_pred_train, Actual = train_df$outcome)
  accuracy_rf_train <- sum(cfm_rf_train["Severe", "Severe"], cfm_rf_train["Non severe", "Non severe"]) / sum(cfm_rf_train)
  
  TP <- cfm_rf["Severe", "Severe"]
  FP <- cfm_rf["Severe", "Non severe"]
  TN <- cfm_rf["Non severe", "Non severe"]
  FN <- cfm_rf["Non severe", "Severe"]
    
  sensitivity_rf <- TP / (TP + FN)
  specificity_rf <- TN / (TN + FP)
  prec_rf <- TP / (TP + FP)
  f1_sc_rf <- 2 * ((prec_rf * sensitivity_rf) / (prec_rf + sensitivity_rf))
    
  rf_pred_res <- ifelse(rf_pred == "Severe", 1, 0)
  roc_rf <- roc(test_df$outcome, rf_pred_res)
  auc_val_rf <- auc(roc_rf)
    
  xvars <- colnames(train_df)[-7]
  pfun_rf <- function(object, newdata) predict(object, newdata, type = "prob")[, 2]
  shap_values_rf <- fastshap::explain(rf_model, X = train_df[, -7], pred_wrapper = pfun_rf)
  shp_rf <- shapviz(shap_values_rf, X = train_df[, -which(names(train_df) == "outcome")])
    
  list(#model = rf_model,
       confusion_matrix = cfm_rf, accuracy_training = accuracy_rf_train, accuracy_testing = accuracy_rf, sensitivity = sensitivity_rf,
       specificity = specificity_rf, precision = prec_rf, F1_score = f1_sc_rf, AUC_value = auc_val_rf,
       #SHAP_values = shp_rf,
       prediction = rf_pred, roc = roc_rf)
}
```

### Stop CPU clusters
```{r, Stop CPU clusters}
stopCluster(cl)
```

### Compile model performance metrics 
```{r, Convert the metrics list into data frame (Exclude the SHAP values figure)}
rf_add3_metrics_df <- map_dfr(seq_along(rf_add3_list), function(i) {
  result <- rf_add3_list[[i]]
  
  tibble(
    run = i,
    accuracy_train = round(result$accuracy_training * 100 , 4),
    accuracy_test = round(result$accuracy_testing * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$F1_score, 4),
    AUC_value = round(result$AUC_value * 100, 4)
  )
})
rf_add3_metrics_df <- as.data.frame(rf_add3_metrics_df)

rf_add3_metrics_summary <- rf_add3_metrics_df %>%
                              summarise(
                                accuracy_train_mean = mean(accuracy_train),
                                accuracy_train_sd = sd(accuracy_train),
                                accuracy_test_mean = mean(accuracy_test),
                                accuracy_test_sd = sd(accuracy_test),
                                sensitivity_mean = mean(sensitivity),
                                sensitivity_sd = sd(sensitivity),
                                specificity_mean = mean(specificity),
                                specificity_sd = sd(specificity),
                                precision_mean = mean(precision),
                                precision_sd = sd(precision),
                                F1_score_mean = mean(F1_score),
                                F1_score_sd = sd(F1_score),
                                AUC_mean = mean(AUC_value),
                                AUC_sd = sd(AUC_value)
                              )

low_acc_train <- quantile(rf_add3_metrics_df$accuracy_train, 0.025)
low_acc_test <- quantile(rf_add3_metrics_df$accuracy_test, 0.025)
low_sens <- quantile(rf_add3_metrics_df$sensitivity, 0.025)
low_spec <- quantile(rf_add3_metrics_df$specificity, 0.025)
low_prec <- quantile(rf_add3_metrics_df$precision, 0.025)
low_f1_sc <- quantile(rf_add3_metrics_df$F1_score, 0.025)
low_auc <- quantile(rf_add3_metrics_df$AUC_value, 0.025)

upp_acc_train <- quantile(rf_add3_metrics_df$accuracy_train, 0.975)
upp_acc_test <- quantile(rf_add3_metrics_df$accuracy_test, 0.975)
upp_sens <- quantile(rf_add3_metrics_df$sensitivity, 0.975)
upp_spec <- quantile(rf_add3_metrics_df$specificity, 0.975)
upp_prec <- quantile(rf_add3_metrics_df$precision, 0.975)
upp_f1_sc <- quantile(rf_add3_metrics_df$F1_score, 0.975)
upp_auc <- quantile(rf_add3_metrics_df$AUC_value, 0.975)

rf_add3_metrics_summary['low_acc_train'] <- low_acc_train
rf_add3_metrics_summary['low_acc_test'] <- low_acc_test
rf_add3_metrics_summary['low_sens'] <- low_sens
rf_add3_metrics_summary['low_spec'] <- low_spec
rf_add3_metrics_summary['low_prec'] <- low_prec
rf_add3_metrics_summary['low_f1_sc'] <- low_f1_sc
rf_add3_metrics_summary['low_auc'] <- low_auc

rf_add3_metrics_summary['upp_acc_train'] <- upp_acc_train
rf_add3_metrics_summary['upp_acc_test'] <- upp_acc_test
rf_add3_metrics_summary['upp_sens'] <- upp_sens
rf_add3_metrics_summary['upp_spec'] <- upp_spec
rf_add3_metrics_summary['upp_prec'] <- upp_prec
rf_add3_metrics_summary['upp_f1_sc'] <- upp_f1_sc
rf_add3_metrics_summary['upp_auc'] <- upp_auc

rf_add3_metrics_summary
```

#### Compile all the performance metrics
```{r, Compile performance metrics for Figure 4C}
rf_acc_add2 <- rf_add2_metrics_summary$accuracy_test_mean
rf_acc_low_add2 <- rf_add2_metrics_summary$low_acc_test
rf_acc_upp_add2 <- rf_add2_metrics_summary$upp_acc_test
rf_sens_add2 <- rf_add2_metrics_summary$sensitivity_mean
rf_sens_low_add2 <- rf_add2_metrics_summary$low_sens
rf_sens_upp_add2 <- rf_add2_metrics_summary$upp_sens
rf_spec_add2 <- rf_add2_metrics_summary$specificity_mean
rf_spec_low_add2 <- rf_add2_metrics_summary$low_spec
rf_spec_upp_add2 <- rf_add2_metrics_summary$upp_spec
rf_prec_add2 <- rf_add2_metrics_summary$precision_mean
rf_prec_low_add2 <- rf_add2_metrics_summary$low_prec
rf_prec_upp_add2 <- rf_add2_metrics_summary$upp_prec
rf_f1_add2 <- rf_add2_metrics_summary$F1_score_mean
rf_f1_low_add2 <- rf_add2_metrics_summary$low_f1_sc
rf_f1_upp_add2 <- rf_add2_metrics_summary$upp_f1_sc
rf_auc_add2 <- rf_add2_metrics_summary$AUC_mean
rf_auc_low_add2 <- rf_add2_metrics_summary$low_auc
rf_auc_upp_add2 <- rf_add2_metrics_summary$upp_auc

rf_acc_add3 <- rf_add3_metrics_summary$accuracy_test_mean
rf_acc_low_add3 <- rf_add3_metrics_summary$low_acc_test
rf_acc_upp_add3 <- rf_add3_metrics_summary$upp_acc_test
rf_sens_add3 <- rf_add3_metrics_summary$sensitivity_mean
rf_sens_low_add3 <- rf_add3_metrics_summary$low_sens
rf_sens_upp_add3 <- rf_add3_metrics_summary$upp_sens
rf_spec_add3 <- rf_add3_metrics_summary$specificity_mean
rf_spec_low_add3 <- rf_add3_metrics_summary$low_spec
rf_spec_upp_add3 <- rf_add3_metrics_summary$upp_spec
rf_prec_add3 <- rf_add3_metrics_summary$precision_mean
rf_prec_low_add3 <- rf_add3_metrics_summary$low_prec
rf_prec_upp_add3 <- rf_add3_metrics_summary$upp_prec
rf_f1_add3 <- rf_add3_metrics_summary$F1_score_mean
rf_f1_low_add3 <- rf_add3_metrics_summary$low_f1_sc
rf_f1_upp_add3 <- rf_add3_metrics_summary$upp_f1_sc
rf_auc_add3 <- rf_add3_metrics_summary$AUC_mean
rf_auc_low_add3 <- rf_add3_metrics_summary$low_auc
rf_auc_upp_add3 <- rf_add3_metrics_summary$upp_auc

perf_metrics_rf2 <- data.frame(
  models = c("Diagnosis + Day 2 post diagnosis", "Diagnosis + Day 1 post diagnosis"),
  Accuracy = c(rf_acc_add2, rf_acc_add3),
  acc_low = c(rf_acc_low_add2, rf_acc_low_add3),
  acc_upp = c(rf_acc_upp_add2, rf_acc_upp_add3),
  Sensitivity = c(rf_sens_add2, rf_sens_add3),
  sens_low = c(rf_sens_low_add2, rf_sens_low_add3),
  sens_upp = c(rf_sens_upp_add2, rf_sens_upp_add3),
  Specificity = c(rf_spec_add2, rf_spec_add3),
  spec_low = c(rf_spec_low_add2, rf_spec_low_add3),
  spec_upp = c(rf_spec_upp_add2, rf_spec_upp_add3),
  Precision = c(rf_prec_add2, rf_prec_add3),
  prec_low = c(rf_prec_low_add2, rf_prec_low_add3),
  prec_upp = c(rf_prec_upp_add2, rf_prec_upp_add3),
  `F1-Score` = c(rf_f1_add2, rf_f1_add3),
  f1_low = c(rf_f1_low_add2, rf_f1_low_add3),
  f1_upp = c(rf_f1_upp_add2, rf_f1_upp_add3),
  AUROC = c(rf_auc_add2, rf_auc_add3),
  auc_low = c(rf_auc_low_add2, rf_auc_low_add3),
  auc_upp = c(rf_auc_upp_add2, rf_auc_upp_add3)
)
df_perf_metrics_rf_diag <- dplyr::bind_rows(df_perf_summary, perf_metrics_rf2)   %>%
  filter(models %in% c("Random forest (Viral load at symptom onset)", "Random forest (Viral load at diagnosis)", "Diagnosis + Day 2 post diagnosis", "Diagnosis + Day 1 post diagnosis")) %>%
  mutate(models = case_when(
    models == "Random forest (Viral load at symptom onset)" ~ "Onset only",
    models == "Random forest (Viral load at diagnosis)" ~ "Diagnosis only",
    TRUE ~ models))
df_perf_metrics_rf_diag
```

##### Perform McNemar Test
```{r, McNemar test for Random forest in three scenarios}
mc_rf_compare_list2 <- list()
for(i in 1:100) {
  # Normalize all factors
  actual_rf_vlsymp <- factor(split_list_vlsim_symp[[i]]$test$outcome)
  actual_rf_vldiag <- factor(split_list_vldiag[[i]]$test$outcome)
  actual_rf <- factor(split_list[[i]]$test$outcome)

  pred_rf_vlsymp <- factor(rf_vlsymp_list[[i]]$prediction, levels = levels(actual_rf_vlsymp))
  pred_rf_vldiag <- factor(rf_vldiag_list[[i]]$prediction, levels = levels(actual_rf_vldiag))
  pred_rf_add3 <- factor(rf_add3_list[[i]]$prediction, levels = levels(actual_rf))
  pred_rf_add2 <- factor(rf_add2_list[[i]]$prediction, levels = levels(actual_rf))

  pos_case <- "Severe"

  idx_pos_vlsymp <- actual_rf_vlsymp == pos_case
  idx_pos_vldiag <- actual_rf_vldiag == pos_case
  idx_pos_rf <- actual_rf == pos_case

  rf_correct_vlsymp <- pred_rf_vlsymp[idx_pos_vlsymp] == actual_rf_vlsymp[idx_pos_vlsymp]
  rf_correct_vldiag <- pred_rf_vldiag[idx_pos_vldiag] == actual_rf_vldiag[idx_pos_vldiag]
  rf_correct_add3 <- pred_rf_add3[idx_pos_rf] == actual_rf[idx_pos_rf]
  rf_correct_add2 <- pred_rf_add2[idx_pos_rf] == actual_rf[idx_pos_rf]

  # Forming the table for McNemar test
  mc_tab_rf_sympvdiag <- mc_tab(rf_correct_vlsymp, rf_correct_vldiag)
  mc_tab_rf_sympvadd3 <- mc_tab(rf_correct_vlsymp, rf_correct_add3)
  mc_tab_rf_sympvadd2 <- mc_tab(rf_correct_vlsymp, rf_correct_add2)
  
  mc_tab_rf_diagvadd3 <- mc_tab(rf_correct_vldiag, rf_correct_add3)
  mc_tab_rf_diagvadd2 <- mc_tab(rf_correct_vldiag, rf_correct_add2)
  
  mc_tab_rf_add3vadd2 <- mc_tab(rf_correct_add3, rf_correct_add2)
  
  # Perform McNemar test
  mc_rf_sympvdiag <- mcnemar.test(mc_tab_rf_sympvdiag, correct = FALSE)
  mc_rf_sympvadd3 <- mcnemar.test(mc_tab_rf_sympvadd3, correct = FALSE)
  mc_rf_sympvadd2 <- mcnemar.test(mc_tab_rf_sympvadd2, correct = FALSE)
  
  mc_rf_diagvadd3 <- mcnemar.test(mc_tab_rf_diagvadd3, correct = FALSE)
  mc_rf_diagvadd2 <- mcnemar.test(mc_tab_rf_diagvadd2, correct = FALSE)
  
  mc_rf_add3vadd2 <- mcnemar.test(mc_tab_rf_add3vadd2, correct = FALSE)
  
  # Getting the p-value of McNemar test
  mc_rf_sympvdiag_p <- tidy(mc_rf_sympvdiag)$p.value
  mc_rf_sympvadd3_p <- tidy(mc_rf_sympvadd3)$p.value
  mc_rf_sympvadd2_p <- tidy(mc_rf_sympvadd2)$p.value
  
  mc_rf_diagvadd3_p <- tidy(mc_rf_diagvadd3)$p.value
  mc_rf_diagvadd2_p <- tidy(mc_rf_diagvadd2)$p.value
  
  mc_rf_add3vadd2_p <- tidy(mc_rf_add3vadd2)$p.value
  
  mc_rf_compare_summary <- tibble(
      group1 = c("Onset only", "Onset only", "Onset only",
                 "Diagnosis only", "Diagnosis only",
                 "Diagnosis + Day 1 post diagnosis", 
                 
                 "Diagnosis only", "Diagnosis + Day 1 post diagnosis", "Diagnosis + Day 2 post diagnosis",
                 "Diagnosis + Day 1 post diagnosis", "Diagnosis + Day 2 post diagnosis",
                 "Diagnosis + Day 2 post diagnosis",
                 
                 "Onset only", "Diagnosis only", "Diagnosis + Day 1 post diagnosis", "Diagnosis + Day 2 post diagnosis"),

      group2 = c("Diagnosis only", "Diagnosis + Day 1 post diagnosis", "Diagnosis + Day 2 post diagnosis",
                 "Diagnosis + Day 1 post diagnosis", "Diagnosis + Day 2 post diagnosis",
                 "Diagnosis + Day 2 post diagnosis",
                 
                 "Onset only", "Onset only", "Onset only",
                 "Diagnosis only", "Diagnosis only",
                 "Diagnosis + Day 1 post diagnosis",
                
                 "Onset only", "Diagnosis only", "Diagnosis + Day 1 post diagnosis", "Diagnosis + Day 2 post diagnosis"),

      p.value = c(mc_rf_sympvdiag_p, mc_rf_sympvadd3_p,mc_rf_sympvadd2_p,
                  mc_rf_diagvadd3_p, mc_rf_diagvadd2_p,
                  mc_rf_add3vadd2_p,
                  mc_rf_sympvdiag_p, mc_rf_sympvadd3_p,mc_rf_sympvadd2_p,
                  mc_rf_diagvadd3_p, mc_rf_diagvadd2_p,
                  mc_rf_add3vadd2_p,
                  2, 2, 2, 2)
  ) %>%
  mutate(label = case_when(
      is.na(p.value) ~ "NS",
      p.value < 0.001 ~ "***",
      p.value < 0.01 ~ "**",
      p.value < 0.05 ~ "*",
      p.value == 2 ~ "NA",
      TRUE ~ "NS"
  ))

  mc_rf_compare_heatmap <- mc_rf_compare_summary %>%
                      select(group1, group2, label) %>%
                      pivot_wider(names_from = group1, values_from = label) %>%
                      column_to_rownames("group2")


  mcnemar_rf_compare_long <- as.data.frame(as.table(as.matrix(mc_rf_compare_heatmap)))
  colnames(mcnemar_rf_compare_long) <- c("Model1", "Model2", "Significance")

  mc_rf_compare_list2[[i]] <- mcnemar_rf_compare_long %>%
                        mutate(
                          Model1 = factor(Model1, levels = c("Diagnosis + Day 2 post diagnosis", "Diagnosis + Day 1 post diagnosis", "Diagnosis only", "Onset only")),
                          Model2 = factor(Model2, levels = c("Onset only", "Diagnosis only", "Diagnosis + Day 1 post diagnosis", "Diagnosis + Day 2 post diagnosis"))
                        )
}

# Summarise the percentage of significance in each scenario cases
mc_rf_compare_percent_sum2 <- dplyr::bind_rows(
  lapply(seq_along(mc_rf_compare_list2), function(i) {
    mc_rf_compare_list2[[i]] %>% mutate(run = i)
    })
  )

# Define labels of statistically significant
sig_labels <- c("*", "**", "***")

# Summarize the percentage significant for each scenario
sig_rf_compare_sum2 <- mc_rf_compare_percent_sum2 %>%
                mutate(is_significant = Significance %in% sig_labels) %>%
                group_by(Model1, Model2) %>%
                summarize(
                  n_sig = sum(is_significant),
                  n_total = n(),
                  percent_sig = 100 * n_sig / n_total,
                  .groups = "drop"
                ) %>%
                mutate(percent_sig = ifelse(Model1 == Model2, NA, percent_sig)) %>%
                mutate(
                  fill = case_when(
                      is.na(percent_sig) ~ "black",
                      percent_sig < 40 ~ "white",
                      percent_sig >= 40 & percent_sig < 60 ~ "grey90",
                      percent_sig >=60 & percent_sig <80 ~ "gold",
                      percent_sig >= 80 ~ "orange"
                    ),
                  percent_label = ifelse(is.na(percent_sig), "", sprintf("%.1f%%", percent_sig))
                )
sig_rf_compare_sum2
```

```{r, Heatmap}
# Plot heatmap
mc_plot_rfcomp2 <- ggplot(sig_rf_compare_sum2, aes(x = Model2, y = Model1, fill = fill)) +
                  geom_tile(color = "black") +
                  geom_text(aes(label = percent_label), color = "black", size = rel(5), fontface = "bold") +
                  scale_fill_manual(values = c("black"= "black", "white" = "white", "grey90" = "grey90", "orange" = "orange", "gold" = "gold"), guide = "none") +
                  theme_classic() +
                  theme(axis.text.x = element_text(hjust = 0.5, face = "bold", size = rel(1)),
                        axis.text.y = element_text(face = "bold", size = rel(1)),
                        axis.title.x = element_blank(),
                        axis.title.y = element_blank(),
                        legend.position = "none")
mc_plot_rfcomp2
```

## Figure 4C
```{r, Fig4C}
model_perf_comp_rf2 <- df_perf_metrics_rf_diag %>%
                pivot_longer(
                    cols = -models,
                    names_to = "metrics",
                    values_to = "Perf"
                ) %>%
                mutate(Metrics = case_when(
                    str_starts(metrics, 'acc_') ~ "Accuracy",
                    str_starts(metrics, "sens_") ~ "Sensitivity",
                    str_starts(metrics, "spec_") ~ "Specificity",
                    str_starts(metrics, "prec_") ~ "Precision",
                    str_starts(metrics, "f1_") ~ "F1-Score",
                    str_starts(metrics, "auc_") ~ "AUROC",
                    metrics == "Accuracy" ~ "Accuracy",
                    metrics == "Sensitivity" ~ "Sensitivity",
                    metrics == "Specificity" ~ "Specificity",
                    metrics == "Precision" ~ "Precision",
                    metrics == "F1.Score" ~ "F1-Score",
                    metrics == "AUROC" ~ "AUROC"
                ),
                bound = case_when(
                    str_ends(metrics, "_low") ~ "lower",
                    str_ends(metrics, "_upp") ~ "upper",
                    TRUE ~ "estimate"
                )) %>%
                select(c("models", "Metrics", "bound", "Perf")) %>%
                pivot_wider(names_from = bound, values_from = Perf) %>%
                mutate(models = factor(models, levels = c("Onset only", "Diagnosis only", "Diagnosis + Day 1 post diagnosis", "Diagnosis + Day 2 post diagnosis")))

# AUROC text positioned just above the Sensitivity upper CI for each model
ann_auroc_rf2 <- model_perf_comp_rf2 %>%
  filter(Metrics %in% c("Sensitivity", "AUROC")) %>%
  select(models, Metrics, estimate, upper) %>%
  pivot_wider(names_from = Metrics, values_from = c(estimate, upper)) %>%
  transmute(
    models,
    Metrics = "AUROC",
    # place text a bit above the Sensitivity bar/errorbar
    y = pmax(upper_Sensitivity, estimate_Sensitivity, na.rm = TRUE) + 1,
    label = sprintf("%.1f", estimate_AUROC)
  )

# Accuracy text positioned just above the Sensitivity upper CI for each model
ann_acc_rf2 <- model_perf_comp_rf2 %>%
  filter(Metrics %in% c("Sensitivity", "Accuracy")) %>%
  select(models, Metrics, estimate, upper) %>%
  pivot_wider(names_from = Metrics, values_from = c(estimate, upper)) %>%
  transmute(
    models,
    Metrics = "Accuracy",
    # place text a bit above the Sensitivity bar/errorbar
    y = pmax(upper_Sensitivity, estimate_Sensitivity, na.rm = TRUE) + 0.4,
    label = sprintf("%.1f", estimate_Accuracy)
  )

# Function to build bracket information for one row facet for each model family
row_signif_comp_diag <- function(sig_df, perf_all, offsets = c(1.6, 2.6, 3.8, 5.4, 7, 9.1)) {
  fam_sens <- perf_all
  if (nrow(fam_sens) == 0) {
    return(NULL)
  }
  
  pairs <- list(c("Onset only", "Diagnosis only"), c("Diagnosis only", "Diagnosis + Day 1 post diagnosis"), c("Diagnosis + Day 1 post diagnosis", "Diagnosis + Day 2 post diagnosis"),
                c("Diagnosis only", "Diagnosis + Day 2 post diagnosis"), c("Onset only", "Diagnosis + Day 1 post diagnosis"), c("Onset only", "Diagnosis + Day 2 post diagnosis"))
  
  pp <- get_pair_percents(sig_df)
  pct_vec <- c(pp[["Diagnosis only-Onset only"]], pp[["Diagnosis + Day 1 post diagnosis-Diagnosis only"]], pp[["Diagnosis + Day 1 post diagnosis-Diagnosis + Day 2 post diagnosis"]],
               pp[["Diagnosis + Day 2 post diagnosis-Diagnosis only"]], pp[["Diagnosis + Day 1 post diagnosis-Onset only"]], pp[["Diagnosis + Day 2 post diagnosis-Onset only"]])
  ann <- pct_to_stars(pct_vec)
  
  y_top <- max(fam_sens$estimate, na.rm = TRUE)
  
  # Return the list compiled
  list(pairs = pairs, annotations = ann, y = y_top - 3 + offsets)
}

rf_row_compare2 <- row_signif_comp_diag(sig_rf_compare_sum2, model_perf_comp_rf2)
#rf_row_compare['pairs'] <- factor(rf_row_compare['pairs'], levels = c())

# Function to add the row of results of comparisons into plot
add_row_signif_compare2 <- function(p, row_spec) {
  if (is.null(row_spec)) {
    return(p)
  }
  p + geom_signif(
    data = model_perf_comp_rf2,
    inherit.aes = FALSE,
    aes(x = as.factor(models), y = estimate),
    comparisons = row_spec$pairs,
    annotations = row_spec$annotations,
    y_position = row_spec$y,
    textsize = 8,
    size = 0.8,
    tip_length = 0.008,
    vjust = 0.1
  )
}

fig4c_temp_rf2 <- ggplot(data = model_perf_comp_rf2 %>% filter(Metrics %in% c("AUROC", "Sensitivity")), aes(x = models, y = estimate, color = Metrics)) +
  geom_col(data = model_perf_comp_rf2 %>% filter(Metrics %in% c("Sensitivity")), aes(x = models, y = estimate, fill = models), alpha = 0.8) +
  geom_errorbar(data = model_perf_comp_rf2 %>% filter(Metrics %in% c("Sensitivity")), aes(ymin = lower, ymax = upper), linewidth = 1.2, width = 0.3, 
                color = "black") +
  geom_text(data = ann_auroc_rf2 %>% filter(Metrics %in% c("AUROC")), aes(x = models, y = y, label = paste0("AUROC ", label, "%"), color = Metrics), inherit.aes = FALSE, size = rel(6),
            vjust = 0) +
  geom_text(data = ann_acc_rf2 %>% filter(Metrics %in% c("Accuracy")), aes(x = models, y = y, label = paste0("Accuracy ", label, "%"), color = Metrics), inherit.aes = FALSE, size = rel(6),
            vjust = 0) +
  ylab("Sensitivity (%)") +
  scale_x_discrete(labels=c("Onset only", "Diagnosis only", "Diagnosis + Day 1", "Diagnosis + Day 2")) +
  scale_fill_manual(name = "", values = c("#0072B2", "#BDBDBD", "#5F9AFB", "#CC79A7")) +
  scale_color_manual(name = "", values = c(AUROC = "#FFC001", Accuracy = "#FA766E")) +
  guides(
    fill  = guide_legend(order = 1, override.aes = list(alpha = 0.6)),
    color = guide_legend(order = 2, override.aes = list(linetype = 1, shape = 16))
  ) +
  scale_y_continuous(breaks = seq(85, 100, 2.5)) +
  coord_cartesian(ylim = c(85, 110)) +
  theme(axis.text = element_text(color = "black"),
        axis.text.x = element_text(vjust = 0.5, hjust = 0.5, face = "bold", size = rel(3)),
        axis.text.y = element_text(face = "bold", size = rel(3)),
        axis.line = element_line(color = "black"),
        strip.text.x = element_text(vjust = 0.5, face = "bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        legend.position = "none",
        legend.box = "horizontal",
        legend.text = element_text(size = rel(4)),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = rel(4))
        )
fig4c_rf2 <- fig4c_temp_rf2 %>%
  add_row_signif_compare2(rf_row_compare2)
fig4c_rf2
#ggsave("Figure4C_rf.png", fig4c_rf2, width = 16, height = 12)
```

```{r, panel B}
SF6B_Sen <- subset(model_perf_comp_rf2, Metrics == "Sensitivity")
SF6B_Acc <- subset(model_perf_comp_rf2, Metrics == "Accuracy")
SF6B_AUC <- subset(model_perf_comp_rf2, Metrics == "AUROC")

SF6B_Sen$group <- c("0","1","3","2")
SF6B_Acc$group <- c("0","1","3","2")
SF6B_AUC$group <- c("0","1","3","2")

lb_C <- 60

sig_df <- data.frame(
  group1 = c("0", "1", "2", "1", "0", "0"),
  group2 = c("1", "2", "3", "3", "2", "3"),
  y.position = c(14 + 30, 16 + 30, 18 + 30, 20 + 30, 22 + 30, 24 + 30),
  label = c("****", "****", "", "****", "", "") 
)

text_df_AUC <- SF6B_Sen %>%
  dplyr::transmute(group, y_top = pmin(pmax(upper - lb_C, 0), 50)) %>%
  dplyr::left_join(
    SF6B_AUC %>% dplyr::select(group, estimate),
    by = "group"
  ) %>%
  dplyr::mutate(
    label = sprintf("AUROC = %.1f%%", estimate),
    y = y_top + 3.3
  )

text_df_Acc <- SF6B_Sen %>%
  dplyr::transmute(group, y_top = pmin(pmax(upper - lb_C, 0), 50)) %>%
  dplyr::left_join(
    SF6B_Acc %>% dplyr::select(group, estimate),
    by = "group"
  ) %>%
  dplyr::mutate(
    label = sprintf("Accuracy = %.1f%%", estimate),
    y = y_top + 1.3
  )

theme_set(theme_classic(base_size = 50, base_family = "Helvetica"))
xlabel <- ""
ylabel <- "Sensitivity (%)"
pnl_sf6b <- ggplot() +
  geom_bar(data = SF6B_Sen, aes(x = group, y = pmax(estimate - lb_C, 0), fill = group), position = "dodge", stat = "identity", width = 0.4) +
  scale_fill_manual(values=c("#D86ECC","#348EC2","#0070C0","#002060")) +
  geom_errorbar(data = SF6B_Sen, aes(x = group, ymin = pmax(lower - lb_C, 0), ymax = pmax(upper - lb_C, 0)), width = 0.2, position = position_dodge(0.4), size = 1.0) +
  stat_pvalue_manual(
    sig_df,
    label = "label",
    xmin  = "group1",
    xmax  = "group2",
    y.position  = "y.position",
    tip.length  = 0.01,
    bracket.size = 1,
    size = 10
  ) +
  scale_x_discrete(labels = c("Onset only", "Diagnosis only", "Diagnosis + Day 1", "Diagnosis + Day 2"), limits = c("0", "1", "2", "3")) +
  scale_y_continuous(
    limits = c(0, 100 - lb_C + 15),
    breaks  = seq(0, 100 - lb_C, by = 10),
    labels  = function(b) sprintf("%d", b + lb_C)) +
  geom_text(
    data = text_df_AUC,
    aes(x = group, y = y, label = label),
    position = position_dodge(0.6), vjust = 0, size = 10, color = "#FFC001"
  ) +
  geom_text(
    data = text_df_Acc,
    aes(x = group, y = y, label = label),
    position = position_dodge(0.6), vjust = 0, size = 10, color = "#FA766E"
  ) +
  xlab(xlabel) +
  ylab(ylabel) +
  theme(plot.title = element_text(colour = "black", size=36),
        axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_line(colour = "black"),
        axis.line = element_line(colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        legend.position='none',
        axis.title.x = element_text(colour = "black"),
        axis.title.y = element_text(colour = "black"))
pnl_sf6b
```

# Comparison of sensitivity with features aggregated
## Preparation for Figure 4D
```{r, Compiling the dataframe of testing set, prediction from model with symptom onset, diagnosis & onset + day 2}
testing_df_rf <- map2_dfr(
  .x = split_list,
  .y = seq_along(split_list),
  ~ .x$test %>%
    mutate(simulation = .y) %>%
    select(simulation, age, gender, vaccination, comorbidity, outcome)
)

pred_onset_df_rf <- imap_dfr(
  rf_vlsymp_list,
  ~ tibble(
    simulation = .y,
    pred_onset = .x$prediction
  )
)

pred_diag_df_rf <- imap_dfr(
  rf_vldiag_list,
  ~ tibble(
    simulation = .y,
    pred_diag = .x$prediction
  )
)

pred_add2_df_rf <- imap_dfr(
  rf_add2_list,
  ~ tibble(
    simulation = .y,
    pred_add2 = .x$prediction
  )
)

pred_add3_df_rf <- imap_dfr(
  rf_add3_list,
  ~ tibble(
    simulation = .y,
    pred_add3 = .x$prediction
  )
)

testing_df_rf['pred_onset'] <- pred_onset_df_rf$pred_onset
testing_df_rf['pred_diag'] <- pred_diag_df_rf$pred_diag
testing_df_rf['pred_add2'] <- pred_add2_df_rf$pred_add2
testing_df_rf['pred_add3'] <- pred_add3_df_rf$pred_add3
```

```{r, Define functions for compute aggregated performance metrics}
# Define function to compute performance metrics
metrics_comp <- function(df_comp, cols) {
  cols <- as.character(cols)
  actual_chr <- trimws(as.character(df_comp$outcome))
  pred_chr   <- trimws(as.character(df_comp[[cols]]))
  keep <- !is.na(actual_chr) & !is.na(pred_chr)
  
  actual <- factor(actual_chr[keep], levels = c("Non severe", "Severe"))
  pred   <- factor(pred_chr[keep],   levels = c("Non severe", "Severe"))
  
  pred_num <- ifelse(pred == "Severe", 1, 0)
  
  cfm <- table(pred, actual, dnn = c("pred", "actual"))
  
  TP <- cfm["Severe", "Severe"]
  FP <- cfm["Severe", "Non severe"]
  TN <- cfm["Non severe", "Non severe"]
  FN <- cfm["Non severe", "Severe"]
  
  acc <- sum(TP, TN) / sum(cfm)
  sens <- TP / (TP + FN)
  spec <- TN / (TN + FP)
  prec <- TP / (TP + FP)
  f1_sc <- 2 * ((prec * sens) / (prec + sens))
    
  roc <- roc(actual, pred_num)
  auc_val <- auc(roc)
  
  list(confusion_matrix = cfm, accuracy = acc, sensitivity = sens, specificity = spec, precision = prec, f1_score = f1_sc, roc_val = roc, AUC = auc_val)
}

# Define function for parallel compute the aggregated performance metrics over 100 simulations
func_agg_met <- function(df_for_comp, criteria, criteria_fil, cols_comp) {
  num_cores <- parallel::detectCores() - 1
  cl <- makeCluster(num_cores)
  registerDoParallel(cl)
  on.exit(parallel::stopCluster(cl), add = TRUE)
  
  res <- foreach(i = 1:100, .packages = c("dplyr", "pROC", "tibble"), .export = c("metrics_comp")) %dopar% {
    df_temp <- df_for_comp[[i]]
    df_temp2 <- dplyr::filter(df_temp, .data[[criteria]] == criteria_fil)
    
    met_list <- metrics_comp(df_temp2, cols = cols_comp)
    
    list(confusion_matrix = met_list$confusion_matrix, accuracy = met_list$accuracy, sensitivity = met_list$sensitivity, specificity = met_list$specificity,
         precision = met_list$specificity, f1_score = met_list$f1_score, roc_val = met_list$roc_val, AUC = met_list$AUC)
  }
  res
}

# Define function to aggregate the computed performance metrics into a dataframe
met_sum_func <- function(perf_list) {
  temp_df <- map_dfr(seq_along(perf_list), function(i) {
    result <- perf_list[[i]]
    
    tibble(
    run = i,
    accuracy = round(result$accuracy * 100, 4),
    sensitivity = round(result$sensitivity * 100, 4),
    specificity = round(result$specificity * 100, 4),
    precision = round(result$precision * 100, 4),
    F1_score = round(result$f1_score, 4),
    AUC_value = round(result$AUC * 100, 4))
  })
  
  temp_df2 <- as.data.frame(temp_df)
  return(temp_df2)
}

# Define function to compile & compute the confidence interval
met_cic_func <- function(perf_df, mod_name) {
  summary_df <- perf_df %>%
    summarise(
      across(
        .cols = c(accuracy, sensitivity, specificity, precision, F1_score, AUC_value),
        .fns = list(mean = mean, low = ~ quantile(.x, 0.025), upp = ~ quantile(.x, 0.975)),
        .names = "{.col}_{.fn}"
      )
    ) %>%
    ungroup() %>%
    mutate(models = as.character(mod_name)) %>%
    pivot_longer(
      cols = -models,
      names_to = "metrics",
      values_to = "perf"
      ) %>%
    mutate(
      Metrics = case_when(
        str_starts(metrics, "accuracy_") ~ "Accuracy",
        str_starts(metrics, "sensitivity") ~ "Sensitivity",
        str_starts(metrics, "specificity") ~ "Specificity",
        str_starts(metrics, "precision") ~ "Precision",
        str_starts(metrics, "F1_score") ~ "F1_score",
        str_starts(metrics, "AUC_value") ~ "AUROC_value"
        ),
      bound = case_when(
        str_ends(metrics, "_low") ~ "lower",
        str_ends(metrics, "_upp") ~ "upper",
        TRUE ~ "estimate"
        )
      ) %>%
    select(c("models", "Metrics", "bound", "perf")) %>%
    pivot_wider(names_from = bound, values_from = perf)
  return(summary_df)
}
```

```{r, Compute sensitivity according the specific features filtering}
# Splitting the dataframe into list
testing_df_list_rf <- list()
for(i in 1:100) {
  testing_df_list_rf[[i]] <- testing_df_rf %>% filter(simulation == i)
}

# Compute the performance metrics of model with viral load since symptom onset which aggregate with different scenario
perf_com3_onset_rf <- func_agg_met(testing_df_list_rf, criteria = "comorbidity", criteria_fil = ">=3", cols_comp = "pred_onset")
perf_com12_onset_rf <- func_agg_met(testing_df_list_rf, criteria = "comorbidity", criteria_fil = "1-2", cols_comp = "pred_onset")
perf_age60_onset_rf <- func_agg_met(testing_df_list_rf, criteria = "age", criteria_fil = "60-79", cols_comp = "pred_onset")
perf_age80_onset_rf <- func_agg_met(testing_df_list_rf, criteria = "age", criteria_fil = ">=80", cols_comp = "pred_onset")
perf_vacfull_onset_rf <- func_agg_met(testing_df_list_rf, criteria = "vaccination", criteria_fil = "Full", cols_comp = "pred_onset")
perf_vacboost_onset_rf <- func_agg_met(testing_df_list_rf, criteria = "vaccination", criteria_fil = "Booster", cols_comp = "pred_onset")

# Compute the performance metrics of model with viral load at diagnosis which aggregate with different scenario
perf_com3_diag_rf <- func_agg_met(testing_df_list_rf, criteria = "comorbidity", criteria_fil = ">=3", cols_comp = "pred_diag")
perf_com12_diag_rf <- func_agg_met(testing_df_list_rf, criteria = "comorbidity", criteria_fil = "1-2", cols_comp = "pred_diag")
perf_age60_diag_rf <- func_agg_met(testing_df_list_rf, criteria = "age", criteria_fil = "60-79", cols_comp = "pred_diag")
perf_age80_diag_rf <- func_agg_met(testing_df_list_rf, criteria = "age", criteria_fil = ">=80", cols_comp = "pred_diag")
perf_vacfull_diag_rf <- func_agg_met(testing_df_list_rf, criteria = "vaccination", criteria_fil = "Full", cols_comp = "pred_diag")
perf_vacboost_diag_rf <- func_agg_met(testing_df_list_rf, criteria = "vaccination", criteria_fil = "Booster", cols_comp = "pred_diag")

# Compute the performance metrics of model with viral load at diagnosis and viral load at day 2 after diagnosis which aggregate with different scenario
perf_com3_add2_rf <- func_agg_met(testing_df_list_rf, criteria = "comorbidity", criteria_fil = ">=3", cols_comp = "pred_add2")
perf_com12_add2_rf <- func_agg_met(testing_df_list_rf, criteria = "comorbidity", criteria_fil = "1-2", cols_comp = "pred_add2")
perf_age60_add2_rf <- func_agg_met(testing_df_list_rf, criteria = "age", criteria_fil = "60-79", cols_comp = "pred_add2")
perf_age80_add2_rf <- func_agg_met(testing_df_list_rf, criteria = "age", criteria_fil = ">=80", cols_comp = "pred_add2")
perf_vacfull_add2_rf <- func_agg_met(testing_df_list_rf, criteria = "vaccination", criteria_fil = "Full", cols_comp = "pred_add2")
perf_vacboost_add2_rf <- func_agg_met(testing_df_list_rf, criteria = "vaccination", criteria_fil = "Booster", cols_comp = "pred_add2")

# Compute the performance metrics of model with viral load at diagnosis and viral load at day 1 after diagnosis which aggregate with different scenario
perf_com3_add3_rf <- func_agg_met(testing_df_list_rf, criteria = "comorbidity", criteria_fil = ">=3", cols_comp = "pred_add3")
perf_com12_add3_rf <- func_agg_met(testing_df_list_rf, criteria = "comorbidity", criteria_fil = "1-2", cols_comp = "pred_add3")
perf_age60_add3_rf <- func_agg_met(testing_df_list_rf, criteria = "age", criteria_fil = "60-79", cols_comp = "pred_add3")
perf_age80_add3_rf <- func_agg_met(testing_df_list_rf, criteria = "age", criteria_fil = ">=80", cols_comp = "pred_add3")
perf_vacfull_add3_rf <- func_agg_met(testing_df_list_rf, criteria = "vaccination", criteria_fil = "Full", cols_comp = "pred_add3")
perf_vacboost_add3_rf <- func_agg_met(testing_df_list_rf, criteria = "vaccination", criteria_fil = "Booster", cols_comp = "pred_add3")

com3_onset_df_rf <- met_sum_func(perf_com3_onset_rf)
com3_onset_sum_rf <- met_cic_func(com3_onset_df_rf, mod_name = "onset_com3")

com12_onset_df_rf <- met_sum_func(perf_com12_onset_rf)
com12_onset_sum_rf <- met_cic_func(com12_onset_df_rf, mod_name = "onset_com12")

age80_onset_df_rf <- met_sum_func(perf_age80_onset_rf)
age80_onset_sum_rf <- met_cic_func(age80_onset_df_rf, mod_name = "onset_age80")

age60_onset_df_rf <- met_sum_func(perf_age60_onset_rf)
age60_onset_sum_rf <- met_cic_func(age60_onset_df_rf, mod_name = "onset_age60")

vacfull_onset_df_rf <- met_sum_func(perf_vacfull_onset_rf)
vacfull_onset_sum_rf <- met_cic_func(vacfull_onset_df_rf, mod_name = "onset_vacfull")

vacboost_onset_df_rf <- met_sum_func(perf_vacboost_onset_rf)
vacboost_onset_sum_rf <- met_cic_func(vacboost_onset_df_rf, mod_name = "onset_vacboost")

com3_diag_df_rf <- met_sum_func(perf_com3_diag_rf)
com3_diag_sum_rf <- met_cic_func(com3_diag_df_rf, mod_name = "diag_com3")

com12_diag_df_rf <- met_sum_func(perf_com12_diag_rf)
com12_diag_sum_rf <- met_cic_func(com12_diag_df_rf, mod_name = "diag_com12")

age80_diag_df_rf <- met_sum_func(perf_age80_diag_rf)
age80_diag_sum_rf <- met_cic_func(age80_diag_df_rf, mod_name = "diag_age80")

age60_diag_df_rf <- met_sum_func(perf_age60_diag_rf)
age60_diag_sum_rf <- met_cic_func(age60_diag_df_rf, mod_name = "diag_age60")

vacfull_diag_df_rf <- met_sum_func(perf_vacfull_diag_rf)
vacfull_diag_sum_rf <- met_cic_func(vacfull_diag_df_rf, mod_name = "diag_vacfull")

vacboost_diag_df_rf <- met_sum_func(perf_vacboost_diag_rf)
vacboost_diag_sum_rf <- met_cic_func(vacboost_diag_df_rf, mod_name = "diag_vacboost")

com3_add2_df_rf <- met_sum_func(perf_com3_add2_rf)
com3_add2_sum_rf <- met_cic_func(com3_add2_df_rf, mod_name = "add2_com3")

com12_add2_df_rf <- met_sum_func(perf_com12_add2_rf)
com12_add2_sum_rf <- met_cic_func(com12_add2_df_rf, mod_name = "add2_com12")

age80_add2_df_rf <- met_sum_func(perf_age80_add2_rf)
age80_add2_sum_rf <- met_cic_func(age80_add2_df_rf, mod_name = "add2_age80")

age60_add2_df_rf <- met_sum_func(perf_age60_add2_rf)
age60_add2_sum_rf <- met_cic_func(age60_add2_df_rf, mod_name = "add2_age60")

vacfull_add2_df_rf <- met_sum_func(perf_vacfull_add2_rf)
vacfull_add2_sum_rf <- met_cic_func(vacfull_add2_df_rf, mod_name = "add2_vacfull")

vacboost_add2_df_rf <- met_sum_func(perf_vacboost_add2_rf)
vacboost_add2_sum_rf <- met_cic_func(vacboost_add2_df_rf, mod_name = "add2_vacboost")

com3_add3_df_rf <- met_sum_func(perf_com3_add3_rf)
com3_add3_sum_rf <- met_cic_func(com3_add3_df_rf, mod_name = "add3_com3")

com12_add3_df_rf <- met_sum_func(perf_com12_add3_rf)
com12_add3_sum_rf <- met_cic_func(com12_add3_df_rf, mod_name = "add3_com12")

age80_add3_df_rf <- met_sum_func(perf_age80_add3_rf)
age80_add3_sum_rf <- met_cic_func(age80_add3_df_rf, mod_name = "add3_age80")

age60_add3_df_rf <- met_sum_func(perf_age60_add3_rf)
age60_add3_sum_rf <- met_cic_func(age60_add3_df_rf, mod_name = "add3_age60")

vacfull_add3_df_rf <- met_sum_func(perf_vacfull_add3_rf)
vacfull_add3_sum_rf <- met_cic_func(vacfull_add3_df_rf, mod_name = "add3_vacfull")

vacboost_add3_df_rf <- met_sum_func(perf_vacboost_add3_rf)
vacboost_add3_sum_rf <- met_cic_func(vacboost_add3_df_rf, mod_name = "add3_vacboost")

com3_df_rf <- dplyr::bind_rows(com3_onset_sum_rf, com3_diag_sum_rf, com3_add2_sum_rf, com3_add3_sum_rf)
com12_df_rf <- dplyr::bind_rows(com12_onset_sum_rf, com12_diag_sum_rf, com12_add2_sum_rf, com12_add3_sum_rf)
age80_df_rf <- dplyr::bind_rows(age80_onset_sum_rf, age80_diag_sum_rf, age80_add2_sum_rf, age80_add3_sum_rf)
age60_df_rf <- dplyr::bind_rows(age60_onset_sum_rf, age60_diag_sum_rf, age60_add2_sum_rf, age60_add3_sum_rf)
vacfull_df_rf <- dplyr::bind_rows(vacfull_onset_sum_rf, vacfull_diag_sum_rf, vacfull_add2_sum_rf, vacfull_add3_sum_rf)
vacboost_df_rf <- dplyr::bind_rows(vacboost_onset_sum_rf, vacboost_diag_sum_rf, vacboost_add2_sum_rf, vacboost_add3_sum_rf)

agg_df_rf <- dplyr::bind_rows(com3_df_rf, com12_df_rf, age80_df_rf, age60_df_rf, vacfull_df_rf, vacboost_df_rf) %>%
  mutate(scenario = case_when(
    str_ends(models, "_com3") ~ "Comorbidity >= 3",
    str_ends(models, "_com12") ~ "Comorbidity 1-2",
    str_ends(models, "_age80") ~ "Age >= 80",
    str_ends(models, "_age60") ~ "Age 60-79",
    str_ends(models, "_vacfull") ~ "Vaccination 2 dose",
    str_ends(models, "_vacboost") ~ "Vaccination 3 dose"
  ),
  scenario = factor(scenario, levels = c("Comorbidity 1-2", "Comorbidity >= 3", "Age 60-79", "Age >= 80", "Vaccination 2 dose", "Vaccination 3 dose")),
  model_sce = case_when(
    str_starts(models, "onset_") ~ "Onset",
    str_starts(models, "diag_") ~ "Diagnosis",
    str_starts(models, "add2_") ~ "Diagnosis + day 2 post diagnosis",
    str_starts(models, "add3_") ~ "Diagnosis + day 1 post diagnosis"
  ),
  model_sce = factor(model_sce, levels = c("Onset", "Diagnosis", "Diagnosis + day 1 post diagnosis", "Diagnosis + day 2 post diagnosis")))
```

```{r}
sens_onset <- as.numeric(model_perf_comp_rf %>% filter(models == "Onset only" & Metrics == "Sensitivity") %>% select(estimate))
sens_diag <- as.numeric(model_perf_comp_rf %>% filter(models == "Diagnosis only" & Metrics == "Sensitivity") %>% select(estimate))
sens_add2 <- as.numeric(model_perf_comp_rf %>% filter(models == "Diagnosis + Day 2 post diagnosis" & Metrics == "Sensitivity") %>% select(estimate))
sens_add3 <- as.numeric(model_perf_comp_rf2 %>% filter(models == "Diagnosis + Day 1 post diagnosis" & Metrics == "Sensitivity") %>% select(estimate))

agg_df2_rf <- agg_df_rf %>%
  mutate(sens_diff = case_when(
    model_sce == "Onset" & Metrics == "Sensitivity" ~ round((estimate - sens_onset), 4),
    model_sce == "Diagnosis" & Metrics == "Sensitivity" ~ round((estimate - sens_diag), 4),
    model_sce == "Diagnosis + day 1 post diagnosis" & Metrics == "Sensitivity" ~ round((estimate - sens_add3), 4),
    model_sce == "Diagnosis + day 2 post diagnosis" & Metrics == "Sensitivity" ~ round((estimate - sens_add2), 4)
  )) %>%
  filter(Metrics == "Sensitivity") %>%
  mutate(
    lower_plot = ifelse(lower < 65, 65, lower),
    lower_flag = lower < 65
  )
```

## Figure 4D
```{r, Figure 4D_diag}
SF6C_Sen <- subset(agg_df2_rf, Metrics == "Sensitivity")
SF6C_Acc <- subset(agg_df2_rf, Metrics == "Accuracy")
SF6C_AUC <- subset(agg_df2_rf, Metrics == "AUROC")

SF6C_Sen <- SF6C_Sen[SF6C_Sen$model_sce != "Onset + day 2",]
SF6C_Sen$group <- rep(c("0", "1", "3", "2"), times = 6)

lb_C <- 60
lb_D <- 60

theme_set(theme_classic(base_size = 50, base_family = "Helvetica"))
fig4d_rf <- ggplot() +
  geom_bar(data = SF6C_Sen, aes(x = factor(scenario), y = pmax(estimate - lb_D, 0), fill = factor(model_sce)), position = "dodge", stat = "identity", width = 0.6) +
  scale_fill_manual(values = c("#D86ECC", "#348EC2", "#0070C0", "#002060")) +
  geom_errorbar(data = SF6C_Sen, aes(x = factor(scenario), ymin = pmax(lower - lb_D, 0), ymax = pmax(upper - lb_D, 0), group = factor(model_sce)), width = 0.2, position = position_dodge(0.6), size = 1.0) +
  scale_x_discrete(labels = function(x) {
    x <- gsub(">=", "≥", x)                    
    x <- sub("\\s+(?=(?:≥|\\d))", "\n", x, perl = TRUE)
    x
  }) +
  scale_y_continuous(
    limits = c(0, 100 - lb_D + 15),
    breaks  = seq(0, 100 - lb_D, by = 10),
    labels  = function(b) sprintf("%d", b + lb_C)) +
  xlab("") +
  ylab("Sensitivity (%)") +
  theme(plot.title = element_text(colour = "black", size = 36),
        axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_line(colour = "black"),
        axis.line = element_line(colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        legend.position ='none',
        axis.title.x = element_text(colour = "black"),
        axis.title.y = element_text(colour = "black"))
fig4d_rf
```

```{r, SF6}
theme_set(theme_classic(base_size = 50, base_family = "Helvetica"))
sf6 <- ggarrange(fig4a_rf_diag, pnl_sf6b, fig4d_rf,
                  nrow = 2, ncol = 2, widths = c(1, 1))
sf6
```

# Saving all data in this session
```{r, Saving RData file}
path <- paste0(getwd(), '/seq_model_rf.RData')
#save.image(file = path)
```

# Session Info
```{r, Session Information}
sessionInfo()
```